### 2020-03-02 sample-sigconf.tex
first commit

\documentclass[sigconf]{acmart}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID. 
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

\begin{document}

\title{Adapting Duplicate Filters to a Sliding Window Context}

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.
\author{R\'emi G\'eraud-Stewart}
\affiliation{%
  \institution{D\'epartement d'informatique de l'ENS, \'Ecole normale sup\'erieure, CNRS, PSL Research University}
  \city{Paris}
  \state{France}
}
\affiliation{%
	\institution{Ingenico}
	\city{Paris}
	\state{France}
}
\email{remi.geraud@ens.fr}

\author{Marius Lombard-Platet}
\affiliation{%
  \institution{D\'epartement d'informatique de l'ENS, \'Ecole normale sup\'erieure, CNRS, PSL Research University}
  \city{Paris}
  \country{France}
}
\affiliation{%
\institution{Be-Studys}
\city{Geneva}
\country{Switzerland}
}
\email{marius.lombard-platet@ens.fr}

\author{David Naccache}
\affiliation{%
  \institution{D\'epartement d'informatique de l'ENS, \'Ecole normale sup\'erieure, CNRS, PSL Research University}
  \city{Paris}
  \country{France}
}
\affiliation{%
	\institution{Ingenico}
	\city{Paris}
	\state{France}
}
\email{david.naccache@ens.fr}

%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

\begin{abstract}
We introduce a generic framework for adapting duplicate filters for sliding windows. Most papers on the literature focus on the fact that a filter must detect a duplicate on the whole stream. In this paper, we recall from previous work that this problem is ill-defined, and that

TODO 
\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}

\end{CCSXML}

\keywords{datasets, neural networks, gaze detection, text tagging}

\maketitle

\section{Introduction}
As the Internet has grown in popularity, data streams have become bigger and bigger. However, while the datasets grow, the need for a quick answer has remained the same. Yet, in many cases, it is not possible to find the optimal solution by storing all the data, may it be for time limitation or memory limitations. Hence, researchers have gone forward and proposed approximate algorithms, that thrive to get as close as possible to the solution, despite the lack of memory and CPU time.

Such algorithms are present in network management \cite{10.5555/647912.740658}, in credit card fraud \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094} and many other topics. A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.

In this paper, we focus on the topic of duplicate detection. While many authors in the literature tackle the problem of approximate duplicate detection with fuzzy matching, \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}, we instead focus on \emph{exact} duplicate detection, in which an element is a duplicate if and only if it has already appeared in the stream.

As it turns out, (exact) duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the Elgamal scheme \cite{10.1007/3-540-39568-7_2}. Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.

%\begin{acks}
%
%\end{acks}

%
% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

% 
% If your work has an appendix, this is the place to put it.
%\appendix

%\section{Research Methods}

\end{document}

### 2020-03-02 sample-sigconf.tex
update

@@
 \documentclass[sigconf]{acmart}
+
+\usepackage{xspace}
+\usepackage{centernot}
+\usepackage{amsmath}
+
+\newcommand{\FPR}{\textsf{FPR}\xspace}
+\newcommand{\FNR}{\textsf{FNR}}
+\newcommand{\DUPLICATE}{\textsf{DUPLICATE}\xspace}
+\newcommand{\UNSEEN}{\textsf{UNSEEN}\xspace}
+\newcommand{\todo}[1][]{{\color{red}{TODO: #1}}}
 
@@
 
-\copyrightyear{2018}
-\acmYear{2018}
-\setcopyright{acmlicensed}
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
-\acmPrice{15.00}
-\acmDOI{10.1145/1122445.1122456}
-\acmISBN{978-1-4503-9999-9/18/06}
+%\copyrightyear{2018}
+%\acmYear{2018}
+%\setcopyright{acmlicensed}
+%\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
+%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
+%\acmPrice{15.00}
+%\acmDOI{10.1145/1122445.1122456}
+%\acmISBN{978-1-4503-9999-9/18/06}
 
@@
 \affiliation{%
-	\institution{Ingenico}
+	\institution{Ingenico Labs Advanced Research}
 	\city{Paris}
@@
 % of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+%\renewcommand{\shortauthors}{G\'eraud-Stewart et al.}
 
@@
 
-TODO 
+\todo 
 \end{abstract}
@@
 \section{Introduction}
+\subsection{Motivation}
 As the Internet has grown in popularity, data streams have become bigger and bigger.
@@
 While many authors in the literature tackle the problem of approximate duplicate detection with fuzzy matching, \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}, we instead focus on \emph{exact} duplicate detection, in which an element is a duplicate if and only if it has already appeared in the stream.
+One can prove (see for instance \cite[][Theorem 2.1]{10.1145/3297280.3297335}) that perfect detection of duplicates over an alphabet of $U$ letters requires $U$ bits of memory.
+Yet, in the case of extremely large alphabets, it is not possible or desirable to use that amount of memory.
 
@@
 Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.
+
+\todo[continuer].
+
+\subsection{Contributions}
+
+\subsection{Related Work}
+
+\subsection{Organisation}
+
+\section{Duplicate Detection and Filter Saturation}
+\subsection{Notations and Initial Problem Statement}
+Let us consider an alphabet $\Gamma$ of $U$ elements.
+A stream $E$ of $n$ elements of $\Gamma$ is noted $E = \{e_1, \dotsc, e_n\}$.
+If the stream is infinite or of unknown size, we note $E = \{e_1, \dotsc, e_n, \dotsc\}$.
+
+\begin{definition}[Duplicate element, unseen element]
+Let $E = \{e_1, \dotsc, e_n, \dotsc\}$ be a stream over $\Gamma$. $e_j$ is called a \emph{duplicate} in $E$ if and only if $\exists i < j, e_i = e_j$. Otherwise, $e_j$ is said to be \emph{unseen}.
+\end{definition}
+
+A filter $\mathcal F$ is defined by $\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$. Furthermore,
+
+\begin{itemize}
+	\item $\mathcal S \in \mathcal M$ represents the current state of the filter amongst all possible memory states $\mathcal M$.
+	\item $\mathsf{Detect}: \mathcal M \times \Gamma \rightarrow \{\DUPLICATE, \UNSEEN\}$ is an algorithm that given the current state $\mathcal S$, guesses if an element $e$ is a duplicate or not.
+	\item $\mathsf{Insert}: \mathcal M \times \Gamma \rightarrow \mathcal M$ takes as input the current state, an element $e$ to insert in the filter, and returns an updated memory state.
+\end{itemize}
+
+Furthermore, since we work in a context where the memory is too small for perfect detection, we have the assumption that $|\mathsf S| \ll U$.
+
+\begin{definition}[False positive, false negative]
+	Let $e$ be an unseen (resp.
+duplicate) element in the stream $E = \{e_1, \dotsc, e_n\}$, and let $\mathcal F$ be a filter.
+$e$ is a \emph{false positive} (resp.
+\emph{false negative}) if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
+$\UNSEEN$).
+\end{definition}
+
+\begin{definition}[False positive rate, false negative rate]
+	Let $E = \{e_1, \dotsc, e_n\}$ be a stream, $\mathcal F$ be a filter.
+The false positive (resp.
+false negative) rate of $\mathcal F$ over the first $i < n$ elements, noted $\FPR_i$ (resp.
+$\FNR_i$), is defined as the number of false positives divided by the number of unseen elements of $\{e_1, \dotsc, e_i\}$ (resp.
+the number of false negative divided by the number of duplicate elements).
+\end{definition}
+
+\subsection{Filter Saturation}
+While the previous definition sounds interesting and is often simpler to work with, especially for the derivation of the FPR and FNR, it has been shown that this kind of duplicate detection is an ill-formed problem, as filters saturate and reach the asymptotic relation $\FPR_\infty + \FNR_\infty = 1$, which means that the filter is not any more efficient than a filter answering randomly.
+We reproduce the statement and proof from \cite{10.1145/3297280.3297335}.
+
+	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
+	Let $\FNR_\infty$ and $\FPR_\infty$ be the asymptotic false negative and false positive rates of a filter of $M$ bits of memory (i.e. the FNR and FPR on a stream of size going to infinity).
+
+	If $U \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
+\end{theorem}
+
+\begin{proof}
+	First note that random filters always verify the relation $\FNR + \FPR = 1$: given that a random filter will return \DUPLICATE with a probability of $p$, an unseen element will be classified as \DUPLICATE with probability $p$, and a duplicate will be classified as \UNSEEN with probability $1-p$, hence the result.
+
+	Now, on infinite streams with infinitely many different elements, filters are saturated with information.
+Given that a filter can only store at most one element per bit (cf.
+\cite[][Section 2.1]{10.1145/3297280.3297335}), thus a filter of size $M$ can remember at most $M$ elements.
+However, after $fM$ insertions (with $f \gg 1$), the filter remembers at most a tiny fraction $\frac 1f \ll 1$ of the stream.
+Having reached its saturated state, the filter has an extremely tiny probability $\frac 1f \approx 0$ of correctly guessing whether the incoming element is a duplicate or not, given what the filter actually knows about the stream.
+For this reason, the best strategy of a saturated filter is almost indistinguishable from a random strategy, i.e.
+randomly outputting \DUPLICATE.
+When the stream grows indefinitely, the filter becomes asymptotically equivalent to a random filter.
+\end{proof}
+
+As a consequence, after a sufficient number of elements, no filter can give a significant answer about the duplicate problem.
+
+However, in most practical cases, it is not essential to detect duplicates since the start of the stream, but only duplicates on a sliding window, i.e., duplicates over the last $W$ elements for some integer $W$.
+
+\subsection{Duplicate Detection over a Sliding Window}
+In this section, we redefine the problem in order to include a sliding window.
+
+\begin{definition}[Duplicate element, unseen element over a sliding window]
+	Let $E = \{e_1, \dotsc, e_n, \dotsc\}$ be a stream over $\Gamma$, let $W\in \mathbb N$ be a sliding window size.
+$e_j$ is called a \emph{duplicate} in $E$ over the sliding window $W$ if and only if $\exists j - W \leq i < j, e_i = e_j$.
+Otherwise, $e_j$ is said to be \emph{unseen}.
+\end{definition}
+
+One observes that a duplicate or unseen element in $E = \{e_1, \dotsc, e_n\}$ over $W$ is equivalent to a duplicate or unseen element in $E' = \{e_{n-W}, \dotsc, e_n\}$ without a sliding window.
+
+Similarly, we redefine the false positive, false negative, false positive rate and false negative rate.
+
+\begin{definition}[False positive, false negative over a sliding window]
+	Let $W$ be the size of a sliding window, $e$ be an unseen (resp.
+duplicate) element in $E = \{e_1, \dotsc, e_n\}$ over $W$, and let $\mathcal F$ be a filter.
+$e$ is a \emph{false positive} (resp.
+\emph{false negative}) over $W$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
+$\UNSEEN$).
+\end{definition}
+
+\begin{definition}[False positive rate, false negative rate over a sliding window]
+	Let $E = \{e_1, \dotsc, e_n\}$ be a stream, $\mathcal F$ be a filter, $W$ be the size of a sliding window.
+The false positive (resp.
+false negative) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $W$, noted $\FPR^W_i$ (resp.
+$\FNR^W_i$), is defined as the number of false positives over $W$ divided by the number of unseen elements in $E$ over $W$ (resp.
+the number of false negative over $W$ divided by the number of duplicate elements over $W$).
+\end{definition}
+
+\subsection{Bounds on the Duplicate Detection over a Sliding Window Problem}
+
+\begin{theorem}
+	Let $W$ be a sliding window size, and let us consider a duplicate detection problem over $W$.
+If the available amount of memory $M$ is such that $M \simeq 2W\log_2W$, then the problem can be solved with almost no error.
+\end{theorem}
+
+\begin{proof}
+Let us consider a duplicate detection problem of a stream $E$ over a sliding window $W$. We first devise a hash function, whose fingerprints are $2 \log_2 W$ bits long.
+
+The birthday paradox, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $H$ over $a$ bits, one must, on average, collect $2^{a/2}$ hashes of different messages before obtaining a collision.
+Hence, in our case, we can store $2^{2 \log_2 W / 2} = W$ fingerprints of different elements before having a collision, i.e., two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ which have the same hash, i.e.
+$H(e_i) = H(e_j)$.
+
+Hence, one can construct a filter $\mathcal F$ which consists in a queue of $W$ hashes: for each new element $e$, \textsf{Detect}(e) returns \DUPLICATE if $H(e)$ is present in the queue, \UNSEEN otherwise.
+\textsf{Insert}(e) just adds $H(e)$ to the queue before popping the list.
+There is no false negative, and a false positive only happens if two elements have the same hash, which does not happen often, hence a low FPR and a null FNR.
+
+The queue stores $W$ hashes, and as such requires $W \cdot 2\log_2 W$ bits of memory.
+\end{proof}
+
+One can also observe that the lookup algorithm on this structure is trivially parallelizable, with a very low error rate, hence having an efficient and near optimal solution.
+
+As such, the problem remains open for cases where $M \ll W \log_2 W$.
+
+\section{Unsuitability of Most Filters for Duplicate Detection over a Sliding Window}
+While the duplicate detection problem over a sliding window is only but a slight reformulation of the original problem of duplicate detection, it turns out that most streaming filters which perform well in the latter problem are not as performant in the former.
+
+From our literature reviews, there are 6 competing duplicate filters adapted for streaming data: 
+\begin{itemize}
+	\item A2 filters \cite{Yoo10}
+	\item Stable Bloom Filters (SBF) \cite{Den06}
+	\item Streaming Quotient Filters (SQF)\footnote{It has been shown in \cite{10.1145/3297280.3297335} that SQFs are strictly less efficient than QHTs.
+As such, they will not be used in the rest of this paper.} \cite{Dut13}
+	\item Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}
+	\item Block-decaying Bloom Filters (b\_DBF) \cite{She08}
+	\item A variation of Cuckoo Filters \cite{Fan14}, suggested by \cite{10.1145/3297280.3297335}
+\end{itemize}
+\todo[Regarder https://www2005.org/cdrom/docs/p12.pdf]
+
+All these filters except the b\_DBF were not defined in the context of a sliding window $W$.
+As a consequence, their parameters do not depend on $W$, and as such, behave poorly when used in the paradigm of duplicate detection over a sliding window.
+
+Experimentally, we observe that the false positive rate of these filters does not decrease to 0 even though the sliding window becomes small; this is because in these filters,
+
+\section{Queuing Filters for Sliding Window Adaptation}
+
+\section{Application on QHT}
+
+\section{Optimal Error rate on a Filter}
+
+\section{Experiments and Benchmarks}
 

### 2020-03-03 qhtv2.tex
Cleanup

--- 2020-03-02 sample-sigconf.tex
@@
-\documentclass[sigconf]{acmart}
-
-\usepackage{xspace}
-\usepackage{centernot}
-\usepackage{amsmath}
-
-\newcommand{\FPR}{\textsf{FPR}\xspace}
-\newcommand{\FNR}{\textsf{FNR}}
-\newcommand{\DUPLICATE}{\textsf{DUPLICATE}\xspace}
-\newcommand{\UNSEEN}{\textsf{UNSEEN}\xspace}
-\newcommand{\todo}[1][]{{\color{red}{TODO: #1}}}
-
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-%\copyrightyear{2018}
-%\acmYear{2018}
-%\setcopyright{acmlicensed}
-%\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
-%\acmPrice{15.00}
-%\acmDOI{10.1145/1122445.1122456}
-%\acmISBN{978-1-4503-9999-9/18/06}
-
-%
-% These commands are for a JOURNAL article.
-%\setcopyright{acmcopyright}
-%\acmJournal{TOG}
-%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
-%\acmDOI{10.1145/1122445.1122456}
-
-%
-% Submission ID. 
-% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
-% of the event, and this ID should be used as the parameter to this command.
-%\acmSubmissionID{123-A56-BU3}
-
-%
-% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
-% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
-% the next command will enable that style.
-%\citestyle{acmauthoryear}
+\input{preamble.tex}
 
@@
 
-%
-% The "author" command and its associated commands are used to define the authors and their affiliations.
-% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
-% used to denote shared contribution to the research.
-\author{R\'emi G\'eraud-Stewart}
+\author{Rémi Géraud-Stewart}
 \affiliation{%
-  \institution{D\'epartement d'informatique de l'ENS, \'Ecole normale sup\'erieure, CNRS, PSL Research University}
-  \city{Paris}
-  \state{France}
-}
-\affiliation{%
-	\institution{Ingenico Labs Advanced Research}
+  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
   \city{Paris}
@@
 \affiliation{%
-  \institution{D\'epartement d'informatique de l'ENS, \'Ecole normale sup\'erieure, CNRS, PSL Research University}
+  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
   \city{Paris}
@@
 }
-\affiliation{%
-	\institution{Ingenico Labs Advanced Research}
-	\city{Paris}
-	\state{France}
-}
 \email{david.naccache@ens.fr}
-
-%
-% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
-% other information printed in the page headers. This command allows the author to define a more concise list
-% of authors' names for this purpose.
-%\renewcommand{\shortauthors}{G\'eraud-Stewart et al.}
 

### 2020-03-03 qhtv2.tex
Cleanup, clarifications in defs

@@
 
+%% Replace by \iffalse when submitting anonymously 
+\iftrue 
 	\author{Rémi Géraud-Stewart}
 	\affiliation{%
-  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
-  \city{Paris}
-  \state{France}
-}
-\email{remi.geraud@ens.fr}
+	\institution{Département d'informatique de l'ENS, École normale supérieure, CNRS, PSL Research University}
+	\city{Paris} \state{France}
+	} \email{remi.geraud@ens.fr}
 
@@
 	\affiliation{%
-  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
-  \city{Paris}
-  \country{France}
+	\institution{Département d'informatique de l'ENS, École normale supérieure, CNRS, PSL Research University}
+	\city{Paris} \country{France}
 	}
@@
 	\institution{Be-Studys}
-\city{Geneva}
-\country{Switzerland}
-}
-\email{marius.lombard-platet@ens.fr}
+	\city{Geneva} \country{Switzerland}
+	} \email{marius.lombard-platet@ens.fr}
 
@@
 	\affiliation{%
-  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
-  \city{Paris}
-  \country{France}
-}
-\email{david.naccache@ens.fr}
+	\institution{Département d'informatique de l'ENS, École normale supérieure, CNRS, PSL Research University}
+	\city{Paris} \country{France}
+	} \email{david.naccache@ens.fr}
+\fi
 
+%% Abstract
 \begin{abstract}
-We introduce a generic framework for adapting duplicate filters for sliding windows.
-Most papers on the literature focus on the fact that a filter must detect a duplicate on the whole stream.
-In this paper, we recall from previous work that this problem is ill-defined, and that
+	A duplicate filter is a data structure designed to efficiently detect repetitions (duplicates) in a stream.
+A well-known instance of such a data structure is the Bloom filter, which has been generalised in several ways.
 
-\todo 
+	In this paper we introduce a generic framework that adapts duplicate filters to sliding windows, rather than on an infinite stream. Indeed, although the
+	infinite stream setting is known to be ill-defined, many duplicate filters are only described in such a scenario. This enables a rigourous mathematical study of such filters.
 \end{abstract}
 
-%
-% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-% Please copy and paste the code instead of the example below.
-%
+%% CCS XML
 \begin{CCSXML}
-
+	% Get code at http://dl.acm.org/ccs.cfm.
+	% Please copy and paste the code
 \end{CCSXML}
 
-\keywords{datasets, neural networks, gaze detection, text tagging}
+%% Keywords
+\keywords{
+	% TODO
+}
 
@@
 \subsection{Motivation}
-As the Internet has grown in popularity, data streams have become bigger and bigger.
-However, while the datasets grow, the need for a quick answer has remained the same.
-Yet, in many cases, it is not possible to find the optimal solution by storing all the data, may it be for time limitation or memory limitations.
-Hence, researchers have gone forward and proposed approximate algorithms, that thrive to get as close as possible to the solution, despite the lack of memory and CPU time.
 
-Such algorithms are present in network management \cite{10.5555/647912.740658}, in credit card fraud \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094} and many other topics.
+\paragraph{Duplicate detection problem.}
+We consider the following problem (duplicate detection problem, DPP): given a stream $S_t = \{s_t, s_{t-1}, \dotsc\}$ and an item $s^\star$, find whether $s^\star \in S_t$.
+It is understood that the stream $S_t$ is updated at every time increment.
+An \emph{efficient} solution to this problem provides an answer with bounded error $\epsilon$, using polynomially many resources (time and memory) in $1/epsilon$.
+
+Instances of this problem abound in computer science, with applications in file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
 A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.
+Even when the stream is bounded, i.e. $\lim_{t\to\infty}|S_t| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable.
 
-In this paper, we focus on the topic of duplicate detection.
-While many authors in the literature tackle the problem of approximate duplicate detection with fuzzy matching, \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}, we instead focus on \emph{exact} duplicate detection, in which an element is a duplicate if and only if it has already appeared in the stream.
-One can prove (see for instance \cite[][Theorem 2.1]{10.1145/3297280.3297335}) that perfect detection of duplicates over an alphabet of $U$ letters requires $U$ bits of memory.
-Yet, in the case of extremely large alphabets, it is not possible or desirable to use that amount of memory.
+\paragraph{Approximate and exact DPP.}
+One way to relax the DPP is to allow \emph{approximate} duplicate detection \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}.
+We instead focus on \emph{exact} duplicate detection, in which an element is considered a duplicate if and only if it has already appeared in the stream.
+One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates over an alphabet of $U$ letters requires $U$ bits of memory.
 
-As it turns out, (exact) duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the Elgamal scheme \cite{10.1007/3-540-39568-7_2}.
+As it turns out, exact duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
 Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.
@@
 \subsection{Notations and Initial Problem Statement}
-Let us consider an alphabet $\Gamma$ of $U$ elements.
-A stream $E$ of $n$ elements of $\Gamma$ is noted $E = \{e_1, \dotsc, e_n\}$.
-If the stream is infinite or of unknown size, we note $E = \{e_1, \dotsc, e_n, \dotsc\}$.
+Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) collection $E = \{e_1, e_2, \dotsc\}$, with each $e_i \in \Gamma$.
 
-\begin{definition}[Duplicate element, unseen element]
-Let $E = \{e_1, \dotsc, e_n, \dotsc\}$ be a stream over $\Gamma$. $e_j$ is called a \emph{duplicate} in $E$ if and only if $\exists i < j, e_i = e_j$. Otherwise, $e_j$ is said to be \emph{unseen}.
+\begin{definition}[Duplicate and unseen element]
+Let $E = \{e_i\}$ be a stream over $\Gamma$.
+Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$.
+Otherwise, $e_j$ is said to be \emph{unseen}.
 \end{definition}
 
-A filter $\mathcal F$ is defined by $\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$. Furthermore,
+\begin{definition}[Duplace detection filter]
+	A \emph{duplicate detection filter} (DDF) is a collection of two algorithms 
+	$\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$ of a state $\mathcal S \in \mathcal M$\footnote{Here, $\mathcal M$ denotes all the memory states that can be reached by the filter.} and two algorithms,
+	\begin{itemize}
+		\item $\mathsf{Detect}: \mathcal M \times \Gamma \to \{\DUPLICATE, \UNSEEN\}$;
+		\item $\mathsf{Insert}: \mathcal M \times \Gamma \to \mathcal M$.
+	\end{itemize}
+	Informally, the $\mathsf{Detect}$ algorithm tentatively labels an element $e$ as duplicate or not, given the current state $\mathcal S$; whereas $\mathsf{Insert}$ takes as input the current state, an element $e$ to insert in the filter, and returns an updated memory state $\mathcal S'$.
+\end{definition}
 
-\begin{itemize}
-	\item $\mathcal S \in \mathcal M$ represents the current state of the filter amongst all possible memory states $\mathcal M$.
-	\item $\mathsf{Detect}: \mathcal M \times \Gamma \rightarrow \{\DUPLICATE, \UNSEEN\}$ is an algorithm that given the current state $\mathcal S$, guesses if an element $e$ is a duplicate or not.
-	\item $\mathsf{Insert}: \mathcal M \times \Gamma \rightarrow \mathcal M$ takes as input the current state, an element $e$ to insert in the filter, and returns an updated memory state.
-\end{itemize}
-
-Furthermore, since we work in a context where the memory is too small for perfect detection, we have the assumption that $|\mathsf S| \ll U$.
+We will usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathsf S| \ll |\Gamma|$.
 
 \begin{definition}[False positive, false negative]
-	Let $e$ be an unseen (resp.
-duplicate) element in the stream $E = \{e_1, \dotsc, e_n\}$, and let $\mathcal F$ be a filter.
-$e$ is a \emph{false positive} (resp.
-\emph{false negative}) if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
+	Let $e \in E$ be an unseen (resp.
+duplicate) and $\mathcal F$ be a filter.
+We say that $e$ is a \emph{false positive} (resp.
+\emph{false negative}) when $\mathcal F.\mathsf{Detect}(e) = \DUPLICATE$ (resp.
 $\UNSEEN$).
@@
 \begin{definition}[False positive rate, false negative rate]
-	Let $E = \{e_1, \dotsc, e_n\}$ be a stream, $\mathcal F$ be a filter.
-The false positive (resp.
-false negative) rate of $\mathcal F$ over the first $i < n$ elements, noted $\FPR_i$ (resp.
-$\FNR_i$), is defined as the number of false positives divided by the number of unseen elements of $\{e_1, \dotsc, e_i\}$ (resp.
-the number of false negative divided by the number of duplicate elements).
+	Let $E$ be a stream, $\mathcal F$ be a filter.
+The \emph{false positive rate} (resp.
+\emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp.
+$\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $\{e_1, \dotsc, e_i\}\subset E$ (resp.
+the ratio of false negative divided by the number of duplicate elements in that subset).
 \end{definition}
@@
 
-%\begin{acks}
-%
-%\end{acks}
+%% Acknowledgements 
+%\begin{acks} \end{acks}
 
-%
-% The next two lines define the bibliography style to be used, and the bibliography file.
+%% Bibliography
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
+\bibliography{qhtv2.bib}
 
-% 
-% If your work has an appendix, this is the place to put it.
+%% Appendix
 %\appendix
 
-%\section{Research Methods}
-
 \end{document}

### 2020-03-03 qhtv2.tex
Allègement des notations

@@
 It is understood that the stream $S_t$ is updated at every time increment.
-An \emph{efficient} solution to this problem provides an answer with bounded error $\epsilon$, using polynomially many resources (time and memory) in $1/epsilon$.
+An \emph{efficient} solution to this problem provides an answer with bounded error $\epsilon$, using polynomially many resources (time and memory) in $1/\epsilon$.
 
@@
 Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$.
-Otherwise, $e_j$ is said to be \emph{unseen}.
+In that case we write $e_j \in^2 E$.
+Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notin^2 E$.
 \end{definition}
@@
 \begin{definition}[False positive, false negative]
-	Let $e \in E$ be an unseen (resp.
-duplicate) and $\mathcal F$ be a filter.
+	Let $e \in^2 E$ (resp.
+$e \notin^2 E$) and $\mathcal F$ be a filter.
 We say that $e$ is a \emph{false positive} (resp.
@@
 
-\subsection{Filter Saturation}
-While the previous definition sounds interesting and is often simpler to work with, especially for the derivation of the FPR and FNR, it has been shown that this kind of duplicate detection is an ill-formed problem, as filters saturate and reach the asymptotic relation $\FPR_\infty + \FNR_\infty = 1$, which means that the filter is not any more efficient than a filter answering randomly.
-We reproduce the statement and proof from \cite{10.1145/3297280.3297335}.
+\subsection{Filter Saturation and Sliding Windows}
+Unfortunately, duplicate detection over an infinite stream has the following effect.
+Since a filter can only store at most one element per bit \cite[Section 2.1]{10.1145/3297280.3297335}, a filter of size $M$ can information-theoretically remember at most $M$ elements.
+Thus after $fM$ insertions (with $f \gg 1$), at most a small fraction $1/f \ll 1$ of the stream can be stored, we say that the filter is \emph{saturated}.
 
+In other terms, any filter is asymptotically as good as a random guess:
 	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
@@
 
-	If $U \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
+	If $|\Gamma| \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
 \end{theorem}
-
-\begin{proof}
-	First note that random filters always verify the relation $\FNR + \FPR = 1$: given that a random filter will return \DUPLICATE with a probability of $p$, an unseen element will be classified as \DUPLICATE with probability $p$, and a duplicate will be classified as \UNSEEN with probability $1-p$, hence the result.
-
-	Now, on infinite streams with infinitely many different elements, filters are saturated with information.
-Given that a filter can only store at most one element per bit (cf.
-\cite[][Section 2.1]{10.1145/3297280.3297335}), thus a filter of size $M$ can remember at most $M$ elements.
-However, after $fM$ insertions (with $f \gg 1$), the filter remembers at most a tiny fraction $\frac 1f \ll 1$ of the stream.
-Having reached its saturated state, the filter has an extremely tiny probability $\frac 1f \approx 0$ of correctly guessing whether the incoming element is a duplicate or not, given what the filter actually knows about the stream.
-For this reason, the best strategy of a saturated filter is almost indistinguishable from a random strategy, i.e.
-randomly outputting \DUPLICATE.
-When the stream grows indefinitely, the filter becomes asymptotically equivalent to a random filter.
-\end{proof}
-
-As a consequence, after a sufficient number of elements, no filter can give a significant answer about the duplicate problem.
-
-However, in most practical cases, it is not essential to detect duplicates since the start of the stream, but only duplicates on a sliding window, i.e., duplicates over the last $W$ elements for some integer $W$.
-
-\subsection{Duplicate Detection over a Sliding Window}
-In this section, we redefine the problem in order to include a sliding window.
-
+One way out of this situation is to lower our expectations and work on a sliding window:
+\begin{definition}[Sliding window DDP]
+	Given a stream of fixed size $S_t = \{s_t, \dotsc, s_{t-w}\}$ and an item $s^\star$, find whether $s^\star \in S_t$.
+\end{definition} 
+We therefore introduce new definitions suited to that setting:
 \begin{definition}[Duplicate element, unseen element over a sliding window]
-	Let $E = \{e_1, \dotsc, e_n, \dotsc\}$ be a stream over $\Gamma$, let $W\in \mathbb N$ be a sliding window size.
-$e_j$ is called a \emph{duplicate} in $E$ over the sliding window $W$ if and only if $\exists j - W \leq i < j, e_i = e_j$.
-Otherwise, $e_j$ is said to be \emph{unseen}.
+	Let $E = \{e_i\}$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
+In this case we write $e_j \in_w^2 E$.
+Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notin_w^2 E$.
 \end{definition}
-
-One observes that a duplicate or unseen element in $E = \{e_1, \dotsc, e_n\}$ over $W$ is equivalent to a duplicate or unseen element in $E' = \{e_{n-W}, \dotsc, e_n\}$ without a sliding window.
-
-Similarly, we redefine the false positive, false negative, false positive rate and false negative rate.
-
 \begin{definition}[False positive, false negative over a sliding window]
-	Let $W$ be the size of a sliding window, $e$ be an unseen (resp.
-duplicate) element in $E = \{e_1, \dotsc, e_n\}$ over $W$, and let $\mathcal F$ be a filter.
-$e$ is a \emph{false positive} (resp.
-\emph{false negative}) over $W$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
+	Let $w \in \mathbb N$, $e \notin_w^2 E$ (resp.
+$e \in_w^2 E$) and let $\mathcal F$ be a filter.
+We say that $e$ is a \emph{false positive} (resp.
+\emph{false negative}) over $w$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
 $\UNSEEN$).
@@
 \begin{definition}[False positive rate, false negative rate over a sliding window]
-	Let $E = \{e_1, \dotsc, e_n\}$ be a stream, $\mathcal F$ be a filter, $W$ be the size of a sliding window.
-The false positive (resp.
-false negative) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $W$, noted $\FPR^W_i$ (resp.
-$\FNR^W_i$), is defined as the number of false positives over $W$ divided by the number of unseen elements in $E$ over $W$ (resp.
-the number of false negative over $W$ divided by the number of duplicate elements over $W$).
+	Let $E$ be a stream, $\mathcal F$ be a filter, $w \in \mathbb N$.
+The \emph{false positive} (resp.
+\emph{false negative}) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $w$, noted $\FPR^w_i$ (resp.
+$\FNR^w_i$), is defined as the number of false positives over $w$ divided by the number of unseen elements in $E$ over $w$ (resp.
+the number of false negative over $w$ divided by the number of duplicate elements over $w$).
 \end{definition}

### 2020-03-03 qhtv2.tex
Nettoyage

@@
 
-\subsection{Bounds on the Duplicate Detection over a Sliding Window Problem}
+\subsection{Bounds on the Sliding Window DDP}
 
 \begin{theorem}
-	Let $W$ be a sliding window size, and let us consider a duplicate detection problem over $W$.
-If the available amount of memory $M$ is such that $M \simeq 2W\log_2W$, then the problem can be solved with almost no error.
+	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.
 \end{theorem}
@@
 \begin{proof}
-Let us consider a duplicate detection problem of a stream $E$ over a sliding window $W$. We first devise a hash function, whose fingerprints are $2 \log_2 W$ bits long.
+	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
+The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
+Therefore $2^{2 \log_2 w / 2} = w$ values $h(e_i)$ can be computed before having a collision, i.e., two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ which have the same hash, i.e.
+$h(e_i) = h(e_j)$.
 
-The birthday paradox, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $H$ over $a$ bits, one must, on average, collect $2^{a/2}$ hashes of different messages before obtaining a collision.
-Hence, in our case, we can store $2^{2 \log_2 W / 2} = W$ fingerprints of different elements before having a collision, i.e., two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ which have the same hash, i.e.
-$H(e_i) = H(e_j)$.
+Let $\mathcal F$ be the following filter: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
+$\mathsf{Insert}(e)$ appends $h(e)$ to the queue before popping the list.
 
-Hence, one can construct a filter $\mathcal F$ which consists in a queue of $W$ hashes: for each new element $e$, \textsf{Detect}(e) returns \DUPLICATE if $H(e)$ is present in the queue, \UNSEEN otherwise.
-\textsf{Insert}(e) just adds $H(e)$ to the queue before popping the list.
-There is no false negative, and a false positive only happens if two elements have the same hash, which does not happen often, hence a low FPR and a null FNR.
-
-The queue stores $W$ hashes, and as such requires $W \cdot 2\log_2 W$ bits of memory.
+There is no false negative, and a false positive only happens if two elements have the same hash, which does not happen often, hence a low FPR and a zero FNR.
+The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
 \end{proof}

### 2020-03-03 qhtv2.tex
Clarifications

@@
 
-\begin{definition}[Duplace detection filter]
+\begin{definition}[Duplicate detection filter]
 	A \emph{duplicate detection filter} (DDF) is a collection of two algorithms 
@@
 Unfortunately, duplicate detection over an infinite stream has the following effect.
-Since a filter can only store at most one element per bit \cite[Section 2.1]{10.1145/3297280.3297335}, a filter of size $M$ can information-theoretically remember at most $M$ elements.
-Thus after $fM$ insertions (with $f \gg 1$), at most a small fraction $1/f \ll 1$ of the stream can be stored, we say that the filter is \emph{saturated}.
+Since a DDF can only store at most one element per bit \cite[Section 2.1]{10.1145/3297280.3297335}, a DDF of size $M$ can information-theoretically remember at most $M$ elements.
+Thus after $fM$ insertions (with $f \gg 1$), at most a small fraction $1/f \ll 1$ of the stream can be stored, we say that the DDF is \emph{saturated}.
 
-In other terms, any filter is asymptotically as good as a random guess:
+In other terms, any DDF is asymptotically as good as a random guess:
 	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
@@
 	Let $w \in \mathbb N$, $e \notin_w^2 E$ (resp.
-$e \in_w^2 E$) and let $\mathcal F$ be a filter.
+$e \in_w^2 E$) and let $\mathcal F$ be a DDF.
 We say that $e$ is a \emph{false positive} (resp.
@@
 \begin{definition}[False positive rate, false negative rate over a sliding window]
-	Let $E$ be a stream, $\mathcal F$ be a filter, $w \in \mathbb N$.
+	Let $E$ be a stream, $\mathcal F$ be a DDF, $w \in \mathbb N$.
 The \emph{false positive} (resp.
@@
 \subsection{Bounds on the Sliding Window DDP}
-
+\todo[R.: je pense qu'on peut donner la probabilité exacte sans beaucoup plus d'effort]
 \begin{theorem}
@@
 
-Let $\mathcal F$ be the following filter: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
+Let $\mathcal F$ be the following DDF: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
 $\mathsf{Insert}(e)$ appends $h(e)$ to the queue before popping the list.
@@
 \end{proof}
+When $|\Gamma| > 2 \log_2 w$ this DDF outperforms the naive strategy, both in terms of time and memory. Whether it is possible to bring the value of $M$ below $O(w \log_2 w)$ is an open problem.
 
-One can also observe that the lookup algorithm on this structure is trivially parallelizable, with a very low error rate, hence having an efficient and near optimal solution.
-
-As such, the problem remains open for cases where $M \ll W \log_2 W$.
+Note that unlike the DDP, we do not necessarily encounter saturation for the sliding window DDP, which makes it possible for different DDF to have different performances in the asymptotic regime.
 

### 2020-03-03 qhtv2.tex
Clarifications

@@
 
-\section{Unsuitability of Most Filters for Duplicate Detection over a Sliding Window}
-While the duplicate detection problem over a sliding window is only but a slight reformulation of the original problem of duplicate detection, it turns out that most streaming filters which perform well in the latter problem are not as performant in the former.
+\subsection{DDP vs Sliding Window DDP}
+The sliding window variant of DDP may seem to be a slight weakening of the original problem.
+Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
+A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF)\footnote{SQFs are a special case of QHTs \cite{10.1145/3297280.3297335}.
+As such, only QHT will be discussed.} \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
 
-From our literature reviews, there are 6 competing duplicate filters adapted for streaming data: 
-\begin{itemize}
-	\item A2 filters \cite{Yoo10}
-	\item Stable Bloom Filters (SBF) \cite{Den06}
-	\item Streaming Quotient Filters (SQF)\footnote{It has been shown in \cite{10.1145/3297280.3297335} that SQFs are strictly less efficient than QHTs.
-As such, they will not be used in the rest of this paper.} \cite{Dut13}
-	\item Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}
-	\item Block-decaying Bloom Filters (b\_DBF) \cite{She08}
-	\item A variation of Cuckoo Filters \cite{Fan14}, suggested by \cite{10.1145/3297280.3297335}
-\end{itemize}
 \todo[Regarder https://www2005.org/cdrom/docs/p12.pdf]
 
-All these filters except the b\_DBF were not defined in the context of a sliding window $W$.
-As a consequence, their parameters do not depend on $W$, and as such, behave poorly when used in the paradigm of duplicate detection over a sliding window.
+Of these, only the b\_DBF was defined in the context of a sliding window.
+The others do not account for a finite-length sliding window, and cannot be adjusted as a function of $w$.
+Another remarkable (but experimental) observation is that these DDFs' false positive rate does not decrease to 0 when the sliding window becomes small.
 
-Experimentally, we observe that the false positive rate of these filters does not decrease to 0 even though the sliding window becomes small; this is because in these filters,
+\todo[Expliquer ?]
 

### 2020-03-03 qhtv2.tex
harmonisation

@@
 \paragraph{Duplicate detection problem.}
-We consider the following problem (duplicate detection problem, DPP): given a stream $S_t = \{s_t, s_{t-1}, \dotsc\}$ and an item $s^\star$, find whether $s^\star \in S_t$.
-It is understood that the stream $S_t$ is updated at every time increment.
-An \emph{efficient} solution to this problem provides an answer with bounded error $\epsilon$, using polynomially many resources (time and memory) in $1/\epsilon$.
+We consider the following problem (duplicate detection problem, DPP): given a stream $E_n = \{e_1, e_2, \dotsc, E_n\}$ and an item $e^\star$, find whether $e^\star \in E_n$.
+It is understood that the stream $E_n$ is updated at every time increment.
+An \emph{efficient} solution to this problem provides an answer with bounded error $\epsilon$, \todo[A verifier using polynomially many resources (time and memory) in $1/\epsilon$].
 
@@
 A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.
-Even when the stream is bounded, i.e. $\lim_{t\to\infty}|S_t| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable.
+Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable.
 
-\paragraph{Approximate and exact DPP.}
-One way to relax the DPP is to allow \emph{approximate} duplicate detection \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}.
-We instead focus on \emph{exact} duplicate detection, in which an element is considered a duplicate if and only if it has already appeared in the stream.
-One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates over an alphabet of $U$ letters requires $U$ bits of memory.
+\paragraph{Fuzzy and approximate DPP}
+A quite popular research topic on the subject of duplicate detection is \emph{fuzzy} detection \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}.
+This is however out of the scope of our work, as we consider an element to be a duplicate if and only if the exact ame element has already appeared in the stream.
+\emph{Approximate} detection states that no attempt will be done to reach perfect accuracy, but rather to limit as much as possible the errors.
+One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates over an alphabet of $U$ letters requires $U$ bits of memory, thus being impracticable in many cases.
 
-As it turns out, exact duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
+As it turns out, approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
 Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.
@@
 \subsection{Notations and Initial Problem Statement}
-Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) collection $E = \{e_1, e_2, \dotsc\}$, with each $e_i \in \Gamma$.
+Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) set $E = \{e_1, e_2, \dotsc\}$, with each $e_i \in \Gamma$.
 
 \begin{definition}[Duplicate and unseen element]
-Let $E = \{e_i\}$ be a stream over $\Gamma$.
+Let $E = \{e_1, e_2, \dotsc\}$ be a stream over $\Gamma$.
 Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$.
-In that case we write $e_j \in^2 E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notin^2 E$.
+In that case we write $e_j \dup E$.
+Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notdup E$.
 \end{definition}
@@
 \begin{definition}[Duplicate detection filter]
-	A \emph{duplicate detection filter} (DDF) is a collection of two algorithms 
-	$\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$ of a state $\mathcal S \in \mathcal M$\footnote{Here, $\mathcal M$ denotes all the memory states that can be reached by the filter.} and two algorithms,
+	A \emph{duplicate detection filter} (DDF) is a collection 
+	$\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$ of a state\footnote{Here, $\mathcal M$ denotes all the memory states that can be reached by the filter.} $\mathcal S \in \mathcal M$ and two algorithms,
 	\begin{itemize}
@@
 
-We will usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathsf S| \ll |\Gamma|$.
+We will usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathcal S| \ll |\Gamma|$.
 
 \begin{definition}[False positive, false negative]
-	Let $e \in^2 E$ (resp.
-$e \notin^2 E$) and $\mathcal F$ be a filter.
+	Let $e \dup E$ (resp.
+$e \notdup E$) and $\mathcal F$ be a filter.
 We say that $e$ is a \emph{false positive} (resp.
@@
 \subsection{Filter Saturation and Sliding Windows}
-Unfortunately, duplicate detection over an infinite stream has the following effect.
-Since a DDF can only store at most one element per bit \cite[Section 2.1]{10.1145/3297280.3297335}, a DDF of size $M$ can information-theoretically remember at most $M$ elements.
-Thus after $fM$ insertions (with $f \gg 1$), at most a small fraction $1/f \ll 1$ of the stream can be stored, we say that the DDF is \emph{saturated}.
+Unfortunately, duplicate detection over an infinite stream has been identified as an ill-posed problem.
+As a matter of fact, as the number of bits of information of the stream grow to infinity, the filter can only remember an ever diminishing proportion of those bits, eventually having no advantage compared to a filter answering randomly.
 
@@
 \begin{definition}[Sliding window DDP]
-	Given a stream of fixed size $S_t = \{s_t, \dotsc, s_{t-w}\}$ and an item $s^\star$, find whether $s^\star \in S_t$.
+	Given a stream $E_n$ of fixed size $w$, with $E_n = \{e_{n-w+1}, \dotsc, e_n\}$ and an item $e^\star$, find whether $e^\star \in E_n$.
 \end{definition} 
@@
 \begin{definition}[Duplicate element, unseen element over a sliding window]
-	Let $E = \{e_i\}$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
-In this case we write $e_j \in_w^2 E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notin_w^2 E$.
+	Let $E = \{e_1, e_2, \dotsc\}$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
+In this case we write $e_j \wdup E$.
+Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notwdup E$.
 \end{definition}
 \begin{definition}[False positive, false negative over a sliding window]
-	Let $w \in \mathbb N$, $e \notin_w^2 E$ (resp.
-$e \in_w^2 E$) and let $\mathcal F$ be a DDF.
+	Let $w \in \mathbb N$, $e \notwdup E$ (resp.
+$e \wdup E$) and let $\mathcal F$ be a DDF.
 We say that $e$ is a \emph{false positive} (resp.
@@
 \subsection{Bounds on the Sliding Window DDP}
-\todo[R.: je pense qu'on peut donner la probabilité exacte sans beaucoup plus d'effort]
+
 \begin{theorem}
 	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.
+
+	More precisely, it is possible to create a filter with a FNR of $0$, and a FPR of $\frac{1}{w}$.
 \end{theorem}
@@
 The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
-Therefore $2^{2 \log_2 w / 2} = w$ values $h(e_i)$ can be computed before having a collision, i.e., two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ which have the same hash, i.e.
-$h(e_i) = h(e_j)$.
+Therefore $2^{2 \log_2 w / 2} = w$ values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
+$h(e_i) = h(e_j)$).
 
@@
 
-There is no false negative, and a false positive only happens if two elements have the same hash, which does not happen often, hence a low FPR and a zero FNR.
+There is no false negative, and a false positive only happens if the new element to be inserted collides with another element, which happens with probability $\frac 12\frac{2}{w}$, hence an FNR of $0$ and a FPR of $\frac{1}{w}$.
 The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
 \end{proof}
-When $|\Gamma| > 2 \log_2 w$ this DDF outperforms the naive strategy, both in terms of time and memory. Whether it is possible to bring the value of $M$ below $O(w \log_2 w)$ is an open problem.
+
+When $|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naive strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w |\Gamma|$ bits of memory.}, both in terms of time and memory.
+Whether it is possible to bring the value of $M$ below $O(w \log_2 w)$ is an open problem.
 
 Note that unlike the DDP, we do not necessarily encounter saturation for the sliding window DDP, which makes it possible for different DDF to have different performances in the asymptotic regime.
+
+Another remark is that when $M \approx w\log_2w$, it may be possible to solve the problem almost optimally in terms of error rate, the proposed solution remains very slow, requiring $O(W)$ computation time (although this complexity can be parallelized).
+Hence, it remains an open question of how to quickly detect duplicates in this context.
 
@@
 Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
-A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF)\footnote{SQFs are a special case of QHTs \cite{10.1145/3297280.3297335}.
-As such, only QHT will be discussed.} \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF)\footnote{QHTs stem from a correction of SQFs, and as such SQFs are less efficient than QHT in every situation \cite{10.1145/3297280.3297335}.
+As such, only QHTs will be discussed.} \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{qhtv2.bib}
+\bibliography{qhtv2}
 

### 2020-03-03 qhtv2.tex
précision

@@
 The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
-Therefore $2^{2 \log_2 w / 2} = w$ values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
+Therefore $2^{2 \log_2 w / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
 $h(e_i) = h(e_j)$).

### 2020-03-04 qhtv2.tex
fix proba optimal filter

--- 2020-03-03 qhtv2.tex
@@
 
-	More precisely, it is possible to create a filter with a FNR of $0$, and a FPR of $\frac{1}{w}$.
+	More precisely, it is possible to create a filter with a FNR of $0$, and a FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$.
 \end{theorem}
@@
 The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
-Therefore $2^{2 \log_2 w / 2} = w$ values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
+Therefore $2^{(2 \log_2 w) / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
 $h(e_i) = h(e_j)$).
@@
 
-There is no false negative, and a false positive only happens if the new element to be inserted collides with another element, which happens with probability $\frac 12\frac{2}{w}$, hence an FNR of $0$ and a FPR of $\frac{1}{w}$.
+There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FNR of $0$ and a FPR of $1 - (1-\frac1{w^2})^w$.
 The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
@@
 
-Another remark is that when $M \approx w\log_2w$, it may be possible to solve the problem almost optimally in terms of error rate, the proposed solution remains very slow, requiring $O(W)$ computation time (although this complexity can be parallelized).
+Another remark is that when $M \approx w\log_2w$, it may be possible to solve the problem almost optimally in terms of error rate, the proposed solution remains very slow, requiring $O(w)$ computation time (although this complexity can be parallelized).
 Hence, it remains an open question of how to quickly detect duplicates in this context.

### 2020-03-04 qhtv2.tex
coquilles

@@
 \paragraph{Duplicate detection problem.}
-We consider the following problem (duplicate detection problem, DPP): given a stream $E_n = \{e_1, e_2, \dotsc, E_n\}$ and an item $e^\star$, find whether $e^\star \in E_n$.
+We consider the following problem (duplicate detection problem, DPP): given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and an item $e^\star$, find whether $e^\star \in E_n$.
 It is understood that the stream $E_n$ is updated at every time increment.
@@
 
-	More precisely, it is possible to create a filter with a FNR of $0$, and a FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$.
+	More precisely, it is possible to create a filter of $M$ bits with an FNR of $0$, and an FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$.
 \end{theorem}
@@
 $h(e_i) = h(e_j)$).
+The 50\% threshold we impose on $h$ is arbitrary but nonetheless practical.
 
@@
 When $|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naive strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w |\Gamma|$ bits of memory.}, both in terms of time and memory.
-Whether it is possible to bring the value of $M$ below $O(w \log_2 w)$ is an open problem.
 

### 2020-03-06 qhtv2.tex
Add pseudocode + FPR

@@
 
+However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^*$ is a false positive (resp. false negative).
+
+\begin{definition}[Probability of false positive, of false negative]
+	Let $E = \{e_1, \dotsc\}$ be a stream, $\mathcal F$ be a filter.
+The \emph{probability of false positive} (resp.
+\emph{probability of false negative}) of $\mathcal F$ after $i$ elements, denoted $\FP_i$ (resp.
+$\FN_i$), is defined as the proabability that $e_{i+1}$ is a false positive (resp.
+false negative).
+\end{definition}
+
+One can observe that $\FPR_n = \frac{1}{n}\sum_{i=1}^m \FP_i$, and similarly for $\FNR_n$.
+
 \subsection{Filter Saturation and Sliding Windows}
@@
 \end{theorem}
+
 One way out of this situation is to lower our expectations and work on a sliding window:
+
 \begin{definition}[Sliding window DDP]
@@
 \end{definition}
+
 We therefore introduce new definitions suited to that setting:
+
 \begin{definition}[Duplicate element, unseen element over a sliding window]
@@
 \end{definition}
+
 \begin{definition}[False positive, false negative over a sliding window]
@@
 \section{Queuing Filters for Sliding Window Adaptation}
+In this section, we propose a way of adapting filters to a sliding window context. We first give the description of the setup, before studying the theoretical error rates.
 
-\section{Application on QHT}
+\subsection{Queueing Filter}
+Let $\mathcal F$ be a streaming filter, not designed to work on a sliding window.
+Our idea is, instead of spawning a filter $\mathcal F$ using as much memory as possible, to create $L$ small versions of $\mathcal F$, which all have a limited timespan and can store up to $c$ elements.
+These small filters are organised in a queue, in chronological order, the oldest filters being at the end of the queue.
+When the oldest filter reaches saturation, it is deleted, and a new small filter is instantiated, and placed at the beginning of the queue.
 
-\section{Optimal Error rate on a Filter}
+Since the goal is to remember all elements from a sliding window of size $w$, we have the relation $Lc \approx w$.
+The relation is only an approximation since it may be difficult, depending on the underlying subfilter, to ensure the equality.
+A scheme describing our structure is detailed in \Cref{fig:scheme}.
+
+\begin{figure}
+	\begin{tikzpicture}[scale=0.4]
+
+	% F_0 under construction
+	\draw[pattern=north west lines, pattern color=gray, draw=none] (1, 0) rectangle (2, 1);
+	\draw (0, 0) rectangle (2, 1) node[midway] {$\mathcal F_0$};
+
+	% Other subfilters
+	\draw[pattern=north west lines, pattern color=gray] (3, 0) rectangle (5, 1) node[midway] {$\mathcal F_1$};
+	\draw[pattern=north west lines, pattern color=gray] (6, 0) rectangle (8, 1) node[midway] {$\mathcal F_2$};
+	\node at (9.5, 0.5) {...};
+	\draw[pattern=north west lines, pattern color=gray] (11, 0) rectangle (13, 1) node[midway] {$\mathcal F_{L-1}$};
+
+	% old subfilters
+	\draw[dashed] (14, 0) rectangle (16, 1) node[midway] {$\mathcal F_{L}$};
+	\draw[dashed] (17, 0) rectangle (19, 1) node[midway] {$\mathcal F_{L+1}$};
+
+	% arrows
+	\draw [<->,>=latex] (6, 1.5) -- (8, 1.5) node[above, midway] {$c$ elements};
+	\draw [<->,>=latex] (0, -3) -- (13, -3) node[below, midway] {$Lc \approx w$ elements};
+	\draw [<->,>=latex] (1, 3) -- (15, 3) node[above, midway] {Current sliding window (of size $w$)};
+
+	%queueing filter
+	\draw (-0.5, 2.5) rectangle (13.5, -2.5) node[anchor=south east] {Queuing filter};
+
+	% legend
+	\draw[draw=none, pattern=north west lines, pattern color=gray] (0.5, -5) rectangle (1, -5.5);
+	\draw (0, -5) rectangle (1, -5.5) node[midway] {\tiny $\mathcal F$};
+	\draw (1.25, -5.25) node[anchor=west] {\tiny Subfilter being populated};
+
+	\draw[pattern=north west lines, pattern color=gray] (7, -5) rectangle (8, -5.5) node[midway] {\tiny $\mathcal F_i$};
+	\draw (8.25, -5.25) node[anchor=west] {\tiny Populated active subfilter};
+
+	\draw[dashed] (14, -5) rectangle (15, -5.5) node[midway] {\tiny $\mathcal F_j$};
+	\draw (1 5.25, -5.25) node[anchor=west] {\tiny Expired subfilter};
+	\end{tikzpicture}
+	\caption{Architecture of the queuing filter.
+The filter is composed of $L$ subfilters $\mathcal F$, each containing up to $c$ elements.
+Once all subfilters are full with $c$ elements each, the oldest one is expired.
+As such, it is dropped and a new one is created and put under population at the beginning of the queue.}\label{fig:scheme}
+\end{figure}
+
+In the rest of this paper, we refer to the small filters constituting the queuing filter as \emph{subfilters}.
+
+When the user wants to lookup for an element, they query all subfilters.
+If any subfilter answers with \DUPLICATE, the queueing filter answers \DUPLICATE.
+Otherwise, it answers \UNSEEN.
+Insertion is a simple insertion in the topmost subfilter.
+
+After $c$ insertions (where $c$ is a filter parameter), the last filter of the queue is removed, and a new (empty) filter is appended in front of the queue.
+We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in \Cref{alg:queueing}.
+
+For the sake of simplicity in the pseudocode, we assume that the subfilter $\mathcal F$ has a function \textsf{Setup} which takes as input the available memory $m$, and returns an initialized empty filter $\mathcal F$ of size at most $m$..
+
+\begin{algorithm}[]
+	\caption{Queueing Filter Setup, Lookup and Insert}\label{alg:queueing}
+
+	\begin{algorithmic}[1]
+	\Function{Setup}{$\mathcal F, M, L, c$}
+		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
+		\State Queue\_storage $\gets$ empty queue
+		\State Counter $\gets 0$
+		\For{$i$ from $0$ to $L-1$}
+			\State Queue\_storage[i] $\gets$ $\mathcal F.\mathsf{Setup}(\lfloor M/L \rfloor)$
+		\EndFor
+		Counter $\gets$ 0
+		\State Store $c$, $M$, $L$, $\mathcal F$
+
+		\State \Return filter
+	\EndFunction 
+	\item[]
+	\end{algorithmic}
+
+	\begin{algorithmic}[1]
+	\Function{Lookup}{$e$}
+		\For{$i$ from $0$ to $L-1$}
+			\If{$\mathcal F_i.\mathsf{Lookup(e)}$}
+				\State \Return $\DUPLICATE$
+			\EndIf
+		\EndFor
+		\State \Return \UNSEEN
+	\EndFunction
+	\item[]
+	\end{algorithmic}
+
+	\begin{algorithmic}[1]
+	\Function{Insert}{$e$}
+		\State $\mathcal F_0.\mathsf{Insert}(e)$
+		\State Counter++
+		\If{Counter == $c$}
+			\State Pop last element of Queue\_Storage
+			\State Insert $\mathcal F$.\textsf{Setup}($\lfloor M/L \rfloor$) at the beginning of Queue\_Storage
+		\EndIf
+	\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+\subsection{Error Rate Analysis}
+Depending on the underlying subfilter, the queueing filter will behave differently.
+However, its false positive and false negative probabilities can be derived from the underlying subfilter's false positive and false negative probabilities.
+
+\subsubsection{Number of Elements in a Queueing Filter}\label{subsub:number_elements}
+Before deriving the error rates, it is important to analyse how many elements are in the filter.
+We know, by design, that no more than $cL$ elements can be present.
+However, after exactly $cL$ insertions, the last subfilter is deleted, to be replaced by an empty one at the beginning of the queue.
+Hence, after $cL$ insertions, only $c(L-1)$ elements are stored in the queueing filter.
+
+Hence, the number of elements in the filter oscillate between $c(L-1)$ and $cL$.
+Furthermore, we have $cL \approx w$, which means that the number of elements in the filter can be higher than $w$.
+These facts must be kept in mind while deriving the error rates.
+
+\subsubsection{Probability of False Positive}
+\begin{theorem}
+	Let $\mathcal Q$ be a queueing filter, consisting of $L$ underlying subfilters $\mathcal F$, each filled with up to $c$ elements.
+Let $\FP_{\mathcal F,m}$ be the probability of false positive of the subfilter $\mathcal F$ after $m$ insertions, let $\FP_{\mathcal Q, m}^w$ be the probability of false positive of $\mathcal Q$ after $m$ insertions on a sliding window of size $w$.
+
+	We have $$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F,c})^{L-1}(1 - \FP_{\mathcal F, m \% cL })$$ where \% is the modulo operator.
+\end{theorem}
+
+\begin{proof}
+	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^* \notwdup E$.
+We first take into account the remark in \Cref{subsub:number_elements} that the filter $\mathcal Q$ may contain more than $w$ elements, and hence potentially contain $e$ in memory, in the last subfilter of the queue.
+However, such event is quite rare, and can be neglected: let $\delta = cL - w$ the number of additional elements that can be stored in $\mathcal Q$.
+The probability that $e^*$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta \approx \frac{\delta}{|\Gamma|} \approx 0$ since $\delta$ is likely to be small, while $|\Gamma|$ is too big for being stored in memory.
+
+	Hence, we can neglect the probability that $e^*$ is present in the filter.
+Therefore, $e^*$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^*)}$ return \DUPLICATE.
+Conversely, $e^*$ is not a false positive if and only if all subqueries $\mathcal F_i.\mathsf{Lookup(e^*)}$ return \UNSEEN.
+This can be rewritten as $e^*$ is not a false positive if and only if $e^*$ is not a false positive for each subfilter.
+
+	Given that each subfilter stores $c$ elements, safe for the first subfilter which only stores $m \% cL$ elements, we get
+	$$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F, m \% cL })(1 - \FP_{\mathcal F,c})^{L-1}$$
+\end{proof}
+
+\subsubsection{False Negative Rate}
+\begin{theorem}
+
+\end{theorem}
+
+\section{Application on Existing Filters}
+
+\subsection{Optimal Error rate on a Subfilter}
+
+\subsection{Filter Comparison}
+
+\subsection{Application on QHT}
 

### 2020-03-06 qhtv2.tex
Clarifications

@@
 \begin{abstract}
-	A duplicate filter is a data structure designed to efficiently detect repetitions (duplicates) in a stream.
-A well-known instance of such a data structure is the Bloom filter, which has been generalised in several ways.
+	A duplicate filter is a data structure designed to efficiently detect repetitions (duplicates) in a stream, when only a limited amount of memory is available.
+A well-known data structure used in this contexte is the Bloom filter, which has been generalised in several ways to
+	improve its performances or strike specific tradeoffs.
 
-	In this paper we introduce a generic framework that adapts duplicate filters to sliding windows, rather than on an infinite stream. Indeed, although the
-	infinite stream setting is known to be ill-defined, many duplicate filters are only described in such a scenario. This enables a rigourous mathematical study of such filters.
+	When analysed in the limit of an infinite stream, error rates of duplicate filters turn out to be heavily constrained; as a consequence they appear to provide no advantage, asymptotically, over a random yes-no coin toss \cite{10.1145/3297280.3297335}.
+
+	In this paper we introduce a generic framework that adapts duplicate filters to the better-behaved context of a sliding window.
+We show that several duplicate filters can be adapted to this context and provide a rigourous mathematical study of such constructions.
 \end{abstract}
@@
 \paragraph{Duplicate detection problem.}
-We consider the following problem (duplicate detection problem, DPP): given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and an item $e^\star$, find whether $e^\star \in E_n$.
+We consider the following problem (duplicate detection problem, DDP): given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$.
 It is understood that the stream $E_n$ is updated at every time increment.
@@
 
-Instances of this problem abound in computer science, with applications in file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
+Instances of this problem abound in computer science, with applications in file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
 A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.
@@
 \paragraph{Fuzzy and approximate DPP}
-A quite popular research topic on the subject of duplicate detection is \emph{fuzzy} detection \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}.
-This is however out of the scope of our work, as we consider an element to be a duplicate if and only if the exact ame element has already appeared in the stream.
+A popular approach for the DDP is \emph{fuzzy} detection \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}. 
+{\color{blue} R.: tu veux dire un mot sur ce que c'est?}
+This is however out of the scope of our work, as we consider an element to be a duplicate if and only if the exact same element has already appeared in the stream.
 \emph{Approximate} detection states that no attempt will be done to reach perfect accuracy, but rather to limit as much as possible the errors.
-One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates over an alphabet of $U$ letters requires $U$ bits of memory, thus being impracticable in many cases.
+One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory: even for modest situations (e.g.
+64-bit nonces, corresponding to $2^{64}$ possible values) this is quickly impractical.
 
-As it turns out, approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
+Approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
 Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.
@@
 
-However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^*$ is a false positive (resp. false negative).
+However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^\star$ is a false positive (resp. false negative).
 
@@
 
-Another remark is that when $M \approx w\log_2w$, it may be possible to solve the problem almost optimally in terms of error rate, the proposed solution remains very slow, requiring $O(w)$ computation time (although this complexity can be parallelized).
-Hence, it remains an open question of how to quickly detect duplicates in this context.
+Another remark is that when $M \approx w\log_2w$, the error rate is minimal but $O(w)$ operations ares required (although this complexity may be reduced using parallelized implementations).
+Detect duplicates faster in this context remains an open question.
 
@@
 Of these, only the b\_DBF was defined in the context of a sliding window.
-The others do not account for a finite-length sliding window, and cannot be adjusted as a function of $w$.
+The others do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
 Another remarkable (but experimental) observation is that these DDFs' false positive rate does not decrease to 0 when the sliding window becomes small.
@@
 \section{Queuing Filters for Sliding Window Adaptation}
-In this section, we propose a way of adapting filters to a sliding window context. We first give the description of the setup, before studying the theoretical error rates.
+In this section, we describe how to turn DDF into sliding window DDFs. We first give the description of the setup, before studying the theoretical error rates.
 

### 2020-03-09 qhtv2.tex
Add FNR + start benchmark

@@
 	\affiliation{%
-	\institution{Département d'informatique de l'ENS, École normale supérieure, CNRS, PSL Research University}
+	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
 	\city{Paris} \state{France}
@@
 	\affiliation{%
-	\institution{Département d'informatique de l'ENS, École normale supérieure, CNRS, PSL Research University}
+	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
 	\city{Paris} \country{France}
@@
 A popular approach for the DDP is \emph{fuzzy} detection \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}.
-{\color{blue} R.: tu veux dire un mot sur ce que c'est?}
+Fuzzy detection deals with detecting \emph{fuzzy} duplicates (i.e., detecting if two elements are similar), which can be useful in several context, such as text processing.
+
 This is however out of the scope of our work, as we consider an element to be a duplicate if and only if the exact same element has already appeared in the stream.
@@
 
-\subsection{Related Work}
-
+\subsection{Related Work}\label{sub:related}
+\todo[continuer]
+The idea of using subfilters, tossing old ones has already been explored in the A2 filter \cite{Yoo10}.
+However, the author only considered a small portion of the problem, as they only discussed about using two subfilters, and only Bloom Filters acting as subfilters.
+In this work, we provide a full abstraction of the mechanism, allowing us to use many other DDF than Bloom Filters.
+We also provide a generalised analysis of the error rates.
 \subsection{Organisation}
@@
 
-Note that unlike the DDP, we do not necessarily encounter saturation for the sliding window DDP, which makes it possible for different DDF to have different performances in the asymptotic regime.
+Note that unlike the DDP, we do not necessarily encounter filter saturation for the sliding window DDP, which makes it possible for different DDF to have different performances in the asymptotic regime and thus to be ranked.
 
 Another remark is that when $M \approx w\log_2w$, the error rate is minimal but $O(w)$ operations ares required (although this complexity may be reduced using parallelized implementations).
-Detect duplicates faster in this context remains an open question.
+Detecting duplicates faster in this context remains an open question.
 
@@
 A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF)\footnote{QHTs stem from a correction of SQFs, and as such SQFs are less efficient than QHT in every situation \cite{10.1145/3297280.3297335}.
-As such, only QHTs will be discussed.} \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+We included them for the sake of completeness.} \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
 
@@
 
-Of these, only the b\_DBF was defined in the context of a sliding window.
+Of these, only the A2 and b\_DBF was defined in the context of a sliding window.
 The others do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
@@
 \subsection{Queueing Filter}
-Let $\mathcal F$ be a streaming filter, not designed to work on a sliding window.
-Our idea is, instead of spawning a filter $\mathcal F$ using as much memory as possible, to create $L$ small versions of $\mathcal F$, which all have a limited timespan and can store up to $c$ elements.
-These small filters are organised in a queue, in chronological order, the oldest filters being at the end of the queue.
-When the oldest filter reaches saturation, it is deleted, and a new small filter is instantiated, and placed at the beginning of the queue.
+Let $\mathcal F$ be a DDF, not designed to work on a sliding window.
+Our idea, instead of spawning a filter $\mathcal F$ using as much memory as possible, is to create $L$ small versions of $\mathcal F$, which all have a limited timespan and can insert up to $c$ elements in their structure.
+We call these small filters subfilters.
+The subfilters are organised in a queue.
 
-Since the goal is to remember all elements from a sliding window of size $w$, we have the relation $Lc \approx w$.
-The relation is only an approximation since it may be difficult, depending on the underlying subfilter, to ensure the equality.
-A scheme describing our structure is detailed in \Cref{fig:scheme}.
+When inserting a new element in the queueing filter, it is inserted in the topmost subfilter of the queue.
+After $c$ insertions, a new empty filter is added to the queue, and the oldest subfilter is popped and erased.
+
+As such, we can consider that each subfilter operates on a sub-sliding window of size $c$.
+Given that we have $L$ subfilters and we want to operate on a sliding window of size $w$, we require $cL \approx w$.
+
+A scheme describing our structure is detailed in \ref{fig:scheme}.
 
@@
 	\draw [<->,>=latex] (6, 1.5) -- (8, 1.5) node[above, midway] {$c$ elements};
-	\draw [<->,>=latex] (0, -3) -- (13, -3) node[below, midway] {$Lc \approx w$ elements};
+	\draw [<->,>=latex] (0, -3) -- (13, -3) node[below, midway] {Capacity of $Lc \approx w$ elements};
 	\draw [<->,>=latex] (1, 3) -- (15, 3) node[above, midway] {Current sliding window (of size $w$)};
+
+	%stream 
+	\draw [<-, >=latex] (0, 5.5) -- (19, 5.5) node[above, midway] {Stream};
+	\foreach \x in {1, 3,...,18}
+	\draw (\x, 5.7) -- node[pos=0.5] (point\x) {} (\x, 5.3);
+
+	\foreach \x in {2, 4,...,18}
+	\draw (\x, 5.6) -- node[pos=0.5] (point\x) {} (\x, 5.4);
+
+	\path (point1) node [below] {$e_m$};
+	\foreach \x [evaluate=\x as \i using int(\x-1)] in {3, 5,..., 9}
+	\path (point\x) node [below] {$e_{m-\i}$};
+	\path (point11) node [below] {$\dots$};
+	\path (point15) node [below] {$e_{m - w + 1}$};
 
@@
 The filter is composed of $L$ subfilters $\mathcal F$, each containing up to $c$ elements.
-Once all subfilters are full with $c$ elements each, the oldest one is expired.
-As such, it is dropped and a new one is created and put under population at the beginning of the queue.}\label{fig:scheme}
+Once the newest subfilter has inserted $c$ elements in its structure, the oldest one is expired.
+As such, it is dropped and a new one is created and put under population at the beginning of the queue.
+In this example, the sub-sliding window of $\mathcal F_1$ is $\{e_{m-2}, e_{m-3}, e_{m-4}\}$.} \label{fig:scheme}
 \end{figure}
-
-In the rest of this paper, we refer to the small filters constituting the queuing filter as \emph{subfilters}.
 
@@
 After $c$ insertions (where $c$ is a filter parameter), the last filter of the queue is removed, and a new (empty) filter is appended in front of the queue.
-We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in \Cref{alg:queueing}.
+We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in \ref{alg:queueing}.
 
@@
 
-	We have $$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F,c})^{L-1}(1 - \FP_{\mathcal F, m \% cL })$$ where \% is the modulo operator.
+	We have $$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F,c})^{L-1}(1 - \FP_{\mathcal F, m \% c })$$ where \% is the modulo operator.
 \end{theorem}
@@
 	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^* \notwdup E$.
-We first take into account the remark in \Cref{subsub:number_elements} that the filter $\mathcal Q$ may contain more than $w$ elements, and hence potentially contain $e$ in memory, in the last subfilter of the queue.
+We first take into account the remark in \ref{subsub:number_elements} that the filter $\mathcal Q$ may contain more than $w$ elements, and hence potentially contain $e$ in memory, in the last subfilter of the queue.
 However, such event is quite rare, and can be neglected: let $\delta = cL - w$ the number of additional elements that can be stored in $\mathcal Q$.
@@
 	Hence, we can neglect the probability that $e^*$ is present in the filter.
-Therefore, $e^*$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^*)}$ return \DUPLICATE.
+Therefore, $e^*$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^*)}$ returns \DUPLICATE.
 Conversely, $e^*$ is not a false positive if and only if all subqueries $\mathcal F_i.\mathsf{Lookup(e^*)}$ return \UNSEEN.
@@
 
-	Given that each subfilter stores $c$ elements, safe for the first subfilter which only stores $m \% cL$ elements, we get
-	$$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F, m \% cL })(1 - \FP_{\mathcal F,c})^{L-1}$$
+	Given that each subfilter stores $c$ elements, safe for the first subfilter which only stores $m \% c$ elements, we get
+	$$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F, m \% c })(1 - \FP_{\mathcal F,c})^{L-1}$$
 \end{proof}
 
-\subsubsection{False Negative Rate}
+\subsubsection{Probability of False Negative}\label{sub:fnr}
 \begin{theorem}
+	Let $\mathcal Q$ be a queueing filter, consisting of $L$ underlying subfilters $\mathcal F$, each filled with up to $c$ elements.
+Let $\FN_{\mathcal F,m}$ be the probability of false negative of the subfilter $\mathcal F$ after $m$ insertions, let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m$ insertions on a sliding window of size $w$.
 
+	For $p_m = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^m}{1-\left(1-\frac 1{|\Gamma|}\right)^w}$, we have 
+	\begin{align*}
+	\FN_{\mathcal Q, m}^w =& \left[p_c\FN_{\mathcal F,c} + \left(1-p_c\right)\left(1-\FP_{\mathcal F,c}\right)\right]^{L-1}
+	\\&\qquad
+	 \cdot \left[p_{m\%c}\FN_{\mathcal F,m\%c} + \left(1-p_{m\%c}\right)\left(1-\FP_{\mathcal F,m\%c}\right)\right]
+	\end{align*}
+
+	where $\%$ is the modulo operator.
 \end{theorem}
 
-\section{Application on Existing Filters}
+\begin{proof}
+	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^* \wdup E$.
+	We first observe that if $cL > w$, there might be some duplicates of $e^*$ that happened before the current sliding window, but might still be remembered by the oldest filter.
+However, as argued in the previous section, the probability of such an event is negligible.
 
-\subsection{Optimal Error rate on a Subfilter}
+	Hence, we consider that the only duplicates are part of the sliding window.
+$e^*$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^*) = \UNSEEN$.
 
-\subsection{Filter Comparison}
+	There can be two cases:
+	\begin{itemize}
+		\item $e^*$ is present in $\mathcal F_i$'s sub-sliding window 
+		\item $e^*$ is present in $\mathcal F_i$'s sub-sliding window
 
-\subsection{Application on QHT}
+	\end{itemize}
+
+In the first case, $\mathcal F_i.\mathsf{Detect}(e^*)$ returns \UNSEEN if and only if $e^*$ is a false negative for $\mathcal F_i$.
+Hence, in this case, the probability of $\mathcal F_i$ to return \UNSEEN is $\FN_{\mathcal F,c}$.
+For the subfilter $\mathcal F_0$, however, the probability is $\FN_{\mathcal F, m\%c}$.
+
+In the second case, $\mathcal F_i.\mathsf{Detect}(e^*)$ returns \UNSEEN if and only if $e^*$ is not a false positive for $\mathcal F_i$.
+Hence, in this case, the probability of $\mathcal F_i$ to return \UNSEEN is $1-\FP_{\mathcal F,c}$.
+For the subfilter $\mathcal F_0$, however, the probability is $1-\FP_{\mathcal F, m\%c}$.
+
+Now, the probability $p_c$ for $e^*$ to be in subfilter $\mathcal F_i$ (which has had $c$ insertions) sub-sliding window is
+
+\begin{align*}
+	p_c =& Pr[\text{$e^*$ is in }\mathcal F_i \text{ sub-sliding window | } e^* \wdup E]\\
+	=& \frac{Pr[\text{$e^*$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^* \wdup E]}{Pr[e^* \wdup E]}\\
+	=& \frac{Pr[\text{$e^*$ is in }\mathcal F_i \text{ sub-sliding window}]}{Pr[e^* \wdup E]}\\
+	=& \frac{1 - Pr[\text{$e^*$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - Pr[e^* \notwdup E]}\\
+	p_c=& \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
+\end{align*}
+
+Finally, we get that the probability of a false positive for $\mathcal Q$ over the sliding window $w$ is 
+\begin{align*}
+\FN^w_{\mathcal Q, m} =& \left[p_c\FN_{\mathcal F,c} + (1-p_c)(1-\FP_{\mathcal F,c})\right]^{L-1}
+\\&\quad
+\cdot \left[p_{m\%c}\FN_{\mathcal F,m\%c} + (1-p_{m\%c})(1-\FP_{\mathcal F,m\%c})\right]\\
+\end{align*}
+\end{proof}
+
+This probability is quite complicated and does not allow, in the general case, for an in-depth analysis of the probability of false negative.
+
+\begin{theorem}
+	In first approximation, a low value of $L$ leads to a higher false negative probability for the queueing filter.
+\end{theorem}
+
+\begin{proof}
+As a matter of fact, on average the queueing filter consists of $L-1$ subfilters with $c$ insertions, and one subfilter with $\frac c2$ insertions.
+As such, we can say that the queueing filter is a representation of the last $(c-\frac12) L$ last elements.
+
+Let us consider a duplicate $e^* \wdup E$.
+If, in the sliding window, all duplicates only happened at least $(c-\frac12)L$ epochs ago (which happens with probability $\left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}$), we know that no duplicates happened in any subfilter's sliding window.
+By using the same reasoning as the theorem's proof, we get a probability of false negative of around $\left[0 + \left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}(1-\FP_{\mathcal F,c})\right]^L$.
+Given that $cL \approx w$ which is a constant, we get that the probability of false positive mostly varies, in this case, with $\left(1-\FP_{\mathcal F,c}\right)^L$.
+
+Hence, the lower $L$ is, the higher the probability of false negative will be.
+
+The approximations made in this proof are backed by experimental results.
+\end{proof}
+
+\section{Application on Existing DDFs}
+As our queuing filter relies on another DDF subfilter, we must pick one existing DDF from the literature.
+However, testing all DDFs may be tedious.
+Instead, we propose a ranking on existing DDFs.
+As \cite{10.1145/3297280.3297335} mentioned, filters all reach a saturation state.
+The idea is then to order DDFs by their resistance to saturation --i.e., by ranking them by the time they take to reach saturation.
+
+Before ranking the DDFs by the error rate, we first introduce a lower bound on said rate.
+
+Note: given we are working on selecting the best subfilter for our queueing filter. As such, in this section we are \emph{not} working on a sliding window.
+
+\subsection{Optimal Error Probability on a DDF}
+    \begin{theorem}
+	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$.
+For any DDF of size $M$, the error probability $ER_n$ (consisting of the sum of the FP and FN probabilities) is such that
+	$$ER_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}$$ for any $n > M$.
+
+	Especially, for any filter of size $M$, the asymptotic error rate $ER_\infty$ is such that $ER_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M}$.
+\end{theorem}
+
+\begin{proof}
+	According to classical results on information theory, a perfect filter must use at least $1$ bit to remember one element from a random uniform source with no possible error.
+
+	Since the filter has $M$ bits of memory, we conclude that a perfect filter can store at most $M$ elements in memory.
+Assume that such a filter exists.
+Because the stream is random, we can assume without loss of generality that the filter stores the M last elements of the stream: any other strategy cannot yield a lower error rate, given the stream is random.
+
+	Let us derive the error rate of such a filter.
+	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
+On the other hand, if the element is not in memory, a perfect filter has no better option than answering randomly.
+Let $p$ be the probability that a filter answers \DUPLICATE when an element is not in memory.
+
+	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, the filter will return \UNSEEN with probability $1-p$.
+For this reason, this optimal filter has an FP probability of $p$.
+
+	On the other hand, a duplicate element $e^* \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
+Let $D$ be the event "\textsf{There is at least one duplicate in the stream} and $C$ be the event \textsf{There is a duplicate of $e^*$ in the $M$ previous elements of the stream}.
+
+	We have that $e^*$ triggers a false negative with probability
+
+	\begin{align*}
+	P_n &= (1 - P[C | D])(1-p) =  \left(1 - \frac{P[C \cap D]}{P[D]}\right)(1-p)\\
+	& = \left(1 - \frac{P[C]}{P[D]}\right)(1-p) =  \left(1 - \frac{1 - P[\bar C]}{1 - P[\bar D]}\right)(1-p) \\
+	P_n &=  \left(1 - \frac{1 - \left(1 - \frac 1U\right)^M}{1 - \left(1 - \frac 1U\right)^n}\right)(1-p)
+	\end{align*}
+
+	Hence, the error rate of the perfect filter is $ER_n = P_n + p =  \left(1 - \frac{1 - \left(1 - \frac{1}{U}\right)^{M}}{1 - \left(1 - \frac 1U\right)^n}\right)(1-p) + p =$ $ 1 - \frac{1-\left(1 - \frac{1}{U}\right)^{M}}{1 - \left(1 - \frac 1U\right)^n}(1-p)$, which is minimized when $p = 0$.
+
+	Given that, by definition, a perfect filter has the lowest error rate of any filter, we get the desired result.
+	\end{proof}
+
+Note, as highlighted in the proof, that this bound is not tight, and that better bounds may exist.
+Also note that this bound only applies when the stream is random: when patterns are found in the stream, information theory informs that data may be stored more efficiently.
+
+As such, the best filter will be the one the closest to this error rate.
+
+\subsection{DDF Comparison}
+A filter comparison was already made in \cite{10.1145/3297280.3297335}.
+Taking the same filters parameters, created another benchmark, studying the resistance of each DDF to saturation.
+We added the lower bound on the error rate.
+More details about the experiments are given in \ref{sub:saturation}.
+We observe in \ref{fig:graph_n} that the two most efficient filters are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
+
+However, as noted in \ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters.
+Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.
+
+\subsection{Parameter Tuning}
+The parameters of a queueing filter are: the parameters of the subfilter, the number $L$ of subfilters and the number $c$ of insertions per subfilter.
+
+However, the goal here is not to modify the parameters of the underlying subfilter, but rather to tune the queueing filter so the subfilter can perform as well as possible.
+Hence, the queueing filter's parameters are only $c$ and $L$.
+
+Furthermore, we have the relation $cL \approx w$, so there is only one free parameter.
+
+As such, an optimal parameter tuning would be to set $L$ so that the error rate (defined as the sum of the FPR and FNR) would be minimal.
+Nonetheless, given the complicated nature of the FPR and FNR formulae, deriving an optimal $L$ is out of reach.
+
+However, one can observe that a small $L$ is undesirable, as was exposed in \ref{sub:fnr}, because it would lead to a greater number of false negatives.
+
+\todo[observation experimentale ?]
 
 \section{Experiments and Benchmarks}
+In this section, we present the different experiments we made. The code is accessible online and will be disclosed after peer review.
 
+We first present a comparison of the resistance of various DDFs against saturation, without any sliding window. This comparison helps us to choose the best subfilter.
+
+Then, we design an experiment in which we compare the error rates of a QHT and a queuing filter, using the same QHT as a subfilter.
+
+\subsection{Saturation Resistance of DDFs}\label{sub:saturation}
+In this section, we compare the resistance of various filters to saturation. We take the same filters and parameters as \cite{10.1145/3297280.3297335}, namely:
+
+\begin{itemize}
+	\item QHT \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint.
+	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$
+	\item Cuckoo Filter \cite{Fan14}, cells containing 1 element of 3 bits each
+	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
+	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
+	\item Block-Decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of 6000 elements.
+\end{itemize}
+
+The stream was a stream of uniform random elements, taken from an alphabet of $2^{26}$ elements, and amounts for about 8\% duplicates on the 150 000 000 elements in the longest stream used.
+Results are plotted in \ref{fig:graph_n}.
+
+\begin{figure}
+	\input{er_n_artificial}
+	\caption{Error rate (times 100) of DDFs of 1Mb, depending on the size of the stream, without any sliding window. Hatched area represents over-optimal (impossible) values}.\label{fig:graph_n}
+\end{figure}
+
+\subsection{Comparison of QHT and QHT-Queueing Filter}
+In this section, we compare
+
+\section{Security}
 %% Acknowledgements 

### 2020-03-10 qhtv2.tex
wip

@@
 \paragraph{Duplicate detection problem.}
-We consider the following problem (duplicate detection problem, DDP): given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$.
+We consider the following problem (duplicate detection problem, DDP): given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$, using only $M$ bits of memory.
 It is understood that the stream $E_n$ is updated at every time increment.
-An \emph{efficient} solution to this problem provides an answer with bounded error $\epsilon$, \todo[A verifier using polynomially many resources (time and memory) in $1/\epsilon$].
+An \emph{efficient} solution to this problem provides an answer with bounded error.
 
@@
 \emph{Approximate} detection states that no attempt will be done to reach perfect accuracy, but rather to limit as much as possible the errors.
+As a matter of fact, in the context of approximate DDT, it is assumed that $M$ is to small for classical naïve solutions.
 One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory: even for modest situations (e.g.
@@
 \emph{probability of false negative}) of $\mathcal F$ after $i$ elements, denoted $\FP_i$ (resp.
-$\FN_i$), is defined as the proabability that $e_{i+1}$ is a false positive (resp.
+$\FN_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp.
 false negative).
@@
 \subsection{Filter Saturation and Sliding Windows}
-Unfortunately, duplicate detection over an infinite stream has been identified as an ill-posed problem.
+Unfortunately, efficient duplicate detection over an infinite stream has been identified as an unsolvable problem \cite{10.1145/3297280.3297335}.
 As a matter of fact, as the number of bits of information of the stream grow to infinity, the filter can only remember an ever diminishing proportion of those bits, eventually having no advantage compared to a filter answering randomly.
@@
 
+Our goal is to minimise both the false positive and false negative rates of a DDF, given a fixed and limited amount of memory.
+Before going into details, we first explore the limits of the problem, i.e., when perfect or very performant solutions exist.
+
+\begin{theorem}
+	For $M = w (\log_2(w) + 1) \log_2(|\Gamma|)$, the sliding window DDP can be solved with 0 errors in constant time.
+\end{theorem}
+
+\begin{proof}
+	To store $w$ elements from a sliding window, the naive idea is to use a queue $Q$ of $w$ elements.
+However, this yields a complexity of $O(w)$ for lookup, which might be impractical.
+Thus, we create a second structure for the sake of quickly answering lookup questions.
+
+	The dictionary $D$ has the form $\Gamma \Rightarrow \mathbb N$: keys are elements from the alphabet, values are integers serving as counters.
+
+	During insertion of $e$, $e$ is appended to the queue and $D[e]$ is incremented. If the key $e$ did not exist in $D$, it is created first.
+
+	The insertion of an element means that another element, at the end of the sliding window, is removed.
+For this, we pop the last element of $Q$, and get $e_{last} \gets Q.pop()$.
+Then, we decrement $D[e_{last}]$ and if $D[e_{last}] = 0$, the key is deleted from $D$.
+
+	Lookup of an element $e^\star$ is simply done by looking whether the key $D[e^\star]$ exists, which is done in constant time.
+
+	It is immediate to see that such a structure has a 0 error rate over the sliding window and that both insertion and lookup times are constant.
+
+	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w \log_2 |\Gamma| \log_2 w$ (as the dictionary cannot have more than $w$ keys as the same time, and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long), hence the claim.
+\end{proof}
+
+However, this implementation depends on $\log_2 |\Gamma|$, which might be arbitrarily large. We thus propose another solution, with a very low error rate but constant time.
+
 \begin{theorem}
@@
 
-When $|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naive strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w |\Gamma|$ bits of memory.}, both in terms of time and memory.
+When $\log_2|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory.
 
-Note that unlike the DDP, we do not necessarily encounter filter saturation for the sliding window DDP, which makes it possible for different DDF to have different performances in the asymptotic regime and thus to be ranked.
+Note that this solution has a time complexity of $O(w)$.
+Using a dictionary like in the previous proof, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, but requiring $5w\log_2 w$ bits of memory.
 
-Another remark is that when $M \approx w\log_2w$, the error rate is minimal but $O(w)$ operations ares required (although this complexity may be reduced using parallelized implementations).
-Detecting duplicates faster in this context remains an open question.
+Hence, very good solutions for situations where $M \approx 5w\log_2 w$ already exist, but efficient solutions and lower bounds on the error rates for smaller amounts of memory are still to be found.
 
@@
 \begin{proof}
-	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^* \notwdup E$.
+	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \notwdup E$.
 We first take into account the remark in \ref{subsub:number_elements} that the filter $\mathcal Q$ may contain more than $w$ elements, and hence potentially contain $e$ in memory, in the last subfilter of the queue.
 However, such event is quite rare, and can be neglected: let $\delta = cL - w$ the number of additional elements that can be stored in $\mathcal Q$.
-The probability that $e^*$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta \approx \frac{\delta}{|\Gamma|} \approx 0$ since $\delta$ is likely to be small, while $|\Gamma|$ is too big for being stored in memory.
+The probability that $e^\star$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta \approx \frac{\delta}{|\Gamma|} \approx 0$ since $\delta$ is likely to be small, while $|\Gamma|$ is too big for being stored in memory.
 
-	Hence, we can neglect the probability that $e^*$ is present in the filter.
-Therefore, $e^*$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^*)}$ returns \DUPLICATE.
-Conversely, $e^*$ is not a false positive if and only if all subqueries $\mathcal F_i.\mathsf{Lookup(e^*)}$ return \UNSEEN.
-This can be rewritten as $e^*$ is not a false positive if and only if $e^*$ is not a false positive for each subfilter.
+	Hence, we can neglect the probability that $e^\star$ is present in the filter.
+Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
+Conversely, $e^\star$ is not a false positive if and only if all subqueries $\mathcal F_i.\mathsf{Lookup(e^\star)}$ return \UNSEEN.
+This can be rewritten as $e^\star$ is not a false positive if and only if $e^\star$ is not a false positive for each subfilter.
 
@@
 \begin{proof}
-	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^* \wdup E$.
-	We first observe that if $cL > w$, there might be some duplicates of $e^*$ that happened before the current sliding window, but might still be remembered by the oldest filter.
+	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
+	We first observe that if $cL > w$, there might be some duplicates of $e^\star$ that happened before the current sliding window, but might still be remembered by the oldest filter.
 However, as argued in the previous section, the probability of such an event is negligible.
@@
 	Hence, we consider that the only duplicates are part of the sliding window.
-$e^*$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^*) = \UNSEEN$.
+$e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$.
 
@@
 	\begin{itemize}
-		\item $e^*$ is present in $\mathcal F_i$'s sub-sliding window 
-		\item $e^*$ is present in $\mathcal F_i$'s sub-sliding window
-
+		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window
+		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window
 	\end{itemize}
 
-In the first case, $\mathcal F_i.\mathsf{Detect}(e^*)$ returns \UNSEEN if and only if $e^*$ is a false negative for $\mathcal F_i$.
+In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
 Hence, in this case, the probability of $\mathcal F_i$ to return \UNSEEN is $\FN_{\mathcal F,c}$.
@@
 
-In the second case, $\mathcal F_i.\mathsf{Detect}(e^*)$ returns \UNSEEN if and only if $e^*$ is not a false positive for $\mathcal F_i$.
+In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$.
 Hence, in this case, the probability of $\mathcal F_i$ to return \UNSEEN is $1-\FP_{\mathcal F,c}$.
@@
 
-Now, the probability $p_c$ for $e^*$ to be in subfilter $\mathcal F_i$ (which has had $c$ insertions) sub-sliding window is
+Now, the probability $p_c$ for $e^\star$ to be in subfilter $\mathcal F_i$ (which has had $c$ insertions) sub-sliding window is
 
 \begin{align*}
-	p_c =& Pr[\text{$e^*$ is in }\mathcal F_i \text{ sub-sliding window | } e^* \wdup E]\\
-	=& \frac{Pr[\text{$e^*$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^* \wdup E]}{Pr[e^* \wdup E]}\\
-	=& \frac{Pr[\text{$e^*$ is in }\mathcal F_i \text{ sub-sliding window}]}{Pr[e^* \wdup E]}\\
-	=& \frac{1 - Pr[\text{$e^*$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - Pr[e^* \notwdup E]}\\
+	p_c =& Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
+	=& \frac{Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{Pr[e^\star \wdup E]}\\
+	=& \frac{Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{Pr[e^\star \wdup E]}\\
+	=& \frac{1 - Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - Pr[e^\star \notwdup E]}\\
 	p_c=& \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
@@
 
-Let us consider a duplicate $e^* \wdup E$.
+Let us consider a duplicate $e^\star \wdup E$.
 If, in the sliding window, all duplicates only happened at least $(c-\frac12)L$ epochs ago (which happens with probability $\left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}$), we know that no duplicates happened in any subfilter's sliding window.
@@
 As our queuing filter relies on another DDF subfilter, we must pick one existing DDF from the literature.
-However, testing all DDFs may be tedious.
+\subsection{DDF Subfilter Selection Strategy}
+As a matter of fact, it is preferable to use only one kind of DDF as subfilter, as proven by the following theorem.
+
+\begin{theorem}
+	An optimal queueing filter only uses one kind of subfilter.
+\end{theorem}
+
+\begin{proof}
+	One could imagine a queueing filter in which subfilters would alternate between, say, subfilter of type $A$ and of type $B$.
+However, we show with a simple symmetry argument that this kind of queueing filter is sub-optimal.
+
+	Let us consider a queueing filter relying on several kinds of subfilters.
+Given that all subfilters play the same role, and that their efficiency is independent of the other subfilters present, we know that one less efficient subfilter can be replaced by a more efficient one, directly improving the efficiency of the queueing filter.
+\end{proof}
+
+However, making a theoretical analysis of all DDFs error rates may be tedious.
 Instead, we propose a ranking on existing DDFs.
@@
 
-Note: given we are working on selecting the best subfilter for our queueing filter. As such, in this section we are \emph{not} working on a sliding window.
+Note: given we are working on selecting the best subfilter for our queueing filter, in this section we are \emph{not} working over a sliding window.
 
-\subsection{Optimal Error Probability on a DDF}
+\subsection{Optimal Error Probability on a DDF}\label{sub:optimal_ddf}
     \begin{theorem}
@@
 \end{theorem}
+We remind that in this section, we are working on DDP over the whole stream and not over a sliding window.
 
@@
 	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
-On the other hand, if the element is not in memory, a perfect filter has no better option than answering randomly.
+On the other hand, if the element is not in memory, a perfect filter can choose to answer randomly.
 Let $p$ be the probability that a filter answers \DUPLICATE when an element is not in memory.
+An optimal filter will lower the error rate of any filter using the same strategy with a different probability.
 
-	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, the filter will return \UNSEEN with probability $1-p$.
-For this reason, this optimal filter has an FP probability of $p$.
+	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
+For this reason, this filter has an FP probability of $p$.
 
-	On the other hand, a duplicate element $e^* \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
-Let $D$ be the event "\textsf{There is at least one duplicate in the stream} and $C$ be the event \textsf{There is a duplicate of $e^*$ in the $M$ previous elements of the stream}.
+	On the other hand, a duplicate element $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
+Let $D$ be the event "\textsf{There is at least one duplicate in the stream} and $C$ be the event \textsf{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}.
 
-	We have that $e^*$ triggers a false negative with probability
+	We have that $e^\star$ triggers a false negative with probability
 
 	\begin{align*}
-	P_n &= (1 - P[C | D])(1-p) =  \left(1 - \frac{P[C \cap D]}{P[D]}\right)(1-p)\\
+	\FN_n &= (1 - P[C | D])(1-p) =  \left(1 - \frac{P[C \cap D]}{P[D]}\right)(1-p)\\
 	& = \left(1 - \frac{P[C]}{P[D]}\right)(1-p) =  \left(1 - \frac{1 - P[\bar C]}{1 - P[\bar D]}\right)(1-p) \\
-	P_n &=  \left(1 - \frac{1 - \left(1 - \frac 1U\right)^M}{1 - \left(1 - \frac 1U\right)^n}\right)(1-p)
+	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
 	\end{align*}
 
-	Hence, the error rate of the perfect filter is $ER_n = P_n + p =  \left(1 - \frac{1 - \left(1 - \frac{1}{U}\right)^{M}}{1 - \left(1 - \frac 1U\right)^n}\right)(1-p) + p =$ $ 1 - \frac{1-\left(1 - \frac{1}{U}\right)^{M}}{1 - \left(1 - \frac 1U\right)^n}(1-p)$, which is minimized when $p = 0$.
+	Hence, the error probability of the filter is $ER_n = \FN_n + p =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p =$ $ 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p)$, which is minimized when $p = 0$.
 
@@
 
-However, one can observe that a small $L$ is undesirable, as was exposed in \ref{sub:fnr}, because it would lead to a greater number of false negatives.
+We have observed in \ref{sub:fnr} that the FN is positively correlated with
+$\left(1-\FP_{\mathcal F,c}\right)^L$, however the FP is negatively correlated with the same value.
+As such, decreasing the probability of false positive leads to an increase in the probability of false negatives.
 
-\todo[observation experimentale ?]
+However, practical tests show (see \ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.
+
+Hence, the (heuristic) optimal solution is to set $L = \sqrt w$.
 
@@
 
+\subsection{Benchmarking Various Queuing Filters}
+In this section, we experimentally prove the heuristic used in \ref{sub:optimal_ddf}, that the best DDF operating on a full stream leads to the best queueing filter operating on a sliding window.
+
+\todo
+
+\subsection{Benchmark of the influence of $L$ parameter}\label{sub:L_bench}
+
 \subsection{Comparison of QHT and QHT-Queueing Filter}
-In this section, we compare
+In this section, we compare the efficiency of QHT and QHT-queueing filter. For this, we use both an artificial dataset, as well as a real one, on various sliding window sizes.
 

### 2020-03-11 qhtv2.tex
related work

@@
 \todo[continuer]
-The idea of using subfilters, tossing old ones has already been explored in the A2 filter \cite{Yoo10}.
+In \cite{10.1145/1060745.1060753}, the authors explore the behaviour of a structure very close to the counting Bloom filter in some specific sliding window context, that they call landmark- and jumping sliding windows.
+However, they do not deal with the problematic of a sliding window where at each new element added to the sliding window, another element is removed.
+Closer to our work, the idea of using subfilters, tossing old ones has already been explored in the A2 filter \cite{Yoo10}.
 However, the author only considered a small portion of the problem, as they only discussed about using two subfilters, and only Bloom Filters acting as subfilters.
-In this work, we provide a full abstraction of the mechanism, allowing us to use many other DDF than Bloom Filters.
-We also provide a generalised analysis of the error rates.
+
+In this work, we provide a full abstraction of the mechanism, allowing us to use many other DDF than Bloom Filters. We also provide a generalised analysis of the error rates.
 \subsection{Organisation}
@@
 We included them for the sake of completeness.} \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+The structure proposed in \cite{10.1145/1060745.1060753} is not suited to either sliding window or no sliding window DDP, as they work on what they call `landmark` sliding window, which is a zero-resetting of the memory at some user-defined epochs.
 
-\todo[Regarder https://www2005.org/cdrom/docs/p12.pdf]
-
-Of these, only the A2 and b\_DBF was defined in the context of a sliding window.
+Of these, only the A2 and b\_DBF were designed for the sliding window DDP.
 The others do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
@@
 \subsection{Benchmark of the influence of $L$ parameter}\label{sub:L_bench}
-
+In this section, we make experiments on the influence of $L$ on the error rate of the queueing filter. 
 \subsection{Comparison of QHT and QHT-Queueing Filter}

### 2020-03-13 qhtv2.tex
wip

@@
 
-\subsection{Bounds on the Sliding Window DDP}
+\subsection{Bounds on the Sliding Window DDP}\label{sub:opt_solutions}
 
@@
 
-However, this implementation depends on $\log_2 |\Gamma|$, which might be arbitrarily large. We thus propose another solution, with a very low error rate but constant time.
+However, this implementation depends on $\log_2 |\Gamma|$, which might be arbitrarily large.
+We thus propose another solution, still in constant time but with a with a very low error rate, and not depending on $|\Gamma|$.
 
@@
 
-	More precisely, it is possible to create a filter of $M$ bits with an FNR of $0$, and an FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$.
+	More precisely, it is possible to create a filter of $M$ bits with an FNR of $0$, and an FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$, and a time complexity of $O(w)$.
+
+	If $M \simeq 5w\log_2 w$, then it is possible to upgrade this filter so its error rates remain the same but the complexity drops to constant time.
 \end{theorem}
@@
 Let $\mathcal F$ be the following DDF: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
-$\mathsf{Insert}(e)$ appends $h(e)$ to the queue before popping the list.
+$\mathsf{Insert}(e)$ appends $h(e)$ to the queue before popping the queue.
 
@@
 The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
+
+Note that this solution has a time complexity of $O(w)$.
+Using an additional dictionary like in the previous proof, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, but requiring $5w\log_2 w$ bits of memory.
 \end{proof}
@@
 When $\log_2|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory.
-
-Note that this solution has a time complexity of $O(w)$.
-Using a dictionary like in the previous proof, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, but requiring $5w\log_2 w$ bits of memory.
 
@@
 Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
-A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF)\footnote{QHTs stem from a correction of SQFs, and as such SQFs are less efficient than QHT in every situation \cite{10.1145/3297280.3297335}.
-We included them for the sake of completeness.} \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-The structure proposed in \cite{10.1145/1060745.1060753} is not suited to either sliding window or no sliding window DDP, as they work on what they call `landmark` sliding window, which is a zero-resetting of the memory at some user-defined epochs.
+A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+The structure proposed in \cite{10.1145/1060745.1060753} is not suited to either sliding window or no sliding window DDP, as they work on what they call `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
 
@@
 
-However, practical tests show (see \ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.
+\todo[FAUX, peut etre log ? However, practical tests show (see \ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
 
-Hence, the (heuristic) optimal solution is to set $L = \sqrt w$.
+%Hence, the (heuristic) optimal solution is to set $L = \sqrt w$.
 
@@
 
+We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in \ref{sub:opt_solutions}.
+However, since we must evaluate the number of duplicates in the streams we use, we cannot benchmark our filter in real-life situations, as doing so would require way too much memory for keeping track of the duplicates.
+
 \subsection{Saturation Resistance of DDFs}\label{sub:saturation}
-In this section, we compare the resistance of various filters to saturation. We take the same filters and parameters as \cite{10.1145/3297280.3297335}, namely:
+In this section, we compare the resistance of various filters to saturation.
+From the streaming filters we found in the literature, we only considered the filters not designed for operating on a sliding window, and parameters as \cite{10.1145/3297280.3297335}, namely:
 
@@
 	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
-	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
-	\item Block-Decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of 6000 elements.
+%	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
+%	\item Block-Decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of 6000 elements.
 \end{itemize}
@@
 	\input{er_n_artificial}
-	\caption{Error rate (times 100) of DDFs of 1Mb, depending on the size of the stream, without any sliding window. Hatched area represents over-optimal (impossible) values}.\label{fig:graph_n}
+	\caption{Error rate (times 100) of DDFs of 1Mb, depending on the size of the stream, without any sliding window. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
 \end{figure}
 
+We observe that the best filters are, in order, QHT, SQF, Cuckoo and SBF.
+We also observe that QHT and SQF have error rates relatively close to the lower bound, hence suggesting that these filters are close to optimality.
+
 \subsection{Benchmarking Various Queuing Filters}
-In this section, we experimentally prove the heuristic used in \ref{sub:optimal_ddf}, that the best DDF operating on a full stream leads to the best queueing filter operating on a sliding window.
+Now that DDF are compared on a full stream, we observe how each of them behave when they act as a subfilter in our queueing scheme.
+The goal is to empirically prove the assumption made in \ref{sub:optimal_ddf}, stating that the best (error-wise) DDF operating on a full stream leads to the best (error-wise) queueing filter operating on a sliding window.
+From \ref{fig:graph_n}, we observe that the best DDF for DDP on a full stream are, in order, QHT, SQF, Cuckoo, SQF.
+
+For this, we used four different queueing filters, with $L = 10$ subfilters each, and with the following subfilters: 
+\begin{itemize}
+	\item QHT subfilter \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint. 
+	\item Cuckoo Filter \cite{Fan14}, adapted for streaming as recommanded by \cite{10.1145/3297280.3297335}, cells containing 1 element of 3 bits each
+	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$
+	\item SBF \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
+\end{itemize}
+
+We used a random stream of $1,000,000$ elements uniformly selected from an alphabet of size $|\Gamma| = 2^{16}$, a memory size $M=100,000$ bits, a sliding window of size $w = 10,000$.
+The error rates (defined as the sum of $\FNR^w$ and $\FPR^w$) are displayed in \ref{tab:comparing_queueing}.
+We see that in all cases, the QHT subfilter performs better or almost as well than any other subfilter, hence validating the heuristic assumption.
+
+\begin{table}[]
+	\begin{tabular}{rccccc}
+			   & $w=1000$ & $w=5000$ & $w=10^4$ & $w=10^5$ & $w=10^6$ \\ \hline
+		QHT    & \textbf{9.84} 	  & \textbf{26.25}	 & \textbf{41.09}	 & \textbf{87.89}	  & 70.76      \\
+		Cuckoo & 84.99	  & 99.94	 & 99.95	 & 99.93	  & 99.80      \\
+		SQF    & 16.73 	  & 48.76	 & 69.25	 & 95.77 	  & \textbf{70.14}     \\
+		SBF    & 54.88 	  & 93.93	 & 97.33	 & 97.41	  & 71.17      \\
+	\end{tabular}
+	\caption{Error rate (times 100) of various queueing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{16}$.
+For each sliding window, the best performance is written in bold.}\label{tab:comparing_queueing}
+\end{table}
 

### 2020-03-16 qhtv2.tex
Amélioration intro

@@
 \begin{abstract}
-	A duplicate filter is a data structure designed to efficiently detect repetitions (duplicates) in a stream, when only a limited amount of memory is available.
-A well-known data structure used in this contexte is the Bloom filter, which has been generalised in several ways to
+	A duplicate detection filter is an online data structure designed to efficiently detect repetitions (duplicates) in a stream, when only a limited amount of memory is available.
+A well-known data structure used in this context is the Bloom filter, which has been generalised in several ways to
 	improve its performances or strike specific tradeoffs.
@@
 
-	In this paper we introduce a generic framework that adapts duplicate filters to the better-behaved context of a sliding window.
-We show that several duplicate filters can be adapted to this context and provide a rigourous mathematical study of such constructions.
+	In this paper we consider a \enquote{windowed} variation on the duplicate detection problem
+	that is better-behaved and thus lends itself to a more thorough 
+	mathematical analysis. We show how existing filters can be adjusted to work
+	in this new setting using a queuing construction. 
 \end{abstract}
@@
 
-\paragraph{Duplicate detection problem.}
-We consider the following problem (duplicate detection problem, DDP): given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$, using only $M$ bits of memory.
-It is understood that the stream $E_n$ is updated at every time increment.
-An \emph{efficient} solution to this problem provides an answer with bounded error.
-
+We begin with the following, ideal problem: 
+\begin{definition}[Duplicate detection problem, DDP] Given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$.\footnote{
+	We do not consider here \emph{fuzzy} detection approaches\cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient} that study situations where $e^\star$ belongs to $E_n$ when there exists a \enquote{similar enough} element in the stream.
+}
+	At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n \cup \{e^\star\}$. 
+\end{definition}
 Instances of this problem abound in computer science, with applications in file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
 A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.
-Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable.
 
-\paragraph{Fuzzy and approximate DPP}
-A popular approach for the DDP is \emph{fuzzy} detection \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}.
-Fuzzy detection deals with detecting \emph{fuzzy} duplicates (i.e., detecting if two elements are similar), which can be useful in several context, such as text processing.
-
-This is however out of the scope of our work, as we consider an element to be a duplicate if and only if the exact same element has already appeared in the stream.
-\emph{Approximate} detection states that no attempt will be done to reach perfect accuracy, but rather to limit as much as possible the errors.
-As a matter of fact, in the context of approximate DDT, it is assumed that $M$ is to small for classical naïve solutions.
+In practice, additional constraints exist that we can capture with the following definition:
+\begin{definition}[DDP with bounded memory]
+	At every time step $n$, given $e^{\star}$ and a current state (dependent on history) of at most $M$ bits, solve the DDP for $E_n$ and $e^{\star}$.
+\end{definition}
+%Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable. 
 One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory: even for modest situations (e.g.
 64-bit nonces, corresponding to $2^{64}$ possible values) this is quickly impractical.
-
+As a result, we need a further relaxation of the DDP that allows for errors:
+\begin{definition}[Approximate DDP with bounded memory]
+	Solve the DDP using at most $M$ bits of memory, with at most $\epsilon < 1/2$ mispredictions.\footnote{Given a classifier with $\epsilon > 1/2$, we obtain a classifier with $\epsilon < 1/2$ by reversing its output.}
+\end{definition}
 Approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
 Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.
+
+Finally, it is clear that the input distribution plays a central role regarding how efficiently the DDP can be solved.
+For instance, some deterministic streams may be expressed very compactly (such as the output of a PRNG with known seed) making the DDP relatively easy.
+Information-theoretically, if the source has $U$ bits of entropy then the situation is equivalent to having an $U$-bit, uniformly distributed input.\footnote{Another motivation for this is pragmatic: in many applications, duplicate detection is performed on \emph{hashes} of actual data rather than on the data itself, and we may assume that hashes are uniformly distributed.}
 

### 2020-03-16 qhtv2.tex
Amélioration Thm 2.11

@@
 \begin{theorem}
-	For $M = w (\log_2(w) + 1) \log_2(|\Gamma|)$, the sliding window DDP can be solved with 0 errors in constant time.
+	For $M \geq w (\log_2(w) + 1) \log_2(|\Gamma|)$, the sliding window DDP can be solved exactly (with no errors) in constant time.
 \end{theorem}
@@
 \begin{proof}
-	To store $w$ elements from a sliding window, the naive idea is to use a queue $Q$ of $w$ elements.
-However, this yields a complexity of $O(w)$ for lookup, which might be impractical.
-Thus, we create a second structure for the sake of quickly answering lookup questions.
+	We explicitly construct a DDF that performs the detection. Storing all $w$ elements in the sliding window takes $w\log_2(|\Gamma|)$ memory, using a FIFO queue $Q$; however 
+	lookup has a worst-time complexity of $O(w)$.
 
-	The dictionary $D$ has the form $\Gamma \Rightarrow \mathbb N$: keys are elements from the alphabet, values are integers serving as counters.
+	We therefore rely on an
+	ancillary data structure for the sake of quickly answering lookup questions.
+	Namely we use a dictionary $D$ whose keys are elements from $\Gamma$ and values are counters.
 
-	During insertion of $e$, $e$ is appended to the queue and $D[e]$ is incremented. If the key $e$ did not exist in $D$, it is created first.
-
-	The insertion of an element means that another element, at the end of the sliding window, is removed.
-For this, we pop the last element of $Q$, and get $e_{last} \gets Q.pop()$.
-Then, we decrement $D[e_{last}]$ and if $D[e_{last}] = 0$, the key is deleted from $D$.
+	Whe an element $e$ is inserted in the DDF, $e$ is stored and $D[e]$ is incremented (if the key $e$ did not exist in $D$, it is created first, and
+	$D[e]$ is set to $1$). In order to keep the number of stored elements to $w$, 
+	we discard the oldest element $e_\text{last}$ in $Q$.
+As we do so, we also decrement $D[e_\text{last}]$, and if $D[e_{last}] = 0$ the key is deleted from $D$.
+The whole insertion procedure is therefore performed in constant time.
 
@@
 
-	It is immediate to see that such a structure has a 0 error rate over the sliding window and that both insertion and lookup times are constant.
+	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w \log_2 |\Gamma| \log_2 w$ (as the dictionary cannot have more than $w$ keys as the same time, and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
+Thus at most $w (\log_2(w) + 1) \log_2(|\Gamma|)$ bits are necessary for this DDF to work.
 
-	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w \log_2 |\Gamma| \log_2 w$ (as the dictionary cannot have more than $w$ keys as the same time, and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long), hence the claim.
+	Finally this filter does not make any mistake, as every positive has a witness in $Q$ and any negative is absent from the last $w$ elements.
 \end{proof}

### 2020-03-16 fig/queuef.tex
Améliorations

--- 2020-03-13 qhtv2.tex
@@
-\input{preamble.tex}
-
-\begin{document}
-
-\title{Adapting Duplicate Filters to a Sliding Window Context}
-
-%% Replace by \iffalse when submitting anonymously 
-\iftrue 
-	\author{Rémi Géraud-Stewart}
-	\affiliation{%
-	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
-	\city{Paris} \state{France}
-	} \email{remi.geraud@ens.fr}
-
-	\author{Marius Lombard-Platet}
-	\affiliation{%
-	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
-	\city{Paris} \country{France}
-	}
-	\affiliation{%
-	\institution{Be-Studys}
-	\city{Geneva} \country{Switzerland}
-	} \email{marius.lombard-platet@ens.fr}
-
-	\author{David Naccache}
-	\affiliation{%
-	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
-	\city{Paris} \country{France}
-	} \email{david.naccache@ens.fr}
-\fi
-
-%% Abstract
-\begin{abstract}
-	A duplicate filter is a data structure designed to efficiently detect repetitions (duplicates) in a stream, when only a limited amount of memory is available.
-A well-known data structure used in this contexte is the Bloom filter, which has been generalised in several ways to
-	improve its performances or strike specific tradeoffs.
-
-	When analysed in the limit of an infinite stream, error rates of duplicate filters turn out to be heavily constrained; as a consequence they appear to provide no advantage, asymptotically, over a random yes-no coin toss \cite{10.1145/3297280.3297335}.
-
-	In this paper we introduce a generic framework that adapts duplicate filters to the better-behaved context of a sliding window.
-We show that several duplicate filters can be adapted to this context and provide a rigourous mathematical study of such constructions.
-\end{abstract}
-
-%% CCS XML
-\begin{CCSXML}
-	% Get code at http://dl.acm.org/ccs.cfm.
-	% Please copy and paste the code
-\end{CCSXML}
-
-%% Keywords
-\keywords{
-	% TODO
-}
-
-\maketitle
-
-\section{Introduction}
-\subsection{Motivation}
-
-\paragraph{Duplicate detection problem.}
-We consider the following problem (duplicate detection problem, DDP): given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$, using only $M$ bits of memory.
-It is understood that the stream $E_n$ is updated at every time increment.
-An \emph{efficient} solution to this problem provides an answer with bounded error.
-
-Instances of this problem abound in computer science, with applications in file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
-A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.
-Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable.
-
-\paragraph{Fuzzy and approximate DPP}
-A popular approach for the DDP is \emph{fuzzy} detection \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}.
-Fuzzy detection deals with detecting \emph{fuzzy} duplicates (i.e., detecting if two elements are similar), which can be useful in several context, such as text processing.
-
-This is however out of the scope of our work, as we consider an element to be a duplicate if and only if the exact same element has already appeared in the stream.
-\emph{Approximate} detection states that no attempt will be done to reach perfect accuracy, but rather to limit as much as possible the errors.
-As a matter of fact, in the context of approximate DDT, it is assumed that $M$ is to small for classical naïve solutions.
-One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory: even for modest situations (e.g.
-64-bit nonces, corresponding to $2^{64}$ possible values) this is quickly impractical.
-
-Approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
-Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.
-
-\todo[continuer].
-
-\subsection{Contributions}
-
-\subsection{Related Work}\label{sub:related}
-\todo[continuer]
-In \cite{10.1145/1060745.1060753}, the authors explore the behaviour of a structure very close to the counting Bloom filter in some specific sliding window context, that they call landmark- and jumping sliding windows.
-However, they do not deal with the problematic of a sliding window where at each new element added to the sliding window, another element is removed.
-Closer to our work, the idea of using subfilters, tossing old ones has already been explored in the A2 filter \cite{Yoo10}.
-However, the author only considered a small portion of the problem, as they only discussed about using two subfilters, and only Bloom Filters acting as subfilters.
-
-In this work, we provide a full abstraction of the mechanism, allowing us to use many other DDF than Bloom Filters. We also provide a generalised analysis of the error rates.
-\subsection{Organisation}
-
-\section{Duplicate Detection and Filter Saturation}
-\subsection{Notations and Initial Problem Statement}
-Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) set $E = \{e_1, e_2, \dotsc\}$, with each $e_i \in \Gamma$.
-
-\begin{definition}[Duplicate and unseen element]
-Let $E = \{e_1, e_2, \dotsc\}$ be a stream over $\Gamma$.
-Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$.
-In that case we write $e_j \dup E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notdup E$.
-\end{definition}
-
-\begin{definition}[Duplicate detection filter]
-	A \emph{duplicate detection filter} (DDF) is a collection 
-	$\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$ of a state\footnote{Here, $\mathcal M$ denotes all the memory states that can be reached by the filter.} $\mathcal S \in \mathcal M$ and two algorithms,
-	\begin{itemize}
-		\item $\mathsf{Detect}: \mathcal M \times \Gamma \to \{\DUPLICATE, \UNSEEN\}$;
-		\item $\mathsf{Insert}: \mathcal M \times \Gamma \to \mathcal M$.
-	\end{itemize}
-	Informally, the $\mathsf{Detect}$ algorithm tentatively labels an element $e$ as duplicate or not, given the current state $\mathcal S$; whereas $\mathsf{Insert}$ takes as input the current state, an element $e$ to insert in the filter, and returns an updated memory state $\mathcal S'$.
-\end{definition}
-
-We will usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathcal S| \ll |\Gamma|$.
-
-\begin{definition}[False positive, false negative]
-	Let $e \dup E$ (resp.
-$e \notdup E$) and $\mathcal F$ be a filter.
-We say that $e$ is a \emph{false positive} (resp.
-\emph{false negative}) when $\mathcal F.\mathsf{Detect}(e) = \DUPLICATE$ (resp.
-$\UNSEEN$).
-\end{definition}
-
-\begin{definition}[False positive rate, false negative rate]
-	Let $E$ be a stream, $\mathcal F$ be a filter.
-The \emph{false positive rate} (resp.
-\emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp.
-$\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $\{e_1, \dotsc, e_i\}\subset E$ (resp.
-the ratio of false negative divided by the number of duplicate elements in that subset).
-\end{definition}
-
-However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^\star$ is a false positive (resp. false negative).
-
-\begin{definition}[Probability of false positive, of false negative]
-	Let $E = \{e_1, \dotsc\}$ be a stream, $\mathcal F$ be a filter.
-The \emph{probability of false positive} (resp.
-\emph{probability of false negative}) of $\mathcal F$ after $i$ elements, denoted $\FP_i$ (resp.
-$\FN_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp.
-false negative).
-\end{definition}
-
-One can observe that $\FPR_n = \frac{1}{n}\sum_{i=1}^m \FP_i$, and similarly for $\FNR_n$.
-
-\subsection{Filter Saturation and Sliding Windows}
-Unfortunately, efficient duplicate detection over an infinite stream has been identified as an unsolvable problem \cite{10.1145/3297280.3297335}.
-As a matter of fact, as the number of bits of information of the stream grow to infinity, the filter can only remember an ever diminishing proportion of those bits, eventually having no advantage compared to a filter answering randomly.
-
-In other terms, any DDF is asymptotically as good as a random guess:
-	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
-	Let $\FNR_\infty$ and $\FPR_\infty$ be the asymptotic false negative and false positive rates of a filter of $M$ bits of memory (i.e. the FNR and FPR on a stream of size going to infinity).
-
-	If $|\Gamma| \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
-\end{theorem}
-
-One way out of this situation is to lower our expectations and work on a sliding window:
-
-\begin{definition}[Sliding window DDP]
-	Given a stream $E_n$ of fixed size $w$, with $E_n = \{e_{n-w+1}, \dotsc, e_n\}$ and an item $e^\star$, find whether $e^\star \in E_n$.
-\end{definition}
-
-We therefore introduce new definitions suited to that setting:
-
-\begin{definition}[Duplicate element, unseen element over a sliding window]
-	Let $E = \{e_1, e_2, \dotsc\}$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
-In this case we write $e_j \wdup E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notwdup E$.
-\end{definition}
-
-\begin{definition}[False positive, false negative over a sliding window]
-	Let $w \in \mathbb N$, $e \notwdup E$ (resp.
-$e \wdup E$) and let $\mathcal F$ be a DDF.
-We say that $e$ is a \emph{false positive} (resp.
-\emph{false negative}) over $w$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
-$\UNSEEN$).
-\end{definition}
-
-\begin{definition}[False positive rate, false negative rate over a sliding window]
-	Let $E$ be a stream, $\mathcal F$ be a DDF, $w \in \mathbb N$.
-The \emph{false positive} (resp.
-\emph{false negative}) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $w$, noted $\FPR^w_i$ (resp.
-$\FNR^w_i$), is defined as the number of false positives over $w$ divided by the number of unseen elements in $E$ over $w$ (resp.
-the number of false negative over $w$ divided by the number of duplicate elements over $w$).
-\end{definition}
-
-\subsection{Bounds on the Sliding Window DDP}\label{sub:opt_solutions}
-
-Our goal is to minimise both the false positive and false negative rates of a DDF, given a fixed and limited amount of memory.
-Before going into details, we first explore the limits of the problem, i.e., when perfect or very performant solutions exist.
-
-\begin{theorem}
-	For $M = w (\log_2(w) + 1) \log_2(|\Gamma|)$, the sliding window DDP can be solved with 0 errors in constant time.
-\end{theorem}
-
-\begin{proof}
-	To store $w$ elements from a sliding window, the naive idea is to use a queue $Q$ of $w$ elements.
-However, this yields a complexity of $O(w)$ for lookup, which might be impractical.
-Thus, we create a second structure for the sake of quickly answering lookup questions.
-
-	The dictionary $D$ has the form $\Gamma \Rightarrow \mathbb N$: keys are elements from the alphabet, values are integers serving as counters.
-
-	During insertion of $e$, $e$ is appended to the queue and $D[e]$ is incremented. If the key $e$ did not exist in $D$, it is created first.
-
-	The insertion of an element means that another element, at the end of the sliding window, is removed.
-For this, we pop the last element of $Q$, and get $e_{last} \gets Q.pop()$.
-Then, we decrement $D[e_{last}]$ and if $D[e_{last}] = 0$, the key is deleted from $D$.
-
-	Lookup of an element $e^\star$ is simply done by looking whether the key $D[e^\star]$ exists, which is done in constant time.
-
-	It is immediate to see that such a structure has a 0 error rate over the sliding window and that both insertion and lookup times are constant.
-
-	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w \log_2 |\Gamma| \log_2 w$ (as the dictionary cannot have more than $w$ keys as the same time, and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long), hence the claim.
-\end{proof}
-
-However, this implementation depends on $\log_2 |\Gamma|$, which might be arbitrarily large.
-We thus propose another solution, still in constant time but with a with a very low error rate, and not depending on $|\Gamma|$.
-
-\begin{theorem}
-	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.
-
-	More precisely, it is possible to create a filter of $M$ bits with an FNR of $0$, and an FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$, and a time complexity of $O(w)$.
-
-	If $M \simeq 5w\log_2 w$, then it is possible to upgrade this filter so its error rates remain the same but the complexity drops to constant time.
-\end{theorem}
-
-\begin{proof}
-	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
-The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
-Therefore $2^{(2 \log_2 w) / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
-$h(e_i) = h(e_j)$).
-The 50\% threshold we impose on $h$ is arbitrary but nonetheless practical.
-
-Let $\mathcal F$ be the following DDF: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
-$\mathsf{Insert}(e)$ appends $h(e)$ to the queue before popping the queue.
-
-There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FNR of $0$ and a FPR of $1 - (1-\frac1{w^2})^w$.
-The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
-
-Note that this solution has a time complexity of $O(w)$.
-Using an additional dictionary like in the previous proof, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, but requiring $5w\log_2 w$ bits of memory.
-\end{proof}
-
-When $\log_2|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory.
-
-Hence, very good solutions for situations where $M \approx 5w\log_2 w$ already exist, but efficient solutions and lower bounds on the error rates for smaller amounts of memory are still to be found.
-
-\subsection{DDP vs Sliding Window DDP}
-The sliding window variant of DDP may seem to be a slight weakening of the original problem.
-Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
-A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-The structure proposed in \cite{10.1145/1060745.1060753} is not suited to either sliding window or no sliding window DDP, as they work on what they call `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
-
-Of these, only the A2 and b\_DBF were designed for the sliding window DDP.
-The others do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
-Another remarkable (but experimental) observation is that these DDFs' false positive rate does not decrease to 0 when the sliding window becomes small.
-
-\todo[Expliquer ?]
-
-\section{Queuing Filters for Sliding Window Adaptation}
-In this section, we describe how to turn DDF into sliding window DDFs. We first give the description of the setup, before studying the theoretical error rates.
-
-\subsection{Queueing Filter}
-Let $\mathcal F$ be a DDF, not designed to work on a sliding window.
-Our idea, instead of spawning a filter $\mathcal F$ using as much memory as possible, is to create $L$ small versions of $\mathcal F$, which all have a limited timespan and can insert up to $c$ elements in their structure.
-We call these small filters subfilters.
-The subfilters are organised in a queue.
-
-When inserting a new element in the queueing filter, it is inserted in the topmost subfilter of the queue.
-After $c$ insertions, a new empty filter is added to the queue, and the oldest subfilter is popped and erased.
-
-As such, we can consider that each subfilter operates on a sub-sliding window of size $c$.
-Given that we have $L$ subfilters and we want to operate on a sliding window of size $w$, we require $cL \approx w$.
-
-A scheme describing our structure is detailed in \ref{fig:scheme}.
-
-\begin{figure}
 \begin{tikzpicture}[scale=0.4]
@@
 	\end{tikzpicture}
-	\caption{Architecture of the queuing filter.
-The filter is composed of $L$ subfilters $\mathcal F$, each containing up to $c$ elements.
-Once the newest subfilter has inserted $c$ elements in its structure, the oldest one is expired.
-As such, it is dropped and a new one is created and put under population at the beginning of the queue.
-In this example, the sub-sliding window of $\mathcal F_1$ is $\{e_{m-2}, e_{m-3}, e_{m-4}\}$.} \label{fig:scheme}
-\end{figure}
-
-When the user wants to lookup for an element, they query all subfilters.
-If any subfilter answers with \DUPLICATE, the queueing filter answers \DUPLICATE.
-Otherwise, it answers \UNSEEN.
-Insertion is a simple insertion in the topmost subfilter.
-
-After $c$ insertions (where $c$ is a filter parameter), the last filter of the queue is removed, and a new (empty) filter is appended in front of the queue.
-We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in \ref{alg:queueing}.
-
-For the sake of simplicity in the pseudocode, we assume that the subfilter $\mathcal F$ has a function \textsf{Setup} which takes as input the available memory $m$, and returns an initialized empty filter $\mathcal F$ of size at most $m$..
-
-\begin{algorithm}[]
-	\caption{Queueing Filter Setup, Lookup and Insert}\label{alg:queueing}
-
-	\begin{algorithmic}[1]
-	\Function{Setup}{$\mathcal F, M, L, c$}
-		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
-		\State Queue\_storage $\gets$ empty queue
-		\State Counter $\gets 0$
-		\For{$i$ from $0$ to $L-1$}
-			\State Queue\_storage[i] $\gets$ $\mathcal F.\mathsf{Setup}(\lfloor M/L \rfloor)$
-		\EndFor
-		Counter $\gets$ 0
-		\State Store $c$, $M$, $L$, $\mathcal F$
-
-		\State \Return filter
-	\EndFunction 
-	\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\Function{Lookup}{$e$}
-		\For{$i$ from $0$ to $L-1$}
-			\If{$\mathcal F_i.\mathsf{Lookup(e)}$}
-				\State \Return $\DUPLICATE$
-			\EndIf
-		\EndFor
-		\State \Return \UNSEEN
-	\EndFunction
-	\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\Function{Insert}{$e$}
-		\State $\mathcal F_0.\mathsf{Insert}(e)$
-		\State Counter++
-		\If{Counter == $c$}
-			\State Pop last element of Queue\_Storage
-			\State Insert $\mathcal F$.\textsf{Setup}($\lfloor M/L \rfloor$) at the beginning of Queue\_Storage
-		\EndIf
-	\EndFunction
-	\end{algorithmic}
-\end{algorithm}
-
-\subsection{Error Rate Analysis}
-Depending on the underlying subfilter, the queueing filter will behave differently.
-However, its false positive and false negative probabilities can be derived from the underlying subfilter's false positive and false negative probabilities.
-
-\subsubsection{Number of Elements in a Queueing Filter}\label{subsub:number_elements}
-Before deriving the error rates, it is important to analyse how many elements are in the filter.
-We know, by design, that no more than $cL$ elements can be present.
-However, after exactly $cL$ insertions, the last subfilter is deleted, to be replaced by an empty one at the beginning of the queue.
-Hence, after $cL$ insertions, only $c(L-1)$ elements are stored in the queueing filter.
-
-Hence, the number of elements in the filter oscillate between $c(L-1)$ and $cL$.
-Furthermore, we have $cL \approx w$, which means that the number of elements in the filter can be higher than $w$.
-These facts must be kept in mind while deriving the error rates.
-
-\subsubsection{Probability of False Positive}
-\begin{theorem}
-	Let $\mathcal Q$ be a queueing filter, consisting of $L$ underlying subfilters $\mathcal F$, each filled with up to $c$ elements.
-Let $\FP_{\mathcal F,m}$ be the probability of false positive of the subfilter $\mathcal F$ after $m$ insertions, let $\FP_{\mathcal Q, m}^w$ be the probability of false positive of $\mathcal Q$ after $m$ insertions on a sliding window of size $w$.
-
-	We have $$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F,c})^{L-1}(1 - \FP_{\mathcal F, m \% c })$$ where \% is the modulo operator.
-\end{theorem}
-
-\begin{proof}
-	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \notwdup E$.
-We first take into account the remark in \ref{subsub:number_elements} that the filter $\mathcal Q$ may contain more than $w$ elements, and hence potentially contain $e$ in memory, in the last subfilter of the queue.
-However, such event is quite rare, and can be neglected: let $\delta = cL - w$ the number of additional elements that can be stored in $\mathcal Q$.
-The probability that $e^\star$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta \approx \frac{\delta}{|\Gamma|} \approx 0$ since $\delta$ is likely to be small, while $|\Gamma|$ is too big for being stored in memory.
-
-	Hence, we can neglect the probability that $e^\star$ is present in the filter.
-Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
-Conversely, $e^\star$ is not a false positive if and only if all subqueries $\mathcal F_i.\mathsf{Lookup(e^\star)}$ return \UNSEEN.
-This can be rewritten as $e^\star$ is not a false positive if and only if $e^\star$ is not a false positive for each subfilter.
-
-	Given that each subfilter stores $c$ elements, safe for the first subfilter which only stores $m \% c$ elements, we get
-	$$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F, m \% c })(1 - \FP_{\mathcal F,c})^{L-1}$$
-\end{proof}
-
-\subsubsection{Probability of False Negative}\label{sub:fnr}
-\begin{theorem}
-	Let $\mathcal Q$ be a queueing filter, consisting of $L$ underlying subfilters $\mathcal F$, each filled with up to $c$ elements.
-Let $\FN_{\mathcal F,m}$ be the probability of false negative of the subfilter $\mathcal F$ after $m$ insertions, let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m$ insertions on a sliding window of size $w$.
-
-	For $p_m = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^m}{1-\left(1-\frac 1{|\Gamma|}\right)^w}$, we have 
-	\begin{align*}
-	\FN_{\mathcal Q, m}^w =& \left[p_c\FN_{\mathcal F,c} + \left(1-p_c\right)\left(1-\FP_{\mathcal F,c}\right)\right]^{L-1}
-	\\&\qquad
-	 \cdot \left[p_{m\%c}\FN_{\mathcal F,m\%c} + \left(1-p_{m\%c}\right)\left(1-\FP_{\mathcal F,m\%c}\right)\right]
-	\end{align*}
-
-	where $\%$ is the modulo operator.
-\end{theorem}
-
-\begin{proof}
-	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
-	We first observe that if $cL > w$, there might be some duplicates of $e^\star$ that happened before the current sliding window, but might still be remembered by the oldest filter.
-However, as argued in the previous section, the probability of such an event is negligible.
-
-	Hence, we consider that the only duplicates are part of the sliding window.
-$e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$.
-
-	There can be two cases:
-	\begin{itemize}
-		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window
-		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window
-	\end{itemize}
-
-In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
-Hence, in this case, the probability of $\mathcal F_i$ to return \UNSEEN is $\FN_{\mathcal F,c}$.
-For the subfilter $\mathcal F_0$, however, the probability is $\FN_{\mathcal F, m\%c}$.
-
-In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$.
-Hence, in this case, the probability of $\mathcal F_i$ to return \UNSEEN is $1-\FP_{\mathcal F,c}$.
-For the subfilter $\mathcal F_0$, however, the probability is $1-\FP_{\mathcal F, m\%c}$.
-
-Now, the probability $p_c$ for $e^\star$ to be in subfilter $\mathcal F_i$ (which has had $c$ insertions) sub-sliding window is
-
-\begin{align*}
-	p_c =& Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
-	=& \frac{Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{Pr[e^\star \wdup E]}\\
-	=& \frac{Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{Pr[e^\star \wdup E]}\\
-	=& \frac{1 - Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - Pr[e^\star \notwdup E]}\\
-	p_c=& \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
-\end{align*}
-
-Finally, we get that the probability of a false positive for $\mathcal Q$ over the sliding window $w$ is 
-\begin{align*}
-\FN^w_{\mathcal Q, m} =& \left[p_c\FN_{\mathcal F,c} + (1-p_c)(1-\FP_{\mathcal F,c})\right]^{L-1}
-\\&\quad
-\cdot \left[p_{m\%c}\FN_{\mathcal F,m\%c} + (1-p_{m\%c})(1-\FP_{\mathcal F,m\%c})\right]\\
-\end{align*}
-\end{proof}
-
-This probability is quite complicated and does not allow, in the general case, for an in-depth analysis of the probability of false negative.
-
-\begin{theorem}
-	In first approximation, a low value of $L$ leads to a higher false negative probability for the queueing filter.
-\end{theorem}
-
-\begin{proof}
-As a matter of fact, on average the queueing filter consists of $L-1$ subfilters with $c$ insertions, and one subfilter with $\frac c2$ insertions.
-As such, we can say that the queueing filter is a representation of the last $(c-\frac12) L$ last elements.
-
-Let us consider a duplicate $e^\star \wdup E$.
-If, in the sliding window, all duplicates only happened at least $(c-\frac12)L$ epochs ago (which happens with probability $\left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}$), we know that no duplicates happened in any subfilter's sliding window.
-By using the same reasoning as the theorem's proof, we get a probability of false negative of around $\left[0 + \left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}(1-\FP_{\mathcal F,c})\right]^L$.
-Given that $cL \approx w$ which is a constant, we get that the probability of false positive mostly varies, in this case, with $\left(1-\FP_{\mathcal F,c}\right)^L$.
-
-Hence, the lower $L$ is, the higher the probability of false negative will be.
-
-The approximations made in this proof are backed by experimental results.
-\end{proof}
-
-\section{Application on Existing DDFs}
-As our queuing filter relies on another DDF subfilter, we must pick one existing DDF from the literature.
-\subsection{DDF Subfilter Selection Strategy}
-As a matter of fact, it is preferable to use only one kind of DDF as subfilter, as proven by the following theorem.
-
-\begin{theorem}
-	An optimal queueing filter only uses one kind of subfilter.
-\end{theorem}
-
-\begin{proof}
-	One could imagine a queueing filter in which subfilters would alternate between, say, subfilter of type $A$ and of type $B$.
-However, we show with a simple symmetry argument that this kind of queueing filter is sub-optimal.
-
-	Let us consider a queueing filter relying on several kinds of subfilters.
-Given that all subfilters play the same role, and that their efficiency is independent of the other subfilters present, we know that one less efficient subfilter can be replaced by a more efficient one, directly improving the efficiency of the queueing filter.
-\end{proof}
-
-However, making a theoretical analysis of all DDFs error rates may be tedious.
-Instead, we propose a ranking on existing DDFs.
-As \cite{10.1145/3297280.3297335} mentioned, filters all reach a saturation state.
-The idea is then to order DDFs by their resistance to saturation --i.e., by ranking them by the time they take to reach saturation.
-
-Before ranking the DDFs by the error rate, we first introduce a lower bound on said rate.
-
-Note: given we are working on selecting the best subfilter for our queueing filter, in this section we are \emph{not} working over a sliding window.
-
-\subsection{Optimal Error Probability on a DDF}\label{sub:optimal_ddf}
-    \begin{theorem}
-	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$.
-For any DDF of size $M$, the error probability $ER_n$ (consisting of the sum of the FP and FN probabilities) is such that
-	$$ER_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}$$ for any $n > M$.
-
-	Especially, for any filter of size $M$, the asymptotic error rate $ER_\infty$ is such that $ER_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M}$.
-\end{theorem}
-We remind that in this section, we are working on DDP over the whole stream and not over a sliding window.
-
-\begin{proof}
-	According to classical results on information theory, a perfect filter must use at least $1$ bit to remember one element from a random uniform source with no possible error.
-
-	Since the filter has $M$ bits of memory, we conclude that a perfect filter can store at most $M$ elements in memory.
-Assume that such a filter exists.
-Because the stream is random, we can assume without loss of generality that the filter stores the M last elements of the stream: any other strategy cannot yield a lower error rate, given the stream is random.
-
-	Let us derive the error rate of such a filter.
-	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
-On the other hand, if the element is not in memory, a perfect filter can choose to answer randomly.
-Let $p$ be the probability that a filter answers \DUPLICATE when an element is not in memory.
-An optimal filter will lower the error rate of any filter using the same strategy with a different probability.
-
-	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
-For this reason, this filter has an FP probability of $p$.
-
-	On the other hand, a duplicate element $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
-Let $D$ be the event "\textsf{There is at least one duplicate in the stream} and $C$ be the event \textsf{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}.
-
-	We have that $e^\star$ triggers a false negative with probability
-
-	\begin{align*}
-	\FN_n &= (1 - P[C | D])(1-p) =  \left(1 - \frac{P[C \cap D]}{P[D]}\right)(1-p)\\
-	& = \left(1 - \frac{P[C]}{P[D]}\right)(1-p) =  \left(1 - \frac{1 - P[\bar C]}{1 - P[\bar D]}\right)(1-p) \\
-	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
-	\end{align*}
-
-	Hence, the error probability of the filter is $ER_n = \FN_n + p =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p =$ $ 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p)$, which is minimized when $p = 0$.
-
-	Given that, by definition, a perfect filter has the lowest error rate of any filter, we get the desired result.
-	\end{proof}
-
-Note, as highlighted in the proof, that this bound is not tight, and that better bounds may exist.
-Also note that this bound only applies when the stream is random: when patterns are found in the stream, information theory informs that data may be stored more efficiently.
-
-As such, the best filter will be the one the closest to this error rate.
-
-\subsection{DDF Comparison}
-A filter comparison was already made in \cite{10.1145/3297280.3297335}.
-Taking the same filters parameters, created another benchmark, studying the resistance of each DDF to saturation.
-We added the lower bound on the error rate.
-More details about the experiments are given in \ref{sub:saturation}.
-We observe in \ref{fig:graph_n} that the two most efficient filters are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
-
-However, as noted in \ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters.
-Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.
-
-\subsection{Parameter Tuning}
-The parameters of a queueing filter are: the parameters of the subfilter, the number $L$ of subfilters and the number $c$ of insertions per subfilter.
-
-However, the goal here is not to modify the parameters of the underlying subfilter, but rather to tune the queueing filter so the subfilter can perform as well as possible.
-Hence, the queueing filter's parameters are only $c$ and $L$.
-
-Furthermore, we have the relation $cL \approx w$, so there is only one free parameter.
-
-As such, an optimal parameter tuning would be to set $L$ so that the error rate (defined as the sum of the FPR and FNR) would be minimal.
-Nonetheless, given the complicated nature of the FPR and FNR formulae, deriving an optimal $L$ is out of reach.
-
-We have observed in \ref{sub:fnr} that the FN is positively correlated with
-$\left(1-\FP_{\mathcal F,c}\right)^L$, however the FP is negatively correlated with the same value.
-As such, decreasing the probability of false positive leads to an increase in the probability of false negatives.
-
-\todo[FAUX, peut etre log ? However, practical tests show (see \ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
-
-%Hence, the (heuristic) optimal solution is to set $L = \sqrt w$.
-
-\section{Experiments and Benchmarks}
-In this section, we present the different experiments we made. The code is accessible online and will be disclosed after peer review.
-
-We first present a comparison of the resistance of various DDFs against saturation, without any sliding window. This comparison helps us to choose the best subfilter.
-
-Then, we design an experiment in which we compare the error rates of a QHT and a queuing filter, using the same QHT as a subfilter.
-
-We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in \ref{sub:opt_solutions}.
-However, since we must evaluate the number of duplicates in the streams we use, we cannot benchmark our filter in real-life situations, as doing so would require way too much memory for keeping track of the duplicates.
-
-\subsection{Saturation Resistance of DDFs}\label{sub:saturation}
-In this section, we compare the resistance of various filters to saturation.
-From the streaming filters we found in the literature, we only considered the filters not designed for operating on a sliding window, and parameters as \cite{10.1145/3297280.3297335}, namely:
-
-\begin{itemize}
-	\item QHT \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint.
-	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$
-	\item Cuckoo Filter \cite{Fan14}, cells containing 1 element of 3 bits each
-	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
-%	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
-%	\item Block-Decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of 6000 elements.
-\end{itemize}
-
-The stream was a stream of uniform random elements, taken from an alphabet of $2^{26}$ elements, and amounts for about 8\% duplicates on the 150 000 000 elements in the longest stream used.
-Results are plotted in \ref{fig:graph_n}.
-
-\begin{figure}
-	\input{er_n_artificial}
-	\caption{Error rate (times 100) of DDFs of 1Mb, depending on the size of the stream, without any sliding window. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
-\end{figure}
-
-We observe that the best filters are, in order, QHT, SQF, Cuckoo and SBF.
-We also observe that QHT and SQF have error rates relatively close to the lower bound, hence suggesting that these filters are close to optimality.
-
-\subsection{Benchmarking Various Queuing Filters}
-Now that DDF are compared on a full stream, we observe how each of them behave when they act as a subfilter in our queueing scheme.
-The goal is to empirically prove the assumption made in \ref{sub:optimal_ddf}, stating that the best (error-wise) DDF operating on a full stream leads to the best (error-wise) queueing filter operating on a sliding window.
-From \ref{fig:graph_n}, we observe that the best DDF for DDP on a full stream are, in order, QHT, SQF, Cuckoo, SQF.
-
-For this, we used four different queueing filters, with $L = 10$ subfilters each, and with the following subfilters: 
-\begin{itemize}
-	\item QHT subfilter \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint. 
-	\item Cuckoo Filter \cite{Fan14}, adapted for streaming as recommanded by \cite{10.1145/3297280.3297335}, cells containing 1 element of 3 bits each
-	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$
-	\item SBF \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
-\end{itemize}
-
-We used a random stream of $1,000,000$ elements uniformly selected from an alphabet of size $|\Gamma| = 2^{16}$, a memory size $M=100,000$ bits, a sliding window of size $w = 10,000$.
-The error rates (defined as the sum of $\FNR^w$ and $\FPR^w$) are displayed in \ref{tab:comparing_queueing}.
-We see that in all cases, the QHT subfilter performs better or almost as well than any other subfilter, hence validating the heuristic assumption.
-
-\begin{table}[]
-	\begin{tabular}{rccccc}
-			   & $w=1000$ & $w=5000$ & $w=10^4$ & $w=10^5$ & $w=10^6$ \\ \hline
-		QHT    & \textbf{9.84} 	  & \textbf{26.25}	 & \textbf{41.09}	 & \textbf{87.89}	  & 70.76      \\
-		Cuckoo & 84.99	  & 99.94	 & 99.95	 & 99.93	  & 99.80      \\
-		SQF    & 16.73 	  & 48.76	 & 69.25	 & 95.77 	  & \textbf{70.14}     \\
-		SBF    & 54.88 	  & 93.93	 & 97.33	 & 97.41	  & 71.17      \\
-	\end{tabular}
-	\caption{Error rate (times 100) of various queueing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{16}$.
-For each sliding window, the best performance is written in bold.}\label{tab:comparing_queueing}
-\end{table}
-
-\todo
-
-\subsection{Benchmark of the influence of $L$ parameter}\label{sub:L_bench}
-In this section, we make experiments on the influence of $L$ on the error rate of the queueing filter. 
-\subsection{Comparison of QHT and QHT-Queueing Filter}
-In this section, we compare the efficiency of QHT and QHT-queueing filter. For this, we use both an artificial dataset, as well as a real one, on various sliding window sizes.
-
-\section{Security}
-%% Acknowledgements 
-%\begin{acks} \end{acks}
-
-%% Bibliography
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{qhtv2}
-
-%% Appendix
-%\appendix
-
-\end{document}

### 2020-03-16 qhtv2.tex
Améliorations

@@
 \end{proof}
-
-However, this implementation depends on $\log_2 |\Gamma|$, which might be arbitrarily large.
-We thus propose another solution, still in constant time but with a with a very low error rate, and not depending on $|\Gamma|$.
-
+The dependence on $\log_2 |\Gamma|$ can be droped, at the cost of allowing 
+errors:
 \begin{theorem}
@@
 
-	If $M \simeq 5w\log_2 w$, then it is possible to upgrade this filter so its error rates remain the same but the complexity drops to constant time.
+	Using $M \simeq 5w\log_2 w$ bits of memory, a constant-time filter with the same error rate can be constructed.
 \end{theorem}
@@
 \begin{proof}
+	Here again we explicitely construct the filters that achieve the theorem's bounds.
+
 	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
@@
 Note that this solution has a time complexity of $O(w)$.
-Using an additional dictionary like in the previous proof, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, but requiring $5w\log_2 w$ bits of memory.
+Using an additional dictionary, as in the previous proof, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, using $5w\log_2 w$ bits of memory.
 \end{proof}
@@
 
-Of these, only the A2 and b\_DBF were designed for the sliding window DDP.
+Of these, only the A2 and b\_DBF were designed in a way immediately applicable to the sliding window DDP.
 The others do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
@@
 
-\section{Queuing Filters for Sliding Window Adaptation}
-In this section, we describe how to turn DDF into sliding window DDFs. We first give the description of the setup, before studying the theoretical error rates.
+\section{Queuing filters}
+In this section, we describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
+A scheme describing our structure is detailed in \ref{fig:scheme}.
 
-\subsection{Queueing Filter}
-Let $\mathcal F$ be a DDF, not designed to work on a sliding window.
-Our idea, instead of spawning a filter $\mathcal F$ using as much memory as possible, is to create $L$ small versions of $\mathcal F$, which all have a limited timespan and can insert up to $c$ elements in their structure.
-We call these small filters subfilters.
+\subsection{The queueing construction}
+
+\paragraph{Principle of operation.}
+Let $\mathcal F$ be a DDF.
+Rather than allocating the whole memory to $\mathcal F$, we will create $L$ copies of $\mathcal F$, each using a fraction of the available memory.
+Each of these \emph{subfilters} as a limited timespan, and is allowed up to $c$ insertions.
 The subfilters are organised in a queue.
@@
 
-As such, we can consider that each subfilter operates on a sub-sliding window of size $c$.
-Given that we have $L$ subfilters and we want to operate on a sliding window of size $w$, we require $cL \approx w$.
-
-A scheme describing our structure is detailed in \ref{fig:scheme}.
+As such, we can consider that each subfilter operates on a sub-sliding window of size $c$, which makes the overall construction a DDF operating over a sliding window of size $w = cL$.
 
 \begin{figure}
-	\begin{tikzpicture}[scale=0.4]
-
-	% F_0 under construction
-	\draw[pattern=north west lines, pattern color=gray, draw=none] (1, 0) rectangle (2, 1);
-	\draw (0, 0) rectangle (2, 1) node[midway] {$\mathcal F_0$};
-
-	% Other subfilters
-	\draw[pattern=north west lines, pattern color=gray] (3, 0) rectangle (5, 1) node[midway] {$\mathcal F_1$};
-	\draw[pattern=north west lines, pattern color=gray] (6, 0) rectangle (8, 1) node[midway] {$\mathcal F_2$};
-	\node at (9.5, 0.5) {...};
-	\draw[pattern=north west lines, pattern color=gray] (11, 0) rectangle (13, 1) node[midway] {$\mathcal F_{L-1}$};
-
-	% old subfilters
-	\draw[dashed] (14, 0) rectangle (16, 1) node[midway] {$\mathcal F_{L}$};
-	\draw[dashed] (17, 0) rectangle (19, 1) node[midway] {$\mathcal F_{L+1}$};
-
-	% arrows
-	\draw [<->,>=latex] (6, 1.5) -- (8, 1.5) node[above, midway] {$c$ elements};
-	\draw [<->,>=latex] (0, -3) -- (13, -3) node[below, midway] {Capacity of $Lc \approx w$ elements};
-	\draw [<->,>=latex] (1, 3) -- (15, 3) node[above, midway] {Current sliding window (of size $w$)};
-
-	%stream 
-	\draw [<-, >=latex] (0, 5.5) -- (19, 5.5) node[above, midway] {Stream};
-	\foreach \x in {1, 3,...,18}
-	\draw (\x, 5.7) -- node[pos=0.5] (point\x) {} (\x, 5.3);
-
-	\foreach \x in {2, 4,...,18}
-	\draw (\x, 5.6) -- node[pos=0.5] (point\x) {} (\x, 5.4);
-
-	\path (point1) node [below] {$e_m$};
-	\foreach \x [evaluate=\x as \i using int(\x-1)] in {3, 5,..., 9}
-	\path (point\x) node [below] {$e_{m-\i}$};
-	\path (point11) node [below] {$\dots$};
-	\path (point15) node [below] {$e_{m - w + 1}$};
-
-	%queueing filter
-	\draw (-0.5, 2.5) rectangle (13.5, -2.5) node[anchor=south east] {Queuing filter};
-
-	% legend
-	\draw[draw=none, pattern=north west lines, pattern color=gray] (0.5, -5) rectangle (1, -5.5);
-	\draw (0, -5) rectangle (1, -5.5) node[midway] {\tiny $\mathcal F$};
-	\draw (1.25, -5.25) node[anchor=west] {\tiny Subfilter being populated};
-
-	\draw[pattern=north west lines, pattern color=gray] (7, -5) rectangle (8, -5.5) node[midway] {\tiny $\mathcal F_i$};
-	\draw (8.25, -5.25) node[anchor=west] {\tiny Populated active subfilter};
-
-	\draw[dashed] (14, -5) rectangle (15, -5.5) node[midway] {\tiny $\mathcal F_j$};
-	\draw (1 5.25, -5.25) node[anchor=west] {\tiny Expired subfilter};
-	\end{tikzpicture}
+	\input{fig/queuef.tex}
 	\caption{Architecture of the queuing filter.
@@
 
-When the user wants to lookup for an element, they query all subfilters.
-If any subfilter answers with \DUPLICATE, the queueing filter answers \DUPLICATE.
-Otherwise, it answers \UNSEEN.
-Insertion is a simple insertion in the topmost subfilter.
+\paragraph{Insertion and lookup.}
+The filter returns \DUPLICATE if and only if at least one subfilter does. Insertion is a simple insertion in the topmost subfilter.
 
-After $c$ insertions (where $c$ is a filter parameter), the last filter of the queue is removed, and a new (empty) filter is appended in front of the queue.
+\paragraph{Queue update.}
+After $c$ insertions, the last filter of the queue is dropped, and a new (empty) filter is appended in front of the queue.
+
+\paragraph{Pseudocode.}
 We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in \ref{alg:queueing}.
-
-For the sake of simplicity in the pseudocode, we assume that the subfilter $\mathcal F$ has a function \textsf{Setup} which takes as input the available memory $m$, and returns an initialized empty filter $\mathcal F$ of size at most $m$..
+We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
+The \texttt{subfilter} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.
 
@@
 		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
-		\State Queue\_storage $\gets$ empty queue
-		\State Counter $\gets 0$
+		\State subfilters $\gets \emptyset$
+		\State counter $\gets 0$
+		\State $m \gets \lfloor M/L \rfloor$
 		\For{$i$ from $0$ to $L-1$}
-			\State Queue\_storage[i] $\gets$ $\mathcal F.\mathsf{Setup}(\lfloor M/L \rfloor)$
+			\State subfilters.push\_first$(\mathcal F.\mathsf{Setup}(m))$
 		\EndFor
-		Counter $\gets$ 0
-		\State Store $c$, $M$, $L$, $\mathcal F$
-
-		\State \Return filter
+		\State \textbf{store} (subfilters, $L$, $m$, counter)
+		\State\Return filter
 	\EndFunction 
@@
 		\For{$i$ from $0$ to $L-1$}
-			\If{$\mathcal F_i.\mathsf{Lookup(e)}$}
+			\If{subfilter[i]$.\mathsf{Lookup(e)}$}
 				\State \Return $\DUPLICATE$
@@
 	\Function{Insert}{$e$}
-		\State $\mathcal F_0.\mathsf{Insert}(e)$
-		\State Counter++
-		\If{Counter == $c$}
-			\State Pop last element of Queue\_Storage
-			\State Insert $\mathcal F$.\textsf{Setup}($\lfloor M/L \rfloor$) at the beginning of Queue\_Storage
+		\State subfilters[0]$.\mathsf{Insert}(e)$
+		\State counter $\gets$ counter + 1 
+		\If{counter == $c$}
+			\State subfilters.pop()
+			\State subfilters.push\_first($\mathcal F.\textsf{Setup}(m)$)
 		\EndIf

### 2020-03-18 qhtv2.tex
Clarifications 3.2.1

@@
 \begin{definition}[Probability of false positive, of false negative]
+	\label{def:pfp-pfn}
 	Let $E = \{e_1, \dotsc\}$ be a stream, $\mathcal F$ be a filter.
@@
 
-\subsection{Error Rate Analysis}
-Depending on the underlying subfilter, the queueing filter will behave differently.
-However, its false positive and false negative probabilities can be derived from the underlying subfilter's false positive and false negative probabilities.
+\subsection{Error rate analysis}
+The queueing filter's properties can be derived from the subfilters'.
+False positive and false negative rates are of particular interest.
+In this section we consider a queuing filter $\mathcal Q$ with $L$ subfilters $\mathcal F_i$ and
+capacity $c$ (which means that the last subfilter is dropeed after $c$ insertions).
 
-\subsubsection{Number of Elements in a Queueing Filter}\label{subsub:number_elements}
-Before deriving the error rates, it is important to analyse how many elements are in the filter.
-We know, by design, that no more than $cL$ elements can be present.
-However, after exactly $cL$ insertions, the last subfilter is deleted, to be replaced by an empty one at the beginning of the queue.
-Hence, after $cL$ insertions, only $c(L-1)$ elements are stored in the queueing filter.
+\paragraph{Remark.}
+	\label{subsub:number_elements}
+	By definition, after $c$ insertions the last subfilter is dropped.
+Information-theoretically, this means that all the information related to the elements inserted in that subfilter has been lost, and there are $c$ such elements by design. 
+Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements(immediatey after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).
 
-Hence, the number of elements in the filter oscillate between $c(L-1)$ and $cL$.
-Furthermore, we have $cL \approx w$, which means that the number of elements in the filter can be higher than $w$.
-These facts must be kept in mind while deriving the error rates.
+As a result, if $w < cL$, the queuing filter can hold information about \emph{more than $w$ elements}.
 
 \subsubsection{Probability of False Positive}
+
 \begin{theorem}
-	Let $\mathcal Q$ be a queueing filter, consisting of $L$ underlying subfilters $\mathcal F$, each filled with up to $c$ elements.
-Let $\FP_{\mathcal F,m}$ be the probability of false positive of the subfilter $\mathcal F$ after $m$ insertions, let $\FP_{\mathcal Q, m}^w$ be the probability of false positive of $\mathcal Q$ after $m$ insertions on a sliding window of size $w$.
-
-	We have $$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F,c})^{L-1}(1 - \FP_{\mathcal F, m \% c })$$ where \% is the modulo operator.
+	\label{thm:queue-pfp}
+	 Let $\FP_{\mathcal Q, m}^w$ be the probability of false positive (def. \ref{def:pfp-pfn}) of $\mathcal Q$ after $m$ insertions, over a sliding window of size $w = cL$, we have:
+	\begin{equation}
+		\label{eq:queue-pfp}
+		\FP_{\mathcal Q, m}^w = 1 - \left(1 - \FP_{\mathcal F,c}\right)^{L-1} \left(1 - \FP_{\mathcal F, m \bmod c }\right)
+	\end{equation}
+	where $\bmod$ is the modulo operator and 
+	 $\FP_{\mathcal F,m}$ be the probability of false positive of any of $\mathcal Q$'s subfilters $\mathcal F_i$ after $m$ insertions.
 \end{theorem}
@@
 \begin{proof}
-	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \notwdup E$.
-We first take into account the remark in \ref{subsub:number_elements} that the filter $\mathcal Q$ may contain more than $w$ elements, and hence potentially contain $e$ in memory, in the last subfilter of the queue.
-However, such event is quite rare, and can be neglected: let $\delta = cL - w$ the number of additional elements that can be stored in $\mathcal Q$.
-The probability that $e^\star$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta \approx \frac{\delta}{|\Gamma|} \approx 0$ since $\delta$ is likely to be small, while $|\Gamma|$ is too big for being stored in memory.
+	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream and $e^\star \notwdup E$.
 
-	Hence, we can neglect the probability that $e^\star$ is present in the filter.
 	Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
-Conversely, $e^\star$ is not a false positive if and only if all subqueries $\mathcal F_i.\mathsf{Lookup(e^\star)}$ return \UNSEEN.
-This can be rewritten as $e^\star$ is not a false positive if and only if $e^\star$ is not a false positive for each subfilter.
+Conversely, $e^\star$ is \emph{not} a false positive when all subqueries $\mathcal F_i.\mathsf{Lookup(e^\star)}$ return \UNSEEN, i.e., when $e^\star$ is not a false positive for each subfilter.
 
-	Given that each subfilter stores $c$ elements, safe for the first subfilter which only stores $m \% c$ elements, we get
-	$$\FP_{\mathcal Q, m}^w = 1 - (1 - \FP_{\mathcal F, m \% c })(1 - \FP_{\mathcal F,c})^{L-1}$$
+	Each subfilter has undergone $c$ insertions, safe for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
 \end{proof}
+
+\paragraph{Remark.} In the case $w < cL$, as mentioned previously, there is a non-zero probability that $e^\star$ is in the last subfilter's memory, despite not belonging to the sliding window.
+
+Assuming a uniformly random input stream, and writing $\delta = cL - w$, the probability that $e^\star$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta$.
+For large $\Gamma$ (as is expected to be the case in most applications), this probability is about $\frac{\delta}{|\Gamma|} \ll 1$.
+Hence, we can neglect the probability that $e^\star$ is present in the filter, and we consider the result of Theorem~\ref{thm:queue-pfp} to be a very good approximation even when $w < cL$.
 

### 2020-03-18 qhtv2.tex
Clarifications 3.2

@@
 	\label{thm:queue-pfp}
-	 Let $\FP_{\mathcal Q, m}^w$ be the probability of false positive (def. \ref{def:pfp-pfn}) of $\mathcal Q$ after $m$ insertions, over a sliding window of size $w = cL$, we have:
+	 Let $\FP_{\mathcal Q, m}^w$ be the probability of false positive (def. \ref{def:pfp-pfn}) of $\mathcal Q$ after $m > w$ insertions, over a sliding window of size $w = cL$, we have:
 	\begin{equation}
@@
 \begin{theorem}
-	Let $\mathcal Q$ be a queueing filter, consisting of $L$ underlying subfilters $\mathcal F$, each filled with up to $c$ elements.
-Let $\FN_{\mathcal F,m}$ be the probability of false negative of the subfilter $\mathcal F$ after $m$ insertions, let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m$ insertions on a sliding window of size $w$.
-
-	For $p_m = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^m}{1-\left(1-\frac 1{|\Gamma|}\right)^w}$, we have 
+	\label{thm:queue-pfn}
+	Let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
 	\begin{align*}
-	\FN_{\mathcal Q, m}^w =& \left[p_c\FN_{\mathcal F,c} + \left(1-p_c\right)\left(1-\FP_{\mathcal F,c}\right)\right]^{L-1}
-	\\&\qquad
-	 \cdot \left[p_{m\%c}\FN_{\mathcal F,m\%c} + \left(1-p_{m\%c}\right)\left(1-\FP_{\mathcal F,m\%c}\right)\right]
+	\FN_{\mathcal Q, m}^w 
+	= & \left[p_c\FN_{\mathcal F,c} + \left(1-p_c\right)\left(1-\FP_{\mathcal F,c}\right)\right]^{L-1} \\
+	 \times & \left[p_{m\bmod c}\FN_{\mathcal F,m\bmod c} + \left(1-p_{m\bmod c}\right)\left(1-\FP_{\mathcal F,m\bmod c}\right)\right]
 	\end{align*}
-
-	where $\%$ is the modulo operator.
+	where $\bmod$ is the modulo operator, $\FN_{\mathcal F,m}$ is the probability of false negative of any subfilter $\mathcal F$ after $m$ insertions, and
+	\begin{equation*}
+		p_m = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^m}{1-\left(1-\frac 1{|\Gamma|}\right)^w}.
+	\end{equation*}
 \end{theorem}
@@
 	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
-	We first observe that if $cL > w$, there might be some duplicates of $e^\star$ that happened before the current sliding window, but might still be remembered by the oldest filter.
-However, as argued in the previous section, the probability of such an event is negligible.
 
-	Hence, we consider that the only duplicates are part of the sliding window.
-$e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$.
+	Then $e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$. There can be two cases:
+	\begin{itemize}
+		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window;
+		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window.
+	\end{itemize}
+In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
+This happens with probability $\FN_{\mathcal F,c}$ by definition, except for $\mathcal F_0$, for which the probability is $\FN_{\mathcal F, m\bmod c}$.
 
-	There can be two cases:
-	\begin{itemize}
-		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window
-		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window
-	\end{itemize}
+In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$, which happens with probability $1-\FP_{\mathcal F,c}$, execpt for $\mathcal F_0$, for which the probability is $1-\FP_{\mathcal F, m\bmod c}$.
 
-In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
-Hence, in this case, the probability of $\mathcal F_i$ to return \UNSEEN is $\FN_{\mathcal F,c}$.
-For the subfilter $\mathcal F_0$, however, the probability is $\FN_{\mathcal F, m\%c}$.
+Finally, each event is weighted by the probability $p_c$ that $e^\star$ is in $\mathcal F_i$'s sub-sliding window:
+\begin{align*}
+	p_c 
+	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
+	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
+	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
+	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
+	& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
+\end{align*}
+This concludes the proof.
+\end{proof}
+\paragraph{Remark.} As previously, the effect of $w < cL$ is negiglible for all practical purposes and Theorem~\ref{thm:queue-pfn} is considered a good approximation in that regime.
 
-In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$.
-Hence, in this case, the probability of $\mathcal F_i$ to return \UNSEEN is $1-\FP_{\mathcal F,c}$.
-For the subfilter $\mathcal F_0$, however, the probability is $1-\FP_{\mathcal F, m\%c}$.
+\subsection{FNR and FPR}
 
-Now, the probability $p_c$ for $e^\star$ to be in subfilter $\mathcal F_i$ (which has had $c$ insertions) sub-sliding window is
+\todo[TODO]
 
-\begin{align*}
-	p_c =& Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
-	=& \frac{Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{Pr[e^\star \wdup E]}\\
-	=& \frac{Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{Pr[e^\star \wdup E]}\\
-	=& \frac{1 - Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - Pr[e^\star \notwdup E]}\\
-	p_c=& \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
-\end{align*}
-
-Finally, we get that the probability of a false positive for $\mathcal Q$ over the sliding window $w$ is 
-\begin{align*}
-\FN^w_{\mathcal Q, m} =& \left[p_c\FN_{\mathcal F,c} + (1-p_c)(1-\FP_{\mathcal F,c})\right]^{L-1}
-\\&\quad
-\cdot \left[p_{m\%c}\FN_{\mathcal F,m\%c} + (1-p_{m\%c})(1-\FP_{\mathcal F,m\%c})\right]\\
-\end{align*}
-\end{proof}
-
-This probability is quite complicated and does not allow, in the general case, for an in-depth analysis of the probability of false negative.
+\section{Optimising queuing filters}
 

### 2020-03-18 qhtv2.tex
typos

--- 2020-03-16 qhtv2.tex
@@
 
-	Finally this filter does not make any mistake, as every positive has a witness in $Q$ and any negative is absent from the last $w$ elements.
+	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact tract of how many times each element was present in the sliding window.
 \end{proof}
@@
 We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
-The \texttt{subfilter} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.
+The \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.
 
@@
 		\For{$i$ from $0$ to $L-1$}
-			\If{subfilter[i]$.\mathsf{Lookup(e)}$}
+			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
 				\State \Return $\DUPLICATE$

### 2020-03-18 qhtv2.tex
+FNR
typos

@@
 In this section, we describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
-A scheme describing our structure is detailed in \ref{fig:scheme}.
+A scheme describing our structure is detailed in Figure~\ref{fig:scheme}.
 
@@
 \paragraph{Pseudocode.}
-We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in \ref{alg:queueing}.
+We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in Algorithm~\ref{alg:queueing}.
 We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
@@
 Information-theoretically, this means that all the information related to the elements inserted in that subfilter has been lost, and there are $c$ such elements by design. 
-Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements(immediatey after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).
+Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements (immediately after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).
 
@@
 We added the lower bound on the error rate.
-More details about the experiments are given in \ref{sub:saturation}.
-We observe in \ref{fig:graph_n} that the two most efficient filters are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
+More details about the experiments are given in Section~\ref{sub:saturation}.
+We observe in Figure~\ref{fig:graph_n} that the two most efficient filters are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
 
-However, as noted in \ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters.
+However, as noted in Section~\ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters.
 Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.
@@
 
-We have observed in \ref{sub:fnr} that the FN is positively correlated with
+We have observed in Section~\ref{sub:fnr} that the FN is positively correlated with
 $\left(1-\FP_{\mathcal F,c}\right)^L$, however the FP is negatively correlated with the same value.
@@
 
-\todo[FAUX, peut etre log ? However, practical tests show (see \ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
+\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
 
@@
 
-We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in \ref{sub:opt_solutions}.
+We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in Section~\ref{sub:opt_solutions}.
 However, since we must evaluate the number of duplicates in the streams we use, we cannot benchmark our filter in real-life situations, as doing so would require way too much memory for keeping track of the duplicates.
@@
 The stream was a stream of uniform random elements, taken from an alphabet of $2^{26}$ elements, and amounts for about 8\% duplicates on the 150 000 000 elements in the longest stream used.
-Results are plotted in \ref{fig:graph_n}.
+Results are plotted in Figure~\ref{fig:graph_n}.
 
@@
 Now that DDF are compared on a full stream, we observe how each of them behave when they act as a subfilter in our queueing scheme.
-The goal is to empirically prove the assumption made in \ref{sub:optimal_ddf}, stating that the best (error-wise) DDF operating on a full stream leads to the best (error-wise) queueing filter operating on a sliding window.
-From \ref{fig:graph_n}, we observe that the best DDF for DDP on a full stream are, in order, QHT, SQF, Cuckoo, SQF.
+The goal is to empirically prove the assumption made in Section~\ref{sub:optimal_ddf}, stating that the best (error-wise) DDF operating on a full stream leads to the best (error-wise) queueing filter operating on a sliding window.
+From Figure~\ref{fig:graph_n}, we observe that the best DDF for DDP on a full stream are, in order, QHT, SQF, Cuckoo, SQF.
 
@@
 We used a random stream of $1,000,000$ elements uniformly selected from an alphabet of size $|\Gamma| = 2^{16}$, a memory size $M=100,000$ bits, a sliding window of size $w = 10,000$.
-The error rates (defined as the sum of $\FNR^w$ and $\FPR^w$) are displayed in \ref{tab:comparing_queueing}.
+The error rates (defined as the sum of $\FNR^w$ and $\FPR^w$) are displayed in Table~\ref{tab:comparing_queueing}.
 We see that in all cases, the QHT subfilter performs better or almost as well than any other subfilter, hence validating the heuristic assumption.

### 2020-03-18 qhtv2.tex
FNR

--- 2020-03-18 qhtv2.tex
@@
 
-One can observe that $\FPR_n = \frac{1}{n}\sum_{i=1}^m \FP_i$, and similarly for $\FNR_n$.
+One can observe that $\FPR_n = \frac{1}{n}\sum_{i=1}^n \FP_i$, and similarly for $\FNR_n$.
 
@@
 
-	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact tract of how many times each element was present in the sliding window.
+	Finally this filter does not make any mistake, as every positive has a witness in $Q$ and any negative is absent from the last $w$ elements.
 \end{proof}
@@
 We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
-The \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.
+The \texttt{subfilter} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.
 
@@
 		\For{$i$ from $0$ to $L-1$}
-			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
+			\If{subfilter[i]$.\mathsf{Lookup(e)}$}
 				\State \Return $\DUPLICATE$
@@
 	Let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{align*}
+	\begin{equation}
 	\FN_{\mathcal Q, m}^w 
-	= & \left[p_c\FN_{\mathcal F,c} + \left(1-p_c\right)\left(1-\FP_{\mathcal F,c}\right)\right]^{L-1} \\
-	 \times & \left[p_{m\bmod c}\FN_{\mathcal F,m\bmod c} + \left(1-p_{m\bmod c}\right)\left(1-\FP_{\mathcal F,m\bmod c}\right)\right]
-	\end{align*}
-	where $\bmod$ is the modulo operator, $\FN_{\mathcal F,m}$ is the probability of false negative of any subfilter $\mathcal F$ after $m$ insertions, and
+	=  u_c^{L-1} u_{m \bmod c}
+	\end{equation}
+	where $\bmod$ is the modulo operator, and we have introduced the short-hand notation $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$ where 
+	$\FN_{\mathcal F,m}$ is the probability of false negative of any subfilter $\mathcal F$ after $m$ insertions, and
 	\begin{equation*}
-		p_m = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^m}{1-\left(1-\frac 1{|\Gamma|}\right)^w}.
+		p_m = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^m}{1-\left(1-\frac 1{|\Gamma|}\right)^w} \approx \frac{m}{w}.
 	\end{equation*}
@@
 
-\todo[TODO]
+\begin{align*}
+	\FPR_{\mathcal Q, cn}^w
+	& = \frac{1}{cn} \sum_{k=1}^{cn} \FP_{\mathcal Q, k}^w 
+	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, k + \ell}^w 
+	 = \frac1c \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, \ell}^w \\
+	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
+	& = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} \FP_{\mathcal F, \ell}
+\end{align*}
+
+\begin{align*}
+	\FNR_{\mathcal Q, cn}^w 
+	& = \frac{1}{cn} \sum_{k=1}^{cn} \FN_{\mathcal Q, k}^w 
+	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, k + \ell}^w 
+	= \frac1c \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, \ell}^w \\
+	& = \frac1c \sum_{\ell = 0}^{c-1} u_c^{L-1} u_{\ell} 
+	 = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
+\end{align*}
 

### 2020-03-19 qhtv2.tex
Minor typo in FNR
Clarifications

@@
 \subsection{FNR and FPR}
-
+From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR:
 \begin{align*}
@@
 	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
-	& = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} \FP_{\mathcal F, \ell}
+	& = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
 \end{align*}
-
 \begin{align*}
@@
 \end{align*}
-
+In particular, these quantities do not depend on $n$. A corollary is that the queuing filter does not exhibit saturation.
 \section{Optimising queuing filters}
-
+\todo[À vérifier je suis pas convaincu encore]
 \begin{theorem}
@@
 
-\section{Application on Existing DDFs}
-As our queuing filter relies on another DDF subfilter, we must pick one existing DDF from the literature.
-\subsection{DDF Subfilter Selection Strategy}
-As a matter of fact, it is preferable to use only one kind of DDF as subfilter, as proven by the following theorem.
+\section{Application to existing DDFs}
+Our queuing construction relies on a choice of subfilters. A first observation 
+is that we may assume that all subfilters can be instances of a single 
+DDF design (rather than a combination of different designs).
+
+Indeed, a simple symmetry argument shows that a heterogenous selection of subfilters is always worse than a homogeneous one: the crux is that all subfilters play the same role in turn.
+Therefore we lose nothing by replacing atomically one subfilter by a more efficient one.
+Applying this to each subfilter we end up with a homogenous selection.
+
+It remains to decide which subfilter construction to choose.
+
+\subsection{Subfilter selection}
+When comparing different DDFs, one interesting metric in our context is how fast
+such filters saturate: indeed, in the original DDP setting, all filters eventually saturate \cite{10.1145/3297280.3297335}.
 
 \begin{theorem}
-	An optimal queueing filter only uses one kind of subfilter.
+	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $ER_n = \FP_n + \FN_n$ satisfies
+	\begin{equation}
+		ER_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
+	\end{equation}
+	for any $n > M$.
 \end{theorem}
+	In particular, the asymptotic error rate $ER_\infty$ satisfies $ER_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|$.
 
 \begin{proof}
-	One could imagine a queueing filter in which subfilters would alternate between, say, subfilter of type $A$ and of type $B$.
-However, we show with a simple symmetry argument that this kind of queueing filter is sub-optimal.
+	By definition, a perfect filter has the lowest possible error rate.
+	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
+Up to reordering the stream, without loss of generality because it is random, we may assumethat the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
 
-	Let us consider a queueing filter relying on several kinds of subfilters.
-Given that all subfilters play the same role, and that their efficiency is independent of the other subfilters present, we know that one less efficient subfilter can be replaced by a more efficient one, directly improving the efficiency of the queueing filter.
-\end{proof}
-
-However, making a theoretical analysis of all DDFs error rates may be tedious.
-Instead, we propose a ranking on existing DDFs.
-As \cite{10.1145/3297280.3297335} mentioned, filters all reach a saturation state.
-The idea is then to order DDFs by their resistance to saturation --i.e., by ranking them by the time they take to reach saturation.
-
-Before ranking the DDFs by the error rate, we first introduce a lower bound on said rate.
-
-Note: given we are working on selecting the best subfilter for our queueing filter, in this section we are \emph{not} working over a sliding window.
-
-\subsection{Optimal Error Probability on a DDF}\label{sub:optimal_ddf}
-    \begin{theorem}
-	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$.
-For any DDF of size $M$, the error probability $ER_n$ (consisting of the sum of the FP and FN probabilities) is such that
-	$$ER_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}$$ for any $n > M$.
-
-	Especially, for any filter of size $M$, the asymptotic error rate $ER_\infty$ is such that $ER_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M}$.
-\end{theorem}
-We remind that in this section, we are working on DDP over the whole stream and not over a sliding window.
-
-\begin{proof}
-	According to classical results on information theory, a perfect filter must use at least $1$ bit to remember one element from a random uniform source with no possible error.
-
-	Since the filter has $M$ bits of memory, we conclude that a perfect filter can store at most $M$ elements in memory.
-Assume that such a filter exists.
-Because the stream is random, we can assume without loss of generality that the filter stores the M last elements of the stream: any other strategy cannot yield a lower error rate, given the stream is random.
-
-	Let us derive the error rate of such a filter.
 	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
@@
 	On the other hand, a duplicate element $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
-Let $D$ be the event "\textsf{There is at least one duplicate in the stream} and $C$ be the event \textsf{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}.
-
-	We have that $e^\star$ triggers a false negative with probability
-
+Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
+Then $e^\star$ triggers a false negative with probability
 	\begin{align*}
-	\FN_n &= (1 - P[C | D])(1-p) =  \left(1 - \frac{P[C \cap D]}{P[D]}\right)(1-p)\\
-	& = \left(1 - \frac{P[C]}{P[D]}\right)(1-p) =  \left(1 - \frac{1 - P[\bar C]}{1 - P[\bar D]}\right)(1-p) \\
+	\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
+	& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
 	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
 	\end{align*}
-
-	Hence, the error probability of the filter is $ER_n = \FN_n + p =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p =$ $ 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p)$, which is minimized when $p = 0$.
-
-	Given that, by definition, a perfect filter has the lowest error rate of any filter, we get the desired result.
+	Hence, the error probability of the filter is
+	\begin{align*}
+		ER_n 
+		& = \FN_n + p \\
+		& =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
+		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
+	\end{align*}
+	which is minimized when $p = 0$. 
 	\end{proof}
 
-Note, as highlighted in the proof, that this bound is not tight, and that better bounds may exist.
-Also note that this bound only applies when the stream is random: when patterns are found in the stream, information theory informs that data may be stored more efficiently.
+Note, as highlighted in the proof, that this bound is \emph{not tight}: better bounds may exist, the study of which we leave as an open question for future work.
 
-As such, the best filter will be the one the closest to this error rate.
+The results of an experimental comparison of different DDFs (details about the benchmark are given in Section~\ref{sub:saturation}) are summarizes in Figure~\ref{fig:graph_n}.
+It appears that the two most efficient filters (in terms of saturation rate) are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
 
-\subsection{DDF Comparison}
-A filter comparison was already made in \cite{10.1145/3297280.3297335}.
-Taking the same filters parameters, created another benchmark, studying the resistance of each DDF to saturation.
-We added the lower bound on the error rate.
-More details about the experiments are given in Section~\ref{sub:saturation}.
-We observe in Figure~\ref{fig:graph_n} that the two most efficient filters are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
+Remarkably, as noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters).
+This raises the question of whether recursive constructions (queuing filters of queuing filters) have particularly interesting properties, which we leave open for future work.
 
-However, as noted in Section~\ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters.
-Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.
+In the experiments we use QHT for practical benchmarking of the queueing filter.
 

### 2020-03-20 qhtv2.tex
benchmark

--- 2020-03-18 qhtv2.tex
@@
 False positive and false negative rates are of particular interest.
-In this section we consider a queuing filter $\mathcal Q$ with $L$ subfilters $\mathcal F_i$ and
-capacity $c$ (which means that the last subfilter is dropeed after $c$ insertions).
+In this section we consider a queuing filter $\mathcal Q$ with $L$ subfilters of type $\mathcal F$ and
+capacity $c$ (which means that the last subfilter is dropped after $c$ insertions).
 
@@
 Information-theoretically, this means that all the information related to the elements inserted in that subfilter has been lost, and there are $c$ such elements by design. 
-Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements (immediately after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).
+Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements (immediately after deleting the last subfilter) and at most $cL - 1$ elements (immediately before this deletion).
 
@@
 	where $\bmod$ is the modulo operator and 
-	 $\FP_{\mathcal F,m}$ be the probability of false positive of any of $\mathcal Q$'s subfilters $\mathcal F_i$ after $m$ insertions.
+	 $\FP_{\mathcal F,m}$ be the probability of false positive a subfilter $\mathcal F$ after $m$ insertions.
 \end{theorem}
@@
 	where $\bmod$ is the modulo operator, and we have introduced the short-hand notation $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$ where 
-	$\FN_{\mathcal F,m}$ is the probability of false negative of any subfilter $\mathcal F$ after $m$ insertions, and
+	$\FN_{\mathcal F,\eta}$ (resp. $\FP_{\mathcal F, \eta}$) is the probability of false negative (resp. false positive) of the subfilter $\mathcal F$ after $\eta$ insertions, and
 	\begin{equation*}
-		p_m = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^m}{1-\left(1-\frac 1{|\Gamma|}\right)^w} \approx \frac{m}{w}.
+		p_\eta = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^\eta}{1-\left(1-\frac 1{|\Gamma|}\right)^w} \approx \frac{\eta}{w}.
 	\end{equation*}
@@
 \subsection{FNR and FPR}
+As stated before, the probabilty of false positive and false negative are not the usual measurement made when benchmarking filters.
+Rather, one prefers to use false positive (and negative) \emph{rates}, defined as the average of the false positive (and negative) probabilities encountered so far.
 
+In this section, we briefly give the expression of these values.
+For the sake of simplicity, we only give the FPR and FNR of a queueing filter $\mathcal Q$ after $m = cn$ insertions, where $n$ is a positive integer.
+\begin{theorem}
+	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w \approx cL$, we have
+	$$\FPR_{\mathcal Q, cn}^w = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})$$
+\end{theorem}
+\begin{proof}
 \begin{align*}
@@
 	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
-	& = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} \FP_{\mathcal F, \ell}
+	& = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
 \end{align*}
+\end{proof}
 
+\begin{theorem}
+	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w \approx cL$, we have
+
+	$$\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell$$
+
+	with the $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$.
+\end{theorem}
+\begin{proof}
 \begin{align*}
@@
 \end{align*}
+\end{proof}
 
@@
 \begin{theorem}
-	In first approximation, a low value of $L$ leads to a higher false negative probability for the queueing filter.
+	In first approximation, a low value of $L$ for constant value $cL$ leads to a higher false negative probability for the queueing filter.
 \end{theorem}
@@
 If, in the sliding window, all duplicates only happened at least $(c-\frac12)L$ epochs ago (which happens with probability $\left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}$), we know that no duplicates happened in any subfilter's sliding window.
-By using the same reasoning as the theorem's proof, we get a probability of false negative of around $\left[0 + \left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}(1-\FP_{\mathcal F,c})\right]^L$.
+By using the same reasoning as Theorem~\ref{thm:queue-pfn}'s proof, we get a probability of false negative of around $\left[0 + \left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}(1-\FP_{\mathcal F,c})\right]^L$.
 Given that $cL \approx w$ which is a constant, we get that the probability of false positive mostly varies, in this case, with $\left(1-\FP_{\mathcal F,c}\right)^L$.
@@
 More details about the experiments are given in Section~\ref{sub:saturation}.
-We observe in Figure~\ref{fig:graph_n} that the two most efficient filters are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
+We observe in Figure~\ref{fig:graph_n} that the most efficient DDF is the QHT \cite{10.1145/3297280.3297335}.
 
-However, as noted in Section~\ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters.
+%However, as noted in Section~\ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters.
 Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.
@@
 	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
-%	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
+	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
 %	\item Block-Decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of 6000 elements.
@@
 
-\begin{figure}
+\begin{figure*}
+	\begin{tikzpicture}
+	\begin{groupplot}[
+	group style = {
+		group size = 2 by 1,
+		horizontal sep = 35pt,
+	},
+	axis lines = left,
+	ylabel near ticks,
+	width = 0.4\textwidth,
+	height = 0.27\textwidth,
+	]
+	\input{er_n_real}
 	\input{er_n_artificial}
-	\caption{Error rate (times 100) of DDFs of 1Mb, depending on the size of the stream, without any sliding window. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
-\end{figure}
+	%\input{10e6_sum_zipf}
+	\end{groupplot}
+    \path (top)--(bot) coordinate[midway] (group center);
+%	\node[above,rotate=90] at (group center -| current bounding box.west) {Error rate (\%)};
+	\node[right=1em,inner sep=0pt] at(group center -| current bounding box.east) {\pgfplotslegendfromname{legend_n}};
+	\end{tikzpicture}
+
+%	\input{er_n_artificial}
+	\caption{Error rate (times 100) of DDFs of 1Mb, over a real and artificial stream, depending on the size of the stream, without any sliding window.
+Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
+\end{figure*}
 
@@
 
-For this, we used four different queueing filters, with $L = 10$ subfilters each, and with the following subfilters: 
-\begin{itemize}
-	\item QHT subfilter \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint. 
-	\item Cuckoo Filter \cite{Fan14}, adapted for streaming as recommanded by \cite{10.1145/3297280.3297335}, cells containing 1 element of 3 bits each
-	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$
-	\item SBF \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
-\end{itemize}
+For this, we reused the same filters are previously mentioned.
+%\begin{itemize}
+%	\item QHT subfilter \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint. 
+%	\item Cuckoo Filter \cite{Fan14}, adapted for streaming as recommanded by \cite{10.1145/3297280.3297335}, cells containing 1 element of 3 bits each
+%	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$
+%	\item SBF \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
+%	\item A2
+%\end{itemize}
 
-We used a random stream of $1,000,000$ elements uniformly selected from an alphabet of size $|\Gamma| = 2^{16}$, a memory size $M=100,000$ bits, a sliding window of size $w = 10,000$.
-The error rates (defined as the sum of $\FNR^w$ and $\FPR^w$) are displayed in Table~\ref{tab:comparing_queueing}.
+We used a random stream of $10,000,000$ elements uniformly selected from an alphabet of size $|\Gamma| = 2^{18}$, a memory size $M=100,000$ bits, a sliding window of size $w = 10,000$.
+The error rates (defined as the sum of $\FNR^w$ and $\FPR^w$) are displayed in Figure~\ref{tab:comparing_queueing}.
 We see that in all cases, the QHT subfilter performs better or almost as well than any other subfilter, hence validating the heuristic assumption.
 
-\begin{table}[]
-	\begin{tabular}{rccccc}
-			   & $w=1000$ & $w=5000$ & $w=10^4$ & $w=10^5$ & $w=10^6$ \\ \hline
-		QHT    & \textbf{9.84} 	  & \textbf{26.25}	 & \textbf{41.09}	 & \textbf{87.89}	  & 70.76      \\
-		Cuckoo & 84.99	  & 99.94	 & 99.95	 & 99.93	  & 99.80      \\
-		SQF    & 16.73 	  & 48.76	 & 69.25	 & 95.77 	  & \textbf{70.14}     \\
-		SBF    & 54.88 	  & 93.93	 & 97.33	 & 97.41	  & 71.17      \\
-	\end{tabular}
-	\caption{Error rate (times 100) of various queueing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{16}$.
+A very interesting observation is that, for $N$ the length of the stream, when $w \approx N/L$ we observe a decrease in the error rates.
+While being interesting on the theoretical side, in practice we usually assume that the stream is infinite, so we cannot rely on this fact for designing our filter.
+As such, the study of the phenomenon is left for future work.
+
+\begin{figure}
+	\input{graphs/compare_queues.tex}
+	\caption{Error rate (times 100) of various queueing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{18}$.}\label{tab:comparing_queueing}
+\end{figure}
+%\begin{table}[]
+%	\begin{tabular}{rccccc}
+%			   & $w=1000$ & $w=5000$ & $w=10^4$ & $w=10^5$ & $w=10^6$ \\ \hline
+%		QHT    & \textbf{9.84} 	  & \textbf{26.25}	 & \textbf{41.09}	 & \textbf{87.89}	  & 70.76      \\
+%		Cuckoo & 84.99	  & 99.94	 & 99.95	 & 99.93	  & 99.80      \\
+%		SQF    & 16.73 	  & 48.76	 & 69.25	 & 95.77 	  & \textbf{70.14}     \\
+%		SBF    & 54.88 	  & 93.93	 & 97.33	 & 97.41	  & 71.17      \\
+%	\end{tabular}
+%	\caption{Error rate (times 100) of various queueing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{16}$.
 For each sliding window, the best performance is written in bold.}\label{tab:comparing_queueing}
-\end{table}
+%\end{table}
 

### 2020-03-20 qhtv2.tex

@@
 \subsection{FNR and FPR}
+
 As stated before, the probabilty of false positive and false negative are not the usual measurement made when benchmarking filters.
@@
 
-In this section, we briefly give the expression of these values.
+From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR.
 For the sake of simplicity, we only give the FPR and FNR of a queueing filter $\mathcal Q$ after $m = cn$ insertions, where $n$ is a positive integer.
@@
 \begin{proof}
+
 \begin{align*}
@@
 \end{align*}
+
 \end{proof}
@@
 \end{theorem}
+
 \begin{proof}
@@
 \section{Optimising queuing filters}
-
+\todo[À vérifier je suis pas convaincu encore]
 \begin{theorem}
@@
 	On the other hand, a duplicate element $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
-Let $D$ be the event "\textsf{There is at least one duplicate in the stream} and $C$ be the event \textsf{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}.
-
-	We have that $e^\star$ triggers a false negative with probability
-
+Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
+Then $e^\star$ triggers a false negative with probability
 	\begin{align*}
-	\FN_n &= (1 - P[C | D])(1-p) =  \left(1 - \frac{P[C \cap D]}{P[D]}\right)(1-p)\\
-	& = \left(1 - \frac{P[C]}{P[D]}\right)(1-p) =  \left(1 - \frac{1 - P[\bar C]}{1 - P[\bar D]}\right)(1-p) \\
+	\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
+	& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
 	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
 	\end{align*}
-
-	Hence, the error probability of the filter is $ER_n = \FN_n + p =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p =$ $ 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p)$, which is minimized when $p = 0$.
-
-	Given that, by definition, a perfect filter has the lowest error rate of any filter, we get the desired result.
+	Hence, the error probability of the filter is
+	\begin{align*}
+		ER_n 
+		& = \FN_n + p \\
+		& =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
+		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
+	\end{align*}
+	which is minimized when $p = 0$. 
 	\end{proof}
 
-Note, as highlighted in the proof, that this bound is not tight, and that better bounds may exist.
-Also note that this bound only applies when the stream is random: when patterns are found in the stream, information theory informs that data may be stored more efficiently.
+Note, as highlighted in the proof, that this bound is \emph{not tight}: better bounds may exist, the study of which we leave as an open question for future work.
 
-As such, the best filter will be the one the closest to this error rate.
+The results of an experimental comparison of different DDFs (details about the benchmark are given in Section~\ref{sub:saturation}) are summarizes in Figure~\ref{fig:graph_n}.
+It appears that the two most efficient filters (in terms of saturation rate) are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
 
@@
 Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.
+
+As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
+This raises the question of whether recursive constructions (queuing filters of queuing filters) have particularly interesting properties, which we leave open for future work.
+
+%In the experiments we use QHT for practical benchmarking of the queueing filter.
 

### 2020-03-20 qhtv2.tex
Clarifications

--- 2020-03-19 qhtv2.tex
@@
 \subsection{Parameter Tuning}
+\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
+
 The parameters of a queueing filter are: the parameters of the subfilter, the number $L$ of subfilters and the number $c$ of insertions per subfilter.
@@
 
-\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
-
 %Hence, the (heuristic) optimal solution is to set $L = \sqrt w$.
@@
 \section{Experiments and Benchmarks}
-In this section, we present the different experiments we made. The code is accessible online and will be disclosed after peer review.
+This section provides details and additional information on the benchmarking experiments run to validate the above analysis. All code is accessible online and will be disclosed after peer review.
 
-We first present a comparison of the resistance of various DDFs against saturation, without any sliding window. This comparison helps us to choose the best subfilter.
-
-Then, we design an experiment in which we compare the error rates of a QHT and a queuing filter, using the same QHT as a subfilter.
-
-We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in Section~\ref{sub:opt_solutions}.
-However, since we must evaluate the number of duplicates in the streams we use, we cannot benchmark our filter in real-life situations, as doing so would require way too much memory for keeping track of the duplicates.
+Our benchmarks cover two aspects: 
+\begin{enumerate}
+\item A measure of DDFs' saturation rate, in the original DDP setting (i.e. without a sliding window), which is used to choose a subfilter design;
+\item A measure of the effect of queuing on error rates, in the sliding window DDP setting. Namely, we compate QHT and a queuing QHT.
+\end{enumerate}
+An important note is that when the sliding window is small compared to the filter's memory size, optimal or nearly optimal solutions can be implemented (see Section~\ref{sub:opt_solutions}).
+This is practical for smaller values because we can measure exactly a filter's response compared to the \enquote{ground truth}.
+However, this is no longer possible for very large parameters as it would require too much memory for keeping track of the duplicates.
 

### 2020-03-20 qhtv2.tex
Merging

@@
 
-\subsection{DDF Comparison}
-A filter comparison was already made in \cite{10.1145/3297280.3297335}.
-Taking the same filters parameters, created another benchmark, studying the resistance of each DDF to saturation.
-We added the lower bound on the error rate.
-More details about the experiments are given in Section~\ref{sub:saturation}.
-We observe in Figure~\ref{fig:graph_n} that the most efficient DDF is the QHT \cite{10.1145/3297280.3297335}.
-
-%However, as noted in Section~\ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters.
-Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.
-
 As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
@@
 
-%In the experiments we use QHT for practical benchmarking of the queueing filter.
+In the experiments we use QHT for the benchmarking of the queueing construction.
 

### 2020-03-20 qhtv2.tex
Precisions

@@
 \subsection{Saturation Resistance of DDFs}\label{sub:saturation}
-In this section, we compare the resistance of various filters to saturation.
-From the streaming filters we found in the literature, we only considered the filters not designed for operating on a sliding window, and parameters as \cite{10.1145/3297280.3297335}, namely:
-
+We evaluate the saturation rate for several DDFs, in the original DDP setting (without sliding window).
+Parameters are chosen to yield equivalent memory footprints and agree with \cite{10.1145/3297280.3297335}, namely:
+%
 \begin{itemize}
@@
 \end{itemize}
-
-The stream was a stream of uniform random elements, taken from an alphabet of $2^{26}$ elements, and amounts for about 8\% duplicates on the 150 000 000 elements in the longest stream used.
+%
+These filters are run against a stream of uniformly sampled elements from an alphabet of $2^{26}$ elements.
+This results in around 8\% duplicates (up to statistical fluctuations) amongst the 150 000 000 elements in the longest stream used.
+As a comparison, we also run the same benchmark against a stream obtained from crawling data, a real-world source which is highly non-uniform --- note that in this case, our lower bound on the error rate does not apply, owing to the stream being compressible.
 Results are plotted in Figure~\ref{fig:graph_n}.
 
-\begin{figure*}
+\begin{figure*}[!ht]
 	\begin{tikzpicture}
@@
 	]
+	\input{er_n_artificial}
 	\input{er_n_real}
-	\input{er_n_artificial}
 	%\input{10e6_sum_zipf}

### 2020-03-20 qhtv2.tex
Clarifications

@@
 
-We observe that the best filters are, in order, QHT, SQF, Cuckoo and SBF.
+The best results are given by the following filters, in order: QHT, SQF, Cuckoo and SBF.
 We also observe that QHT and SQF have error rates relatively close to the lower bound, hence suggesting that these filters are close to optimality.
 
-\subsection{Benchmarking Various Queuing Filters}
-Now that DDF are compared on a full stream, we observe how each of them behave when they act as a subfilter in our queueing scheme.
-The goal is to empirically prove the assumption made in Section~\ref{sub:optimal_ddf}, stating that the best (error-wise) DDF operating on a full stream leads to the best (error-wise) queueing filter operating on a sliding window.
-From Figure~\ref{fig:graph_n}, we observe that the best DDF for DDP on a full stream are, in order, QHT, SQF, Cuckoo, SQF.
+\subsection{Benchmarking Queuing Filters}
+We now use the queuing construction on the DDFs discussed previously.
+In Section~\ref{sub:optimal_ddf} we suggested the heuristic that the DDFs with the least saturation rate in the DDP would yield the best (error-wise) queueing filter for the sliding window DDP.
+This heuristic is supported by results, summarized in Figure~\ref{tab:comparing_queueing}.
+For this benchmark we used the following parameters: uniform stream from an alphabet of size $|\Gamma| = 2^{18}$, memory size $M=100,000$ bits, sliding window of size $w = 10,000$, and we measure the error rate (sum of $\FNR^w$ and $\FPR^w$).
 
-For this, we reused the same filters are previously mentioned.
-%\begin{itemize}
-%	\item QHT subfilter \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint. 
-%	\item Cuckoo Filter \cite{Fan14}, adapted for streaming as recommanded by \cite{10.1145/3297280.3297335}, cells containing 1 element of 3 bits each
-%	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$
-%	\item SBF \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
-%	\item A2
-%\end{itemize}
+A very interesting observation is that $Lw$ approaches the size of the stream, there is a drop in the error.
+This is an artifact due to the finite size of our simulations; the stream should be considered infinite, and this drop disappears as the simulation is run for longer.
+This effect also alters the error rates for smaller window sizes, albeit much less, and we expect that filter designers care primarily about the small window regime.
+Nevertheless a complete understanding of this effect would be of theoretical interest, and we leave the study of this phenomenon for future work.
 
-We used a random stream of $10,000,000$ elements uniformly selected from an alphabet of size $|\Gamma| = 2^{18}$, a memory size $M=100,000$ bits, a sliding window of size $w = 10,000$.
-The error rates (defined as the sum of $\FNR^w$ and $\FPR^w$) are displayed in Figure~\ref{tab:comparing_queueing}.
-We see that in all cases, the QHT subfilter performs better or almost as well than any other subfilter, hence validating the heuristic assumption.
-
-A very interesting observation is that, for $N$ the length of the stream, when $w \approx N/L$ we observe a decrease in the error rates.
-While being interesting on the theoretical side, in practice we usually assume that the stream is infinite, so we cannot rely on this fact for designing our filter.
-As such, the study of the phenomenon is left for future work.
-
-\begin{figure}
+\begin{figure}[!ht]
 	\input{graphs/compare_queues.tex}

### 2020-03-20 qhtv2.tex
Clarifications

@@
 \subsection{FNR and FPR}
-
-As stated before, the probabilty of false positive and false negative are not the usual measurement made when benchmarking filters.
-Rather, one prefers to use false positive (and negative) \emph{rates}, defined as the average of the false positive (and negative) probabilities encountered so far.
-
-From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR.
-For the sake of simplicity, we only give the FPR and FNR of a queueing filter $\mathcal Q$ after $m = cn$ insertions, where $n$ is a positive integer.
+From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR when $m = cn$ for $n$ a positive integer.
 \begin{theorem}
-	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w \approx cL$, we have
-	$$\FPR_{\mathcal Q, cn}^w = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})$$
+	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
+	\begin{equation}
+	\FPR_{\mathcal Q, cn}^w = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
+	\end{equation}
 \end{theorem}
@@
 \end{align*}
-
 \end{proof}
@@
 \begin{theorem}
-	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w \approx cL$, we have
-
-	$$\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell$$
-
-	with the $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$.
+	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
+	\begin{equation}
+	\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
+	\end{equation}
 \end{theorem}
@@
 \end{align*}
-
 \end{proof}
+As for the probabilities, the expressions derived above for the FNR and FNR are valid to first order in $(w - cL)/|\Gamma|$, i.e. they are good approximations even when $w \approx cL$.
 

### 2020-03-20 qhtv2.tex
Clarifications
add part 7 + small fixes

--- 2020-03-20 qhtv2.tex
@@
 We begin with the following, ideal problem: 
-\begin{definition}[Duplicate detection problem, DDP] Given a stream $E_n = \{e_1, e_2, \dotsc, e_n\}$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$.\footnote{
+\begin{definition}[Duplicate detection problem, DDP] Given a stream $E_n = (e_1, e_2, \dotsc, e_n)$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$.\footnote{
 	We do not consider here \emph{fuzzy} detection approaches\cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient} that study situations where $e^\star$ belongs to $E_n$ when there exists a \enquote{similar enough} element in the stream.
 }
-	At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n \cup \{e^\star\}$. 
+	At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n | (e^\star)$ where | denotes the concatenation . 
 \end{definition}
@@
 \subsection{Notations and Initial Problem Statement}
-Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) set $E = \{e_1, e_2, \dotsc\}$, with each $e_i \in \Gamma$.
+Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) set $E = (e_1, e_2, \dotsc)$, with each $e_i \in \Gamma$.
 
 \begin{definition}[Duplicate and unseen element]
-Let $E = \{e_1, e_2, \dotsc\}$ be a stream over $\Gamma$.
+Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$.
 Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$.
@@
 \emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp.
-$\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $\{e_1, \dotsc, e_i\}\subset E$ (resp.
+$\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $(e_1, \dotsc, e_i)\subset E$ (resp.
 the ratio of false negative divided by the number of duplicate elements in that subset).
@@
 	\label{def:pfp-pfn}
-	Let $E = \{e_1, \dotsc\}$ be a stream, $\mathcal F$ be a filter.
+	Let $E = (e_1, \dotsc)$ be a stream, $\mathcal F$ be a filter.
 The \emph{probability of false positive} (resp.
@@
 \begin{definition}[Sliding window DDP]
-	Given a stream $E_n$ of fixed size $w$, with $E_n = \{e_{n-w+1}, \dotsc, e_n\}$ and an item $e^\star$, find whether $e^\star \in E_n$.
+	Given a stream $E_n$ of fixed size $w$, with $E_n = (e_{n-w+1}, \dotsc, e_n)$ and an item $e^\star$, find whether $e^\star \in E_n$.
 \end{definition}
@@
 \begin{definition}[Duplicate element, unseen element over a sliding window]
-	Let $E = \{e_1, e_2, \dotsc\}$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
+	Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
 In this case we write $e_j \wdup E$.
@@
 As such, it is dropped and a new one is created and put under population at the beginning of the queue.
-In this example, the sub-sliding window of $\mathcal F_1$ is $\{e_{m-2}, e_{m-3}, e_{m-4}\}$.} \label{fig:scheme}
+In this example, the sub-sliding window of $\mathcal F_1$ is $(e_{m-2}, e_{m-3}, e_{m-4})$.} \label{fig:scheme}
 \end{figure}
@@
 Information-theoretically, this means that all the information related to the elements inserted in that subfilter has been lost, and there are $c$ such elements by design. 
-Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements (immediately after deleting the last subfilter) and at most $cL - 1$ elements (immediately before this deletion).
+Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements (immediately after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).
 
@@
 \begin{proof}
-	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream and $e^\star \notwdup E$.
+	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream and $e^\star \notwdup E$.
 
@@
 
+\subsection{DDF Comparison}
+A filter comparison was already made in \cite{10.1145/3297280.3297335}.
+Taking the same filters parameters, created another benchmark, studying the resistance of each DDF to saturation.
+We added the lower bound on the error rate.
+More details about the experiments are given in Section~\ref{sub:saturation}.
+We observe in Figure~\ref{fig:graph_n} that the most efficient DDF is the QHT \cite{10.1145/3297280.3297335}.
+
+%However, as noted in Section~\ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters.
+Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.
+
 As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
@@
 
-In the experiments we use QHT for the benchmarking of the queueing construction.
+%In the experiments we use QHT for practical benchmarking of the queueing filter.
 
 \subsection{Parameter Tuning}
-\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
-
 The parameters of a queueing filter are: the parameters of the subfilter, the number $L$ of subfilters and the number $c$ of insertions per subfilter.
@@
 
+\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
+
 %Hence, the (heuristic) optimal solution is to set $L = \sqrt w$.
@@
 \section{Experiments and Benchmarks}
-This section provides details and additional information on the benchmarking experiments run to validate the above analysis. All code is accessible online and will be disclosed after peer review.
+In this section, we present the different experiments we made. The code is accessible online and will be disclosed after peer review.
 
-Our benchmarks cover two aspects: 
-\begin{enumerate}
-\item A measure of DDFs' saturation rate, in the original DDP setting (i.e. without a sliding window), which is used to choose a subfilter design;
-\item A measure of the effect of queuing on error rates, in the sliding window DDP setting. Namely, we compate QHT and a queuing QHT.
-\end{enumerate}
-An important note is that when the sliding window is small compared to the filter's memory size, optimal or nearly optimal solutions can be implemented (see Section~\ref{sub:opt_solutions}).
-This is practical for smaller values because we can measure exactly a filter's response compared to the \enquote{ground truth}.
-However, this is no longer possible for very large parameters as it would require too much memory for keeping track of the duplicates.
+We first present a comparison of the resistance of various DDFs against saturation, without any sliding window. This comparison helps us to choose the best subfilter.
+
+Then, we design an experiment in which we compare the error rates of a QHT and a queuing filter, using the same QHT as a subfilter.
+
+We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in Section~\ref{sub:opt_solutions}.
+However, since we must evaluate the number of duplicates in the streams we use, we cannot benchmark our filter in real-life situations, as doing so would require way too much memory for keeping track of the duplicates.
 
 \subsection{Saturation Resistance of DDFs}\label{sub:saturation}
-We evaluate the saturation rate for several DDFs, in the original DDP setting (without sliding window).
-Parameters are chosen to yield equivalent memory footprints and agree with \cite{10.1145/3297280.3297335}, namely:
-%
+In this section, we compare the resistance of various filters to saturation.
+From the streaming filters we found in the literature, we only considered the filters not designed for operating on a sliding window, and parameters as \cite{10.1145/3297280.3297335}, namely:
+
 \begin{itemize}
@@
 \end{itemize}
-%
-These filters are run against a stream of uniformly sampled elements from an alphabet of $2^{26}$ elements.
-This results in around 8\% duplicates (up to statistical fluctuations) amongst the 150 000 000 elements in the longest stream used.
-As a comparison, we also run the same benchmark against a stream obtained from crawling data, a real-world source which is highly non-uniform --- note that in this case, our lower bound on the error rate does not apply, owing to the stream being compressible.
+
+We used two streams.
+The first one was a real stream, collected from \cite{10.1145/3297280.3297335}, which is a web crawler's log, of alphabet size unknown, with about 10\% duplicates on the longest stream, consisting of 150 000 000 elements.
+The second one was a stream of random elements, taken from an alphabet of $2^{26}$ elements, with around 8\% duplicates on the longest stream.
 Results are plotted in Figure~\ref{fig:graph_n}.
 
-\begin{figure*}[!ht]
+\begin{figure*}
 	\begin{tikzpicture}
@@
 	]
+	\input{er_n_real}
 	\input{er_n_artificial}
-	\input{er_n_real}
 	%\input{10e6_sum_zipf}
@@
 In this section, we make experiments on the influence of $L$ on the error rate of the queueing filter.
+
 \subsection{Comparison of QHT and QHT-Queueing Filter}
 In this section, we compare the efficiency of QHT and QHT-queueing filter. For this, we use both an artificial dataset, as well as a real one, on various sliding window sizes.
+\todo[]
 
-\section{Security}
+\section{Adversarial Resistance}
+
+In this section, we now focus on the security on the queueing filter.
+We consider an adversarial game in which the attacker wants to trigger false positives or false negatives over the sliding window.
+This has practical applications in several topics of security, including cache saturation or denial of service by forcing cache misses, or by making undetected fraudulent payments.
+\todo[source].
+
+We first recall the definition of an adversarial game, adapted to our context.
+
+\begin{definition}
+	An adversary $\mathcal A$ feeds data to a sliding window DDF $\mathcal Q$, and for each inserted element, $\mathcal A$ knows whether $\mathcal Q$ answers $\DUPLICATE$ or $\UNSEEN$, but has not access to $\mathcal Q$'s internal state $\mathcal M$.
+The game has two distinct parts.
+
+\begin{itemize}
+	\item In the first part, $\mathcal A$ can feed up to $n$ elements to $\mathcal Q$ and learn $\mathcal Q$'s response for each insertion.
+	\item In the second part, $\mathcal A$ sends a unique element $e^\star$.
+\end{itemize} 
+ $\mathcal A$ wins the $n$-false positive adversarial game (resp. $n$-false negative adversarial game) if and only if $e^\star$ is a false positive (resp. a false negative).
+
+ \end{definition}
+
+This adversarial game can be trivially adapted for a false positive (resp. false negative) adversarial game over a sliding window of size $w$, hence we omit its formal definition.
+
+\subsection{First Approach on the Whole Sliding Window}
+We first define what an adversarial false positive resistance over a sliding window is, before giving its value for any queueing filter based on the subfilter's properties.
+
+\begin{definition}{Adversarial False Positive Resistance}
+	Let $\mathcal F$ be a filter, let $E$ be a stream.
+We say that $\mathcal F$ is $(p, n)$-resistant to adversarial false positives if no polynomial-time probabilistic (PPT) adversary $\mathcal A$ can win the $n-$false positive adversarial game with probability more than $p$.
+\end{definition}
+
+Note that if $\mathcal F$ is $(p,n)$-resistant, it is as well $(p, m)$-resistant for any $m < n$.
+
+This definition can be trivially adapted for false negative resistance, and for resistance over a sliding window.
+
+\begin{theorem}
+	Let $\mathcal Q$ be a filter of $L$ subfilters $\mathcal F_i$, with $c$ insertions maximum per subfilter, let $E$ be a stream, let $w$ be a sliding window size.
+
+	If $\mathcal F$ is $(p, c)$-resistant to adversarial false positive attacks and $cL \leq w$, then $\mathcal Q$ is $(1-(1-p)^L, w)$-resistant to adversarial false positive attacks on a sliding window of size $w$.
+
+	If $cL > w$, the adversary has a probability of success of at least $(1-(1-p)^L$.
+\end{theorem}
+
+\begin{proof}
+	Let us first assume that $cL \leq w$. This implies that information-theory wise, the elements remembered by each subfilter belong to the sliding window.
+
+	The probability of false positive for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$.
+As we see, the probability of false positive in $\mathcal Q$ over the sliding window $w$ is strictly increasing with the probability of false positive in any subfilter $\mathcal F_i$.
+Hence, the optimal solution is to maximise the probability of false positive in each subfilter $\mathcal F_i$, which by hypothesis is bounded above by $p$ after $c$ insertions.
+
+	On the other hand, if $cL > w$, it means that the oldest filter remembers elements that do not belong to the sliding window anymore.
+Hence, a strategy for the attacker trying to trigger a false positive on $e^\star$ could be to make it so these oldest elements are all equal to $e^\star$.
+Let $E$ be the optimal adversarial stream for triggering a false positive on the sliding window $w$ with the element $e^\star$, when $cL \leq w$.
+The adversary $\mathcal A$ can create a new stream $E' = e^\star | e^\star | \dotsc | E$ where $e^\star$ is prepended $cL - w$ times to $E$.
+
+	After $w$ insertions, it is quite likely that the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ probability of success.
+
+	Note that if, for some reason, the last subfilter answers $\DUPLICATE$ with probability less than $p$, then the default policy the same reasoning as for when $cL \leq w$ still applies, hence the lower bound (which is, in this case, an equality).
+\end{proof}
+
+\subsection{Adversarial False Negative}
+
+\begin{theorem}
+	Let $\mathcal Q$ be a filter of $L$ subfilters of kind $\mathcal F$, with $c$ insertions maximum per subfilter, let $E$ be a stream, let $w$ be a sliding window size.
+
+	If $\mathcal F$ is $(p, c)$-resistant to adversarial false negative attacks, then $\mathcal A$ can win the adversarial game on the sliding window $w$ with probability at least $p^L$.
+
+	Furthermore, for $q$ the lower bound on the probability of false positive $\FP_{\mathcal F,c}$ for a given stream, if $w \leq (L-1)c$ then $\mathcal Q$ is $(\min(1 - q, p)^{L-1}p, w)$-resistant to false negative attacks on the sliding window $w$.
+	On the other hand if $w > (L-1)c$ then $\mathcal Q$ is  $(\min(1 - q, p)^{L}, w)$-resistant to false negative attacks on the sliding window $w$.
+\end{theorem}
+
+\begin{proof}
+	Let us first prove that a PPT adversary $\mathcal A$ can win the game with probability at least $p^L$.
+	For this, let us consider the adversarial game against the subfilter $\mathcal F$: after $c$ insertions from an aversarial stream $E_c$, $\mathcal A$ choses a duplicate $e^\star$ which will be a false negative with proability $p$.
+	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c | E_c | \dotsc | E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a probability of success for $\mathcal A$ of $p^L$.
+
+	Now, Let us prove the case where $w\leq (L-1)c$.
+In this case, at any time, $\mathcal Q$ remembers all elements from inside the sliding window.
+As we have seen in the previous example, the probability of success of $\mathcal A$ is strictly increasing with the probability of each subfilter to answer $\UNSEEN$.
+The probability of a subfilter to answer $\UNSEEN$ is:
+
+	\begin{itemize}
+		\item $\FN'_{\mathcal F,c}$ if $e^\star$ is in the subfilter's sub-sliding window;
+		\item $1 - \FP'_{\mathcal F, c}$ if $e^\star$ is not in the subfilter's sub-sliding window
+	\end{itemize}
+	where $\FN'$ and $\FP'$ are the probabilities of false negative and positives on the adversarial stream (which may be different from a random uniform stream).
+
+	However, since $e^\star$ is a duplicate, it is in at least one subfilter's sub-sliding window.
+As such, the optimal strategy for $\mathcal A$ is to maximise the probability of all subfilters to answer $\UNSEEN$.
+	Now, $\FN'_{\mathcal F,c}$ is bounded above by $p$ and $1 - \FP'_{\mathcal F, c}$ is bounded above by $1-q$, so the best strategy is where as many filters as possible answer $\UNSEEN$ with probability $\max(p, 1-q)$, knowing that at least one filter must contain $e^\star$ and as such its probability for returning $\UNSEEN$ is at most $p$, hence the result.
+
+	Now, let us consider the case when $w > (L-1)c$.
+We have already introduce the element $e^\star$ in the last $w$ elements, and we want to insert it again.
+It is possible, for the adversary, to create the following stream $E = (e_1, e_2, \dotsc, e_{c-1}, e^\star, e_{c+1}, \dotsc, e_{Lc}, e_{Lc + 1})$, and to insert $e^\star$ afterwards.
+
+	When $e_{Lc+1}$ is inserted, all elements $(e_1, \dotsc, e_{c-1}, e^\star)$ are dropped as the oldest subfilter is popped.
+Hence, in this context $e^\star$ is not in any subfilter anymore, so by adapting the previous analysis, $\mathcal A$ can get a false negative with probability at most $\min(1 - q, p)^{L}$.
+\end{proof}
 %% Acknowledgements 

### 2020-03-20 qhtv2.tex

@@
 \subsection{FNR and FPR}
-
-As stated before, the probabilty of false positive and false negative are not the usual measurement made when benchmarking filters.
-Rather, one prefers to use false positive (and negative) \emph{rates}, defined as the average of the false positive (and negative) probabilities encountered so far.
-
-From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR.
-For the sake of simplicity, we only give the FPR and FNR of a queueing filter $\mathcal Q$ after $m = cn$ insertions, where $n$ is a positive integer.
+From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR when $m = cn$ for $n$ a positive integer.
 \begin{theorem}
-	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w \approx cL$, we have
-	$$\FPR_{\mathcal Q, cn}^w = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})$$
+	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
+	\begin{equation}
+	\FPR_{\mathcal Q, cn}^w = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell}).
+	\end{equation}
 \end{theorem}
@@
 \begin{theorem}
-	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w \approx cL$, we have
-
-	$$\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell$$
-
-	with the $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$.
+	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
+	\begin{equation}
+	\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell.
+	\end{equation}
 \end{theorem}
@@
 
-%In the experiments we use QHT for practical benchmarking of the queueing filter.
+In the experiments we use QHT for the benchmarking of the queueing construction.
 
 \subsection{Parameter Tuning}
+\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
+
 The parameters of a queueing filter are: the parameters of the subfilter, the number $L$ of subfilters and the number $c$ of insertions per subfilter.
@@
 \section{Experiments and Benchmarks}
-In this section, we present the different experiments we made. The code is accessible online and will be disclosed after peer review.
+This section provides details and additional information on the benchmarking experiments run to validate the above analysis. All code is accessible online and will be disclosed after peer review.
 
-We first present a comparison of the resistance of various DDFs against saturation, without any sliding window. This comparison helps us to choose the best subfilter.
-
-Then, we design an experiment in which we compare the error rates of a QHT and a queuing filter, using the same QHT as a subfilter.
-
-We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in Section~\ref{sub:opt_solutions}.
-However, since we must evaluate the number of duplicates in the streams we use, we cannot benchmark our filter in real-life situations, as doing so would require way too much memory for keeping track of the duplicates.
+Our benchmarks cover two aspects: 
+\begin{enumerate}
+\item A measure of DDFs' saturation rate, in the original DDP setting (i.e. without a sliding window), which is used to choose a subfilter design;
+\item A measure of the effect of queuing on error rates, in the sliding window DDP setting. Namely, we compate QHT and a queuing QHT.
+\end{enumerate}
+An important note is that when the sliding window is small compared to the filter's memory size, optimal or nearly optimal solutions can be implemented (see Section~\ref{sub:opt_solutions}).
+This is practical for smaller values because we can measure exactly a filter's response compared to the \enquote{ground truth}.
+However, this is no longer possible for very large parameters as it would require too much memory for keeping track of the duplicates.
 
 \subsection{Saturation Resistance of DDFs}\label{sub:saturation}
-In this section, we compare the resistance of various filters to saturation.
-From the streaming filters we found in the literature, we only considered the filters not designed for operating on a sliding window, and parameters as \cite{10.1145/3297280.3297335}, namely:
-
+We evaluate the saturation rate for several DDFs, in the original DDP setting (without sliding window).
+Parameters are chosen to yield equivalent memory footprints and agree with \cite{10.1145/3297280.3297335}, namely:
+%
 \begin{itemize}
@@
 \end{itemize}
-
-We used two streams.
-The first one was a real stream, collected from \cite{10.1145/3297280.3297335}, which is a web crawler's log, of alphabet size unknown, with about 10\% duplicates on the longest stream, consisting of 150 000 000 elements.
-The second one was a stream of random elements, taken from an alphabet of $2^{26}$ elements, with around 8\% duplicates on the longest stream.
+%
+These filters are run against a stream of uniformly sampled elements from an alphabet of $2^{26}$ elements.
+This results in around 8\% duplicates (up to statistical fluctuations) amongst the 150 000 000 elements in the longest stream used.
+As a comparison, we also run the same benchmark against a stream obtained from crawling data, the same one as \cite{10.1145/3297280.3297335}, a real-world source which is highly non-uniform --- note that in this case, our lower bound on the error rate does not apply, owing to the stream being compressible.
+In that stream, around 10\% were duplicates amongst the 150 000 000 elements.
 Results are plotted in Figure~\ref{fig:graph_n}.
 
-\begin{figure*}
+\begin{figure*}[!ht]
 	\begin{tikzpicture}
@@
 %\end{table}
-
-\todo
 

### 2020-03-20 qhtv2.tex
Clarifications

@@
 
-\subsection{Benchmark of the influence of $L$ parameter}\label{sub:L_bench}
+\subsection{How many subfilters?}\label{sub:L_bench}
+\todo[À faire]
 In this section, we make experiments on the influence of $L$ on the error rate of the queueing filter.
@@
 \subsection{Comparison of QHT and QHT-Queueing Filter}
+\todo[À faire]
 In this section, we compare the efficiency of QHT and QHT-queueing filter. For this, we use both an artificial dataset, as well as a real one, on various sliding window sizes.
-\todo[]
 
@@
 
-In this section, we now focus on the security on the queueing filter.
+As DDFs have numerous security applications, we now discuss the queuing construction from an adversarial standpoint.
 We consider an adversarial game in which the attacker wants to trigger false positives or false negatives over the sliding window.
-This has practical applications in several topics of security, including cache saturation or denial of service by forcing cache misses, or by making undetected fraudulent payments.
-\todo[source].
+One motivation for doing so is causing cache saturation or denial of service by forcing cache misses, triggering false alarms or crafting fradulent transactions without triggering fraud detection systems.
+\todo[source, sans doute le papier sur les adversarial bloom filters?].
 
 We first recall the definition of an adversarial game, adapted to our context.
-
 \begin{definition}
@@
  \end{definition}
+Variants of these games over a sliding window of size $w$ are immediate.
 
-This adversarial game can be trivially adapted for a false positive (resp. false negative) adversarial game over a sliding window of size $w$, hence we omit its formal definition.
+\subsection{False positive and false negative resistance}
 
-\subsection{First Approach on the Whole Sliding Window}
-We first define what an adversarial false positive resistance over a sliding window is, before giving its value for any queueing filter based on the subfilter's properties.
+\begin{definition}[Adversarial False Positive Resistance]
+	We say that a DDF $\mathcal F$ is $(p, n)$-\emph{resistant to adversarial false positives} if no polynomial-time probabilistic (PPT) adversary $\mathcal A$ can win the $n-$false positive adversarial game with probability more than $p$.
+\end{definition}
+Note that if $\mathcal F$ is $(p,n)$-resistant, then it is $(p, m)$-resistant for all $m < n$.
 
-\begin{definition}{Adversarial False Positive Resistance}
-	Let $\mathcal F$ be a filter, let $E$ be a stream.
-We say that $\mathcal F$ is $(p, n)$-resistant to adversarial false positives if no polynomial-time probabilistic (PPT) adversary $\mathcal A$ can win the $n-$false positive adversarial game with probability more than $p$.
-\end{definition}
+We define similarly the notion of being \emph{resistant to adversarial false negatives}. Finally, both definitions also make sense in a sliding window context.
 
-Note that if $\mathcal F$ is $(p,n)$-resistant, it is as well $(p, m)$-resistant for any $m < n$.
-
-This definition can be trivially adapted for false negative resistance, and for resistance over a sliding window.
+\subsection{Bound on false positive resistance}
 
 \begin{theorem}
-	Let $\mathcal Q$ be a filter of $L$ subfilters $\mathcal F_i$, with $c$ insertions maximum per subfilter, let $E$ be a stream, let $w$ be a sliding window size.
+	Let $\mathcal Q$ be a filter of $L$ subfilters $\mathcal F_i$, with $c$ insertions maximum per subfilter, let $w$ be a sliding window.
 
@@
 \begin{proof}
-	Let us first assume that $cL \leq w$. This implies that information-theory wise, the elements remembered by each subfilter belong to the sliding window.
+	If $cL \leq w$, then information-theoretically the subfilters only have information on elements in the sliding window.
+	The probability of false positive for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$, which is strictly increasing with $\FP_{\mathcal F,c}$.
+Hence, the optimal solution is reached by to maximising the probability of false positive in each subfilter $\mathcal F_i$.
+By hypothesis the latter is bounded above by $p$ after $c$ insertions.
 
-	The probability of false positive for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$.
-As we see, the probability of false positive in $\mathcal Q$ over the sliding window $w$ is strictly increasing with the probability of false positive in any subfilter $\mathcal F_i$.
-Hence, the optimal solution is to maximise the probability of false positive in each subfilter $\mathcal F_i$, which by hypothesis is bounded above by $p$ after $c$ insertions.
-
-	On the other hand, if $cL > w$, it means that the oldest filter remembers elements that do not belong to the sliding window anymore.
+	On the other hand, if $cL > w$ then oldest filter holds information about elements that are not in the sliding window anymore.
 Hence, a strategy for the attacker trying to trigger a false positive on $e^\star$ could be to make it so these oldest elements are all equal to $e^\star$.
@@
 
-	After $w$ insertions, it is quite likely that the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ probability of success.
-
-	Note that if, for some reason, the last subfilter answers $\DUPLICATE$ with probability less than $p$, then the default policy the same reasoning as for when $cL \leq w$ still applies, hence the lower bound (which is, in this case, an equality).
+	After $w$ insertions, the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ probability of success.
+If, for some reason, the last subfilter answers $\DUPLICATE$ with probability less than $p$, then the same reasoning as for when $cL \leq w$ still applies, hence we get the correspondig lower bound (which is, in this case, an equality).
 \end{proof}
 
-\subsection{Adversarial False Negative}
+\subsection{Bounds on false negative resistance}
 
 \begin{theorem}
-	Let $\mathcal Q$ be a filter of $L$ subfilters of kind $\mathcal F$, with $c$ insertions maximum per subfilter, let $E$ be a stream, let $w$ be a sliding window size.
+	Let $\mathcal Q$ be a filter of $L$ subfilters of kind $\mathcal F$, with $c$ insertions maximum per subfilter, and let $w$ be a sliding window.
 

### 2020-03-20 qhtv2.tex
Various typo

@@
 \begin{definition}[Duplicate detection problem, DDP] Given a stream $E_n = (e_1, e_2, \dotsc, e_n)$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$.\footnote{
-	We do not consider here \emph{fuzzy} detection approaches\cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient} that study situations where $e^\star$ belongs to $E_n$ when there exists a \enquote{similar enough} element in the stream.
+	We do not consider here \emph{fuzzy} detection approaches \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient} that study situations where $e^\star$ belongs to $E_n$ when there exists a \enquote{similar enough} element in the stream.
 }
-	At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n | (e^\star)$ where | denotes the concatenation . 
+	At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n \mid e^\star$ where $\mid$ denotes concatenation. 
 \end{definition}
@@
 
-Let us consider a duplicate $e^\star \wdup E$.
+Let us consider $e^\star \wdup E$.
 If, in the sliding window, all duplicates only happened at least $(c-\frac12)L$ epochs ago (which happens with probability $\left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}$), we know that no duplicates happened in any subfilter's sliding window.
@@
 \subsection{Subfilter selection}
+\label{sec:optimal_ddf}
 When comparing different DDFs, one interesting metric in our context is how fast
@@
 
-	On the other hand, a duplicate element $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
+	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
 Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
@@
 \section{Experiments and Benchmarks}
+
 This section provides details and additional information on the benchmarking experiments run to validate the above analysis. All code is accessible online and will be disclosed after peer review.
@@
 We now use the queuing construction on the DDFs discussed previously.
-In Section~\ref{sub:optimal_ddf} we suggested the heuristic that the DDFs with the least saturation rate in the DDP would yield the best (error-wise) queueing filter for the sliding window DDP.
+In Section~\ref{sec:optimal_ddf} we suggested the heuristic that the DDFs with the least saturation rate in the DDP would yield the best (error-wise) queueing filter for the sliding window DDP.
 This heuristic is supported by results, summarized in Figure~\ref{tab:comparing_queueing}.
@@
 
-	If $cL > w$, the adversary has a probability of success of at least $(1-(1-p)^L$.
+	If $cL > w$, the adversary has a probability of success of at least $1-(1-p)^L$.
 \end{theorem}
@@
 	For this, let us consider the adversarial game against the subfilter $\mathcal F$: after $c$ insertions from an aversarial stream $E_c$, $\mathcal A$ choses a duplicate $e^\star$ which will be a false negative with proability $p$.
-	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c | E_c | \dotsc | E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a probability of success for $\mathcal A$ of $p^L$.
+	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c \mid E_c \mid \cdots \mid E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a probability of success for $\mathcal A$ of $p^L$.
 

### 2020-03-20 qhtv2.tex
+Contributions

@@
 \subsection{Contributions}
+We introduce a variant of the DDP over a sliding window, which enables the design of filters that avoids the saturation issue identified in \cite{10.1145/3297280.3297335} (Section~\ref{sec:filsat}).
+We provide explicit upper bounds, and corresponding constructions, for the amount of memory necessary to solve this problem (Section~\ref{sub:opt_solutions}), then introduce the \emph{queuing construction} as a generic approach to build windowed-DDP-friendly filters from existing filters (Sections~\ref{sec:queue} and \ref{sec:subfilter-select}).
+We analyse the queuing construction's error rates and parameters (Section~\ref{sec:optimising}), which are confirmed by benchmarks (Section~\ref{sec:bench}).
+Finally, we provide an analysis of the queueing construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).
 
-\subsection{Related Work}\label{sub:related}
+\subsection{Related work}\label{sub:related}
 \todo[continuer]
@@
 
-\subsection{Filter Saturation and Sliding Windows}
+\subsection{Filter Saturation and Sliding Windows}\label{sec:filsat}
 Unfortunately, efficient duplicate detection over an infinite stream has been identified as an unsolvable problem \cite{10.1145/3297280.3297335}.
@@
 
-\section{Queuing filters}
+\section{Queuing filters}\label{sec:queue}
 In this section, we describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
@@
 \section{Optimising queuing filters}
+\label{sec:optimising}
 \todo[À vérifier je suis pas convaincu encore]
@@
 
-\section{Application to existing DDFs}
+\section{Queuing filters from existing DDFs}\label{sec:subfilter-select}
 Our queuing construction relies on a choice of subfilters. A first observation 
@@
 
-\section{Experiments and Benchmarks}
+\section{Experiments and Benchmarks}\label{sec:bench}
 
@@
 \section{Adversarial Resistance}
+\label{sec:adversarial}
 

### 2020-03-20 qhtv2.tex
+Appendix

@@
 %% Appendix
-%\appendix
+\appendix
+
+\section{Effects of the finite simulation}
+Theoretical results about the queuing construction apply in principe to an infinite stream.
+However, simulations are necessarily finite, and for very large windows (that are approximately the same size as the whole stream) this causes interesting artifacts in the error rates.
+Note that these effects have very little impact on practical implementations of queuing filters, since almost all use cases assume a window size much smaller than the stream (or, equivalently, a very large stream).
+Nevertheless we illustrate the effect of the finite simulation and the parameters affecting it, if only to motivate a further analytical study of this phenomenon.
+
+To accentuate this effect we use the Pearson $\phi$ coefficient that measures statistical correlation (between -1 and +1) between the filter's predictions and the expected answers.
+A coefficient of $1$ corresponds to an always correct filter, a coefficient of $-1$ to an always incorrect one, and a coefficient of $0$ means the filter produces answers that are statistically independent from the correct ones.
+
+Figure~\ref{fig:strangess} measures $\phi$ as a function of $w$, for different stream sizes $N$. A visible peak in $\phi$ can be found around $w\approx N$.
+
+\begin{figure*}[!ht]
+	\centering
+	\input{graphs/stream_size.tex}
+	\caption{Pearson $\phi$ for queuing SQF ($L = 10$, $M = 10^5$, $|\Gamma| = 2^16$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
+\end{figure*}
+
+As can be seen on this simulation, there is only disagreement around $w \approx N/L$, and increasing $N$ results in a later and smaller peak.
+
+It is also possible to run simulations for different alphabet sizes $\Gamma$, which shows that the peak's position increases with $|\Gamma|$, although the relationship is not obvious to quantify.
 

### 2020-03-20 qhtv2.tex
fixes

--- 2020-03-20 qhtv2.tex
@@
 One motivation for doing so is causing cache saturation or denial of service by forcing cache misses, triggering false alarms or crafting fradulent transactions without triggering fraud detection systems.
-\todo[source, sans doute le papier sur les adversarial bloom filters?].
+
+In order to create a realistic adversary model, we assume like in \cite{DBLP:journals/corr/abs-1709-08920} that the adversary does not have access to the internal memory representation of the filter.
+Nonetheless, after every insertion she knows whether the inserted element was detected as a duplicate or not.
 
@@
 	Furthermore, for $q$ the lower bound on the probability of false positive $\FP_{\mathcal F,c}$ for a given stream, if $w \leq (L-1)c$ then $\mathcal Q$ is $(\min(1 - q, p)^{L-1}p, w)$-resistant to false negative attacks on the sliding window $w$.
-	On the other hand if $w > (L-1)c$ then $\mathcal Q$ is  $(\min(1 - q, p)^{L}, w)$-resistant to false negative attacks on the sliding window $w$.
+	On the other hand if $w > (L-1)c$ then $\mathcal Q$ is  $(\max(1 - q, p)^{L}, w)$-resistant to false negative attacks on the sliding window $w$.
 \end{theorem}
@@
 	When $e_{Lc+1}$ is inserted, all elements $(e_1, \dotsc, e_{c-1}, e^\star)$ are dropped as the oldest subfilter is popped.
-Hence, in this context $e^\star$ is not in any subfilter anymore, so by adapting the previous analysis, $\mathcal A$ can get a false negative with probability at most $\min(1 - q, p)^{L}$.
+Hence, in this context $e^\star$ is not in any subfilter anymore, so by adapting the previous analysis, $\mathcal A$ can get a false negative with probability at most $\max(1 - q, p)^{L}$.
 \end{proof}

### 2020-03-20 qhtv2.tex
Fix FPR + Formule pour L

--- 2020-03-20 qhtv2.tex
@@
 	\begin{equation}
-	\FPR_{\mathcal Q, cn}^w = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell}).
+	\FPR_{\mathcal Q, cn}^w = 1 -  \frac{(1 - \FP_{\mathcal F, c})^{L-1}}{c}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell}).
 	\end{equation}
@@
 	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
-	& = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
+	& = 1 - \frac1c(1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
 \end{align*}
@@
 
-\subsection{Parameter Tuning}
-\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]
-
-The parameters of a queueing filter are: the parameters of the subfilter, the number $L$ of subfilters and the number $c$ of insertions per subfilter.
-
-However, the goal here is not to modify the parameters of the underlying subfilter, but rather to tune the queueing filter so the subfilter can perform as well as possible.
-Hence, the queueing filter's parameters are only $c$ and $L$.
-
-Furthermore, we have the relation $cL \approx w$, so there is only one free parameter.
-
-As such, an optimal parameter tuning would be to set $L$ so that the error rate (defined as the sum of the FPR and FNR) would be minimal.
-Nonetheless, given the complicated nature of the FPR and FNR formulae, deriving an optimal $L$ is out of reach.
-
-We have observed in Section~\ref{sub:fnr} that the FN is positively correlated with
-$\left(1-\FP_{\mathcal F,c}\right)^L$, however the FP is negatively correlated with the same value.
-As such, decreasing the probability of false positive leads to an increase in the probability of false negatives.
-
-%Hence, the (heuristic) optimal solution is to set $L = \sqrt w$.
+\subsection{How many subfilters?}
+The parameter $L$ determines how many subfilters appear in the queueing construction. Summing up the false positive and false negative rates, we have a total error rate 
+\begin{equation}
+	\operatorname{ER}_{\mathcal Q, cn}^{w}
+	= 1 - \alpha \beta^{L-1} + \alpha' \beta'^{L-1}
+\end{equation}
+where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
+$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ only depend on $c$ and the choice of subfilter type $\mathcal F$.
+Differentiating with respect to $L$ and equating to zero gives an optimum
+\begin{equation*}
+	L = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
+\end{equation*}
 
@@
 A very interesting observation is that $Lw$ approaches the size of the stream, there is a drop in the error.
-This is an artifact due to the finite size of our simulations; the stream should be considered infinite, and this drop disappears as the simulation is run for longer.
+This is an artifact due to the finite size of our simulations; the stream should be considered infinite, and this drop disappears as the simulation is run for longer (see Appendix~\ref{app:finite}).
 This effect also alters the error rates for smaller window sizes, albeit much less, and we expect that filter designers care primarily about the small window regime.
@@
 \todo[À faire]
-In this section, we make experiments on the influence of $L$ on the error rate of the queueing filter.
 
@@
 
-\section{Effects of the finite simulation}
+\section{Effects of the simulation's finiteness}
+\label{app:finite}
+
 Theoretical results about the queuing construction apply in principe to an infinite stream.
@@
 	\input{graphs/stream_size.tex}
-	\caption{Pearson $\phi$ for queuing SQF ($L = 10$, $M = 10^5$, $|\Gamma| = 2^16$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
+	\caption{Pearson $\phi$ for queuing SQF ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
 \end{figure*}

### 2020-03-20 qhtv2.tex
Améliorations variées

@@
 
-	When analysed in the limit of an infinite stream, error rates of duplicate filters turn out to be heavily constrained; as a consequence they appear to provide no advantage, asymptotically, over a random yes-no coin toss \cite{10.1145/3297280.3297335}.
+	When analysed in the limit of an infinite stream, error rates of duplicate filters turn out to be heavily constrained; as a consequence they appear to provide no advantage, asymptotically, over a random biased coin toss \cite{10.1145/3297280.3297335}.
 
@@
 
-Finally, it is clear that the input distribution plays a central role regarding how efficiently the DDP can be solved.
+On a side note, it is clear that the input distribution plays a central role regarding how efficiently the DDP can be solved.
 For instance, some deterministic streams may be expressed very compactly (such as the output of a PRNG with known seed) making the DDP relatively easy.
-Information-theoretically, if the source has $U$ bits of entropy then the situation is equivalent to having an $U$-bit, uniformly distributed input.\footnote{Another motivation for this is pragmatic: in many applications, duplicate detection is performed on \emph{hashes} of actual data rather than on the data itself, and we may assume that hashes are uniformly distributed.}
+Information-theoretically, if the source has $U$ bits of entropy then the situation is equivalent to having an $U$-bit, uniformly distributed input.
 
-\todo[continuer].
+Several algorithms have been proposed to solve the DDP, but
+they \emph{all} face a phenomenon called \enquote{saturation} on large data streams \cite{10.1145/3297280.3297335}.
+Essentially, when saturation happens the algorithm performs no better than at random.
+This is problematic on two grounds: it makes the comparison of several algorithms difficult (since they all asymptotically behave in that fashion), and the unavoidable saturation ruins any particular design's merits.
 
 \subsection{Contributions}
-We introduce a variant of the DDP over a sliding window, which enables the design of filters that avoids the saturation issue identified in \cite{10.1145/3297280.3297335} (Section~\ref{sec:filsat}).
-We provide explicit upper bounds, and corresponding constructions, for the amount of memory necessary to solve this problem (Section~\ref{sub:opt_solutions}), then introduce the \emph{queuing construction} as a generic approach to build windowed-DDP-friendly filters from existing filters (Sections~\ref{sec:queue} and \ref{sec:subfilter-select}).
+To circumvent the aforementioned limitations, we introduce a variant of the DDP \emph{over a sliding window}, which enables the design of filters that avoids the saturation issue altogether (Section~\ref{sec:dudefisa}).
+We provide explicit upper bounds for the amount of memory necessary to solve this problem, and corresponding constructions.
+
+We then introduce the \emph{queuing construction}, a generic approach to build windowed-DDP-friendly filters from existing filters (Sections~\ref{sec:queue} and \ref{sec:subfilter-select}).
 We analyse the queuing construction's error rates and parameters (Section~\ref{sec:optimising}), which are confirmed by benchmarks (Section~\ref{sec:bench}).
-Finally, we provide an analysis of the queueing construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).
+
+Finally, we provide an analysis of the queuing construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).
 
 \subsection{Related work}\label{sub:related}
+\cite{10.1145/1060745.1060753} studies a structure aking to the counting Bloom filter, in a \enquote{landmark-} and \enquote{jumping-} sliding window setting.
+Despite the name, these are different from the sliding window discussed in this paper.
+
+Closer to our work, the idea of using subfilters may be found in the A2 filter's design \cite{Yoo10}.
+The A2 is built from two Bloom filters, a situation which we generalise and analyse generically in this paper.
+
 \todo[continuer]
-In \cite{10.1145/1060745.1060753}, the authors explore the behaviour of a structure very close to the counting Bloom filter in some specific sliding window context, that they call landmark- and jumping sliding windows.
-However, they do not deal with the problematic of a sliding window where at each new element added to the sliding window, another element is removed.
-Closer to our work, the idea of using subfilters, tossing old ones has already been explored in the A2 filter \cite{Yoo10}.
-However, the author only considered a small portion of the problem, as they only discussed about using two subfilters, and only Bloom Filters acting as subfilters.
 
-In this work, we provide a full abstraction of the mechanism, allowing us to use many other DDF than Bloom Filters. We also provide a generalised analysis of the error rates.
 \subsection{Organisation}
@@
 \section{Duplicate Detection and Filter Saturation}
+\label{sec:dudefisa}
 \subsection{Notations and Initial Problem Statement}
@@
 \begin{proof}
-	Here again we explicitely construct the filters that achieve the theorem's bounds.
+	Here again we explicitly construct the filters that attain the theorem's bounds.
 
@@
 
-\subsection{The queueing construction}
+\subsection{The queuing construction}
 
@@
 
-When inserting a new element in the queueing filter, it is inserted in the topmost subfilter of the queue.
+When inserting a new element in the queuing filter, it is inserted in the topmost subfilter of the queue.
 After $c$ insertions, a new empty filter is added to the queue, and the oldest subfilter is popped and erased.
@@
 \paragraph{Pseudocode.}
-We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in Algorithm~\ref{alg:queueing}.
+We give a brief pseudocode for the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in Algorithm~\ref{alg:queuing}.
 We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
-The \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.
+Here \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first position.\footnote{Two standard ways to implement this are a double-ended queue (deque) and a ring buffer.}
 
 \begin{algorithm}[]
-	\caption{Queueing Filter Setup, Lookup and Insert}\label{alg:queueing}
+	\caption{Queuing Filter Setup, Lookup and Insert}\label{alg:queuing}
 
@@
 \subsection{Error rate analysis}
-The queueing filter's properties can be derived from the subfilters'.
+The queuing filter's properties can be derived from the subfilters'.
 False positive and false negative rates are of particular interest.
@@
 \label{sec:optimising}
-\todo[À vérifier je suis pas convaincu encore]
+
+The parameter $L$ determines how many subfilters appear in the queuing construction. Summing up the false positive and false negative rates, we have a total error rate 
+\begin{equation}
+	\operatorname{ER}_{\mathcal Q, cn}^{w}
+	= 1 - \alpha \beta^{L-1} + \alpha' \beta'^{L-1}
+\end{equation}
+where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
+$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ only depend on $c$ and the choice of subfilter type $\mathcal F$.
+Differentiating with respect to $L$ and equating to zero gives an optimum
+\begin{equation*}
+	L = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
+\end{equation*}
+
+\todo[À vérifier la suite je suis pas convaincu encore]
 \begin{theorem}
-	In first approximation, a low value of $L$ for constant value $cL$ leads to a higher false negative probability for the queueing filter.
+	In first approximation, a low value of $L$ for constant value $cL$ leads to a higher false negative probability for the queuing filter.
 \end{theorem}
@@
 \begin{proof}
-As a matter of fact, on average the queueing filter consists of $L-1$ subfilters with $c$ insertions, and one subfilter with $\frac c2$ insertions.
-As such, we can say that the queueing filter is a representation of the last $(c-\frac12) L$ last elements.
+As a matter of fact, on average the queuing filter consists of $L-1$ subfilters with $c$ insertions, and one subfilter with $\frac c2$ insertions.
+As such, we can say that the queuing filter is a representation of the last $(c-\frac12) L$ last elements.
 
@@
 
-\section{Queuing filters from existing DDFs}\label{sec:subfilter-select}
+\section{Queuing filters from existing DDFs}
+\label{sec:subfilter-select}
+\label{sec:optimal_ddf}
 Our queuing construction relies on a choice of subfilters. A first observation 
@@
 It remains to decide which subfilter construction to choose. 
-
-\subsection{Subfilter selection}
-\label{sec:optimal_ddf}
 When comparing different DDFs, one interesting metric in our context is how fast
-such filters saturate: indeed, in the original DDP setting, all filters eventually saturate \cite{10.1145/3297280.3297335}.
+such filters saturate: indeed, in the original DDP setting, all filters eventually saturate \cite{10.1145/3297280.3297335}, but they may reach that state more or less quickly.
+The following result gives the behaviour of a perfect filter regarding this question:
 
@@
 
-In the experiments we use QHT for the benchmarking of the queueing construction.
-
-\subsection{How many subfilters?}
-The parameter $L$ determines how many subfilters appear in the queueing construction. Summing up the false positive and false negative rates, we have a total error rate 
-\begin{equation}
-	\operatorname{ER}_{\mathcal Q, cn}^{w}
-	= 1 - \alpha \beta^{L-1} + \alpha' \beta'^{L-1}
-\end{equation}
-where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
-$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ only depend on $c$ and the choice of subfilter type $\mathcal F$.
-Differentiating with respect to $L$ and equating to zero gives an optimum
-\begin{equation*}
-	L = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
-\end{equation*}
+%In the experiments we use QHT for the benchmarking of the queuing construction.
 
@@
 We now use the queuing construction on the DDFs discussed previously.
-In Section~\ref{sec:optimal_ddf} we suggested the heuristic that the DDFs with the least saturation rate in the DDP would yield the best (error-wise) queueing filter for the sliding window DDP.
-This heuristic is supported by results, summarized in Figure~\ref{tab:comparing_queueing}.
+In Section~\ref{sec:optimal_ddf} we suggested the heuristic that the DDFs with the least saturation rate in the DDP would yield the best (error-wise) queuing filter for the sliding window DDP.
+This heuristic is supported by results, summarized in Figure~\ref{tab:comparing_queuing}.
 For this benchmark we used the following parameters: uniform stream from an alphabet of size $|\Gamma| = 2^{18}$, memory size $M=100,000$ bits, sliding window of size $w = 10,000$, and we measure the error rate (sum of $\FNR^w$ and $\FPR^w$).
@@
 	\input{graphs/compare_queues.tex}
-	\caption{Error rate (times 100) of various queueing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{18}$.}\label{tab:comparing_queueing}
+	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{18}$.}\label{tab:comparing_queuing}
 \end{figure}
@@
 %	\end{tabular}
-%	\caption{Error rate (times 100) of various queueing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{16}$.
-For each sliding window, the best performance is written in bold.}\label{tab:comparing_queueing}
+%	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{16}$.
+For each sliding window, the best performance is written in bold.}\label{tab:comparing_queuing}
 %\end{table}
 
-\subsection{How many subfilters?}\label{sub:L_bench}
+\subsection{The number of subfilters}\label{sub:L_bench}
 \todo[À faire]
 
-\subsection{Comparison of QHT and QHT-Queueing Filter}
+\subsection{Comparison of QHT and QHT-Queuing Filter}
 \todo[À faire]
-In this section, we compare the efficiency of QHT and QHT-queueing filter. For this, we use both an artificial dataset, as well as a real one, on various sliding window sizes.
+In this section, we compare the efficiency of QHT and QHT-queuing filter. For this, we use both an artificial dataset, as well as a real one, on various sliding window sizes.
 

### 2020-03-21 qhtv2.tex
Clarifications section 4

--- 2020-03-20 qhtv2.tex
@@
 \label{sec:optimising}
-
-The parameter $L$ determines how many subfilters appear in the queuing construction. Summing up the false positive and false negative rates, we have a total error rate 
+Let us relax, temporarily, the a priori constraint that $w = cL$.
+The parameter $L$ determines how many subfilters appear in the queuing construction.
+Summing up the false positive and false negative rates, we have a total error rate
 \begin{equation}
@@
 \begin{equation*}
-	L = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
+	L_{c, \mathcal F} = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
 \end{equation*} 
+Thus for a given $c$ and choice of subfilter $\mathcal F$ we get an optimal value of $L = L_{c, \mathcal F}$,
+and we set, \emph{a posteriori}, $w \gets cL$.
+
+If instead $w$ is a given value, solving $w = c L_{c, \mathcal F}$ analytically may be challenging.
+A practical solution is to interpolate between explicitly computed values $cL_{c, \mathcal F}$ to find the 
+closest match for the target $w$.
 

### 2020-03-22 qhtv2.tex
stuff

--- 2020-03-21 qhtv2.tex
@@
 where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
-$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ only depend on $c$ and the choice of subfilter type $\mathcal F$.
-Differentiating with respect to $L$ and equating to zero gives an optimum
-\begin{equation*}
-	L = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
-\end{equation*}
+$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ depend on $w$, $c$ and the choice of subfilter type $\mathcal F$.
 
-\todo[À vérifier la suite je suis pas convaincu encore]
-\begin{theorem}
-	In first approximation, a low value of $L$ for constant value $cL$ leads to a higher false negative probability for the queuing filter.
-\end{theorem}
+Because $u_\eta = p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$, differentiating with respect to $L$, knowing that $w = Lc$, and equating the derivative to $0$, one can find the optimal value for $L$ by solving for $x$, which has been obtained via Mathematica:
 
-\begin{proof}
-As a matter of fact, on average the queuing filter consists of $L-1$ subfilters with $c$ insertions, and one subfilter with $\frac c2$ insertions.
+%\begin{equation*}
+\begin{align*}
+&-\alpha \beta^{-1+x} \log(\beta)  \\ 
+&+ \left(\beta + \FN_{\mathcal F, c} (-1+x)\right)^{-2+x} x^{-x} \left[\vphantom{\left(\FN^{\FN}\right)}\right. \\
+&\quad
+	-\alpha \beta + \FN_{\mathcal F, c} \left(-\beta (-2+x)+ \FN_{\mathcal F, c} (-1+x)\right) \\
+&\quad	+ \left(\alpha+ \FN_{\mathcal F, c} (-1+x)\right) \\
+& \quad \quad \times\left(\beta + \FN_{\mathcal F, c} (-1+x)\right) \left(\log\left(\beta + \FN_{\mathcal F, c} (-1+x)\right)-\log(x)\right) \\
+&\left.\vphantom{\left(\FN^{\FN}\right)}\right] = 0
+\end{align*}
+
+If solving the equation for individual cases is 
+%\end{equation*}
+
+%Differentiating with respect to $L$ and equating to zero gives an optimum
+%\begin{equation*}
+%	L_{c, \mathcal F} = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
+%\end{equation*} 
+%Thus for a given $c$ and choice of subfilter $\mathcal F$ we get an optimal value of $L = L_{c, \mathcal F}$,
+%and we set, \emph{a posteriori}, $w \gets cL$.
+%
+%If instead $w$ is a given value, solving $w = c L_{c, \mathcal F}$ analytically may be challenging.
+%A practical solution is to interpolate between explicitly computed values $cL_{c, \mathcal F}$ to find the 
+%closest match for the target $w$.
+%
+%\todo[À vérifier la suite je suis pas convaincu encore]
+%\begin{theorem}
+%	In first approximation, a low value of $L$ for constant value $cL$ leads to a higher false negative probability for the queuing filter.
+%\end{theorem}
+%
+%\begin{proof}
+%As a matter of fact, on average the queuing filter consists of $L-1$ subfilters with $c$ insertions, and one subfilter with $\frac c2$ insertions.
 As such, we can say that the queuing filter is a representation of the last $(c-\frac12) L$ last elements.
-
-Let us consider $e^\star \wdup E$.
+%
+%Let us consider $e^\star \wdup E$.
 If, in the sliding window, all duplicates only happened at least $(c-\frac12)L$ epochs ago (which happens with probability $\left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}$), we know that no duplicates happened in any subfilter's sliding window.
@@
 Given that $cL \approx w$ which is a constant, we get that the probability of false positive mostly varies, in this case, with $\left(1-\FP_{\mathcal F,c}\right)^L$.
-
-Hence, the lower $L$ is, the higher the probability of false negative will be.
-
-The approximations made in this proof are backed by experimental results.
-\end{proof}
+%
+%Hence, the lower $L$ is, the higher the probability of false negative will be.
+%
+%The approximations made in this proof are backed by experimental results.
+%\end{proof}
 
@@
 This results in around 8\% duplicates (up to statistical fluctuations) amongst the 150 000 000 elements in the longest stream used.
-As a comparison, we also run the same benchmark against a stream obtained from crawling data, the same one as \cite{10.1145/3297280.3297335}, a real-world source which is highly non-uniform --- note that in this case, our lower bound on the error rate does not apply, owing to the stream being compressible.
+%As a comparison, we also run the same benchmark against a stream obtained from crawling data, the same one as \cite{10.1145/3297280.3297335}, a real-world source which is highly non-uniform --- note that in this case, our lower bound on the error rate does not apply, owing to the stream being compressible.
 In that stream, around 10\% were duplicates amongst the 150 000 000 elements.
@@
 
-\begin{figure*}[!ht]
+%\begin{figure*}[!ht]
+%	\begin{tikzpicture}
+%	\begin{groupplot}[
+%	group style = {
+%		group size = 2 by 1,
+%		horizontal sep = 35pt,
+%	},
+%	axis lines = left,
+%	ylabel near ticks,
+%	width = 0.4\textwidth,
+%	height = 0.27\textwidth,
+%	]
+%	\input{er_n_artificial}
+%	\input{er_n_real}
+%	%\input{10e6_sum_zipf}
+%	\end{groupplot}
+%    \path (top)--(bot) coordinate[midway] (group center);
+%%	\node[above,rotate=90] at (group center -| current bounding box.west) {Error rate (\%)};
+%	\node[right=1em,inner sep=0pt] at(group center -| current bounding box.east) {\pgfplotslegendfromname{legend_n}};
+%	\end{tikzpicture}
+%
+%%	\input{er_n_artificial}
+%	\caption{Error rate (times 100) of DDFs of 1Mb, over a real and artificial stream, depending on the size of the stream, without any sliding window.
+Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
+%\end{figure*}
+
+\begin{figure}
 	\begin{tikzpicture}
-	\begin{groupplot}[
-	group style = {
-		group size = 2 by 1,
-		horizontal sep = 35pt,
-	},
-	axis lines = left,
-	ylabel near ticks,
-	width = 0.4\textwidth,
-	height = 0.27\textwidth,
-	]
 	\input{er_n_artificial}
-	\input{er_n_real}
-	%\input{10e6_sum_zipf}
-	\end{groupplot}
-    \path (top)--(bot) coordinate[midway] (group center);
-%	\node[above,rotate=90] at (group center -| current bounding box.west) {Error rate (\%)};
-	\node[right=1em,inner sep=0pt] at(group center -| current bounding box.east) {\pgfplotslegendfromname{legend_n}};
 	\end{tikzpicture}
-
-%	\input{er_n_artificial}
-	\caption{Error rate (times 100) of DDFs of 1Mb, over a real and artificial stream, depending on the size of the stream, without any sliding window.
+	\caption{Error rate (times 100) of DDFs of 1Mb, over an artificial stream, depending on the size of the stream, without any sliding window.
 Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
-\end{figure*}
+\end{figure}
 
@@
 	\input{graphs/compare_queues.tex}
-	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{18}$.}\label{tab:comparing_queuing}
+	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
 \end{figure}
@@
 \subsection{The number of subfilters}\label{sub:L_bench}
-\todo[À faire]
+We now compare the efficiency of the queueing filter, depending on the number of subfilters $L$.
+For this, we used a queueing QQHTD, on an artificial dataset of alphabet size $\Gamma = 2^{16}$, with 100 000 elements in the stream, on various sliding window sizes.
 
+Results are displayed in Figure~\ref{fig:bench_l}.
+
+\begin{figure}
+	\input{graphs/bench_l.tex}
+	\caption{Evolution of the error rate of a queueing QHT depending on the $L$ value, for various sliding window sizes, with $M=100000$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
+\end{figure}
+
+We observe that the optimal value for $L$ does indeed depend on the desired sliding window.
+However, other experiments on alphabets of other sizes yield very similar results, hence validating the observation made in Section~\ref{sec:optimising} that the optimal number of subfilters does not depends on the alphabet (in first approximation).
 \subsection{Comparison of QHT and QHT-Queuing Filter}
 \todo[À faire]
-In this section, we compare the efficiency of QHT and QHT-queuing filter. For this, we use both an artificial dataset, as well as a real one, on various sliding window sizes.
+In this section, we compare the efficiency of QHT and QHT-queuing filter. For this, we use an artificial dataset on various sliding window sizes.
 

### 2020-03-24 qhtv2.tex
add "improvement" graph + fixes in optimal solution

@@
 \begin{theorem}
-	For $M \geq w (\log_2(w) + 1) \log_2(|\Gamma|)$, the sliding window DDP can be solved exactly (with no errors) in constant time.
+	For $M \geq w (2\log_2(w) + \log_2(|\Gamma|))$, the sliding window DDP can be solved exactly (with no errors) in constant time.
 \end{theorem}
@@
 
-	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w \log_2 |\Gamma| \log_2 w$ (as the dictionary cannot have more than $w$ keys as the same time, and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
-Thus at most $w (\log_2(w) + 1) \log_2(|\Gamma|)$ bits are necessary for this DDF to work.
+	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
+Thus a requirement of $w (2\log_2(w) + \log_2(|\Gamma|))$ bits for this DDF to work.
 
-	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact tract of how many times each element was present in the sliding window.
+	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element was present in the sliding window.
 \end{proof}
@@
 Note that this solution has a time complexity of $O(w)$.
-Using an additional dictionary, as in the previous proof, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, using $5w\log_2 w$ bits of memory.
+Using an additional dictionary, as in the previous proof, but with keys of size $2\log_2(w)$, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, using $w \cdot 2\log_2 w + w \cdot (2\log_2(w) + \log_2(w)) = 5w\log_2 w$ bits of memory.
 \end{proof}
@@
 	\input{graphs/compare_queues.tex}
-	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
+	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=10^5$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
 \end{figure}
@@
 	\input{graphs/bench_l.tex}
-	\caption{Evolution of the error rate of a queueing QHT depending on the $L$ value, for various sliding window sizes, with $M=100000$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
+	\caption{Evolution of the error rate of a queueing QHT depending on the $L$ value, for various sliding window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
 \end{figure}
@@
 In this section, we compare the efficiency of QHT and QHT-queuing filter. For this, we use an artificial dataset on various sliding window sizes.
+
+\begin{figure}
+	\input{graphs/improvement.tex}
+	\caption{Comparing performances of various filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:improvement}
+\end{figure}
 
@@
 
-Theoretical results about the queuing construction apply in principe to an infinite stream.
-However, simulations are necessarily finite, and for very large windows (that are approximately the same size as the whole stream) this causes interesting artifacts in the error rates.
+Theoretical results about the queuing construction apply in principle to an infinite stream.
+However, simulations are necessarily finite, and for very large windows (that are approximately the same size as the whole stream) this causes interesting artefacts in the error rates.
 Note that these effects have very little impact on practical implementations of queuing filters, since almost all use cases assume a window size much smaller than the stream (or, equivalently, a very large stream).
@@
 
-To accentuate this effect we use the Pearson $\phi$ coefficient that measures statistical correlation (between -1 and +1) between the filter's predictions and the expected answers.
-A coefficient of $1$ corresponds to an always correct filter, a coefficient of $-1$ to an always incorrect one, and a coefficient of $0$ means the filter produces answers that are statistically independent from the correct ones.
-
-Figure~\ref{fig:strangess} measures $\phi$ as a function of $w$, for different stream sizes $N$. A visible peak in $\phi$ can be found around $w\approx N$.
+Figure~\ref{fig:strangess} measures the error rate as a function of $w$, for different stream sizes $N$.
+A visible decrease in $ER$ can be found around $w\approx N$.
+While we do not have any explanation for the difference in the peaks sizes and exact location, we give the hypothesis that it is related to the choice of $|\Gamma|$.
 
@@
 	\centering
-	\input{graphs/stream_size.tex}
-	\caption{Pearson $\phi$ for queuing SQF ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
+	\input{graphs/stream_size_qht.tex}
+	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
 \end{figure*}

### 2020-03-26 qhtv2.tex
fixes on optimal solution

@@
 \begin{theorem}
-	For $M \geq w (2\log_2(w) + \log_2(|\Gamma|))$, the sliding window DDP can be solved exactly (with no errors) in constant time.
+	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the sliding window DDP can be solved exactly (with no errors) in constant time.
 \end{theorem}
@@
 	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
-Thus a requirement of $w (2\log_2(w) + \log_2(|\Gamma|))$ bits for this DDF to work.
+Thus a requirement of $w (\log_2(w) + 2\log_2(|\Gamma|))$ bits for this DDF to work.
 
@@
 \end{proof}
-The dependence on $\log_2 |\Gamma|$ can be droped, at the cost of allowing 
+The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing 
 errors:
@@
 
-When $\log_2|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory.
+When $\log_2|\Gamma| > 5 \log_2 w$ this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory, at the cost of a minimal error.
+When $\log_2|\Gamma| > 2 \log_2 w$, it outperforms the exact solution described sooner in terms of memory.
 

### 2020-03-26 qhtv2.tex
wip

@@
 
-We begin with the following, ideal problem: 
-\begin{definition}[Duplicate detection problem, DDP] Given a stream $E_n = (e_1, e_2, \dotsc, e_n)$ and a \enquote{new} item $e^\star$, find whether $e^\star \in E_n$.\footnote{
-	We do not consider here \emph{fuzzy} detection approaches \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient} that study situations where $e^\star$ belongs to $E_n$ when there exists a \enquote{similar enough} element in the stream.
-}
+We study the following problem: 
+\begin{definition}[Duplicate detection problem on a sliding window, wDDP] Given a stream $E_n = (e_1, e_2, \dotsc, e_n)$, a sliding window size $w$ and a \enquote{new} item $e^\star$, find whether $e^\star$ is also present in the last $w$ elements of the stream, ie., whether $e^\star \in \{e_{n-w+1}, \dotsc, e_n\}$.
 At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n \mid e^\star$ where $\mid$ denotes concatenation. 
@@
 In practice, additional constraints exist that we can capture with the following definition:
-\begin{definition}[DDP with bounded memory]
-	At every time step $n$, given $e^{\star}$ and a current state (dependent on history) of at most $M$ bits, solve the DDP for $E_n$ and $e^{\star}$.
+\begin{definition}[wDDP with bounded memory]
+	At every time step $n$, given $e^{\star}$ and a current state (dependent on history) of at most $M$ bits, solve the wDDP for $E_n$ and $e^{\star}$.
 \end{definition}
@@
 As a result, we need a further relaxation of the DDP that allows for errors:
-\begin{definition}[Approximate DDP with bounded memory]
-	Solve the DDP using at most $M$ bits of memory, with at most $\epsilon < 1/2$ mispredictions.\footnote{Given a classifier with $\epsilon > 1/2$, we obtain a classifier with $\epsilon < 1/2$ by reversing its output.}
+\begin{definition}[Approximate wDDP with bounded memory]
+	Solve the wDDP using at most $M$ bits of memory, with at most $\epsilon < 1/2$ mispredictions.\footnote{Given a classifier with $\epsilon > 1/2$, we obtain a classifier with $\epsilon < 1/2$ by reversing its output.}
 \end{definition}
@@
 
-Several algorithms have been proposed to solve the DDP, but
-they \emph{all} face a phenomenon called \enquote{saturation} on large data streams \cite{10.1145/3297280.3297335}.
+We observe that in the litterature, there exists a similar problem, which we call DDP, and which does not make use of any sliding window.
+For instance, in DDP on a stream $E_n$ the problem is to find whether $e^\star \in E_n$.
+However, even though several algorithms have been proposed for this problem (\cite{Den06,10.1145/3297280.3297335,Dut13} and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}), they \emph{all} face a phenomenon called \enquote{saturation} on large data streams \cite{10.1145/3297280.3297335}.
+This phenomenon is not related to the filter, but rater to the nature of the DDP itself.
 Essentially, when saturation happens the algorithm performs no better than at random.
@@
 \subsection{Contributions}
-To circumvent the aforementioned limitations, we introduce a variant of the DDP \emph{over a sliding window}, which enables the design of filters that avoids the saturation issue altogether (Section~\ref{sec:dudefisa}).
+%To circumvent the aforementioned limitations, we introduce a variant of the DDP \emph{over a sliding window}, which enables the design of filters that avoids the saturation issue altogether (Section~\ref{sec:dudefisa}).
 We provide explicit upper bounds for the amount of memory necessary to solve this problem, and corresponding constructions.
-
-We then introduce the \emph{queuing construction}, a generic approach to build windowed-DDP-friendly filters from existing filters (Sections~\ref{sec:queue} and \ref{sec:subfilter-select}).
+%
+%We then introduce the \emph{queuing construction}, a generic approach to build windowed-DDP-friendly filters from existing filters (Sections~\ref{sec:queue} and \ref{sec:subfilter-select}).
 We analyse the queuing construction's error rates and parameters (Section~\ref{sec:optimising}), which are confirmed by benchmarks (Section~\ref{sec:bench}).
-
-Finally, we provide an analysis of the queuing construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).
+%
+%Finally, we provide an analysis of the queuing construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).
+\todo
 
 \subsection{Related work}\label{sub:related}
-\cite{10.1145/1060745.1060753} studies a structure aking to the counting Bloom filter, in a \enquote{landmark-} and \enquote{jumping-} sliding window setting.
-Despite the name, these are different from the sliding window discussed in this paper.
+The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}.
+However, the definition is not the one we use, as several variations exist such as \cite{shtul2020agepartitioned}.
+Instead, the wDDP formulation we used was already introduced in \cite{Yoo10,She08}.
+Both of these papers propose an algorithm for the wDDP.
 
-Closer to our work, the idea of using subfilters may be found in the A2 filter's design \cite{Yoo10}.
+Closer to our work, the idea of using subfilters can be found in the A2 filter's design \cite{Yoo10} and a variation of our idea can be found in a very recent construction, on a slightly different DDP formulation \cite{shtul2020agepartitioned}.
 The A2 is built from two Bloom filters, a situation which we generalise and analyse generically in this paper.
-
-\todo[continuer]
+Similarly, the solution in \cite{shtul2020agepartitioned} only works with Bloom Filters.
 
 \subsection{Organisation}
+\todo
 
@@
 Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) set $E = (e_1, e_2, \dotsc)$, with each $e_i \in \Gamma$.
-
-\begin{definition}[Duplicate and unseen element]
-Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$.
-Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$.
-In that case we write $e_j \dup E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notdup E$.
-\end{definition}
 
@@
 
-We will usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathcal S| \ll |\Gamma|$.
-
-\begin{definition}[False positive, false negative]
-	Let $e \dup E$ (resp.
-$e \notdup E$) and $\mathcal F$ be a filter.
-We say that $e$ is a \emph{false positive} (resp.
-\emph{false negative}) when $\mathcal F.\mathsf{Detect}(e) = \DUPLICATE$ (resp.
-$\UNSEEN$).
-\end{definition}
-
-\begin{definition}[False positive rate, false negative rate]
-	Let $E$ be a stream, $\mathcal F$ be a filter.
-The \emph{false positive rate} (resp.
-\emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp.
-$\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $(e_1, \dotsc, e_i)\subset E$ (resp.
-the ratio of false negative divided by the number of duplicate elements in that subset).
-\end{definition}
-
-However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^\star$ is a false positive (resp. false negative).
-
-\begin{definition}[Probability of false positive, of false negative]
-	\label{def:pfp-pfn}
-	Let $E = (e_1, \dotsc)$ be a stream, $\mathcal F$ be a filter.
-The \emph{probability of false positive} (resp.
-\emph{probability of false negative}) of $\mathcal F$ after $i$ elements, denoted $\FP_i$ (resp.
-$\FN_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp.
-false negative).
-\end{definition}
-
-One can observe that $\FPR_n = \frac{1}{n}\sum_{i=1}^n \FP_i$, and similarly for $\FNR_n$.
-
-\subsection{Filter Saturation and Sliding Windows}\label{sec:filsat}
-Unfortunately, efficient duplicate detection over an infinite stream has been identified as an unsolvable problem \cite{10.1145/3297280.3297335}.
-As a matter of fact, as the number of bits of information of the stream grow to infinity, the filter can only remember an ever diminishing proportion of those bits, eventually having no advantage compared to a filter answering randomly.
-
-In other terms, any DDF is asymptotically as good as a random guess:
-	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
-	Let $\FNR_\infty$ and $\FPR_\infty$ be the asymptotic false negative and false positive rates of a filter of $M$ bits of memory (i.e. the FNR and FPR on a stream of size going to infinity).
-
-	If $|\Gamma| \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
-\end{theorem}
-
-One way out of this situation is to lower our expectations and work on a sliding window:
-
-\begin{definition}[Sliding window DDP]
-	Given a stream $E_n$ of fixed size $w$, with $E_n = (e_{n-w+1}, \dotsc, e_n)$ and an item $e^\star$, find whether $e^\star \in E_n$.
-\end{definition}
-
-We therefore introduce new definitions suited to that setting:
+We usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathcal S| \ll |\Gamma|$.
+Otherwise, if $|\mathcal S| = |\Gamma|$ then solutions in constant time and without errors exist \cite{10.1145/3297280.3297335}.
 
@@
 
-\subsection{Bounds on the Sliding Window DDP}\label{sub:opt_solutions}
+%\begin{definition}[Duplicate and unseen element]
+%Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$.
+Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$.
+In that case we write $e_j \dup E$.
+Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notdup E$.
+%\end{definition}
+%
+
+%
+%\begin{definition}[False positive, false negative]
+%	Let $e \dup E$ (resp.
+$e \notdup E$) and $\mathcal F$ be a filter.
+We say that $e$ is a \emph{false positive} (resp.
+\emph{false negative}) when $\mathcal F.\mathsf{Detect}(e) = \DUPLICATE$ (resp.
+$\UNSEEN$).
+%\end{definition}
+%
+%\begin{definition}[False positive rate, false negative rate]
+%	Let $E$ be a stream, $\mathcal F$ be a filter.
+The \emph{false positive rate} (resp.
+\emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp.
+$\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $(e_1, \dotsc, e_i)\subset E$ (resp.
+the ratio of false negative divided by the number of duplicate elements in that subset).
+%\end{definition}
+%
+%However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^\star$ is a false positive (resp. false negative). 
+%
+%\begin{definition}[Probability of false positive, of false negative]
+%	\label{def:pfp-pfn}
+%	Let $E = (e_1, \dotsc)$ be a stream, $\mathcal F$ be a filter.
+The \emph{probability of false positive} (resp.
+\emph{probability of false negative}) of $\mathcal F$ after $i$ elements, denoted $\FP_i$ (resp.
+$\FN_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp.
+false negative).
+%\end{definition}
+
+One can observe that $\FPR^w_n = \frac{1}{n}\sum_{i=1}^n \FP^w_i$, and similarly for $\FNR^w_n$.
+
+%\subsection{Filter Saturation and Sliding Windows}\label{sec:filsat}
+%Unfortunately, efficient duplicate detection over an infinite stream has been identified as an unsolvable problem \cite{10.1145/3297280.3297335}.
+As a matter of fact, as the number of bits of information of the stream grow to infinity, the filter can only remember an ever diminishing proportion of those bits, eventually having no advantage compared to a filter answering randomly.
+%
+%In other terms, any DDF is asymptotically as good as a random guess:
+%	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
+%	Let $\FNR_\infty$ and $\FPR_\infty$ be the asymptotic false negative and false positive rates of a filter of $M$ bits of memory (i.e. the FNR and FPR on a stream of size going to infinity).
+%	
+%	If $|\Gamma| \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
+%\end{theorem}
+%
+%One way out of this situation is to lower our expectations and work on a sliding window:
+%
+%\begin{definition}[Sliding window DDP]
+%	Given a stream $E_n$ of fixed size $w$, with $E_n = (e_{n-w+1}, \dotsc, e_n)$ and an item $e^\star$, find whether $e^\star \in E_n$.
+%\end{definition} 
+%
+%We therefore introduce new definitions suited to that setting:
+%
+%\begin{definition}[Duplicate element, unseen element over a sliding window]
+%	Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
+In this case we write $e_j \wdup E$.
+Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notwdup E$.
+%\end{definition}
+%
+%\begin{definition}[False positive, false negative over a sliding window]
+%	Let $w \in \mathbb N$, $e \notwdup E$ (resp.
+$e \wdup E$) and let $\mathcal F$ be a DDF.
+We say that $e$ is a \emph{false positive} (resp.
+\emph{false negative}) over $w$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
+$\UNSEEN$).
+%\end{definition}
+%
+%\begin{definition}[False positive rate, false negative rate over a sliding window]
+%	Let $E$ be a stream, $\mathcal F$ be a DDF, $w \in \mathbb N$.
+The \emph{false positive} (resp.
+\emph{false negative}) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $w$, noted $\FPR^w_i$ (resp.
+$\FNR^w_i$), is defined as the number of false positives over $w$ divided by the number of unseen elements in $E$ over $w$ (resp.
+the number of false negative over $w$ divided by the number of duplicate elements over $w$).
+%\end{definition}
+
+\subsection{DDP vs wDDP}
+As noted before, some DDF were defined on the DDP, thus not offering a simple analysis of their error rates on the wDDP.
+
+The sliding window variant of DDP may seem to be a slight weakening of the original problem.% Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
+A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+The structure proposed in \cite{10.1145/1060745.1060753} is not suited to either sliding window or no sliding window DDP, as they work on what they call `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
+
+Of these, only the A2 and b\_DBF were designed in a way immediately applicable to the sliding window DDP.
+The others do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
+Another remarkable (but experimental) observation is that these DDFs' false positive rate does not decrease to 0 when the sliding window becomes small.
+
+\section{Optimal and Approximate Solutions}
+\subsection{Optimal wDDF}\label{sub:opt_solutions}
 
@@
 \begin{theorem}
-	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the sliding window DDP can be solved exactly (with no errors) in constant time.
+	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the wDDP can be solved exactly (with no errors) in constant time.
 \end{theorem}
@@
 \end{proof}
-The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing 
-errors:
-\begin{theorem}
-	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.
+
+\subsection{Approximate Optimal wDDF}
+In the previous section, the optimal filter requires to know the size of $\Gamma$, which might be unknown, unbounded or simply too big for practical applications. 
+The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing errors.
+
+\begin{theorem}\label{thm:SHF}
+	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the wDDP can be solved with almost no error using $M$ bits of memory.
 
@@
 
-When $\log_2|\Gamma| > 5 \log_2 w$ this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory, at the cost of a minimal error.
+When $\log_2|\Gamma| > 2 \log_2 w$ this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory, at the cost of a minimal error.
 When $\log_2|\Gamma| > 2 \log_2 w$, it outperforms the exact solution described sooner in terms of memory.
 
-Hence, very good solutions for situations where $M \approx 5w\log_2 w$ already exist, but efficient solutions and lower bounds on the error rates for smaller amounts of memory are still to be found.
+\section{Short Hash Filter}
+\subsection{Short Hash Filter Algorithm}
+The approximate filter we described uses hashes of size $2\log_2(w)$ for a given sliding window $w$.
+However, this hash size is arbitrary, and while it guarantees a very low error rate, it can be changed.
+More importantly, in some practical cases the maximal amount of available memory is fixed beforehand.
+Fixing the memory is also more practical for benchmarking various data structures, as it gives the guarantee that all filters operate under the same conditions.
 
-\subsection{DDP vs Sliding Window DDP}
-The sliding window variant of DDP may seem to be a slight weakening of the original problem.
-Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
-A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-The structure proposed in \cite{10.1145/1060745.1060753} is not suited to either sliding window or no sliding window DDP, as they work on what they call `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
+This gives us the Short Hash Filter (SHF), described in Algorithm~\ref{alg:SHF}.
 
-Of these, only the A2 and b\_DBF were designed in a way immediately applicable to the sliding window DDP.
-The others do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
-Another remarkable (but experimental) observation is that these DDFs' false positive rate does not decrease to 0 when the sliding window becomes small.
+\begin{algorithm}[]
+	\caption{SHF Setup, Lookup and Insert}\label{alg:SHF}
 
-\todo[Expliquer ?]
+	\begin{algorithmic}[1]
+		\Function{Setup}{$\mathcal M, w$}
+		\Comment $M$ is the available memory, $w$ the size of the sliding window
+		\State $h \gets$ hash function of codomain size $\lfloor \frac M{2w} - \frac 12 \log_2 w \rfloor$
+		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
+		\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h$ => counter (of max value $w$)
+
+		\State\Return filter
+		\EndFunction 
+		\item[]
+	\end{algorithmic}
+
+	\begin{algorithmic}[1]
+	\Function{Lookup}{$e$}
+		\If{$D[h(e)] > 0$}
+		\State \Return \DUPLICATE
+		\EndIf
+		\State \Return \UNSEEN
+	\EndFunction
+	\item[]
+	\end{algorithmic}
+
+	\begin{algorithmic}[1]
+	\Function{Insert}{$e$}
+		\State $Q.\mathsf{Push\_Front}(h(e))$
+		\State $D[h(e)]$++
+
+		\If{$Q.\mathsf{length}() > w$}
+			\State $h' \gets Q.\mathsf{Pop\_back}()$
+			\State $D[h']$-{}-
+			\If{$D[h'] = 0$}
+				\State Erase key $D[h']$
+			\EndIf
+		\EndIf
+	\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+\subsection{Compact Short Hash Filter}
+For the sake of completeness, we also introduce the Compact Short Hash Filter, which is very similar to the Short Hash Filter, but does not use any dictionnary.
+Hence, the filter is much slower (complexity of $O(w)$), but also has fewer errors since there is more place for the queue.
+
+A quick description of the Compact Short Hash Filter (CSHF) is given in Algorithm~\ref{alg:CSHF}.
+
+\begin{algorithm}[]
+	\caption{CSHF, Lookup and Insert}\label{alg:CSHF}
+
+	\begin{algorithmic}[1]
+		\Function{Setup}{$\mathcal M, w$}
+		\Comment $M$ is the available memory, $w$ the size of the sliding window
+		\State $h \gets$ hash function of codomain size $\lfloor \frac Mw \rfloor$
+		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
+		\State\Return filter
+		\EndFunction 
+		\item[]
+	\end{algorithmic}
+
+	\begin{algorithmic}[1]
+		\Function{Lookup}{$e$}
+		\State \Return $h(e) \in Q$ 
+		\EndFunction
+		\item[]
+	\end{algorithmic}
+
+	\begin{algorithmic}[1]
+		\Function{Insert}{$e$}
+		\Comment Same as SHF, but removing all instructions about its dictionnary $D$.
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+\subsection{Error Rates}
+\begin{theorem}
+	Let $w \in \mathbb N$.
+Let $M \in \mathbb N$ be the available memory size.
+Let $\FN^w_{SHF}$ be the probability of false negative of an SHF with these parameters.
+We similarly define $\FP^w_{SHF}$, $\FN^w_{CSHF}$, $\FP^w_{CSHF}$
+	Both SHF and QSHF have $\FN^w = 0$.
+
+	Furthermore we have $\FP_{SHF}^w = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w$ and $\FP_{CSHF}^w = 1 - \left(1 - 2^{-M/w}\right)^w$.
+\end{theorem}
+
+\begin{proof}
+	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$, while a CSHF has fingerprints of size $h' = \frac Mw$.
+\end{proof}
+
+It can be noted that a CSHF of size $M$ has the same error rate than an SHF of size $(2 + \frac {\log_2 w}h)M$.
+\subsection{Saturation}
+When benchmarking both structures, it appears they saturate very quickly when changing $w$: in other words, most SHF will either have an error rate of $0$ or $1$.
+
+For instance, we benchmarked the performance of CSHF and SHF with a memory $M=100000$, on a stream of size 1 000 000 consisting of uniformly random elements from an alphabet of size $2^{18}$.
+Results are given in Figure~\ref{fig:shorts}.
+
+\begin{figure}
+	\input{graphs/bench_shorts.tex}
+	\caption{Error rates of SHFs and CSHFs of $100000$ bits, for various $w$.}\label{fig:shorts}
+\end{figure}
+
+More specifically, \todo[Trouver la formule pour laquelle CSHF sature à 50\% ou quelque chose du genre]
 
@@
 
-If solving the equation for individual cases is 
+If solving the equation for individual cases is doable, it however does not seem possible to derive a generic formula.
 %\end{equation*}

### 2020-03-27 qhtv2.tex
Abstract

@@
 
-\title{Adapting Duplicate Filters to a Sliding Window Context}
+\title{Optimal Duplicate Detection in a Sliding Window}
 
@@
 \begin{abstract}
-	A duplicate detection filter is an online data structure designed to efficiently detect repetitions (duplicates) in a stream, when only a limited amount of memory is available.
-A well-known data structure used in this context is the Bloom filter, which has been generalised in several ways to
-	improve its performances or strike specific tradeoffs.
+	Duplicate detection is the problem of identifying whether a given item has previously appeared in a (possibly infinite) stream of data, when only a limited amount of memory is available.
 
-	When analysed in the limit of an infinite stream, error rates of duplicate filters turn out to be heavily constrained; as a consequence they appear to provide no advantage, asymptotically, over a random biased coin toss \cite{10.1145/3297280.3297335}.
+	Building on the Bloom filter \cite{bloom_spacetime_1970}, an early data structure amenable to duplicate detection, several generalisations and variants were proposed tthat reduce error rates while maintaining constant memory.
 
-	In this paper we consider a \enquote{windowed} variation on the duplicate detection problem
-	that is better-behaved and thus lends itself to a more thorough 
-	mathematical analysis. We show how existing filters can be adjusted to work
-	in this new setting using a queuing construction. 
+	Unfortunately the infinite stream setting is ill-posed, and error rates of duplicate detection filters turn out to be heavily constrained: as a consequence they appear to provide no advantage, asymptotically, over a random biased coin toss \cite{10.1145/3297280.3297335}.
+
+	Both as a better-behaved setting and as a construction technique, a
+	\emph{windowed} variant of the duplicate detection problem was 
+	introduced in \cite{She08,Yoo10}, which consists in finding duplicate 
+	entries amongst the last $w$ elements of the stream for a fixed integer $w$.
+
+	In this paper we formalise this setting, and show that a perfect (zero error) solution can be used up to a maximal window size $w_\text{max}$.
+Above this threshold we show that some existing duplicate detection filters (designed for the \emph{non-windowed} setting) perform better that those targeting the windowed problem.
+Finally, we introduced a \enquote{queuing construction} that improves on the performance of some duplicate detection filters in the windowed setting.
 \end{abstract}

### 2020-03-27 qhtv2.tex
esthétique

@@
 Finally, we introduced a \enquote{queuing construction} that improves on the performance of some duplicate detection filters in the windowed setting.
+
+	We also analyse the security of our filters in an adversarial setting. 
 \end{abstract}
@@
 
+\begin{definition}[Probability of false positive, of false negative]
+	\label{def:pfp-pfn}
+	Let $E = (e_1, \dotsc)$ be a stream, $w\in \mathbb N$, $\mathcal F$ be a filter.
+The \emph{probability of false positive} (resp.
+\emph{probability of false negative}) of $\mathcal F$ after $i$ elements over a sliding window of size $w$, denoted $\FP^w_i$ (resp.
+$\FN^w_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp.
+false negative) over $w$.
+\end{definition}
+
 \begin{definition}[False positive rate, false negative rate over a sliding window]
@@
 
-The sliding window variant of DDP may seem to be a slight weakening of the original problem.% Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
+The sliding window variant of DDP may seem to be a slight weakening of the original problem.
+However, it is more appropriated for many use cases, such as caching or click fraud.
+% Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
 A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-The structure proposed in \cite{10.1145/1060745.1060753} is not suited to either sliding window or no sliding window DDP, as they work on what they call `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
-
-Of these, only the A2 and b\_DBF were designed in a way immediately applicable to the sliding window DDP.
+The structure proposed in \cite{10.1145/1060745.1060753} is not desined for either wDDP or DDP, as they work on what they call `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
+
+Of these, only the A2 and b\_DBF were designed for the wDDP.
 The others do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
@@
 
-	More precisely, it is possible to create a filter of $M$ bits with an FNR of $0$, and an FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$, and a time complexity of $O(w)$.
+	More precisely, it is possible to create a filter of $M$ bits with an FN of $0$, and an FP of $1 - (1-\frac1{w^2})^w \sim \frac 1w$, and a time complexity of $O(w)$.
 
@@
 \end{theorem}
+Note that we only consider the probability of false positive after the filter has inserted at least $w$ elements, i.e., once the filter is full and has reached the stationary phase.
 
@@
 
-When $\log_2|\Gamma| > 2 \log_2 w$ this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory, at the cost of a minimal error.
+When $\log_2|\Gamma| > 5 \log_2 w$ this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory, at the cost of a minimal error.
 When $\log_2|\Gamma| > 2 \log_2 w$, it outperforms the exact solution described sooner in terms of memory.
@@
 Let $\FN^w_{SHF}$ be the probability of false negative of an SHF with these parameters.
-We similarly define $\FP^w_{SHF}$, $\FN^w_{CSHF}$, $\FP^w_{CSHF}$
+We similarly define $\FP^w_{SHF}$, $\FN^w_{CSHF}$, $\FP^w_{CSHF}$.
 	Both SHF and QSHF have $\FN^w = 0$.
@@
 
-It can be noted that a CSHF of size $M$ has the same error rate than an SHF of size $(2 + \frac {\log_2 w}h)M$.
+It can be noted that a CSHF of size $M$ has the same error rate than an SHF of size $2M + w\log_2 w$.
 \subsection{Saturation}
@@
 	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation}
+	\begin{equation*}
 	\FPR_{\mathcal Q, cn}^w = 1 -  \frac{(1 - \FP_{\mathcal F, c})^{L-1}}{c}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell}).
-	\end{equation}
+	\end{equation*}
 \end{theorem}
@@
 	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation}
+	\begin{equation*}
 	\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell.
-	\end{equation}
+	\end{equation*}
 \end{theorem}
@@
 Summing up the false positive and false negative rates, we have a total error rate
-\begin{equation}
-	\operatorname{ER}_{\mathcal Q, cn}^{w}
+$	\operatorname{ER}_{\mathcal Q, cn}^{w}
 	= 1 - \alpha \beta^{L-1} + \alpha' \beta'^{L-1}
-\end{equation}
+$,
 where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
@@
 		ER_n 
-		& = \FN_n + p \\
-		& =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
+		& = \FN_n + p
+		 =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
 		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
@@
 However, other experiments on alphabets of other sizes yield very similar results, hence validating the observation made in Section~\ref{sec:optimising} that the optimal number of subfilters does not depends on the alphabet (in first approximation).
+
 \subsection{Comparison of QHT and QHT-Queuing Filter}
-\todo[À faire]
-In this section, we compare the efficiency of QHT and QHT-queuing filter. For this, we use an artificial dataset on various sliding window sizes.
+In this section, we compare the efficiency of QHT and QHT-queuing filter.
+For this, we used the same artificial dataset as previously, as well as the same QHT filter than in previous sections.
+Moreover, we add a queuing QHT with an optimal value $L$ for each considered sliding window.
+For the sake of completeness, we also ran the comparison on the other DDFs.
+Results on the QHT and SQF are shown in Figure~\ref{fig:improvement}, results for the Cuckoo and SBF are shown in Appendix~\ref{app:improvement}.
 
@@
 
-\begin{figure*}[!ht]
+\begin{figure}[!ht]
 	\centering
@@
 	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
+\end{figure}
+
+As can be seen on this simulation, there is only disagreement around $w \approx N/L$, and increasing $N$ results in a later and smaller peak.
+
+It is also possible to run simulations for different alphabet sizes $\Gamma$, which shows that the peak's position increases with $|\Gamma|$, although the relationship is not obvious to quantify.
+
+\section{Comparing DDFs and their Queueing Counterpart}\label{app:improvement}
+We here run a comparison of the Cuckoo Filter relative to the Queueing Cuckoo Filter, as well as the SBF relatively to the queueing SBF. The results are given in Figure~\ref{fig:appendix_improvement}.
+
+\begin{figure*}[!ht]
+\begin{tikzpicture}
+	\begin{semilogxaxis}[legend cell align = left, legend pos=outer north east, xlabel=$w$, ylabel=$\FPR^w + \FNR^w (\times 100)$]
+	\addplot[color=teal, mark=triangle] table[x=w,y=Error] {Queueing_Cuckoo.dat};
+	\addlegendentry{Q\_Cuckoo};
+	\addplot[color=teal, mark=triangle, dashed] table[x=w,y=Error] {Cuckoo.dat};
+	\addlegendentry{Cuckoo};
+	%%
+	\addplot[color=olive, mark=square, mark options = {scale=0.7}] table[x=w,y=Error] {Queueing_StableBloom.dat};
+	\addlegendentry{$Q\_SBF$};
+	\addplot[color=olive, mark=square, mark options = {scale=0.7}, dashed] table[x=w,y=Error] {SBF.dat};
+	\addlegendentry{$SBF$};
+
+	%\addplot[mark=x,^8$}
+	\end{semilogxaxis}
+
+\end{tikzpicture}
+	\caption{Comparing performances of various filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
 \end{figure*}
 
-As can be seen on this simulation, there is only disagreement around $w \approx N/L$, and increasing $N$ results in a later and smaller peak.
-
-It is also possible to run simulations for different alphabet sizes $\Gamma$, which shows that the peak's position increases with $|\Gamma|$, although the relationship is not obvious to quantify.
-
 \end{document}

### 2020-03-27 qhtv2.tex
1.1 and 1.2

@@
 Above this threshold we show that some existing duplicate detection filters (designed for the \emph{non-windowed} setting) perform better that those targeting the windowed problem.
-Finally, we introduced a \enquote{queuing construction} that improves on the performance of some duplicate detection filters in the windowed setting.
+Finally, we introduce a \enquote{queuing construction} that improves on the performance of some duplicate detection filters in the windowed setting.
 
@@
 
-We study the following problem: 
-\begin{definition}[Duplicate detection problem on a sliding window, wDDP] Given a stream $E_n = (e_1, e_2, \dotsc, e_n)$, a sliding window size $w$ and a \enquote{new} item $e^\star$, find whether $e^\star$ is also present in the last $w$ elements of the stream, ie., whether $e^\star \in \{e_{n-w+1}, \dotsc, e_n\}$.
+Throughout this paper, we are interested in the following problem: 
+\begin{definition}[Duplicate detection problem over a sliding window, wDDP] Given a stream $E_n = (e_1, e_2, \dotsc, e_n)$, a sliding window size $w$ and a \enquote{new} item $e^\star$, find whether $e^\star$ is also present in the last $w$ elements of the stream, ie., whether $e^\star \in \{e_{n-w+1}, \dotsc, e_n\}$.
 At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n \mid e^\star$ where $\mid$ denotes concatenation. 
 \end{definition}
-Instances of this problem abound in computer science, with applications in file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
+Instances of this problem abound in computer science, with applications to file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
 A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.
@@
 %Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable. 
-One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory: even for modest situations (e.g.
+Perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory \cite[Theorem 2.1]{10.1145/3297280.3297335}: even for modest situations (e.g.
 64-bit nonces, corresponding to $2^{64}$ possible values) this is quickly impractical.
@@
 Information-theoretically, if the source has $U$ bits of entropy then the situation is equivalent to having an $U$-bit, uniformly distributed input.
-
-We observe that in the litterature, there exists a similar problem, which we call DDP, and which does not make use of any sliding window.
-For instance, in DDP on a stream $E_n$ the problem is to find whether $e^\star \in E_n$.
-However, even though several algorithms have been proposed for this problem (\cite{Den06,10.1145/3297280.3297335,Dut13} and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}), they \emph{all} face a phenomenon called \enquote{saturation} on large data streams \cite{10.1145/3297280.3297335}.
-This phenomenon is not related to the filter, but rater to the nature of the DDP itself.
-Essentially, when saturation happens the algorithm performs no better than at random.
+This is the setting we consider here.
+
+As the window size in wDDP grows infinitely large, it becomes the following problem: find whether $e^\star \in E_n$.
+This \enquote{non-windowed} problem predates in fact the definition of wDDP, and several algorithms have been proposed for this problem: \cite{Den06,10.1145/3297280.3297335,Dut13} and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+Unfortunately \emph{all} these solutions face a phenomenon called \enquote{saturation} on large enough data streams.
+In fact, saturation is inevitable with infinite windows \cite{10.1145/3297280.3297335}, and when it happens the algorithm performs no better than at random.
+
 This is problematic on two grounds: it makes the comparison of several algorithms difficult (since they all asymptotically behave in that fashion), and the unavoidable saturation ruins any particular design's merits.
@@
 \subsection{Contributions}
-%To circumvent the aforementioned limitations, we introduce a variant of the DDP \emph{over a sliding window}, which enables the design of filters that avoids the saturation issue altogether (Section~\ref{sec:dudefisa}).
-We provide explicit upper bounds for the amount of memory necessary to solve this problem, and corresponding constructions.
-%
-%We then introduce the \emph{queuing construction}, a generic approach to build windowed-DDP-friendly filters from existing filters (Sections~\ref{sec:queue} and \ref{sec:subfilter-select}).
-We analyse the queuing construction's error rates and parameters (Section~\ref{sec:optimising}), which are confirmed by benchmarks (Section~\ref{sec:bench}).
-%
-%Finally, we provide an analysis of the queuing construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).
-\todo
+In this paper we show that the wDDP problem can be solved exactly using $M$ bits of memory, up to a window size $w_\text{max}$; we provide an explicit algorithm achieving this, which can run in constant time.
+Allowing small errors makes it possible to push $w_\text{max}$ further; we provide the corresponding constant-time (SHF) and linear-time (CSHF) constructions.
+
+Unfortunately, for $w > w_\text{max}$ the performance of these algorithms degrade very rapidly.
+We therefore turn our attention to existing data structures designed for the \enquote{non-windowed} setting.
+We show that some of them outperform dedicated data structures, including SHF/CSHF, in the $w > w_\text{max}$ regime.
+
+We then introduce the \enquote{queuing construction}, a black box transformation of non-windowed data structures into windowed ones, that improves their performance in the wDDP setting.
+
+Finally, we provide an analysis of our construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).
 

### 2020-03-27 qhtv2.tex
add w_opt

--- 2020-03-27 qhtv2.tex
@@
 
-More specifically, \todo[Trouver la formule pour laquelle CSHF sature à 50\% ou quelque chose du genre]
+Finding an exact formula of the $w_{max}$ for which those filters reach an error of 50\% proved to be tedious.
+However, we numerically solved the equation $\FP^w = 0.5$ for these two filters, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$.
+Results are given in Figure~\ref{fig:w_opt}.
+As it turns out, the relation between $w_{max}$ and $M$ is quasi-linear, and we get the following linear regressions, with values rounded to the third significant digit:
+
+\begin{figure}
+	\input{graphs/w_opt_shf.tex}
+	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 50\% ($\pm 0.001$), for various values of $M$.}\label{fig:w_opt}
+\end{figure}
+
+\begin{itemize}
+	\item For CSHF, $w_{max}^{CSHF} = 0.0627 M + 443$, with an $r^2 = 0.9981$
+	\item For SHF, $w_{max}^{SHF} = 0.0233 M + 186$, with an $r^2 = 0.9977$
+\end{itemize}
 

### 2020-03-27 qhtv2.tex
esthétique

@@
 		\EndFunction 
-		\item[]
+%		\item[]
 	\end{algorithmic}
@@
 	\EndFunction
-	\item[]
+%	\item[]
 	\end{algorithmic}
@@
 
-A quick description of the Compact Short Hash Filter (CSHF) is given in Algorithm~\ref{alg:CSHF}.
+A quick description of the Compact Short Hash Filter (CSHF) Setup function is given in Algorithm~\ref{alg:CSHF}.
+The other functions are similar to the ones of Algorithm~\ref{alg:SHF}, removing all references to the dictionary.
 
 \begin{algorithm}[]
-	\caption{CSHF, Lookup and Insert}\label{alg:CSHF}
+	\caption{CSHF, Setup}\label{alg:CSHF}
 
@@
 	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-		\Function{Lookup}{$e$}
-		\State \Return $h(e) \in Q$ 
-		\EndFunction
-		\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-		\Function{Insert}{$e$}
-		\Comment Same as SHF, but removing all instructions about its dictionnary $D$.
-		\EndFunction
-	\end{algorithmic}
+%	
+%	\begin{algorithmic}[1]
+%		\Function{Lookup}{$e$}
+%		\State \Return $h(e) \in Q$ 
+%		\EndFunction
+%		\item[]
+%	\end{algorithmic}
+%	
+%	\begin{algorithmic}[1]
+%		\Function{Insert}{$e$}
+%		\Comment Same as SHF, but removing all instructions about its dictionnary $D$.
+%		\EndFunction
+%	\end{algorithmic}
 \end{algorithm}
@@
 	\input{graphs/w_opt_shf.tex}
-	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 50\% ($\pm 0.001$), for various values of $M$.}\label{fig:w_opt}
+	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 0.5 ($\pm 0.001$), for various values of $M$.}\label{fig:w_opt}
 \end{figure}
@@
 
-\begin{figure}[!ht]
+\begin{figure*}[!ht]
 	\centering
@@
 	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
-\end{figure}
+\end{figure*}
 
@@
 \end{figure*}
-
 \end{document}

### 2020-03-27 qhtv2.tex
Various fixes, restructuration

--- 2020-03-27 qhtv2.tex
@@
 The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}.
-However, the definition is not the one we use, as several variations exist such as \cite{shtul2020agepartitioned}.
-Instead, the wDDP formulation we used was already introduced in \cite{Yoo10,She08}.
-Both of these papers propose an algorithm for the wDDP.
-
-Closer to our work, the idea of using subfilters can be found in the A2 filter's design \cite{Yoo10} and a variation of our idea can be found in a very recent construction, on a slightly different DDP formulation \cite{shtul2020agepartitioned}.
+However, several variations exist and describe incompatible situations, such as \cite{shtul2020agepartitioned}.
+Instead, the wDDP formulation we rely on is due to \cite{Yoo10,She08}, which also introduce algorithms for solving the wDDP approximately.
+
+The notion of using subfilters, as in the queuing construction, can be found in the A2 filter's design \cite{Yoo10} and a variation thereof can be found in \cite{shtul2020agepartitioned} but in a different DDP formulation.
 The A2 is built from two Bloom filters, a situation which we generalise and analyse generically in this paper.
-Similarly, the solution in \cite{shtul2020agepartitioned} only works with Bloom Filters.
-
-\subsection{Organisation}
-\todo
+Similarly, the construction in \cite{shtul2020agepartitioned} only works with Bloom Filters.
 
@@
 \label{sec:dudefisa}
-\subsection{Notations and Initial Problem Statement}
+\subsection{Notations and basic definitions}
 Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) set $E = (e_1, e_2, \dotsc)$, with each $e_i \in \Gamma$.
@@
 We usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathcal S| \ll |\Gamma|$.
-Otherwise, if $|\mathcal S| = |\Gamma|$ then solutions in constant time and without errors exist \cite{10.1145/3297280.3297335}.
+Otherwise, if $|\mathcal S| = |\Gamma|$ then the problem can be solved in constant time without errors \cite{10.1145/3297280.3297335}.
 
@@
 
-One can observe that $\FPR^w_n = \frac{1}{n}\sum_{i=1}^n \FP^w_i$, and similarly for $\FNR^w_n$.
+We have $\FPR^w_n = \frac{1}{n}\sum_{i=1}^n \FP^w_i$, and similarly for $\FNR^w_n$.
 
@@
 
-\subsection{DDP vs wDDP}
-As noted before, some DDF were defined on the DDP, thus not offering a simple analysis of their error rates on the wDDP.
-
-The sliding window variant of DDP may seem to be a slight weakening of the original problem.
-However, it is more appropriated for many use cases, such as caching or click fraud.
-% Remarkably, it turns out that DDFs which perform well for the DDP do rather poorly for the sliding window DDP.
+\section{DDFs and the wDDP}
 A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-The structure proposed in \cite{10.1145/1060745.1060753} is not desined for either wDDP or DDP, as they work on what they call `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
-
-Of these, only the A2 and b\_DBF were designed for the wDDP.
-The others do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
+The structure proposed in \cite{10.1145/1060745.1060753} is not desined for wDDP but a variant called `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
+
+Of these, only the A2 and b\_DBF were designed explicitly for the wDDP.
+Others DDFs do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
 Another remarkable (but experimental) observation is that these DDFs' false positive rate does not decrease to 0 when the sliding window becomes small.
@@
 \subsection{Approximate Optimal wDDF}
-In the previous section, the optimal filter requires to know the size of $\Gamma$, which might be unknown, unbounded or simply too big for practical applications. 
-The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing errors.
+The optimal filter described above requires that the size of $\Gamma$ is known in advance. The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing errors.
 
@@
 
-	More precisely, it is possible to create a filter of $M$ bits with an FN of $0$, and an FP of $1 - (1-\frac1{w^2})^w \sim \frac 1w$, and a time complexity of $O(w)$.
+	More precisely, it is possible to create a filter of $M$ bits with an FN of $0$, an FP of $1 - (1-\frac1{w^2})^w \sim \frac 1w$, and a time complexity of $O(w)$.
 
@@
 \end{theorem}
-Note that we only consider the probability of false positive after the filter has inserted at least $w$ elements, i.e., once the filter is full and has reached the stationary phase.
-
+Note that we only consider the probability of false positive after the filter has inserted at least $w$ elements, i.e., once the filter is full and has reached a stationary regime.
 \begin{proof}
@@
 	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
-The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
+The birthday theorem \cite{10.1007/3-540-45708-9_19} states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
 Therefore $2^{(2 \log_2 w) / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
@@
 This gives us the Short Hash Filter (SHF), described in Algorithm~\ref{alg:SHF}.
-
-\begin{algorithm}[]
+The implementation relies on a double-ended queue or a ring buffer, which allows pushing at beggining of a queue and popping at the end in constant time.
+
+\begin{algorithm}[!ht]
 	\caption{SHF Setup, Lookup and Insert}\label{alg:SHF}
@@
 \subsection{Compact Short Hash Filter}
-For the sake of completeness, we also introduce the Compact Short Hash Filter, which is very similar to the Short Hash Filter, but does not use any dictionnary.
-Hence, the filter is much slower (complexity of $O(w)$), but also has fewer errors since there is more place for the queue.
-
-A quick description of the Compact Short Hash Filter (CSHF) is given in Algorithm~\ref{alg:CSHF}.
-
-\begin{algorithm}[]
+Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
+The CSHF performs in linear time in $w$ and is described in Algorithm~\ref{alg:CSHF}.
+
+\begin{algorithm}[!ht]
 	\caption{CSHF, Lookup and Insert}\label{alg:CSHF}
@@
 		\Function{Insert}{$e$}
-		\Comment Same as SHF, but removing all instructions about its dictionnary $D$.
-		\EndFunction
-	\end{algorithmic}
-\end{algorithm}
-
-\subsection{Error Rates}
-\begin{theorem}
-	Let $w \in \mathbb N$.
-Let $M \in \mathbb N$ be the available memory size.
-Let $\FN^w_{SHF}$ be the probability of false negative of an SHF with these parameters.
-We similarly define $\FP^w_{SHF}$, $\FN^w_{CSHF}$, $\FP^w_{CSHF}$.
-	Both SHF and QSHF have $\FN^w = 0$.
-
-	Furthermore we have $\FP_{SHF}^w = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w$ and $\FP_{CSHF}^w = 1 - \left(1 - 2^{-M/w}\right)^w$.
-\end{theorem}
-
-\begin{proof}
-	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$, while a CSHF has fingerprints of size $h' = \frac Mw$.
-\end{proof}
-
-It can be noted that a CSHF of size $M$ has the same error rate than an SHF of size $2M + w\log_2 w$.
-\subsection{Saturation}
-When benchmarking both structures, it appears they saturate very quickly when changing $w$: in other words, most SHF will either have an error rate of $0$ or $1$.
-
-For instance, we benchmarked the performance of CSHF and SHF with a memory $M=100000$, on a stream of size 1 000 000 consisting of uniformly random elements from an alphabet of size $2^{18}$.
-Results are given in Figure~\ref{fig:shorts}.
-
-\begin{figure}
-	\input{graphs/bench_shorts.tex}
-	\caption{Error rates of SHFs and CSHFs of $100000$ bits, for various $w$.}\label{fig:shorts}
-\end{figure}
-
-Finding an exact formula of the $w_{max}$ for which those filters reach an error of 50\% proved to be tedious.
-However, we numerically solved the equation $\FP^w = 0.5$ for these two filters, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$.
-Results are given in Figure~\ref{fig:w_opt}.
-As it turns out, the relation between $w_{max}$ and $M$ is quasi-linear, and we get the following linear regressions, with values rounded to the third significant digit:
-
-\begin{figure}
-	\input{graphs/w_opt_shf.tex}
-	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 50\% ($\pm 0.001$), for various values of $M$.}\label{fig:w_opt}
-\end{figure}
-
-\begin{itemize}
-	\item For CSHF, $w_{max}^{CSHF} = 0.0627 M + 443$, with an $r^2 = 0.9981$
-	\item For SHF, $w_{max}^{SHF} = 0.0233 M + 186$, with an $r^2 = 0.9977$
-\end{itemize}
-
-\section{Queuing filters}\label{sec:queue}
-In this section, we describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
-A scheme describing our structure is detailed in Figure~\ref{fig:scheme}.
-
-\subsection{The queuing construction}
-
-\paragraph{Principle of operation.}
-Let $\mathcal F$ be a DDF.
-Rather than allocating the whole memory to $\mathcal F$, we will create $L$ copies of $\mathcal F$, each using a fraction of the available memory.
-Each of these \emph{subfilters} as a limited timespan, and is allowed up to $c$ insertions.
-The subfilters are organised in a queue.
-
-When inserting a new element in the queuing filter, it is inserted in the topmost subfilter of the queue.
-After $c$ insertions, a new empty filter is added to the queue, and the oldest subfilter is popped and erased.
-
-As such, we can consider that each subfilter operates on a sub-sliding window of size $c$, which makes the overall construction a DDF operating over a sliding window of size $w = cL$.
-
-\begin{figure}
-	\input{fig/queuef.tex}
-	\caption{Architecture of the queuing filter.
-The filter is composed of $L$ subfilters $\mathcal F$, each containing up to $c$ elements.
-Once the newest subfilter has inserted $c$ elements in its structure, the oldest one is expired.
-As such, it is dropped and a new one is created and put under population at the beginning of the queue.
-In this example, the sub-sliding window of $\mathcal F_1$ is $(e_{m-2}, e_{m-3}, e_{m-4})$.} \label{fig:scheme}
-\end{figure}
-
-\paragraph{Insertion and lookup.}
-The filter returns \DUPLICATE if and only if at least one subfilter does. Insertion is a simple insertion in the topmost subfilter.
-
-\paragraph{Queue update.}
-After $c$ insertions, the last filter of the queue is dropped, and a new (empty) filter is appended in front of the queue.
-
-\paragraph{Pseudocode.}
-We give a brief pseudocode for the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in Algorithm~\ref{alg:queuing}.
-We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
-Here \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first position.\footnote{Two standard ways to implement this are a double-ended queue (deque) and a ring buffer.}
-
-\begin{algorithm}[]
-	\caption{Queuing Filter Setup, Lookup and Insert}\label{alg:queuing}
-
-	\begin{algorithmic}[1]
-	\Function{Setup}{$\mathcal F, M, L, c$}
-		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
-		\State subfilters $\gets \emptyset$
-		\State counter $\gets 0$
-		\State $m \gets \lfloor M/L \rfloor$
-		\For{$i$ from $0$ to $L-1$}
-			\State subfilters.push\_first$(\mathcal F.\mathsf{Setup}(m))$
-		\EndFor
-		\State \textbf{store} (subfilters, $L$, $m$, counter)
-		\State\Return filter
-	\EndFunction 
-	\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\Function{Lookup}{$e$}
-		\For{$i$ from $0$ to $L-1$}
-			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
-				\State \Return $\DUPLICATE$
-			\EndIf
-		\EndFor
-		\State \Return \UNSEEN
-	\EndFunction
-	\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\Function{Insert}{$e$}
-		\State subfilters[0]$.\mathsf{Insert}(e)$
-		\State counter $\gets$ counter + 1 
-		\If{counter == $c$}
-			\State subfilters.pop()
-			\State subfilters.push\_first($\mathcal F.\textsf{Setup}(m)$)
+		\State $Q.\mathsf{Push\_Front}(h(e))$
+
+		\If{$Q.\mathsf{length}() > w$}
+			\State $h' \gets Q.\mathsf{Pop\_back}()$
 		\EndIf
@@
 
-\subsection{Error rate analysis}
-The queuing filter's properties can be derived from the subfilters'.
-False positive and false negative rates are of particular interest.
-In this section we consider a queuing filter $\mathcal Q$ with $L$ subfilters of type $\mathcal F$ and
-capacity $c$ (which means that the last subfilter is dropped after $c$ insertions).
-
-\paragraph{Remark.}
-	\label{subsub:number_elements}
-	By definition, after $c$ insertions the last subfilter is dropped.
-Information-theoretically, this means that all the information related to the elements inserted in that subfilter has been lost, and there are $c$ such elements by design. 
-Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements (immediately after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).
-
-As a result, if $w < cL$, the queuing filter can hold information about \emph{more than $w$ elements}.
-
-\subsubsection{Probability of False Positive}
+\subsection{Error Rates}
+Let $w> 0$ be a window size and $M > 0$ the available memory.
+
+We write $\FN^w_\text{SHF}$ the probability of false negative of an SHF with these parameters. We similarly define $\FP^w_\text{SHF}$, $\FN^w_\text{CSHF}$, $\FP^w_\text{CSHF}$.
 
 \begin{theorem}	
-	\label{thm:queue-pfp}
-	 Let $\FP_{\mathcal Q, m}^w$ be the probability of false positive (def. \ref{def:pfp-pfn}) of $\mathcal Q$ after $m > w$ insertions, over a sliding window of size $w = cL$, we have:
-	\begin{equation}
-		\label{eq:queue-pfp}
-		\FP_{\mathcal Q, m}^w = 1 - \left(1 - \FP_{\mathcal F,c}\right)^{L-1} \left(1 - \FP_{\mathcal F, m \bmod c }\right)
-	\end{equation}
-	where $\bmod$ is the modulo operator and 
-	 $\FP_{\mathcal F,m}$ be the probability of false positive a subfilter $\mathcal F$ after $m$ insertions.
+	\begin{align*}
+		\FN_\text{SHF}^w&  = \FN_\text{CSHF}^w =0 \\
+		\FP_\text{SHF}^w & = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w \\
+		\FP_\text{CSHF}^w & = 1 - \left(1 - 2^{-M/w}\right)^w
+	\end{align*}
 \end{theorem}
@@
 \begin{proof}
-	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream and $e^\star \notwdup E$.
-
-	Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
-Conversely, $e^\star$ is \emph{not} a false positive when all subqueries $\mathcal F_i.\mathsf{Lookup(e^\star)}$ return \UNSEEN, i.e., when $e^\star$ is not a false positive for each subfilter.
-
-	Each subfilter has undergone $c$ insertions, safe for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
+	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$, while a CSHF has fingerprints of size $h' = \frac Mw$.
 \end{proof}
 
-\paragraph{Remark.} In the case $w < cL$, as mentioned previously, there is a non-zero probability that $e^\star$ is in the last subfilter's memory, despite not belonging to the sliding window.
-
-Assuming a uniformly random input stream, and writing $\delta = cL - w$, the probability that $e^\star$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta$.
-For large $\Gamma$ (as is expected to be the case in most applications), this probability is about $\frac{\delta}{|\Gamma|} \ll 1$.
-Hence, we can neglect the probability that $e^\star$ is present in the filter, and we consider the result of Theorem~\ref{thm:queue-pfp} to be a very good approximation even when $w < cL$.
-
-\subsubsection{Probability of False Negative}\label{sub:fnr}
-\begin{theorem}
-	\label{thm:queue-pfn}
-	Let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation}
-	\FN_{\mathcal Q, m}^w 
-	=  u_c^{L-1} u_{m \bmod c}
-	\end{equation}
-	where $\bmod$ is the modulo operator, and we have introduced the short-hand notation $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$ where 
-	$\FN_{\mathcal F,\eta}$ (resp. $\FP_{\mathcal F, \eta}$) is the probability of false negative (resp. false positive) of the subfilter $\mathcal F$ after $\eta$ insertions, and
-	\begin{equation*}
-		p_\eta = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^\eta}{1-\left(1-\frac 1{|\Gamma|}\right)^w} \approx \frac{\eta}{w}.
-	\end{equation*}
-\end{theorem}
-
-\begin{proof}
-	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
-
-	Then $e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$. There can be two cases:
-	\begin{itemize}
-		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window;
-		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window.
-	\end{itemize}
-In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
-This happens with probability $\FN_{\mathcal F,c}$ by definition, except for $\mathcal F_0$, for which the probability is $\FN_{\mathcal F, m\bmod c}$.
-
-In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$, which happens with probability $1-\FP_{\mathcal F,c}$, execpt for $\mathcal F_0$, for which the probability is $1-\FP_{\mathcal F, m\bmod c}$.
-
-Finally, each event is weighted by the probability $p_c$ that $e^\star$ is in $\mathcal F_i$'s sub-sliding window:
-\begin{align*}
-	p_c 
-	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
-	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
-	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
-	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
-	& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
-\end{align*}
-This concludes the proof.
-\end{proof}
-\paragraph{Remark.} As previously, the effect of $w < cL$ is negiglible for all practical purposes and Theorem~\ref{thm:queue-pfn} is considered a good approximation in that regime.
-
-\subsection{FNR and FPR}
-From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR when $m = cn$ for $n$ a positive integer.
-\begin{theorem}
-	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation*}
-	\FPR_{\mathcal Q, cn}^w = 1 -  \frac{(1 - \FP_{\mathcal F, c})^{L-1}}{c}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell}).
-	\end{equation*}
-\end{theorem}
-\begin{proof}
-
-\begin{align*}
-	\FPR_{\mathcal Q, cn}^w
-	& = \frac{1}{cn} \sum_{k=1}^{cn} \FP_{\mathcal Q, k}^w 
-	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, k + \ell}^w 
-	 = \frac1c \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, \ell}^w \\
-	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
-	& = 1 - \frac1c(1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
-\end{align*}
-\end{proof}
-
-\begin{theorem}
-	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation*}
-	\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell.
-	\end{equation*}
-\end{theorem}
-
-\begin{proof}
-\begin{align*}
-	\FNR_{\mathcal Q, cn}^w 
-	& = \frac{1}{cn} \sum_{k=1}^{cn} \FN_{\mathcal Q, k}^w 
-	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, k + \ell}^w 
-	= \frac1c \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, \ell}^w \\
-	& = \frac1c \sum_{\ell = 0}^{c-1} u_c^{L-1} u_{\ell} 
-	 = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
-\end{align*}
-\end{proof}
-As for the probabilities, the expressions derived above for the FNR and FNR are valid to first order in $(w - cL)/|\Gamma|$, i.e. they are good approximations even when $w \approx cL$.
-
-\section{Optimising queuing filters}
-\label{sec:optimising}
-Let us relax, temporarily, the a priori constraint that $w = cL$.
-The parameter $L$ determines how many subfilters appear in the queuing construction.
-Summing up the false positive and false negative rates, we have a total error rate
-$	\operatorname{ER}_{\mathcal Q, cn}^{w}
-	= 1 - \alpha \beta^{L-1} + \alpha' \beta'^{L-1}
-$,
-where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
-$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ depend on $w$, $c$ and the choice of subfilter type $\mathcal F$.
-
-Because $u_\eta = p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$, differentiating with respect to $L$, knowing that $w = Lc$, and equating the derivative to $0$, one can find the optimal value for $L$ by solving for $x$, which has been obtained via Mathematica:
-
-%\begin{equation*}
-\begin{align*}
-&-\alpha \beta^{-1+x} \log(\beta)  \\ 
-&+ \left(\beta + \FN_{\mathcal F, c} (-1+x)\right)^{-2+x} x^{-x} \left[\vphantom{\left(\FN^{\FN}\right)}\right. \\
-&\quad
-	-\alpha \beta + \FN_{\mathcal F, c} \left(-\beta (-2+x)+ \FN_{\mathcal F, c} (-1+x)\right) \\
-&\quad	+ \left(\alpha+ \FN_{\mathcal F, c} (-1+x)\right) \\
-& \quad \quad \times\left(\beta + \FN_{\mathcal F, c} (-1+x)\right) \left(\log\left(\beta + \FN_{\mathcal F, c} (-1+x)\right)-\log(x)\right) \\
-&\left.\vphantom{\left(\FN^{\FN}\right)}\right] = 0
-\end{align*}
-
-If solving the equation for individual cases is doable, it however does not seem possible to derive a generic formula.
-%\end{equation*}
-
-%Differentiating with respect to $L$ and equating to zero gives an optimum
-%\begin{equation*}
-%	L_{c, \mathcal F} = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
-%\end{equation*} 
-%Thus for a given $c$ and choice of subfilter $\mathcal F$ we get an optimal value of $L = L_{c, \mathcal F}$,
-%and we set, \emph{a posteriori}, $w \gets cL$.
-%
-%If instead $w$ is a given value, solving $w = c L_{c, \mathcal F}$ analytically may be challenging.
-%A practical solution is to interpolate between explicitly computed values $cL_{c, \mathcal F}$ to find the 
-%closest match for the target $w$.
-%
-%\todo[À vérifier la suite je suis pas convaincu encore]
-%\begin{theorem}
-%	In first approximation, a low value of $L$ for constant value $cL$ leads to a higher false negative probability for the queuing filter.
-%\end{theorem}
-%
-%\begin{proof}
-%As a matter of fact, on average the queuing filter consists of $L-1$ subfilters with $c$ insertions, and one subfilter with $\frac c2$ insertions.
-As such, we can say that the queuing filter is a representation of the last $(c-\frac12) L$ last elements.
-%
-%Let us consider $e^\star \wdup E$.
-If, in the sliding window, all duplicates only happened at least $(c-\frac12)L$ epochs ago (which happens with probability $\left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}$), we know that no duplicates happened in any subfilter's sliding window.
-By using the same reasoning as Theorem~\ref{thm:queue-pfn}'s proof, we get a probability of false negative of around $\left[0 + \left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}(1-\FP_{\mathcal F,c})\right]^L$.
-Given that $cL \approx w$ which is a constant, we get that the probability of false positive mostly varies, in this case, with $\left(1-\FP_{\mathcal F,c}\right)^L$.
-%
-%Hence, the lower $L$ is, the higher the probability of false negative will be.
-%
-%The approximations made in this proof are backed by experimental results.
-%\end{proof}
-
-\section{Queuing filters from existing DDFs}
-\label{sec:subfilter-select}
-\label{sec:optimal_ddf}
-Our queuing construction relies on a choice of subfilters. A first observation 
-is that we may assume that all subfilters can be instances of a single 
-DDF design (rather than a combination of different designs).
-
-Indeed, a simple symmetry argument shows that a heterogenous selection of subfilters is always worse than a homogeneous one: the crux is that all subfilters play the same role in turn.
-Therefore we lose nothing by replacing atomically one subfilter by a more efficient one.
-Applying this to each subfilter we end up with a homogenous selection.
-
-It remains to decide which subfilter construction to choose. 
-When comparing different DDFs, one interesting metric in our context is how fast
-such filters saturate: indeed, in the original DDP setting, all filters eventually saturate \cite{10.1145/3297280.3297335}, but they may reach that state more or less quickly.
-The following result gives the behaviour of a perfect filter regarding this question:
-
-\begin{theorem}
-	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $ER_n = \FP_n + \FN_n$ satisfies
-	\begin{equation}
-		ER_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
-	\end{equation}
-	for any $n > M$.
-\end{theorem}
-	In particular, the asymptotic error rate $ER_\infty$ satisfies $ER_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|$.
-
-\begin{proof}
-	By definition, a perfect filter has the lowest possible error rate.
-	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
-Up to reordering the stream, without loss of generality because it is random, we may assumethat the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
-
-	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
-On the other hand, if the element is not in memory, a perfect filter can choose to answer randomly.
-Let $p$ be the probability that a filter answers \DUPLICATE when an element is not in memory.
-An optimal filter will lower the error rate of any filter using the same strategy with a different probability.
-
-	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
-For this reason, this filter has an FP probability of $p$.
-
-	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
-Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
-Then $e^\star$ triggers a false negative with probability
-	\begin{align*}
-	\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
-	& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
-	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
-	\end{align*}
-	Hence, the error probability of the filter is
-	\begin{align*}
-		ER_n 
-		& = \FN_n + p
-		 =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
-		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
-	\end{align*}
-	which is minimized when $p = 0$. 
-	\end{proof}
-
-Note, as highlighted in the proof, that this bound is \emph{not tight}: better bounds may exist, the study of which we leave as an open question for future work.
-
-The results of an experimental comparison of different DDFs (details about the benchmark are given in Section~\ref{sub:saturation}) are summarizes in Figure~\ref{fig:graph_n}.
-It appears that the two most efficient filters (in terms of saturation rate) are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
-
-As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
-This raises the question of whether recursive constructions (queuing filters of queuing filters) have particularly interesting properties, which we leave open for future work.
-
-%In the experiments we use QHT for the benchmarking of the queuing construction.
-
-\section{Experiments and Benchmarks}\label{sec:bench}
-
-This section provides details and additional information on the benchmarking experiments run to validate the above analysis. All code is accessible online and will be disclosed after peer review.
-
-Our benchmarks cover two aspects: 
-\begin{enumerate}
-\item A measure of DDFs' saturation rate, in the original DDP setting (i.e. without a sliding window), which is used to choose a subfilter design;
-\item A measure of the effect of queuing on error rates, in the sliding window DDP setting. Namely, we compate QHT and a queuing QHT.
-\end{enumerate}
-An important note is that when the sliding window is small compared to the filter's memory size, optimal or nearly optimal solutions can be implemented (see Section~\ref{sub:opt_solutions}).
-This is practical for smaller values because we can measure exactly a filter's response compared to the \enquote{ground truth}.
-However, this is no longer possible for very large parameters as it would require too much memory for keeping track of the duplicates.
-
+\paragraph{Remark:} A CSHF of size $M$ has the same error rate than an SHF of size $2M + w\log_2 w$.
+\subsection{Saturation}
+Both SHF and CSHF have strictly increasing error rates, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
+Beyond this value, these filters saturate extremely quickly: in other words, most SHF will either have an error rate of $0$ or $1$.
+
+An illustration of this phenomenon can be seen in Figure~\ref{fig:shorts}, 
+which shows the error rates for CSHF and SHF with $M=100000$, against 
+a uniformly random stream of $18$-bit elements ($|\Gamma| = 2^{18}$). The benchmark used a finite stream of length $10^6$.
+
+\begin{figure}[!ht]
+	\centering
+	\input{graphs/bench_shorts.tex}
+	\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for various window sizes $w$.}\label{fig:shorts}
+\end{figure}
+
+The value $w_\text{max}$ can be obtained by solving (numerically) for $\FP^{w_\text{max}} = 1/2$ for a given $M$.
+Experimentally, we observed an approximately linear relationship between $M$ and $w_\text{max}$ for large values of $M$.
+
+\section{Non-windowed DDFs in a wDDP setting}
 \subsection{Saturation Resistance of DDFs}\label{sub:saturation}
@@
 
-\begin{figure}
+\begin{figure}[!ht]
 	\begin{tikzpicture}
@@
 	\end{tikzpicture}
-	\caption{Error rate (times 100) of DDFs of 1Mb, over an artificial stream, depending on the size of the stream, without any sliding window.
-Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
+	\caption{Error rate (times 100) of DDFs of 1Mb as a function of stream length. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
 \end{figure}
@@
 We also observe that QHT and SQF have error rates relatively close to the lower bound, hence suggesting that these filters are close to optimality.
+
+\subsection{Performance in wDDF}
+We now consider the performance of the filters just discussed in the \emph{windowed} setting, for which they were \emph{not} designed.
+In particular, it is not possible to adjust their parameters as a function of $w$.
+
+Remarkably, some of these filters still outperform dedicated windowed filters for some window sizes at least, as shown in Figure~\label{fig:improvement}.
+Nevertheless, we will now discuss the queuing construction, which allow us to build windowed filters from these.
+
+\section{Queuing filters}\label{sec:queue}
+We now describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
+A scheme describing our structure is detailed in Figure~\ref{fig:scheme}.
+
+\subsection{The queuing construction}
+
+\paragraph{Principle of operation.}
+Let $\mathcal F$ be a DDF.
+Rather than allocating the whole memory to $\mathcal F$, we will create $L$ copies of $\mathcal F$, each using a fraction of the available memory.
+Each of these \emph{subfilters} as a limited timespan, and is allowed up to $c$ insertions.
+The subfilters are organised in a queue.
+
+When inserting a new element in the queuing filter, it is inserted in the topmost subfilter of the queue.
+After $c$ insertions, a new empty filter is added to the queue, and the oldest subfilter is popped and erased.
+
+As such, we can consider that each subfilter operates on a sub-sliding window of size $c$, which makes the overall construction a DDF operating over a sliding window of size $w = cL$.
+
+\begin{figure}
+	\input{fig/queuef.tex}
+	\caption{Architecture of the queuing filter.
+The filter is composed of $L$ subfilters $\mathcal F$, each containing up to $c$ elements.
+Once the newest subfilter has inserted $c$ elements in its structure, the oldest one is expired.
+As such, it is dropped and a new one is created and put under population at the beginning of the queue.
+In this example, the sub-sliding window of $\mathcal F_1$ is $(e_{m-2}, e_{m-3}, e_{m-4})$.} \label{fig:scheme}
+\end{figure}
+
+\paragraph{Insertion and lookup.}
+The filter returns \DUPLICATE if and only if at least one subfilter does. Insertion is a simple insertion in the topmost subfilter.
+
+\paragraph{Queue update.}
+After $c$ insertions, the last filter of the queue is dropped, and a new (empty) filter is appended in front of the queue.
+
+\paragraph{Pseudocode.}
+We give a brief pseudocode for the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in Algorithm~\ref{alg:queuing}.
+We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
+Here \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first position.\footnote{Two standard ways to implement this are a double-ended queue (deque) and a ring buffer.}
+
+\begin{algorithm}[]
+	\caption{Queuing Filter Setup, Lookup and Insert}\label{alg:queuing}
+
+	\begin{algorithmic}[1]
+	\Function{Setup}{$\mathcal F, M, L, c$}
+		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
+		\State subfilters $\gets \emptyset$
+		\State counter $\gets 0$
+		\State $m \gets \lfloor M/L \rfloor$
+		\For{$i$ from $0$ to $L-1$}
+			\State subfilters.push\_first$(\mathcal F.\mathsf{Setup}(m))$
+		\EndFor
+		\State \textbf{store} (subfilters, $L$, $m$, counter)
+		\State\Return filter
+	\EndFunction 
+	\item[]
+	\end{algorithmic}
+
+	\begin{algorithmic}[1]
+	\Function{Lookup}{$e$}
+		\For{$i$ from $0$ to $L-1$}
+			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
+				\State \Return $\DUPLICATE$
+			\EndIf
+		\EndFor
+		\State \Return \UNSEEN
+	\EndFunction
+	\item[]
+	\end{algorithmic}
+
+	\begin{algorithmic}[1]
+	\Function{Insert}{$e$}
+		\State subfilters[0]$.\mathsf{Insert}(e)$
+		\State counter $\gets$ counter + 1 
+		\If{counter == $c$}
+			\State subfilters.pop()
+			\State subfilters.push\_first($\mathcal F.\textsf{Setup}(m)$)
+		\EndIf
+	\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+\subsection{Error rate analysis}
+The queuing filter's properties can be derived from the subfilters'.
+False positive and false negative rates are of particular interest.
+In this section we consider a queuing filter $\mathcal Q$ with $L$ subfilters of type $\mathcal F$ and
+capacity $c$ (which means that the last subfilter is dropped after $c$ insertions).
+
+\paragraph{Remark.}
+	\label{subsub:number_elements}
+	By definition, after $c$ insertions the last subfilter is dropped.
+Information-theoretically, this means that all the information related to the elements inserted in that subfilter has been lost, and there are $c$ such elements by design. 
+Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements (immediately after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).
+
+As a result, if $w < cL$, the queuing filter can hold information about \emph{more than $w$ elements}.
+
+\subsubsection{Probability of False Positive}
+
+\begin{theorem}
+	\label{thm:queue-pfp}
+	 Let $\FP_{\mathcal Q, m}^w$ be the probability of false positive (def. \ref{def:pfp-pfn}) of $\mathcal Q$ after $m > w$ insertions, over a sliding window of size $w = cL$, we have:
+	\begin{equation}
+		\label{eq:queue-pfp}
+		\FP_{\mathcal Q, m}^w = 1 - \left(1 - \FP_{\mathcal F,c}\right)^{L-1} \left(1 - \FP_{\mathcal F, m \bmod c }\right)
+	\end{equation}
+	where $\bmod$ is the modulo operator and 
+	 $\FP_{\mathcal F,m}$ be the probability of false positive a subfilter $\mathcal F$ after $m$ insertions.
+\end{theorem}
+
+\begin{proof}
+	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream and $e^\star \notwdup E$.
+
+	Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
+Conversely, $e^\star$ is \emph{not} a false positive when all subqueries $\mathcal F_i.\mathsf{Lookup(e^\star)}$ return \UNSEEN, i.e., when $e^\star$ is not a false positive for each subfilter.
+
+	Each subfilter has undergone $c$ insertions, safe for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
+\end{proof}
+
+\paragraph{Remark.} In the case $w < cL$, as mentioned previously, there is a non-zero probability that $e^\star$ is in the last subfilter's memory, despite not belonging to the sliding window.
+
+Assuming a uniformly random input stream, and writing $\delta = cL - w$, the probability that $e^\star$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta$.
+For large $\Gamma$ (as is expected to be the case in most applications), this probability is about $\frac{\delta}{|\Gamma|} \ll 1$.
+Hence, we can neglect the probability that $e^\star$ is present in the filter, and we consider the result of Theorem~\ref{thm:queue-pfp} to be a very good approximation even when $w < cL$.
+
+\subsubsection{Probability of False Negative}\label{sub:fnr}
+\begin{theorem}
+	\label{thm:queue-pfn}
+	Let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
+	\begin{equation}
+	\FN_{\mathcal Q, m}^w 
+	=  u_c^{L-1} u_{m \bmod c}
+	\end{equation}
+	where $\bmod$ is the modulo operator, and we have introduced the short-hand notation $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$ where 
+	$\FN_{\mathcal F,\eta}$ (resp. $\FP_{\mathcal F, \eta}$) is the probability of false negative (resp. false positive) of the subfilter $\mathcal F$ after $\eta$ insertions, and
+	\begin{equation*}
+		p_\eta = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^\eta}{1-\left(1-\frac 1{|\Gamma|}\right)^w} \approx \frac{\eta}{w}.
+	\end{equation*}
+\end{theorem}
+
+\begin{proof}
+	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
+
+	Then $e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$. There can be two cases:
+	\begin{itemize}
+		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window;
+		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window.
+	\end{itemize}
+In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
+This happens with probability $\FN_{\mathcal F,c}$ by definition, except for $\mathcal F_0$, for which the probability is $\FN_{\mathcal F, m\bmod c}$.
+
+In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$, which happens with probability $1-\FP_{\mathcal F,c}$, execpt for $\mathcal F_0$, for which the probability is $1-\FP_{\mathcal F, m\bmod c}$.
+
+Finally, each event is weighted by the probability $p_c$ that $e^\star$ is in $\mathcal F_i$'s sub-sliding window:
+\begin{align*}
+	p_c 
+	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
+	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
+	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
+	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
+	& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
+\end{align*}
+This concludes the proof.
+\end{proof}
+\paragraph{Remark.} As previously, the effect of $w < cL$ is negiglible for all practical purposes and Theorem~\ref{thm:queue-pfn} is considered a good approximation in that regime.
+
+\subsection{FNR and FPR}
+From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR when $m = cn$ for $n$ a positive integer.
+\begin{theorem}
+	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
+	\begin{equation*}
+	\FPR_{\mathcal Q, cn}^w = 1 -  \frac{(1 - \FP_{\mathcal F, c})^{L-1}}{c}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell}).
+	\end{equation*}
+\end{theorem}
+\begin{proof}
+
+\begin{align*}
+	\FPR_{\mathcal Q, cn}^w
+	& = \frac{1}{cn} \sum_{k=1}^{cn} \FP_{\mathcal Q, k}^w 
+	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, k + \ell}^w 
+	 = \frac1c \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, \ell}^w \\
+	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
+	& = 1 - \frac1c(1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
+\end{align*}
+\end{proof}
+
+\begin{theorem}
+	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
+	\begin{equation*}
+	\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell.
+	\end{equation*}
+\end{theorem}
+
+\begin{proof}
+\begin{align*}
+	\FNR_{\mathcal Q, cn}^w 
+	& = \frac{1}{cn} \sum_{k=1}^{cn} \FN_{\mathcal Q, k}^w 
+	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, k + \ell}^w 
+	= \frac1c \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, \ell}^w \\
+	& = \frac1c \sum_{\ell = 0}^{c-1} u_c^{L-1} u_{\ell} 
+	 = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
+\end{align*}
+\end{proof}
+As for the probabilities, the expressions derived above for the FNR and FNR are valid to first order in $(w - cL)/|\Gamma|$, i.e. they are good approximations even when $w \approx cL$.
+
+\section{Optimising queuing filters}
+\label{sec:optimising}
+Let us relax, temporarily, the a priori constraint that $w = cL$.
+The parameter $L$ determines how many subfilters appear in the queuing construction.
+Summing up the false positive and false negative rates, we have a total error rate
+$	\operatorname{ER}_{\mathcal Q, cn}^{w}
+	= 1 - \alpha \beta^{L-1} + \alpha' \beta'^{L-1}
+$,
+where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
+$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ depend on $w$, $c$ and the choice of subfilter type $\mathcal F$.
+
+Because $u_\eta = p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$, differentiating with respect to $L$, knowing that $w = Lc$, and equating the derivative to $0$, one can find the optimal value for $L$ by solving for $x$, which has been obtained via Mathematica:
+
+%\begin{equation*}
+\begin{align*}
+&-\alpha \beta^{-1+x} \log(\beta)  \\ 
+&+ \left(\beta + \FN_{\mathcal F, c} (-1+x)\right)^{-2+x} x^{-x} \left[\vphantom{\left(\FN^{\FN}\right)}\right. \\
+&\quad
+	-\alpha \beta + \FN_{\mathcal F, c} \left(-\beta (-2+x)+ \FN_{\mathcal F, c} (-1+x)\right) \\
+&\quad	+ \left(\alpha+ \FN_{\mathcal F, c} (-1+x)\right) \\
+& \quad \quad \times\left(\beta + \FN_{\mathcal F, c} (-1+x)\right) \left(\log\left(\beta + \FN_{\mathcal F, c} (-1+x)\right)-\log(x)\right) \\
+&\left.\vphantom{\left(\FN^{\FN}\right)}\right] = 0
+\end{align*}
+
+If solving the equation for individual cases is doable, it however does not seem possible to derive a generic formula.
+%\end{equation*}
+
+%Differentiating with respect to $L$ and equating to zero gives an optimum
+%\begin{equation*}
+%	L_{c, \mathcal F} = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
+%\end{equation*} 
+%Thus for a given $c$ and choice of subfilter $\mathcal F$ we get an optimal value of $L = L_{c, \mathcal F}$,
+%and we set, \emph{a posteriori}, $w \gets cL$.
+%
+%If instead $w$ is a given value, solving $w = c L_{c, \mathcal F}$ analytically may be challenging.
+%A practical solution is to interpolate between explicitly computed values $cL_{c, \mathcal F}$ to find the 
+%closest match for the target $w$.
+%
+%\todo[À vérifier la suite je suis pas convaincu encore]
+%\begin{theorem}
+%	In first approximation, a low value of $L$ for constant value $cL$ leads to a higher false negative probability for the queuing filter.
+%\end{theorem}
+%
+%\begin{proof}
+%As a matter of fact, on average the queuing filter consists of $L-1$ subfilters with $c$ insertions, and one subfilter with $\frac c2$ insertions.
+As such, we can say that the queuing filter is a representation of the last $(c-\frac12) L$ last elements.
+%
+%Let us consider $e^\star \wdup E$.
+If, in the sliding window, all duplicates only happened at least $(c-\frac12)L$ epochs ago (which happens with probability $\left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}$), we know that no duplicates happened in any subfilter's sliding window.
+By using the same reasoning as Theorem~\ref{thm:queue-pfn}'s proof, we get a probability of false negative of around $\left[0 + \left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}(1-\FP_{\mathcal F,c})\right]^L$.
+Given that $cL \approx w$ which is a constant, we get that the probability of false positive mostly varies, in this case, with $\left(1-\FP_{\mathcal F,c}\right)^L$.
+%
+%Hence, the lower $L$ is, the higher the probability of false negative will be.
+%
+%The approximations made in this proof are backed by experimental results.
+%\end{proof}
+
+\section{Queuing filters from existing DDFs}
+\label{sec:subfilter-select}
+\label{sec:optimal_ddf}
+Our queuing construction relies on a choice of subfilters. A first observation 
+is that we may assume that all subfilters can be instances of a single 
+DDF design (rather than a combination of different designs).
+
+Indeed, a simple symmetry argument shows that a heterogenous selection of subfilters is always worse than a homogeneous one: the crux is that all subfilters play the same role in turn.
+Therefore we lose nothing by replacing atomically one subfilter by a more efficient one.
+Applying this to each subfilter we end up with a homogenous selection.
+
+It remains to decide which subfilter construction to choose. 
+When comparing different DDFs, one interesting metric in our context is how fast
+such filters saturate: indeed, in the original DDP setting, all filters eventually saturate \cite{10.1145/3297280.3297335}, but they may reach that state more or less quickly.
+The following result gives the behaviour of a perfect filter regarding this question:
+
+\begin{theorem}
+	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $ER_n = \FP_n + \FN_n$ satisfies
+	\begin{equation}
+		ER_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
+	\end{equation}
+	for any $n > M$.
+\end{theorem}
+	In particular, the asymptotic error rate $ER_\infty$ satisfies $ER_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|$.
+
+\begin{proof}
+	By definition, a perfect filter has the lowest possible error rate.
+	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
+Up to reordering the stream, without loss of generality because it is random, we may assumethat the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
+
+	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
+On the other hand, if the element is not in memory, a perfect filter can choose to answer randomly.
+Let $p$ be the probability that a filter answers \DUPLICATE when an element is not in memory.
+An optimal filter will lower the error rate of any filter using the same strategy with a different probability.
+
+	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
+For this reason, this filter has an FP probability of $p$.
+
+	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
+Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
+Then $e^\star$ triggers a false negative with probability
+	\begin{align*}
+	\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
+	& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
+	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
+	\end{align*}
+	Hence, the error probability of the filter is
+	\begin{align*}
+		ER_n 
+		& = \FN_n + p
+		 =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
+		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
+	\end{align*}
+	which is minimized when $p = 0$. 
+	\end{proof}
+
+Note, as highlighted in the proof, that this bound is \emph{not tight}: better bounds may exist, the study of which we leave as an open question for future work.
+
+The results of an experimental comparison of different DDFs (details about the benchmark are given in Section~\ref{sub:saturation}) are summarizes in Figure~\ref{fig:graph_n}.
+It appears that the two most efficient filters (in terms of saturation rate) are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
+
+As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
+This raises the question of whether recursive constructions (queuing filters of queuing filters) have particularly interesting properties, which we leave open for future work.
+
+%In the experiments we use QHT for the benchmarking of the queuing construction.
+
+\section{Experiments and Benchmarks}\label{sec:bench}
+
+This section provides details and additional information on the benchmarking experiments run to validate the above analysis. All code is accessible online and will be disclosed after peer review.
+
+Our benchmarks cover two aspects: 
+\begin{enumerate}
+\item A measure of DDFs' saturation rate, in the original DDP setting (i.e. without a sliding window), which is used to choose a subfilter design;
+\item A measure of the effect of queuing on error rates, in the sliding window DDP setting. Namely, we compate QHT and a queuing QHT.
+\end{enumerate}
+An important note is that when the sliding window is small compared to the filter's memory size, optimal or nearly optimal solutions can be implemented (see Section~\ref{sub:opt_solutions}).
+This is practical for smaller values because we can measure exactly a filter's response compared to the \enquote{ground truth}.
+However, this is no longer possible for very large parameters as it would require too much memory for keeping track of the duplicates.
 

### 2020-03-27 qhtv2.tex

@@
 More importantly, in some practical cases the maximal amount of available memory is fixed beforehand.
-Fixing the memory is also more practical for benchmarking various data structures, as it gives the guarantee that all filters operate under the same conditions.
+Fixing the memory is also more practical for benchmarking data structures, as it gives the guarantee that all filters operate under the same conditions.
 
@@
 An illustration of this phenomenon can be seen in Figure~\ref{fig:shorts}, 
-which shows the error rates for CSHF and SHF with $M=100000$, against 
+which shows the error rates for CSHF and SHF with $M=10^5$, against 
 a uniformly random stream of $18$-bit elements ($|\Gamma| = 2^{18}$). The benchmark used a finite stream of length $10^6$.
@@
 	\input{graphs/bench_shorts.tex}
-	\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for various window sizes $w$.}\label{fig:shorts}
+	\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:shorts}
 \end{figure}
@@
 The value $w_\text{max}$ can be obtained by solving (numerically) for $\FP^{w_\text{max}} = 1/2$ for a given $M$.
-Experimentally, we observed an approximately linear relationship between $M$ and $w_\text{max}$ for large values of $M$.
+We numerically solved the equation $\FP^w = 0.5$ for these two filters, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$.
+Results are given in Figure~\ref{fig:w_opt} and indicate an approximately linear relationship between $M$ and $w_\text{max}$ for large values of $M$: $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).
+
+\begin{figure}[]
+	\input{graphs/w_opt_shf.tex}
+	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 0.5 ($\pm 0.001$), for several values of $M$.}\label{fig:w_opt}
+\end{figure}
 
@@
 
-\subsection{Performance in wDDF}
+\subsection{Performance in wDDP}
 We now consider the performance of the filters just discussed in the \emph{windowed} setting, for which they were \emph{not} designed.
@@
 
-Remarkably, some of these filters still outperform dedicated windowed filters for some window sizes at least, as shown in Figure~\label{fig:improvement}.
+Remarkably, some of these filters still outperform dedicated windowed filters for some window sizes at least, as shown in Figure~\label{fig:nwddf-in-wddp}.
 Nevertheless, we will now discuss the queuing construction, which allow us to build windowed filters from these.
+
+\begin{figure}
+	\centering
+	[TODO]
+	\caption{TODO}
+	\label{fig:nwddf-in-wddp}
+\end{figure}
 
@@
 
-\section{Optimising queuing filters}
+\subsection{Optimising queuing filters}
 \label{sec:optimising}
@@
 \end{align*}
-
-If solving the equation for individual cases is doable, it however does not seem possible to derive a generic formula.
+If numerically solving the equation for individual cases is feasible, it seems unlikely that a closed-form formula exists.
 %\end{equation*}
@@
 
-Our benchmarks cover two aspects: 
-\begin{enumerate}
-\item A measure of DDFs' saturation rate, in the original DDP setting (i.e. without a sliding window), which is used to choose a subfilter design;
-\item A measure of the effect of queuing on error rates, in the sliding window DDP setting. Namely, we compate QHT and a queuing QHT.
-\end{enumerate}
-An important note is that when the sliding window is small compared to the filter's memory size, optimal or nearly optimal solutions can be implemented (see Section~\ref{sub:opt_solutions}).
-This is practical for smaller values because we can measure exactly a filter's response compared to the \enquote{ground truth}.
-However, this is no longer possible for very large parameters as it would require too much memory for keeping track of the duplicates.
-
-\subsection{Benchmarking Queuing Filters}
-We now use the queuing construction on the DDFs discussed previously.
-In Section~\ref{sec:optimal_ddf} we suggested the heuristic that the DDFs with the least saturation rate in the DDP would yield the best (error-wise) queuing filter for the sliding window DDP.
+\paragraph{Benchmarking queuing filters.}
+Applying the queuing construction to DDFs from the literature, we get new filters which are compared in the wDDP setting.
+
+In Section~\ref{sec:optimal_ddf} we suggested the heuristic that the DDFs with the least saturation rate in the DDP would yield the best (error-wise) queuing filter for the wDDP.
 This heuristic is supported by results, summarized in Figure~\ref{tab:comparing_queuing}.
@@
 	\input{graphs/compare_queues.tex}
-	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=10^5$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
+	\caption{Error rate (times 100) of queuing filters as a function of window size, $M=10^5$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
 \end{figure}
@@
 
-\subsection{The number of subfilters}\label{sub:L_bench}
-We now compare the efficiency of the queueing filter, depending on the number of subfilters $L$.
-For this, we used a queueing QQHTD, on an artificial dataset of alphabet size $\Gamma = 2^{16}$, with 100 000 elements in the stream, on various sliding window sizes.
-
-Results are displayed in Figure~\ref{fig:bench_l}.
-
-\begin{figure}
+\paragraph{The number of subfilters}\label{sub:L_bench}
+The number of subfilters $L$ is an important parameter in the queuing construction, as it affects the filter's error rate in a nontrivial way.
+An illustration of this dependence is shown in Figure~\ref{fig:bench_l} which plots the error rate of a queueing QQHTD on an uniform stream of alphabet size $\Gamma = 2^{16}$, with $10^5$ elements in the stream, on various sliding window sizes.
+
+\begin{figure}[!ht]
 	\input{graphs/bench_l.tex}
-	\caption{Evolution of the error rate of a queueing QHT depending on the $L$ value, for various sliding window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
+	\caption{Evolution of the error rate of a queueing QHT as a function of $L$, for several window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
 \end{figure}
@@
 We observe that the optimal value for $L$ does indeed depend on the desired sliding window.
-However, other experiments on alphabets of other sizes yield very similar results, hence validating the observation made in Section~\ref{sec:optimising} that the optimal number of subfilters does not depends on the alphabet (in first approximation).
-
-\subsection{Comparison of QHT and QHT-Queuing Filter}
-In this section, we compare the efficiency of QHT and QHT-queuing filter.
-For this, we used the same artificial dataset as previously, as well as the same QHT filter than in previous sections.
-Moreover, we add a queuing QHT with an optimal value $L$ for each considered sliding window.
-For the sake of completeness, we also ran the comparison on the other DDFs.
+However, other experiments on alphabets of other sizes yield very similar results, hence validating the observation made in Section~\ref{sec:optimising} that the optimal number of subfilters does not depends on the alphabet, at least in first approximation.
+
+\paragraph{Filters vs queued filters.}
+Using the same stream as previously, we can build queued filters (with an optimal value $L$ for each considered sliding window) and compare their performances to that of non-modified filters.
 Results on the QHT and SQF are shown in Figure~\ref{fig:improvement}, results for the Cuckoo and SBF are shown in Appendix~\ref{app:improvement}.
 
-\begin{figure}
+\begin{figure}[!ht]
 	\input{graphs/improvement.tex}
-	\caption{Comparing performances of various filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:improvement}
+	\caption{Comparing performances of QHT and SQF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:improvement}
 \end{figure}
@@
 However, simulations are necessarily finite, and for very large windows (that are approximately the same size as the whole stream) this causes interesting artefacts in the error rates.
+
 Note that these effects have very little impact on practical implementations of queuing filters, since almost all use cases assume a window size much smaller than the stream (or, equivalently, a very large stream).
@@
 
-\section{Comparing DDFs and their Queueing Counterpart}\label{app:improvement}
+\section{Filters vs queued filters (complement)}\label{app:improvement}
 We here run a comparison of the Cuckoo Filter relative to the Queueing Cuckoo Filter, as well as the SBF relatively to the queueing SBF. The results are given in Figure~\ref{fig:appendix_improvement}.
@@
 \end{tikzpicture}
-	\caption{Comparing performances of various filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
+	\caption{Comparing performances of the Cuckoo and SBF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
 \end{figure*}
-
 \end{document}

### 2020-03-27 qhtv2.tex
Insert graph + some fixes
Fix graphs

@@
 
-\begin{algorithm}[!ht]
+\begin{algorithm}[!h]
 	\caption{SHF Setup, Lookup and Insert}\label{alg:SHF}
@@
 
-\begin{algorithm}[!ht]
+\begin{algorithm}[!h]
 	\caption{CSHF, Lookup and Insert}\label{alg:CSHF}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
 	\centering
@@
 We numerically solved the equation $\FP^w = 0.5$ for these two filters, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$.
-Results are given in Figure~\ref{fig:w_opt} and indicate an approximately linear relationship between $M$ and $w_\text{max}$ for large values of $M$: $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).
-
-\begin{figure}[]
-	\input{graphs/w_opt_shf.tex}
-	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 0.5 ($\pm 0.001$), for several values of $M$.}\label{fig:w_opt}
-\end{figure}
+Results
+% are given in Figure~\ref{fig:w_opt} and 
+indicate an approximately linear relationship between $M$ and $w_\text{max}$ for large values of $M$: $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).
+
+%\begin{figure}[]
+%	\input{graphs/w_opt_shf.tex}
+%	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 0.5 ($\pm 0.001$), for several values of $M$.}\label{fig:w_opt}
+%\end{figure}
 
@@
 
-%\begin{figure*}[!ht]
+%\begin{figure*}[!h]
 %	\begin{tikzpicture}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
 	\begin{tikzpicture}
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
-	[TODO]
-	\caption{TODO}
+	\input{graphs/compare_qht_bdbf_a2.tex}
+	\caption{Error rates for QHT, b\_DBF, and A2. While A2 and b\_DBF were designed and ajusted to the wDDP, this is not the case of QHT. Still, QHT outperforms these filters for some values of $w$.}
 	\label{fig:nwddf-in-wddp}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
 	\input{graphs/compare_queues.tex}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
 	\input{graphs/bench_l.tex}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
 	\input{graphs/improvement.tex}
@@
 
-\begin{figure*}[!ht]
+\begin{figure}[]
 	\centering
@@
 	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[!ht]
+\begin{figure}[]
 \begin{tikzpicture}
-	\begin{semilogxaxis}[legend cell align = left, legend pos=outer north east, xlabel=$w$, ylabel=$\FPR^w + \FNR^w (\times 100)$]
+	\begin{semilogxaxis}[legend cell align = left,%
+		 %legend pos=outer north east, 
+	legend style={at={(0.02,0.98)},anchor=north west},%
+		 xlabel=$w$, ylabel=$\FPR^w + \FNR^w (\times 100)$]
 	\addplot[color=teal, mark=triangle] table[x=w,y=Error] {Queueing_Cuckoo.dat};
@@
 	\addplot[color=olive, mark=square, mark options = {scale=0.7}] table[x=w,y=Error] {Queueing_StableBloom.dat};
-	\addlegendentry{$Q\_SBF$};
+	\addlegendentry{Q\_SBF};
 	\addplot[color=olive, mark=square, mark options = {scale=0.7}, dashed] table[x=w,y=Error] {SBF.dat};
-	\addlegendentry{$SBF$};
+	\addlegendentry{SBF};
 
@@
 	\caption{Comparing performances of the Cuckoo and SBF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
-\end{figure*}
+\end{figure}
 \end{document}

### 2020-03-30 qhtv2.tex
mise en page

@@
 %Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable. 
-Perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory \cite[Theorem 2.1]{10.1145/3297280.3297335}: even for modest situations (e.g.
+%Perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory \cite[Theorem 2.1]{10.1145/3297280.3297335}: even for modest situations (e.g.
 64-bit nonces, corresponding to $2^{64}$ possible values) this is quickly impractical.
 As a result, we need a further relaxation of the DDP that allows for errors:
+Perfect detection is however not always reachable and it might be more practical to work on a further relaxation of the problem, allowing for errors:
 \begin{definition}[Approximate wDDP with bounded memory]
@@
 As the window size in wDDP grows infinitely large, it becomes the following problem: find whether $e^\star \in E_n$.
-This \enquote{non-windowed} problem predates in fact the definition of wDDP, and several algorithms have been proposed for this problem: \cite{Den06,10.1145/3297280.3297335,Dut13} and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-Unfortunately \emph{all} these solutions face a phenomenon called \enquote{saturation} on large enough data streams.
+%This \enquote{non-windowed} problem predates in fact the definition of wDDP, and several algorithms have been proposed for this problem: \cite{Den06,10.1145/3297280.3297335,Dut13} and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+Unfortunately any solution to this problem faces a phenomenon called \enquote{saturation} on large enough data streams.
 In fact, saturation is inevitable with infinite windows \cite{10.1145/3297280.3297335}, and when it happens the algorithm performs no better than at random.
@@
 The notion of using subfilters, as in the queuing construction, can be found in the A2 filter's design \cite{Yoo10} and a variation thereof can be found in \cite{shtul2020agepartitioned} but in a different DDP formulation.
-The A2 is built from two Bloom filters, a situation which we generalise and analyse generically in this paper.
+The A2 is built from two Bloom filters, a construction which we generalise and analyse generically in this paper.
 Similarly, the construction in \cite{shtul2020agepartitioned} only works with Bloom Filters.
@@
 
+\paragraph{Remark.} For benchmarking, we usually measure the error rate $ER = \FPR^w + \FNR^w$, as it allows a practical ranking of the solutions.
+An error rate of $0$ means a perfect filter, while a filter answering randomly has an error rate of $1$.
+A filter being always wrong has an error rate of $2$.
+
 %\subsection{Filter Saturation and Sliding Windows}\label{sec:filsat}
@@
 
-	Whe an element $e$ is inserted in the DDF, $e$ is stored and $D[e]$ is incremented (if the key $e$ did not exist in $D$, it is created first, and
+	When an element $e$ is inserted in the DDF, $e$ is stored and $D[e]$ is incremented (if the key $e$ did not exist in $D$, it is created first, and
 	$D[e]$ is set to $1$). In order to keep the number of stored elements to $w$, 
@@
 
-	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element was present in the sliding window.
+	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element is present in the sliding window.
 \end{proof}
@@
 \begin{algorithm}[!h]
-	\caption{CSHF, Lookup and Insert}\label{alg:CSHF}
+	\caption{CSHF, Setup, Lookup and Insert}\label{alg:CSHF}
 
@@
 \section{Non-windowed DDFs in a wDDP setting}
+\subsection{Lower Bound on the Saturation Resistance}
+As said in the introduction, it has been proven \cite{10.1145/3297280.3297335} that all filters will reach saturation on the DDP setting.
+However, they sometimes prove to be efficient in some specific wDDP settings.
+
+This bound is useful for several reasons, notably it provides an estimation of how close to optimality existing filters are.
+
+\begin{theorem}
+	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $ER_n = \FP_n + \FN_n$ satisfies
+	\begin{equation}
+	ER_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
+	\end{equation}
+	for any $n > M$.
+\end{theorem}
+In particular, the asymptotic error rate $ER_\infty$ satisfies $ER_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|$.
+
+\begin{proof}
+	By definition, a perfect filter has the lowest possible error rate.
+	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
+Up to reordering the stream, without loss of generality because it is random, we may assumethat the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
+
+	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
+On the other hand, if the element is not in memory, a perfect filter can choose to answer randomly.
+Let $p$ be the probability that a filter answers \DUPLICATE when an element is not in memory.
+An optimal filter will lower the error rate of any filter using the same strategy with a different probability.
+
+	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
+For this reason, this filter has an FP probability of $p$.
+
+	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
+Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
+Then $e^\star$ triggers a false negative with probability
+	\begin{align*}
+		\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
+		& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
+		\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
+	\end{align*}
+	Hence, the error probability of the filter is
+	\begin{align*}
+		E_n 
+		& = \FN_n + p
+		=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
+		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
+	\end{align*}
+	which is minimized when $p = 0$. 
+\end{proof}
+
+Note, as highlighted in the proof, that this bound is \emph{not tight}: better bounds may exist, the study of which we leave as an open question for future work.
+
 \subsection{Saturation Resistance of DDFs}\label{sub:saturation}
-We evaluate the saturation rate for several DDFs, in the original DDP setting (without sliding window).
-Parameters are chosen to yield equivalent memory footprints and agree with \cite{10.1145/3297280.3297335}, namely:
+We now evaluate the saturation rate for several DDFs, in the original DDP setting (without sliding window).
+Parameters are chosen to yield equivalent memory footprints and were taken from \cite{10.1145/3297280.3297335}, namely:
 %
@@
 	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
-	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
+%	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
 %	\item Block-Decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of 6000 elements.
@@
 %
+
 These filters are run against a stream of uniformly sampled elements from an alphabet of $2^{26}$ elements.
@@
 The best results are given by the following filters, in order: QHT, SQF, Cuckoo and SBF.
-We also observe that QHT and SQF have error rates relatively close to the lower bound, hence suggesting that these filters are close to optimality.
+We also observe that QHT and SQF have error rates relatively close to the lower bound, hence suggesting that these filters are close to optimality, especially since the lower bound is not tight.
 
@@
 
-Remarkably, some of these filters still outperform dedicated windowed filters for some window sizes at least, as shown in Figure~\label{fig:nwddf-in-wddp}.
-Nevertheless, we will now discuss the queuing construction, which allow us to build windowed filters from these.
+Remarkably, some of these filters still outperform dedicated windowed filters for some window sizes at least, as shown in Figure~\ref{fig:nwddf-in-wddp}.
+In this benchmark, we used the following filters:
+\begin{itemize}
+	\item block decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of size $w$
+	\item A2 filter \cite{Yoo10}, changing subfilter every $w/2$ insertions
+	\item QHT \cite{10.1145/1060745.1060753}, 1 bucket per row, $3$ bits per fingerprint
+\end{itemize}
+
+Nevertheless, we will now discuss the queuing construction, which allow us to build windowed filters from the DDP filters.
 
@@
 	\input{graphs/compare_qht_bdbf_a2.tex}
-	\caption{Error rates for QHT, b\_DBF, and A2. While A2 and b\_DBF were designed and ajusted to the wDDP, this is not the case of QHT. Still, QHT outperforms these filters for some values of $w$.}
+	\caption{Error rates for QHT, b\_DBF, and A2. While A2 and b\_DBF were designed and adjusted to the wDDP, this is not the case of QHT. Still, QHT outperforms these filters for some values of $w$.}
 	\label{fig:nwddf-in-wddp}
@@
 Assuming a uniformly random input stream, and writing $\delta = cL - w$, the probability that $e^\star$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta$.
-For large $\Gamma$ (as is expected to be the case in most applications), this probability is about $\frac{\delta}{|\Gamma|} \ll 1$.
+For large $|\Gamma|$ (as is expected to be the case in most applications), this probability is about $\frac{\delta}{|\Gamma|} \ll 1$.
 Hence, we can neglect the probability that $e^\star$ is present in the filter, and we consider the result of Theorem~\ref{thm:queue-pfp} to be a very good approximation even when $w < cL$.
@@
 	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
+		\end{align*}\begin{align*}p_c
 	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
@@
 It remains to decide which subfilter construction to choose.
-When comparing different DDFs, one interesting metric in our context is how fast
-such filters saturate: indeed, in the original DDP setting, all filters eventually saturate \cite{10.1145/3297280.3297335}, but they may reach that state more or less quickly.
-The following result gives the behaviour of a perfect filter regarding this question:
-
-\begin{theorem}
-	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $ER_n = \FP_n + \FN_n$ satisfies
-	\begin{equation}
-		ER_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
-	\end{equation}
-	for any $n > M$.
-\end{theorem}
-	In particular, the asymptotic error rate $ER_\infty$ satisfies $ER_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|$.
-
-\begin{proof}
-	By definition, a perfect filter has the lowest possible error rate.
-	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
-Up to reordering the stream, without loss of generality because it is random, we may assumethat the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
-
-	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
-On the other hand, if the element is not in memory, a perfect filter can choose to answer randomly.
-Let $p$ be the probability that a filter answers \DUPLICATE when an element is not in memory.
-An optimal filter will lower the error rate of any filter using the same strategy with a different probability.
-
-	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
-For this reason, this filter has an FP probability of $p$.
-
-	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
-Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
-Then $e^\star$ triggers a false negative with probability
-	\begin{align*}
-	\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
-	& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
-	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
-	\end{align*}
-	Hence, the error probability of the filter is
-	\begin{align*}
-		ER_n 
-		& = \FN_n + p
-		 =  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
-		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
-	\end{align*}
-	which is minimized when $p = 0$. 
-	\end{proof}
-
-Note, as highlighted in the proof, that this bound is \emph{not tight}: better bounds may exist, the study of which we leave as an open question for future work.
-
 The results of an experimental comparison of different DDFs (details about the benchmark are given in Section~\ref{sub:saturation}) are summarizes in Figure~\ref{fig:graph_n}.
-It appears that the two most efficient filters (in terms of saturation rate) are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.
-
-As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
+It appears that the most efficient filter (in terms of saturation rate) is the QHT \cite{10.1145/3297280.3297335}.
+
+%As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
 This raises the question of whether recursive constructions (queuing filters of queuing filters) have particularly interesting properties, which we leave open for future work.
@@
 
+We observe that queueing filters do not necessarily behave better than their 'vanilla' counterparts, especially on large sliding windows.
+This can be interpreted by the fact that the DDPs were optimised for infinite sliding windows, and as such operate better than their queueing equivalent on large sliding windows.
+
 \section{Adversarial Resistance}

### 2020-03-30 qhtv2.tex
fini réécriture

@@
 \subsection{Contributions}
-In this paper we show that the wDDP problem can be solved exactly using $M$ bits of memory, up to a window size $w_\text{max}$; we provide an explicit algorithm achieving this, which can run in constant time.
-Allowing small errors makes it possible to push $w_\text{max}$ further; we provide the corresponding constant-time (SHF) and linear-time (CSHF) constructions.
+In this paper, we start from a naïve solution for the wDDP to then derive bounds for when it can be solved within $M$ bits of memory, up to a window size $w_\text{max}$, in constant time.
+We then introduce a generalisation of the naïve solution, and study its error rate.
+We show that this construction, which we call Short Hash Filter (SHF), can push the value $w_\text{max}$ further while operating at being constant time --at the cost of some errors.
+If allowing for linear time, we also provide a better alternative, the Compact Short Hash Filter (CSHF).
 
@@
 
-Finally, we provide an analysis of our construction's resistance to adversarial streams (Section~\ref{sec:adversarial}).
+Finally, we provide an analysis of our queueing construction's resistance to adversarial streams. (Section~\ref{sec:adversarial}).
 
@@
 
-There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FNR of $0$ and a FPR of $1 - (1-\frac1{w^2})^w$.
+There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FN of $0$ and a FP of $1 - (1-\frac1{w^2})^w$.
 The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
@@
 Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
-The CSHF performs in linear time in $w$ and is described in Algorithm~\ref{alg:CSHF}.
-
-\begin{algorithm}[!h]
-	\caption{CSHF, Setup, Lookup and Insert}\label{alg:CSHF}
-
-	\begin{algorithmic}[1]
-		\Function{Setup}{$\mathcal M, w$}
-		\Comment $M$ is the available memory, $w$ the size of the sliding window
-		\State $h \gets$ hash function of codomain size $\lfloor \frac Mw \rfloor$
-		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
-		\State\Return filter
-		\EndFunction 
-		\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-		\Function{Lookup}{$e$}
-		\State \Return $h(e) \in Q$ 
-		\EndFunction
-		\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-		\Function{Insert}{$e$}
-		\State $Q.\mathsf{Push\_Front}(h(e))$
-
-		\If{$Q.\mathsf{length}() > w$}
-			\State $h' \gets Q.\mathsf{Pop\_back}()$
-		\EndIf
-		\EndFunction
-	\end{algorithmic}
-\end{algorithm}
+The CSHF performs in linear time in $w$, and is a simple queue, the only point is that instead of storing $e$, one stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.
+
+%\begin{algorithm}[!h]
+%	\caption{CSHF, Setup, Lookup and Insert}\label{alg:CSHF}
+%	
+%	\begin{algorithmic}[1]
+%		\Function{Setup}{$\mathcal M, w$}
+%		\Comment $M$ is the available memory, $w$ the size of the sliding window
+%		\State $h \gets$ hash function of codomain size $\lfloor \frac Mw \rfloor$
+%		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
+%		\State\Return filter
+%		\EndFunction 
+%		\item[]
+%	\end{algorithmic}
+%	
+%	\begin{algorithmic}[1]
+%		\Function{Lookup}{$e$}
+%		\State \Return $h(e) \in Q$ 
+%		\EndFunction
+%		\item[]
+%	\end{algorithmic}
+%	
+%	\begin{algorithmic}[1]
+%		\Function{Insert}{$e$}
+%		\State $Q.\mathsf{Push\_Front}(h(e))$
+%		
+%		\If{$Q.\mathsf{length}() > w$}
+%			\State $h' \gets Q.\mathsf{Pop\_back}()$
+%		\EndIf
+%		\EndFunction
+%	\end{algorithmic}
+%\end{algorithm}
 
@@
 % are given in Figure~\ref{fig:w_opt} and 
-indicate an approximately linear relationship between $M$ and $w_\text{max}$ for large values of $M$: $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).
+indicate an approximately linear relationship between $M$ and $w_\text{max}$: %for large values of $M$:
+ $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).
 
@@
 	\begin{equation}
-	ER_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
+	E_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
 	\end{equation}
@@
 \end{theorem}
-In particular, the asymptotic error rate $ER_\infty$ satisfies $ER_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|$.
+In particular, the asymptotic error rate $E_\infty$ satisfies $E_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|$.
 
@@
 \begin{itemize}
-	\item block decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of size $w$
+	\item block decaying Bloom Filter\footnote{Note that by design, a b\_DBF of $10^5$ bits cannot be built over a sliding window bigger than $6000$.} (b\_DBF) \cite{She08}, sliding window of size $w$
 	\item A2 filter \cite{Yoo10}, changing subfilter every $w/2$ insertions
@@
 	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
-		\end{align*}\begin{align*}p_c
+%		\end{align*}\begin{align*}p_c
 	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
@@
 
-\section{Adversarial Resistance}
+\section{Adversarial Resistance of Queueing Filters}
 \label{sec:adversarial}

### 2020-03-30 qhtv2.tex
Typos

@@
 
-	Building on the Bloom filter \cite{bloom_spacetime_1970}, an early data structure amenable to duplicate detection, several generalisations and variants were proposed tthat reduce error rates while maintaining constant memory.
-
-	Unfortunately the infinite stream setting is ill-posed, and error rates of duplicate detection filters turn out to be heavily constrained: as a consequence they appear to provide no advantage, asymptotically, over a random biased coin toss \cite{10.1145/3297280.3297335}.
+	Building on the Bloom filter \cite{bloom_spacetime_1970}, an early data structure amenable to duplicate detection, several generalizations and variants were proposed that reduce error rates while maintaining constant memory.
+
+	Unfortunately the infinite stream setting is ill-posed, and error rates of duplicate detection filters turn out to be heavily constrained: as a consequence they appear to provide no advantage, asymptotically, over a biased coin toss \cite{10.1145/3297280.3297335}.
 
@@
 	\emph{windowed} variant of the duplicate detection problem was 
-	introduced in \cite{She08,Yoo10}, which consists in finding duplicate 
+	introduced in \cite{She08,Yoo10} which consists in finding duplicate 
 	entries amongst the last $w$ elements of the stream for a fixed integer $w$.
 
-	In this paper we formalise this setting, and show that a perfect (zero error) solution can be used up to a maximal window size $w_\text{max}$.
+	In this paper we formalize this setting, and show that a perfect (zero error) solution can be used up to a maximal window size $w_\text{max}$.
 Above this threshold we show that some existing duplicate detection filters (designed for the \emph{non-windowed} setting) perform better that those targeting the windowed problem.
@@
 In this paper, we start from a naïve solution for the wDDP to then derive bounds for when it can be solved within $M$ bits of memory, up to a window size $w_\text{max}$, in constant time.
-We then introduce a generalisation of the naïve solution, and study its error rate.
-We show that this construction, which we call Short Hash Filter (SHF), can push the value $w_\text{max}$ further while operating at being constant time --at the cost of some errors.
-If allowing for linear time, we also provide a better alternative, the Compact Short Hash Filter (CSHF).
+We then introduce a generalization of the naïve solution, and study its error rate.
+We show that this construction, which we call Short Hash Filter (SHF), can push the value $w_\text{max}$ further while operating in constant time --- at the cost of some errors.
+We also provide a different tradeoff, the Compact Short Hash Filter (CSHF), which uses fewer memory but operates in linear time.
 
@@
 
-Finally, we provide an analysis of our queueing construction's resistance to adversarial streams. (Section~\ref{sec:adversarial}).
+Finally, we provide an analysis of our queueing construction's resistance to adversarial streams.
 
 \subsection{Related work}\label{sub:related}
-The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}.
-However, several variations exist and describe incompatible situations, such as \cite{shtul2020agepartitioned}.
-Instead, the wDDP formulation we rely on is due to \cite{Yoo10,She08}, which also introduce algorithms for solving the wDDP approximately.
+The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}; but several variations exist that are incomparable to one another (e.g.
+\cite{shtul2020agepartitioned}).
+The wDDP formulation we rely on is due to \cite{Yoo10,She08}, which also introduce algorithms for solving the wDDP approximately.
 
 The notion of using subfilters, as in the queuing construction, can be found in the A2 filter's design \cite{Yoo10} and a variation thereof can be found in \cite{shtul2020agepartitioned} but in a different DDP formulation.
-The A2 is built from two Bloom filters, a construction which we generalise and analyse generically in this paper.
+The A2 is built from two Bloom filters, a construction which we generalize and analyse generically in this paper.
 Similarly, the construction in \cite{shtul2020agepartitioned} only works with Bloom Filters.
@@
 \end{theorem}
-In particular, the asymptotic error rate $E_\infty$ satisfies $E_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|$.
+In particular, the asymptotic error rate $E_\infty$ satisfies 
+\begin{equation*}
+	E_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|.
+\end{equation*}
 
@@
 
-\section{Queuing filters from existing DDFs}
+\subsection{Queuing filters from existing DDFs}
 \label{sec:subfilter-select}

### 2020-04-15 appendix.tex
COCOON version

--- 2020-03-30 qhtv2.tex
@@
-\input{preamble.tex}
+\section{Effects of the simulation's finiteness}
+\label{app:finite}
 
-\begin{document}
+Theoretical results about the queuing construction apply in principle to an infinite stream.
+However, simulations are necessarily finite, and for very large windows (that are approximately the same size as the whole stream) this causes interesting artefacts in the error rates.
 
-\title{Optimal Duplicate Detection in a Sliding Window}
+Note that these effects have very little impact on practical implementations of queuing filters, since almost all use cases assume a window size much smaller than the stream (or, equivalently, a very large stream).
+Nevertheless we illustrate the effect of the finite simulation and the parameters affecting it, if only to motivate a further analytical study of this phenomenon.
 
-%% Replace by \iffalse when submitting anonymously 
-\iftrue 
-	\author{Rémi Géraud-Stewart}
-	\affiliation{%
-	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
-	\city{Paris} \state{France}
-	} \email{remi.geraud@ens.fr}
+Figure~\ref{fig:strangess} measures the error rate as a function of $w$, for different stream sizes $N$.
+A visible decrease in $ER$ can be found around $w\approx N$.
+While we do not have any explanation for the difference in the peaks sizes and exact location, we give the hypothesis that it is related to the choice of $|\Gamma|$.
 
-	\author{Marius Lombard-Platet}
-	\affiliation{%
-	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
-	\city{Paris} \country{France}
-	}
-	\affiliation{%
-	\institution{Be-Studys}
-	\city{Geneva} \country{Switzerland}
-	} \email{marius.lombard-platet@ens.fr}
+\begin{figure}[t]
+\makebox[\textwidth]{\makebox[1.05\textwidth]{%
+	\begin{minipage}{.5\textwidth}
+	\centering
+		\input{graphs/stream_size_qht.tex}
+		\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
+	\end{minipage}
+\hfill
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\begin{tikzpicture}
+		\begin{semilogxaxis}[
+			width=\textwidth,
+			legend cell align = left,%
+			legend pos=south east,
+			legend style={nodes={scale=0.7, transform shape}},
+%			legend style={at={(0.02,0.98)},anchor=north west},%
+			xlabel=$w$, ylabel=$\FPR^w + \FNR^w (\times 100)$]
+		\addplot[color=teal, mark=triangle] table[x=w,y=Error] {graphs/Queueing_Cuckoo.dat};
+		\addlegendentry{Q\_Cuckoo};
+		\addplot[color=teal, mark=triangle, dashed] table[x=w,y=Error] {graphs/Cuckoo.dat};
+		\addlegendentry{Cuckoo};
+		%%
+		\addplot[color=olive, mark=square, mark options = {scale=0.7}] table[x=w,y=Error] {graphs/Queueing_StableBloom.dat};
+		\addlegendentry{Q\_SBF};
+		\addplot[color=olive, mark=square, mark options = {scale=0.7}, dashed] table[x=w,y=Error] {graphs/SBF.dat};
+		\addlegendentry{SBF};
 
-	\author{David Naccache}
-	\affiliation{%
-	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
-	\city{Paris} \country{France}
-	} \email{david.naccache@ens.fr}
-\fi
+		%\addplot[mark=x,^8$}
+		\end{semilogxaxis}
 
-%% Abstract
-\begin{abstract}
-	Duplicate detection is the problem of identifying whether a given item has previously appeared in a (possibly infinite) stream of data, when only a limited amount of memory is available.
+		\end{tikzpicture}
+		\caption{Comparing performances of the Cuckoo and SBF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
+	\end{minipage}
+}}
+\end{figure}
 
-	Building on the Bloom filter \cite{bloom_spacetime_1970}, an early data structure amenable to duplicate detection, several generalizations and variants were proposed that reduce error rates while maintaining constant memory.
+As can be seen on this simulation, there is only disagreement around $w \approx N/L$, and increasing $N$ results in a later and smaller peak.
 
-	Unfortunately the infinite stream setting is ill-posed, and error rates of duplicate detection filters turn out to be heavily constrained: as a consequence they appear to provide no advantage, asymptotically, over a biased coin toss \cite{10.1145/3297280.3297335}.
+It is also possible to run simulations for different alphabet sizes $\Gamma$, which shows that the peak's position increases with $|\Gamma|$, although the relationship is not obvious to quantify.
 
-	Both as a better-behaved setting and as a construction technique, a
-	\emph{windowed} variant of the duplicate detection problem was 
-	introduced in \cite{She08,Yoo10} which consists in finding duplicate 
-	entries amongst the last $w$ elements of the stream for a fixed integer $w$.
+\section{Filters vs queued filters (complement)}\label{app:improvement}
+We here run a comparison of the Cuckoo Filter relative to the Queueing Cuckoo Filter, as well as the SBF relatively to the queueing SBF. The results are given in Figure~\ref{fig:appendix_improvement}.
 
-	In this paper we formalize this setting, and show that a perfect (zero error) solution can be used up to a maximal window size $w_\text{max}$.
-Above this threshold we show that some existing duplicate detection filters (designed for the \emph{non-windowed} setting) perform better that those targeting the windowed problem.
-Finally, we introduce a \enquote{queuing construction} that improves on the performance of some duplicate detection filters in the windowed setting.
+\section{Proofs}\label{app:proofs}
+In this appendix, we give the proofs of all theorems stated in the paper. For the sake of convenience, each theorem is restated before giving its proof.
 
-	We also analyse the security of our filters in an adversarial setting. 
-\end{abstract}
-
-%% CCS XML
-\begin{CCSXML}
-	% Get code at http://dl.acm.org/ccs.cfm.
-	% Please copy and paste the code
-\end{CCSXML}
-
-%% Keywords
-\keywords{
-	% TODO
-}
-
-\maketitle
-
-\section{Introduction}
-\subsection{Motivation}
-
-Throughout this paper, we are interested in the following problem: 
-\begin{definition}[Duplicate detection problem over a sliding window, wDDP] Given a stream $E_n = (e_1, e_2, \dotsc, e_n)$, a sliding window size $w$ and a \enquote{new} item $e^\star$, find whether $e^\star$ is also present in the last $w$ elements of the stream, ie., whether $e^\star \in \{e_{n-w+1}, \dotsc, e_n\}$.
-At every time increment, the new item is added to the stream, i.e., $E_{n+1} = E_n \mid e^\star$ where $\mid$ denotes concatenation. 
-\end{definition}
-Instances of this problem abound in computer science, with applications to file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
-A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.
-
-In practice, additional constraints exist that we can capture with the following definition:
-\begin{definition}[wDDP with bounded memory]
-	At every time step $n$, given $e^{\star}$ and a current state (dependent on history) of at most $M$ bits, solve the wDDP for $E_n$ and $e^{\star}$.
-\end{definition}
-%Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable. 
-%Perfect detection of duplicates in a stream with $U$ possible values requires $U$ bits of memory \cite[Theorem 2.1]{10.1145/3297280.3297335}: even for modest situations (e.g.
-64-bit nonces, corresponding to $2^{64}$ possible values) this is quickly impractical.
-As a result, we need a further relaxation of the DDP that allows for errors:
-Perfect detection is however not always reachable and it might be more practical to work on a further relaxation of the problem, allowing for errors:
-\begin{definition}[Approximate wDDP with bounded memory]
-	Solve the wDDP using at most $M$ bits of memory, with at most $\epsilon < 1/2$ mispredictions.\footnote{Given a classifier with $\epsilon > 1/2$, we obtain a classifier with $\epsilon < 1/2$ by reversing its output.}
-\end{definition}
-Approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
-Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.
-
-On a side note, it is clear that the input distribution plays a central role regarding how efficiently the DDP can be solved.
-For instance, some deterministic streams may be expressed very compactly (such as the output of a PRNG with known seed) making the DDP relatively easy.
-Information-theoretically, if the source has $U$ bits of entropy then the situation is equivalent to having an $U$-bit, uniformly distributed input.
-This is the setting we consider here.
-
-As the window size in wDDP grows infinitely large, it becomes the following problem: find whether $e^\star \in E_n$.
-%This \enquote{non-windowed} problem predates in fact the definition of wDDP, and several algorithms have been proposed for this problem: \cite{Den06,10.1145/3297280.3297335,Dut13} and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-Unfortunately any solution to this problem faces a phenomenon called \enquote{saturation} on large enough data streams.
-In fact, saturation is inevitable with infinite windows \cite{10.1145/3297280.3297335}, and when it happens the algorithm performs no better than at random.
-
-This is problematic on two grounds: it makes the comparison of several algorithms difficult (since they all asymptotically behave in that fashion), and the unavoidable saturation ruins any particular design's merits.
-
-\subsection{Contributions}
-In this paper, we start from a naïve solution for the wDDP to then derive bounds for when it can be solved within $M$ bits of memory, up to a window size $w_\text{max}$, in constant time.
-We then introduce a generalization of the naïve solution, and study its error rate.
-We show that this construction, which we call Short Hash Filter (SHF), can push the value $w_\text{max}$ further while operating in constant time --- at the cost of some errors.
-We also provide a different tradeoff, the Compact Short Hash Filter (CSHF), which uses fewer memory but operates in linear time.
-
-Unfortunately, for $w > w_\text{max}$ the performance of these algorithms degrade very rapidly.
-We therefore turn our attention to existing data structures designed for the \enquote{non-windowed} setting.
-We show that some of them outperform dedicated data structures, including SHF/CSHF, in the $w > w_\text{max}$ regime.
-
-We then introduce the \enquote{queuing construction}, a black box transformation of non-windowed data structures into windowed ones, that improves their performance in the wDDP setting.
-
-Finally, we provide an analysis of our queueing construction's resistance to adversarial streams.
-
-\subsection{Related work}\label{sub:related}
-The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}; but several variations exist that are incomparable to one another (e.g.
-\cite{shtul2020agepartitioned}).
-The wDDP formulation we rely on is due to \cite{Yoo10,She08}, which also introduce algorithms for solving the wDDP approximately.
-
-The notion of using subfilters, as in the queuing construction, can be found in the A2 filter's design \cite{Yoo10} and a variation thereof can be found in \cite{shtul2020agepartitioned} but in a different DDP formulation.
-The A2 is built from two Bloom filters, a construction which we generalize and analyse generically in this paper.
-Similarly, the construction in \cite{shtul2020agepartitioned} only works with Bloom Filters.
-
-\section{Duplicate Detection and Filter Saturation}
-\label{sec:dudefisa}
-\subsection{Notations and basic definitions}
-Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) set $E = (e_1, e_2, \dotsc)$, with each $e_i \in \Gamma$.
-
-\begin{definition}[Duplicate detection filter]
-	A \emph{duplicate detection filter} (DDF) is a collection 
-	$\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$ of a state\footnote{Here, $\mathcal M$ denotes all the memory states that can be reached by the filter.} $\mathcal S \in \mathcal M$ and two algorithms,
-	\begin{itemize}
-		\item $\mathsf{Detect}: \mathcal M \times \Gamma \to \{\DUPLICATE, \UNSEEN\}$;
-		\item $\mathsf{Insert}: \mathcal M \times \Gamma \to \mathcal M$.
-	\end{itemize}
-	Informally, the $\mathsf{Detect}$ algorithm tentatively labels an element $e$ as duplicate or not, given the current state $\mathcal S$; whereas $\mathsf{Insert}$ takes as input the current state, an element $e$ to insert in the filter, and returns an updated memory state $\mathcal S'$.
-\end{definition}
-
-We usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathcal S| \ll |\Gamma|$.
-Otherwise, if $|\mathcal S| = |\Gamma|$ then the problem can be solved in constant time without errors \cite{10.1145/3297280.3297335}.
-
-\begin{definition}[Duplicate element, unseen element over a sliding window]
-	Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
-In this case we write $e_j \wdup E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notwdup E$.
-\end{definition}
-
-\begin{definition}[False positive, false negative over a sliding window]
-	Let $w \in \mathbb N$, $e \notwdup E$ (resp.
-$e \wdup E$) and let $\mathcal F$ be a DDF.
-We say that $e$ is a \emph{false positive} (resp.
-\emph{false negative}) over $w$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
-$\UNSEEN$).
-\end{definition}
-
-\begin{definition}[Probability of false positive, of false negative]
-	\label{def:pfp-pfn}
-	Let $E = (e_1, \dotsc)$ be a stream, $w\in \mathbb N$, $\mathcal F$ be a filter.
-The \emph{probability of false positive} (resp.
-\emph{probability of false negative}) of $\mathcal F$ after $i$ elements over a sliding window of size $w$, denoted $\FP^w_i$ (resp.
-$\FN^w_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp.
-false negative) over $w$.
-\end{definition}
-
-\begin{definition}[False positive rate, false negative rate over a sliding window]
-	Let $E$ be a stream, $\mathcal F$ be a DDF, $w \in \mathbb N$.
-The \emph{false positive} (resp.
-\emph{false negative}) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $w$, noted $\FPR^w_i$ (resp.
-$\FNR^w_i$), is defined as the number of false positives over $w$ divided by the number of unseen elements in $E$ over $w$ (resp.
-the number of false negative over $w$ divided by the number of duplicate elements over $w$).
-\end{definition}
-
-%\begin{definition}[Duplicate and unseen element]
-%Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$.
-Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$.
-In that case we write $e_j \dup E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notdup E$.
-%\end{definition}
-%
-
-%
-%\begin{definition}[False positive, false negative]
-%	Let $e \dup E$ (resp.
-$e \notdup E$) and $\mathcal F$ be a filter.
-We say that $e$ is a \emph{false positive} (resp.
-\emph{false negative}) when $\mathcal F.\mathsf{Detect}(e) = \DUPLICATE$ (resp.
-$\UNSEEN$).
-%\end{definition}
-%
-%\begin{definition}[False positive rate, false negative rate]
-%	Let $E$ be a stream, $\mathcal F$ be a filter.
-The \emph{false positive rate} (resp.
-\emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp.
-$\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $(e_1, \dotsc, e_i)\subset E$ (resp.
-the ratio of false negative divided by the number of duplicate elements in that subset).
-%\end{definition}
-%
-%However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^\star$ is a false positive (resp. false negative). 
-%
-%\begin{definition}[Probability of false positive, of false negative]
-%	\label{def:pfp-pfn}
-%	Let $E = (e_1, \dotsc)$ be a stream, $\mathcal F$ be a filter.
-The \emph{probability of false positive} (resp.
-\emph{probability of false negative}) of $\mathcal F$ after $i$ elements, denoted $\FP_i$ (resp.
-$\FN_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp.
-false negative).
-%\end{definition}
-
-We have $\FPR^w_n = \frac{1}{n}\sum_{i=1}^n \FP^w_i$, and similarly for $\FNR^w_n$.
-
-\paragraph{Remark.} For benchmarking, we usually measure the error rate $ER = \FPR^w + \FNR^w$, as it allows a practical ranking of the solutions.
-An error rate of $0$ means a perfect filter, while a filter answering randomly has an error rate of $1$.
-A filter being always wrong has an error rate of $2$.
-
-%\subsection{Filter Saturation and Sliding Windows}\label{sec:filsat}
-%Unfortunately, efficient duplicate detection over an infinite stream has been identified as an unsolvable problem \cite{10.1145/3297280.3297335}.
-As a matter of fact, as the number of bits of information of the stream grow to infinity, the filter can only remember an ever diminishing proportion of those bits, eventually having no advantage compared to a filter answering randomly.
-%
-%In other terms, any DDF is asymptotically as good as a random guess:
-%	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
-%	Let $\FNR_\infty$ and $\FPR_\infty$ be the asymptotic false negative and false positive rates of a filter of $M$ bits of memory (i.e. the FNR and FPR on a stream of size going to infinity).
-%	
-%	If $|\Gamma| \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
-%\end{theorem}
-%
-%One way out of this situation is to lower our expectations and work on a sliding window:
-%
-%\begin{definition}[Sliding window DDP]
-%	Given a stream $E_n$ of fixed size $w$, with $E_n = (e_{n-w+1}, \dotsc, e_n)$ and an item $e^\star$, find whether $e^\star \in E_n$.
-%\end{definition} 
-%
-%We therefore introduce new definitions suited to that setting:
-%
-%\begin{definition}[Duplicate element, unseen element over a sliding window]
-%	Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
-In this case we write $e_j \wdup E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notwdup E$.
-%\end{definition}
-%
-%\begin{definition}[False positive, false negative over a sliding window]
-%	Let $w \in \mathbb N$, $e \notwdup E$ (resp.
-$e \wdup E$) and let $\mathcal F$ be a DDF.
-We say that $e$ is a \emph{false positive} (resp.
-\emph{false negative}) over $w$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
-$\UNSEEN$).
-%\end{definition}
-%
-%\begin{definition}[False positive rate, false negative rate over a sliding window]
-%	Let $E$ be a stream, $\mathcal F$ be a DDF, $w \in \mathbb N$.
-The \emph{false positive} (resp.
-\emph{false negative}) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $w$, noted $\FPR^w_i$ (resp.
-$\FNR^w_i$), is defined as the number of false positives over $w$ divided by the number of unseen elements in $E$ over $w$ (resp.
-the number of false negative over $w$ divided by the number of duplicate elements over $w$).
-%\end{definition}
-
-\section{DDFs and the wDDP}
-A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-The structure proposed in \cite{10.1145/1060745.1060753} is not desined for wDDP but a variant called `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
-
-Of these, only the A2 and b\_DBF were designed explicitly for the wDDP.
-Others DDFs do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
-Another remarkable (but experimental) observation is that these DDFs' false positive rate does not decrease to 0 when the sliding window becomes small.
-
-\section{Optimal and Approximate Solutions}
-\subsection{Optimal wDDF}\label{sub:opt_solutions}
-
-Our goal is to minimise both the false positive and false negative rates of a DDF, given a fixed and limited amount of memory.
-Before going into details, we first explore the limits of the problem, i.e., when perfect or very performant solutions exist.
-
-\begin{theorem}
-	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the wDDP can be solved exactly (with no errors) in constant time.
-\end{theorem}
+\optwddf*
 
@@
 	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element is present in the sliding window.
-\end{proof}
+\qed\end{proof}
 
-\subsection{Approximate Optimal wDDF}
-The optimal filter described above requires that the size of $\Gamma$ is known in advance. The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing errors.
-
-\begin{theorem}\label{thm:SHF}
-	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the wDDP can be solved with almost no error using $M$ bits of memory.
-
-	More precisely, it is possible to create a filter of $M$ bits with an FN of $0$, an FP of $1 - (1-\frac1{w^2})^w \sim \frac 1w$, and a time complexity of $O(w)$.
-
-	Using $M \simeq 5w\log_2 w$ bits of memory, a constant-time filter with the same error rate can be constructed.
-\end{theorem}
-Note that we only consider the probability of false positive after the filter has inserted at least $w$ elements, i.e., once the filter is full and has reached a stationary regime.
+\shf*
 \begin{proof}
@@
 Using an additional dictionary, as in the previous proof, but with keys of size $2\log_2(w)$, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, using $w \cdot 2\log_2 w + w \cdot (2\log_2(w) + \log_2(w)) = 5w\log_2 w$ bits of memory.
-\end{proof}
+\qed\end{proof}
 
-When $\log_2|\Gamma| > 5 \log_2 w$ this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory, at the cost of a minimal error.
-When $\log_2|\Gamma| > 2 \log_2 w$, it outperforms the exact solution described sooner in terms of memory.
-
-\section{Short Hash Filter}
-\subsection{Short Hash Filter Algorithm}
-The approximate filter we described uses hashes of size $2\log_2(w)$ for a given sliding window $w$.
-However, this hash size is arbitrary, and while it guarantees a very low error rate, it can be changed.
-More importantly, in some practical cases the maximal amount of available memory is fixed beforehand.
-Fixing the memory is also more practical for benchmarking data structures, as it gives the guarantee that all filters operate under the same conditions.
-
-This gives us the Short Hash Filter (SHF), described in Algorithm~\ref{alg:SHF}.
-The implementation relies on a double-ended queue or a ring buffer, which allows pushing at beggining of a queue and popping at the end in constant time.
-
-\begin{algorithm}[!h]
-	\caption{SHF Setup, Lookup and Insert}\label{alg:SHF}
-
-	\begin{algorithmic}[1]
-		\Function{Setup}{$\mathcal M, w$}
-		\Comment $M$ is the available memory, $w$ the size of the sliding window
-		\State $h \gets$ hash function of codomain size $\lfloor \frac M{2w} - \frac 12 \log_2 w \rfloor$
-		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
-		\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h$ => counter (of max value $w$)
-
-		\State\Return filter
-		\EndFunction 
-%		\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\Function{Lookup}{$e$}
-		\If{$D[h(e)] > 0$}
-		\State \Return \DUPLICATE
-		\EndIf
-		\State \Return \UNSEEN
-	\EndFunction
-%	\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\Function{Insert}{$e$}
-		\State $Q.\mathsf{Push\_Front}(h(e))$
-		\State $D[h(e)]$++
-
-		\If{$Q.\mathsf{length}() > w$}
-			\State $h' \gets Q.\mathsf{Pop\_back}()$
-			\State $D[h']$-{}-
-			\If{$D[h'] = 0$}
-				\State Erase key $D[h']$
-			\EndIf
-		\EndIf
-	\EndFunction
-	\end{algorithmic}
-\end{algorithm}
-
-\subsection{Compact Short Hash Filter}
-Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
-The CSHF performs in linear time in $w$, and is a simple queue, the only point is that instead of storing $e$, one stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.
-
-%\begin{algorithm}[!h]
-%	\caption{CSHF, Setup, Lookup and Insert}\label{alg:CSHF}
-%	
-%	\begin{algorithmic}[1]
-%		\Function{Setup}{$\mathcal M, w$}
-%		\Comment $M$ is the available memory, $w$ the size of the sliding window
-%		\State $h \gets$ hash function of codomain size $\lfloor \frac Mw \rfloor$
-%		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
-%		\State\Return filter
-%		\EndFunction 
-%		\item[]
-%	\end{algorithmic}
-%	
-%	\begin{algorithmic}[1]
-%		\Function{Lookup}{$e$}
-%		\State \Return $h(e) \in Q$ 
-%		\EndFunction
-%		\item[]
-%	\end{algorithmic}
-%	
-%	\begin{algorithmic}[1]
-%		\Function{Insert}{$e$}
-%		\State $Q.\mathsf{Push\_Front}(h(e))$
-%		
-%		\If{$Q.\mathsf{length}() > w$}
-%			\State $h' \gets Q.\mathsf{Pop\_back}()$
-%		\EndIf
-%		\EndFunction
-%	\end{algorithmic}
-%\end{algorithm}
-
-\subsection{Error Rates}
-Let $w> 0$ be a window size and $M > 0$ the available memory.
-
-We write $\FN^w_\text{SHF}$ the probability of false negative of an SHF with these parameters. We similarly define $\FP^w_\text{SHF}$, $\FN^w_\text{CSHF}$, $\FP^w_\text{CSHF}$.
-
-\begin{theorem}	
-	\begin{align*}
-		\FN_\text{SHF}^w&  = \FN_\text{CSHF}^w =0 \\
-		\FP_\text{SHF}^w & = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w \\
-		\FP_\text{CSHF}^w & = 1 - \left(1 - 2^{-M/w}\right)^w
-	\end{align*}
-\end{theorem}
+\fprSHF*
 
 \begin{proof}
-	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$, while a CSHF has fingerprints of size $h' = \frac Mw$.
-\end{proof}
+	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}.
+An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$.%, while a CSHF has fingerprints of size $h' = \frac Mw$.
+\qed\end{proof}
 
-\paragraph{Remark:} A CSHF of size $M$ has the same error rate than an SHF of size $2M + w\log_2 w$.
-\subsection{Saturation}
-Both SHF and CSHF have strictly increasing error rates, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
-Beyond this value, these filters saturate extremely quickly: in other words, most SHF will either have an error rate of $0$ or $1$.
-
-An illustration of this phenomenon can be seen in Figure~\ref{fig:shorts}, 
-which shows the error rates for CSHF and SHF with $M=10^5$, against 
-a uniformly random stream of $18$-bit elements ($|\Gamma| = 2^{18}$). The benchmark used a finite stream of length $10^6$.
-
-\begin{figure}[!h]
-	\centering
-	\input{graphs/bench_shorts.tex}
-	\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:shorts}
-\end{figure}
-
-The value $w_\text{max}$ can be obtained by solving (numerically) for $\FP^{w_\text{max}} = 1/2$ for a given $M$.
-We numerically solved the equation $\FP^w = 0.5$ for these two filters, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$.
-Results
-% are given in Figure~\ref{fig:w_opt} and 
-indicate an approximately linear relationship between $M$ and $w_\text{max}$: %for large values of $M$:
- $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).
-
-%\begin{figure}[]
-%	\input{graphs/w_opt_shf.tex}
-%	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 0.5 ($\pm 0.001$), for several values of $M$.}\label{fig:w_opt}
-%\end{figure}
-
-\section{Non-windowed DDFs in a wDDP setting}
-\subsection{Lower Bound on the Saturation Resistance}
-As said in the introduction, it has been proven \cite{10.1145/3297280.3297335} that all filters will reach saturation on the DDP setting.
-However, they sometimes prove to be efficient in some specific wDDP settings.
-
-This bound is useful for several reasons, notably it provides an estimation of how close to optimality existing filters are.
-
-\begin{theorem}
-	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $ER_n = \FP_n + \FN_n$ satisfies
-	\begin{equation}
-	E_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
-	\end{equation}
-	for any $n > M$.
-\end{theorem}
-In particular, the asymptotic error rate $E_\infty$ satisfies 
-\begin{equation*}
-	E_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|.
-\end{equation*}
+\asymptoticSaturation*
 
@@
 	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
-Up to reordering the stream, without loss of generality because it is random, we may assumethat the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
+Up to reordering the stream, without loss of generality because it is random, we may assume that the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
 
@@
 		& = \FN_n + p
-		=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
-		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
+		=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p
+		= 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
 	\end{align*}
 	which is minimized when $p = 0$. 
-\end{proof}
+\qed\end{proof}
 
-Note, as highlighted in the proof, that this bound is \emph{not tight}: better bounds may exist, the study of which we leave as an open question for future work.
-
-\subsection{Saturation Resistance of DDFs}\label{sub:saturation}
-We now evaluate the saturation rate for several DDFs, in the original DDP setting (without sliding window).
-Parameters are chosen to yield equivalent memory footprints and were taken from \cite{10.1145/3297280.3297335}, namely:
-%
-\begin{itemize}
-	\item QHT \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint.
-	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$
-	\item Cuckoo Filter \cite{Fan14}, cells containing 1 element of 3 bits each
-	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
-%	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
-%	\item Block-Decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of 6000 elements.
-\end{itemize}
-%
-
-These filters are run against a stream of uniformly sampled elements from an alphabet of $2^{26}$ elements.
-This results in around 8\% duplicates (up to statistical fluctuations) amongst the 150 000 000 elements in the longest stream used.
-%As a comparison, we also run the same benchmark against a stream obtained from crawling data, the same one as \cite{10.1145/3297280.3297335}, a real-world source which is highly non-uniform --- note that in this case, our lower bound on the error rate does not apply, owing to the stream being compressible.
-In that stream, around 10\% were duplicates amongst the 150 000 000 elements.
-Results are plotted in Figure~\ref{fig:graph_n}.
-
-%\begin{figure*}[!h]
-%	\begin{tikzpicture}
-%	\begin{groupplot}[
-%	group style = {
-%		group size = 2 by 1,
-%		horizontal sep = 35pt,
-%	},
-%	axis lines = left,
-%	ylabel near ticks,
-%	width = 0.4\textwidth,
-%	height = 0.27\textwidth,
-%	]
-%	\input{er_n_artificial}
-%	\input{er_n_real}
-%	%\input{10e6_sum_zipf}
-%	\end{groupplot}
-%    \path (top)--(bot) coordinate[midway] (group center);
-%%	\node[above,rotate=90] at (group center -| current bounding box.west) {Error rate (\%)};
-%	\node[right=1em,inner sep=0pt] at(group center -| current bounding box.east) {\pgfplotslegendfromname{legend_n}};
-%	\end{tikzpicture}
-%
-%%	\input{er_n_artificial}
-%	\caption{Error rate (times 100) of DDFs of 1Mb, over a real and artificial stream, depending on the size of the stream, without any sliding window.
-Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
-%\end{figure*}
-
-\begin{figure}[!h]
-	\begin{tikzpicture}
-	\input{er_n_artificial}
-	\end{tikzpicture}
-	\caption{Error rate (times 100) of DDFs of 1Mb as a function of stream length. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
-\end{figure}
-
-The best results are given by the following filters, in order: QHT, SQF, Cuckoo and SBF.
-We also observe that QHT and SQF have error rates relatively close to the lower bound, hence suggesting that these filters are close to optimality, especially since the lower bound is not tight.
-
-\subsection{Performance in wDDP}
-We now consider the performance of the filters just discussed in the \emph{windowed} setting, for which they were \emph{not} designed.
-In particular, it is not possible to adjust their parameters as a function of $w$.
-
-Remarkably, some of these filters still outperform dedicated windowed filters for some window sizes at least, as shown in Figure~\ref{fig:nwddf-in-wddp}.
-In this benchmark, we used the following filters:
-\begin{itemize}
-	\item block decaying Bloom Filter\footnote{Note that by design, a b\_DBF of $10^5$ bits cannot be built over a sliding window bigger than $6000$.} (b\_DBF) \cite{She08}, sliding window of size $w$
-	\item A2 filter \cite{Yoo10}, changing subfilter every $w/2$ insertions
-	\item QHT \cite{10.1145/1060745.1060753}, 1 bucket per row, $3$ bits per fingerprint
-\end{itemize}
-
-Nevertheless, we will now discuss the queuing construction, which allow us to build windowed filters from the DDP filters.
-
-\begin{figure}[h]
-	\centering
-	\input{graphs/compare_qht_bdbf_a2.tex}
-	\caption{Error rates for QHT, b\_DBF, and A2. While A2 and b\_DBF were designed and adjusted to the wDDP, this is not the case of QHT. Still, QHT outperforms these filters for some values of $w$.}
-	\label{fig:nwddf-in-wddp}
-\end{figure}
-
-\section{Queuing filters}\label{sec:queue}
-We now describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
-A scheme describing our structure is detailed in Figure~\ref{fig:scheme}.
-
-\subsection{The queuing construction}
-
-\paragraph{Principle of operation.}
-Let $\mathcal F$ be a DDF.
-Rather than allocating the whole memory to $\mathcal F$, we will create $L$ copies of $\mathcal F$, each using a fraction of the available memory.
-Each of these \emph{subfilters} as a limited timespan, and is allowed up to $c$ insertions.
-The subfilters are organised in a queue.
-
-When inserting a new element in the queuing filter, it is inserted in the topmost subfilter of the queue.
-After $c$ insertions, a new empty filter is added to the queue, and the oldest subfilter is popped and erased.
-
-As such, we can consider that each subfilter operates on a sub-sliding window of size $c$, which makes the overall construction a DDF operating over a sliding window of size $w = cL$.
-
-\begin{figure}
-	\input{fig/queuef.tex}
-	\caption{Architecture of the queuing filter.
-The filter is composed of $L$ subfilters $\mathcal F$, each containing up to $c$ elements.
-Once the newest subfilter has inserted $c$ elements in its structure, the oldest one is expired.
-As such, it is dropped and a new one is created and put under population at the beginning of the queue.
-In this example, the sub-sliding window of $\mathcal F_1$ is $(e_{m-2}, e_{m-3}, e_{m-4})$.} \label{fig:scheme}
-\end{figure}
-
-\paragraph{Insertion and lookup.}
-The filter returns \DUPLICATE if and only if at least one subfilter does. Insertion is a simple insertion in the topmost subfilter.
-
-\paragraph{Queue update.}
-After $c$ insertions, the last filter of the queue is dropped, and a new (empty) filter is appended in front of the queue.
-
-\paragraph{Pseudocode.}
-We give a brief pseudocode for the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in Algorithm~\ref{alg:queuing}.
-We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
-Here \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first position.\footnote{Two standard ways to implement this are a double-ended queue (deque) and a ring buffer.}
-
-\begin{algorithm}[]
-	\caption{Queuing Filter Setup, Lookup and Insert}\label{alg:queuing}
-
-	\begin{algorithmic}[1]
-	\Function{Setup}{$\mathcal F, M, L, c$}
-		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
-		\State subfilters $\gets \emptyset$
-		\State counter $\gets 0$
-		\State $m \gets \lfloor M/L \rfloor$
-		\For{$i$ from $0$ to $L-1$}
-			\State subfilters.push\_first$(\mathcal F.\mathsf{Setup}(m))$
-		\EndFor
-		\State \textbf{store} (subfilters, $L$, $m$, counter)
-		\State\Return filter
-	\EndFunction 
-	\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\Function{Lookup}{$e$}
-		\For{$i$ from $0$ to $L-1$}
-			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
-				\State \Return $\DUPLICATE$
-			\EndIf
-		\EndFor
-		\State \Return \UNSEEN
-	\EndFunction
-	\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\Function{Insert}{$e$}
-		\State subfilters[0]$.\mathsf{Insert}(e)$
-		\State counter $\gets$ counter + 1 
-		\If{counter == $c$}
-			\State subfilters.pop()
-			\State subfilters.push\_first($\mathcal F.\textsf{Setup}(m)$)
-		\EndIf
-	\EndFunction
-	\end{algorithmic}
-\end{algorithm}
-
-\subsection{Error rate analysis}
-The queuing filter's properties can be derived from the subfilters'.
-False positive and false negative rates are of particular interest.
-In this section we consider a queuing filter $\mathcal Q$ with $L$ subfilters of type $\mathcal F$ and
-capacity $c$ (which means that the last subfilter is dropped after $c$ insertions).
-
-\paragraph{Remark.}
-	\label{subsub:number_elements}
-	By definition, after $c$ insertions the last subfilter is dropped.
-Information-theoretically, this means that all the information related to the elements inserted in that subfilter has been lost, and there are $c$ such elements by design. 
-Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements (immediately after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).
-
-As a result, if $w < cL$, the queuing filter can hold information about \emph{more than $w$ elements}.
-
-\subsubsection{Probability of False Positive}
-
-\begin{theorem}
-	\label{thm:queue-pfp}
-	 Let $\FP_{\mathcal Q, m}^w$ be the probability of false positive (def. \ref{def:pfp-pfn}) of $\mathcal Q$ after $m > w$ insertions, over a sliding window of size $w = cL$, we have:
-	\begin{equation}
-		\label{eq:queue-pfp}
-		\FP_{\mathcal Q, m}^w = 1 - \left(1 - \FP_{\mathcal F,c}\right)^{L-1} \left(1 - \FP_{\mathcal F, m \bmod c }\right)
-	\end{equation}
-	where $\bmod$ is the modulo operator and 
-	 $\FP_{\mathcal F,m}$ be the probability of false positive a subfilter $\mathcal F$ after $m$ insertions.
-\end{theorem}
+\pfpQueue*
 
@@
 	Each subfilter has undergone $c$ insertions, safe for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
-\end{proof}
+\qed\end{proof}
 
-\paragraph{Remark.} In the case $w < cL$, as mentioned previously, there is a non-zero probability that $e^\star$ is in the last subfilter's memory, despite not belonging to the sliding window.
-
-Assuming a uniformly random input stream, and writing $\delta = cL - w$, the probability that $e^\star$ has occurred in $\{e_{m-cL}, \dotsc e_{m-w+1}\}$ is $1-\left(1-\frac1{|\Gamma|}\right)^\delta$.
-For large $|\Gamma|$ (as is expected to be the case in most applications), this probability is about $\frac{\delta}{|\Gamma|} \ll 1$.
-Hence, we can neglect the probability that $e^\star$ is present in the filter, and we consider the result of Theorem~\ref{thm:queue-pfp} to be a very good approximation even when $w < cL$.
-
-\subsubsection{Probability of False Negative}\label{sub:fnr}
-\begin{theorem}
-	\label{thm:queue-pfn}
-	Let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation}
-	\FN_{\mathcal Q, m}^w 
-	=  u_c^{L-1} u_{m \bmod c}
-	\end{equation}
-	where $\bmod$ is the modulo operator, and we have introduced the short-hand notation $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$ where 
-	$\FN_{\mathcal F,\eta}$ (resp. $\FP_{\mathcal F, \eta}$) is the probability of false negative (resp. false positive) of the subfilter $\mathcal F$ after $\eta$ insertions, and
-	\begin{equation*}
-		p_\eta = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^\eta}{1-\left(1-\frac 1{|\Gamma|}\right)^w} \approx \frac{\eta}{w}.
-	\end{equation*}
-\end{theorem}
+\pfnQueue*
 
 \begin{proof}
-	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
+	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
 
@@
 This concludes the proof.
-\end{proof}
-\paragraph{Remark.} As previously, the effect of $w < cL$ is negiglible for all practical purposes and Theorem~\ref{thm:queue-pfn} is considered a good approximation in that regime.
+\qed\end{proof}
 
-\subsection{FNR and FPR}
-From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR when $m = cn$ for $n$ a positive integer.
-\begin{theorem}
-	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation*}
-	\FPR_{\mathcal Q, cn}^w = 1 -  \frac{(1 - \FP_{\mathcal F, c})^{L-1}}{c}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell}).
-	\end{equation*}
-\end{theorem}
+\fprQueue*
+
 \begin{proof}
@@
 \end{align*}
-\end{proof}
+\qed\end{proof}
 
-\begin{theorem}
-	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation*}
-	\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell.
-	\end{equation*}
-\end{theorem}
+\fnrQueue*
 
@@
 \end{align*}
-\end{proof}
-As for the probabilities, the expressions derived above for the FNR and FNR are valid to first order in $(w - cL)/|\Gamma|$, i.e. they are good approximations even when $w \approx cL$.
+\qed\end{proof}
 
-\subsection{Optimising queuing filters}
-\label{sec:optimising}
-Let us relax, temporarily, the a priori constraint that $w = cL$.
-The parameter $L$ determines how many subfilters appear in the queuing construction.
-Summing up the false positive and false negative rates, we have a total error rate
-$	\operatorname{ER}_{\mathcal Q, cn}^{w}
-	= 1 - \alpha \beta^{L-1} + \alpha' \beta'^{L-1}
-$,
-where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
-$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ depend on $w$, $c$ and the choice of subfilter type $\mathcal F$.
-
-Because $u_\eta = p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$, differentiating with respect to $L$, knowing that $w = Lc$, and equating the derivative to $0$, one can find the optimal value for $L$ by solving for $x$, which has been obtained via Mathematica:
-
-%\begin{equation*}
-\begin{align*}
-&-\alpha \beta^{-1+x} \log(\beta)  \\ 
-&+ \left(\beta + \FN_{\mathcal F, c} (-1+x)\right)^{-2+x} x^{-x} \left[\vphantom{\left(\FN^{\FN}\right)}\right. \\
-&\quad
-	-\alpha \beta + \FN_{\mathcal F, c} \left(-\beta (-2+x)+ \FN_{\mathcal F, c} (-1+x)\right) \\
-&\quad	+ \left(\alpha+ \FN_{\mathcal F, c} (-1+x)\right) \\
-& \quad \quad \times\left(\beta + \FN_{\mathcal F, c} (-1+x)\right) \left(\log\left(\beta + \FN_{\mathcal F, c} (-1+x)\right)-\log(x)\right) \\
-&\left.\vphantom{\left(\FN^{\FN}\right)}\right] = 0
-\end{align*}
-If numerically solving the equation for individual cases is feasible, it seems unlikely that a closed-form formula exists.
-%\end{equation*}
-
-%Differentiating with respect to $L$ and equating to zero gives an optimum
-%\begin{equation*}
-%	L_{c, \mathcal F} = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
-%\end{equation*} 
-%Thus for a given $c$ and choice of subfilter $\mathcal F$ we get an optimal value of $L = L_{c, \mathcal F}$,
-%and we set, \emph{a posteriori}, $w \gets cL$.
-%
-%If instead $w$ is a given value, solving $w = c L_{c, \mathcal F}$ analytically may be challenging.
-%A practical solution is to interpolate between explicitly computed values $cL_{c, \mathcal F}$ to find the 
-%closest match for the target $w$.
-%
-%\todo[À vérifier la suite je suis pas convaincu encore]
-%\begin{theorem}
-%	In first approximation, a low value of $L$ for constant value $cL$ leads to a higher false negative probability for the queuing filter.
-%\end{theorem}
-%
-%\begin{proof}
-%As a matter of fact, on average the queuing filter consists of $L-1$ subfilters with $c$ insertions, and one subfilter with $\frac c2$ insertions.
-As such, we can say that the queuing filter is a representation of the last $(c-\frac12) L$ last elements.
-%
-%Let us consider $e^\star \wdup E$.
-If, in the sliding window, all duplicates only happened at least $(c-\frac12)L$ epochs ago (which happens with probability $\left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}$), we know that no duplicates happened in any subfilter's sliding window.
-By using the same reasoning as Theorem~\ref{thm:queue-pfn}'s proof, we get a probability of false negative of around $\left[0 + \left(1-\frac1{|\Gamma|}\right)^{(c-\frac12)L}(1-\FP_{\mathcal F,c})\right]^L$.
-Given that $cL \approx w$ which is a constant, we get that the probability of false positive mostly varies, in this case, with $\left(1-\FP_{\mathcal F,c}\right)^L$.
-%
-%Hence, the lower $L$ is, the higher the probability of false negative will be.
-%
-%The approximations made in this proof are backed by experimental results.
-%\end{proof}
-
-\subsection{Queuing filters from existing DDFs}
-\label{sec:subfilter-select}
-\label{sec:optimal_ddf}
-Our queuing construction relies on a choice of subfilters. A first observation 
-is that we may assume that all subfilters can be instances of a single 
-DDF design (rather than a combination of different designs).
-
-Indeed, a simple symmetry argument shows that a heterogenous selection of subfilters is always worse than a homogeneous one: the crux is that all subfilters play the same role in turn.
-Therefore we lose nothing by replacing atomically one subfilter by a more efficient one.
-Applying this to each subfilter we end up with a homogenous selection.
-
-It remains to decide which subfilter construction to choose.
-The results of an experimental comparison of different DDFs (details about the benchmark are given in Section~\ref{sub:saturation}) are summarizes in Figure~\ref{fig:graph_n}.
-It appears that the most efficient filter (in terms of saturation rate) is the QHT \cite{10.1145/3297280.3297335}.
-
-%As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
-This raises the question of whether recursive constructions (queuing filters of queuing filters) have particularly interesting properties, which we leave open for future work.
-
-%In the experiments we use QHT for the benchmarking of the queuing construction.
-
-\section{Experiments and Benchmarks}\label{sec:bench}
-
-This section provides details and additional information on the benchmarking experiments run to validate the above analysis. All code is accessible online and will be disclosed after peer review.
-
-\paragraph{Benchmarking queuing filters.}
-Applying the queuing construction to DDFs from the literature, we get new filters which are compared in the wDDP setting.
-
-In Section~\ref{sec:optimal_ddf} we suggested the heuristic that the DDFs with the least saturation rate in the DDP would yield the best (error-wise) queuing filter for the wDDP.
-This heuristic is supported by results, summarized in Figure~\ref{tab:comparing_queuing}.
-For this benchmark we used the following parameters: uniform stream from an alphabet of size $|\Gamma| = 2^{18}$, memory size $M=100,000$ bits, sliding window of size $w = 10,000$, and we measure the error rate (sum of $\FNR^w$ and $\FPR^w$).
-
-A very interesting observation is that $Lw$ approaches the size of the stream, there is a drop in the error.
-This is an artifact due to the finite size of our simulations; the stream should be considered infinite, and this drop disappears as the simulation is run for longer (see Appendix~\ref{app:finite}).
-This effect also alters the error rates for smaller window sizes, albeit much less, and we expect that filter designers care primarily about the small window regime.
-Nevertheless a complete understanding of this effect would be of theoretical interest, and we leave the study of this phenomenon for future work.
-
-\begin{figure}[!h]
-	\input{graphs/compare_queues.tex}
-	\caption{Error rate (times 100) of queuing filters as a function of window size, $M=10^5$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
-\end{figure}
-%\begin{table}[]
-%	\begin{tabular}{rccccc}
-%			   & $w=1000$ & $w=5000$ & $w=10^4$ & $w=10^5$ & $w=10^6$ \\ \hline
-%		QHT    & \textbf{9.84} 	  & \textbf{26.25}	 & \textbf{41.09}	 & \textbf{87.89}	  & 70.76      \\
-%		Cuckoo & 84.99	  & 99.94	 & 99.95	 & 99.93	  & 99.80      \\
-%		SQF    & 16.73 	  & 48.76	 & 69.25	 & 95.77 	  & \textbf{70.14}     \\
-%		SBF    & 54.88 	  & 93.93	 & 97.33	 & 97.41	  & 71.17      \\
-%	\end{tabular}
-%	\caption{Error rate (times 100) of various queuing filters on various sliding window sizes, $M=100000$, $L=10$, $|\Gamma| = 2^{16}$.
-For each sliding window, the best performance is written in bold.}\label{tab:comparing_queuing}
-%\end{table}
-
-\paragraph{The number of subfilters}\label{sub:L_bench}
-The number of subfilters $L$ is an important parameter in the queuing construction, as it affects the filter's error rate in a nontrivial way.
-An illustration of this dependence is shown in Figure~\ref{fig:bench_l} which plots the error rate of a queueing QQHTD on an uniform stream of alphabet size $\Gamma = 2^{16}$, with $10^5$ elements in the stream, on various sliding window sizes.
-
-\begin{figure}[!h]
-	\input{graphs/bench_l.tex}
-	\caption{Evolution of the error rate of a queueing QHT as a function of $L$, for several window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
-\end{figure}
-
-We observe that the optimal value for $L$ does indeed depend on the desired sliding window.
-However, other experiments on alphabets of other sizes yield very similar results, hence validating the observation made in Section~\ref{sec:optimising} that the optimal number of subfilters does not depends on the alphabet, at least in first approximation.
-
-\paragraph{Filters vs queued filters.}
-Using the same stream as previously, we can build queued filters (with an optimal value $L$ for each considered sliding window) and compare their performances to that of non-modified filters.
-Results on the QHT and SQF are shown in Figure~\ref{fig:improvement}, results for the Cuckoo and SBF are shown in Appendix~\ref{app:improvement}.
-
-\begin{figure}[!h]
-	\input{graphs/improvement.tex}
-	\caption{Comparing performances of QHT and SQF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:improvement}
-\end{figure}
-
-We observe that queueing filters do not necessarily behave better than their 'vanilla' counterparts, especially on large sliding windows.
-This can be interpreted by the fact that the DDPs were optimised for infinite sliding windows, and as such operate better than their queueing equivalent on large sliding windows.
-
-\section{Adversarial Resistance of Queueing Filters}
-\label{sec:adversarial}
-
-As DDFs have numerous security applications, we now discuss the queuing construction from an adversarial standpoint.
-We consider an adversarial game in which the attacker wants to trigger false positives or false negatives over the sliding window.
-One motivation for doing so is causing cache saturation or denial of service by forcing cache misses, triggering false alarms or crafting fradulent transactions without triggering fraud detection systems.
-
-In order to create a realistic adversary model, we assume like in \cite{DBLP:journals/corr/abs-1709-08920} that the adversary does not have access to the internal memory representation of the filter.
-Nonetheless, after every insertion she knows whether the inserted element was detected as a duplicate or not.
-
-We first recall the definition of an adversarial game, adapted to our context.
-\begin{definition}
-	An adversary $\mathcal A$ feeds data to a sliding window DDF $\mathcal Q$, and for each inserted element, $\mathcal A$ knows whether $\mathcal Q$ answers $\DUPLICATE$ or $\UNSEEN$, but has not access to $\mathcal Q$'s internal state $\mathcal M$.
-The game has two distinct parts.
-
-\begin{itemize}
-	\item In the first part, $\mathcal A$ can feed up to $n$ elements to $\mathcal Q$ and learn $\mathcal Q$'s response for each insertion.
-	\item In the second part, $\mathcal A$ sends a unique element $e^\star$.
-\end{itemize} 
- $\mathcal A$ wins the $n$-false positive adversarial game (resp. $n$-false negative adversarial game) if and only if $e^\star$ is a false positive (resp. a false negative).
-
- \end{definition}
-Variants of these games over a sliding window of size $w$ are immediate.
-
-\subsection{False positive and false negative resistance}
-
-\begin{definition}[Adversarial False Positive Resistance]
-	We say that a DDF $\mathcal F$ is $(p, n)$-\emph{resistant to adversarial false positives} if no polynomial-time probabilistic (PPT) adversary $\mathcal A$ can win the $n-$false positive adversarial game with probability more than $p$.
-\end{definition}
-Note that if $\mathcal F$ is $(p,n)$-resistant, then it is $(p, m)$-resistant for all $m < n$.
-
-We define similarly the notion of being \emph{resistant to adversarial false negatives}. Finally, both definitions also make sense in a sliding window context.
-
-\subsection{Bound on false positive resistance}
-
-\begin{theorem}
-	Let $\mathcal Q$ be a filter of $L$ subfilters $\mathcal F_i$, with $c$ insertions maximum per subfilter, let $w$ be a sliding window.
-
-	If $\mathcal F$ is $(p, c)$-resistant to adversarial false positive attacks and $cL \leq w$, then $\mathcal Q$ is $(1-(1-p)^L, w)$-resistant to adversarial false positive attacks on a sliding window of size $w$.
-
-	If $cL > w$, the adversary has a probability of success of at least $1-(1-p)^L$.
-\end{theorem}
+\fprRes*
 
@@
 If, for some reason, the last subfilter answers $\DUPLICATE$ with probability less than $p$, then the same reasoning as for when $cL \leq w$ still applies, hence we get the correspondig lower bound (which is, in this case, an equality).
-\end{proof}
+\qed\end{proof}
 
-\subsection{Bounds on false negative resistance}
-
-\begin{theorem}
-	Let $\mathcal Q$ be a filter of $L$ subfilters of kind $\mathcal F$, with $c$ insertions maximum per subfilter, and let $w$ be a sliding window.
-
-	If $\mathcal F$ is $(p, c)$-resistant to adversarial false negative attacks, then $\mathcal A$ can win the adversarial game on the sliding window $w$ with probability at least $p^L$.
-
-	Furthermore, for $q$ the lower bound on the probability of false positive $\FP_{\mathcal F,c}$ for a given stream, if $w \leq (L-1)c$ then $\mathcal Q$ is $(\min(1 - q, p)^{L-1}p, w)$-resistant to false negative attacks on the sliding window $w$.
-	On the other hand if $w > (L-1)c$ then $\mathcal Q$ is  $(\max(1 - q, p)^{L}, w)$-resistant to false negative attacks on the sliding window $w$.
-\end{theorem}
+\fnrRes*
 
@@
 Hence, in this context $e^\star$ is not in any subfilter anymore, so by adapting the previous analysis, $\mathcal A$ can get a false negative with probability at most $\max(1 - q, p)^{L}$.
+\qed
 \end{proof}
-%% Acknowledgements 
-%\begin{acks} \end{acks}
-
-%% Bibliography
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{qhtv2}
-
-%% Appendix
-\appendix
-
-\section{Effects of the simulation's finiteness}
-\label{app:finite}
-
-Theoretical results about the queuing construction apply in principle to an infinite stream.
-However, simulations are necessarily finite, and for very large windows (that are approximately the same size as the whole stream) this causes interesting artefacts in the error rates.
-
-Note that these effects have very little impact on practical implementations of queuing filters, since almost all use cases assume a window size much smaller than the stream (or, equivalently, a very large stream).
-Nevertheless we illustrate the effect of the finite simulation and the parameters affecting it, if only to motivate a further analytical study of this phenomenon.
-
-Figure~\ref{fig:strangess} measures the error rate as a function of $w$, for different stream sizes $N$.
-A visible decrease in $ER$ can be found around $w\approx N$.
-While we do not have any explanation for the difference in the peaks sizes and exact location, we give the hypothesis that it is related to the choice of $|\Gamma|$.
-
-\begin{figure}[]
-	\centering
-	\input{graphs/stream_size_qht.tex}
-	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
-\end{figure}
-
-As can be seen on this simulation, there is only disagreement around $w \approx N/L$, and increasing $N$ results in a later and smaller peak.
-
-It is also possible to run simulations for different alphabet sizes $\Gamma$, which shows that the peak's position increases with $|\Gamma|$, although the relationship is not obvious to quantify.
-
-\section{Filters vs queued filters (complement)}\label{app:improvement}
-We here run a comparison of the Cuckoo Filter relative to the Queueing Cuckoo Filter, as well as the SBF relatively to the queueing SBF. The results are given in Figure~\ref{fig:appendix_improvement}.
-
-\begin{figure}[]
-\begin{tikzpicture}
-	\begin{semilogxaxis}[legend cell align = left,%
-		 %legend pos=outer north east, 
-	legend style={at={(0.02,0.98)},anchor=north west},%
-		 xlabel=$w$, ylabel=$\FPR^w + \FNR^w (\times 100)$]
-	\addplot[color=teal, mark=triangle] table[x=w,y=Error] {Queueing_Cuckoo.dat};
-	\addlegendentry{Q\_Cuckoo};
-	\addplot[color=teal, mark=triangle, dashed] table[x=w,y=Error] {Cuckoo.dat};
-	\addlegendentry{Cuckoo};
-	%%
-	\addplot[color=olive, mark=square, mark options = {scale=0.7}] table[x=w,y=Error] {Queueing_StableBloom.dat};
-	\addlegendentry{Q\_SBF};
-	\addplot[color=olive, mark=square, mark options = {scale=0.7}, dashed] table[x=w,y=Error] {SBF.dat};
-	\addlegendentry{SBF};
-
-	%\addplot[mark=x,^8$}
-	\end{semilogxaxis}
-
-\end{tikzpicture}
-	\caption{Comparing performances of the Cuckoo and SBF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
-\end{figure}
-\end{document}

### 2020-04-15 article_content.tex
COCOON version

--- 2020-03-30 qhtv2.tex
@@
-\input{preamble.tex}
-
-\begin{document}
-
-\title{Optimal Duplicate Detection in a Sliding Window}
-
-%% Replace by \iffalse when submitting anonymously 
-\iftrue 
-	\author{Rémi Géraud-Stewart}
-	\affiliation{%
-	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
-	\city{Paris} \state{France}
-	} \email{remi.geraud@ens.fr}
-
-	\author{Marius Lombard-Platet}
-	\affiliation{%
-	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
-	\city{Paris} \country{France}
-	}
-	\affiliation{%
-	\institution{Be-Studys}
-	\city{Geneva} \country{Switzerland}
-	} \email{marius.lombard-platet@ens.fr}
-
-	\author{David Naccache}
-	\affiliation{%
-	\institution{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University}
-	\city{Paris} \country{France}
-	} \email{david.naccache@ens.fr}
-\fi
-
-%% Abstract
-\begin{abstract}
-	Duplicate detection is the problem of identifying whether a given item has previously appeared in a (possibly infinite) stream of data, when only a limited amount of memory is available.
-
-	Building on the Bloom filter \cite{bloom_spacetime_1970}, an early data structure amenable to duplicate detection, several generalizations and variants were proposed that reduce error rates while maintaining constant memory.
-
-	Unfortunately the infinite stream setting is ill-posed, and error rates of duplicate detection filters turn out to be heavily constrained: as a consequence they appear to provide no advantage, asymptotically, over a biased coin toss \cite{10.1145/3297280.3297335}.
-
-	Both as a better-behaved setting and as a construction technique, a
-	\emph{windowed} variant of the duplicate detection problem was 
-	introduced in \cite{She08,Yoo10} which consists in finding duplicate 
-	entries amongst the last $w$ elements of the stream for a fixed integer $w$.
-
-	In this paper we formalize this setting, and show that a perfect (zero error) solution can be used up to a maximal window size $w_\text{max}$.
-Above this threshold we show that some existing duplicate detection filters (designed for the \emph{non-windowed} setting) perform better that those targeting the windowed problem.
-Finally, we introduce a \enquote{queuing construction} that improves on the performance of some duplicate detection filters in the windowed setting.
-
-	We also analyse the security of our filters in an adversarial setting. 
-\end{abstract}
-
-%% CCS XML
-\begin{CCSXML}
-	% Get code at http://dl.acm.org/ccs.cfm.
-	% Please copy and paste the code
-\end{CCSXML}
-
-%% Keywords
-\keywords{
-	% TODO
-}
-
-\maketitle
-
 \section{Introduction}
@@
 \end{definition}
-Instances of this problem abound in computer science, with applications to file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
+
+Note that for $w = \infty$, the problem becomes finding whether an element is a duplicate amongst all previous stream elements.
+For simplicity in the notation, when we refer to $\infty$DDP we instead write DDP.
+
+Instances of the wDDP abound in computer science, with applications to file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud detection \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc.
 A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.
@@
 As a result, we need a further relaxation of the DDP that allows for errors:
-Perfect detection is however not always reachable and it might be more practical to work on a further relaxation of the problem, allowing for errors:
-\begin{definition}[Approximate wDDP with bounded memory]
-	Solve the wDDP using at most $M$ bits of memory, with at most $\epsilon < 1/2$ mispredictions.\footnote{Given a classifier with $\epsilon > 1/2$, we obtain a classifier with $\epsilon < 1/2$ by reversing its output.}
-\end{definition}
+Perfect detection is however not always reachable and it might be more practical to work on a further relaxation of the problem, allowing for errors.
+
+%\begin{definition}[Approximate wDDP with bounded memory]
+%	Solve the wDDP using at most $M$ bits of memory, with at most $\epsilon < 1/2$ mispredictions.\footnote{Given a classifier with $\epsilon > 1/2$, we obtain a classifier with $\epsilon < 1/2$ by reversing its output.}
+%\end{definition}
+
 Approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
@@
 
-On a side note, it is clear that the input distribution plays a central role regarding how efficiently the DDP can be solved.
-For instance, some deterministic streams may be expressed very compactly (such as the output of a PRNG with known seed) making the DDP relatively easy.
+On a side note, it is clear that the input distribution plays a central role regarding how efficiently the wDDP can be solved.
+For instance, some deterministic streams may be expressed very compactly (such as the output of a PRNG with known seed) making the wDDP relatively easy.
 Information-theoretically, if the source has $U$ bits of entropy then the situation is equivalent to having an $U$-bit, uniformly distributed input.
@@
 
-As the window size in wDDP grows infinitely large, it becomes the following problem: find whether $e^\star \in E_n$.
+As said before, when the window size in wDDP grows infinitely large, it becomes the following problem: find whether $e^\star \in E_n$.
 %This \enquote{non-windowed} problem predates in fact the definition of wDDP, and several algorithms have been proposed for this problem: \cite{Den06,10.1145/3297280.3297335,Dut13} and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-Unfortunately any solution to this problem faces a phenomenon called \enquote{saturation} on large enough data streams.
-In fact, saturation is inevitable with infinite windows \cite{10.1145/3297280.3297335}, and when it happens the algorithm performs no better than at random.
+Unfortunately any solution to this problem will necessary encounter a phenomenon called \enquote{saturation} on large enough data streams \cite{10.1145/3297280.3297335}, and when it happens the algorithm performs no better than at random.
 
 This is problematic on two grounds: it makes the comparison of several algorithms difficult (since they all asymptotically behave in that fashion), and the unavoidable saturation ruins any particular design's merits.
+As such, it is more interesting to focus on wDDP rather than DDP.
 
@@
 We show that this construction, which we call Short Hash Filter (SHF), can push the value $w_\text{max}$ further while operating in constant time --- at the cost of some errors.
-We also provide a different tradeoff, the Compact Short Hash Filter (CSHF), which uses fewer memory but operates in linear time.
+%We also provide a different tradeoff, the Compact Short Hash Filter (CSHF), which uses fewer memory but operates in linear time.
 
-Unfortunately, for $w > w_\text{max}$ the performance of these algorithms degrade very rapidly.
+Unfortunately, for $w > w_\text{max}$ the performance of SHF degrades very rapidly.
 We therefore turn our attention to existing data structures designed for the \enquote{non-windowed} setting.
-We show that some of them outperform dedicated data structures, including SHF/CSHF, in the $w > w_\text{max}$ regime.
+We show that some of them outperform dedicated data structures, including SHF, in the $w > w_\text{max}$ regime.
 
@@
 \subsection{Related work}\label{sub:related}
-The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}; but several variations exist that are incomparable to one another (e.g.
+The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}.%; but several variations exist that are incomparable to one another (e.g.
 \cite{shtul2020agepartitioned}).
@@
 
-\section{Duplicate Detection and Filter Saturation}
+%\section{Duplicate Detection and Filter Saturation}
 \label{sec:dudefisa}
-\subsection{Notations and basic definitions}
-Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) set $E = (e_1, e_2, \dotsc)$, with each $e_i \in \Gamma$.
+\section{Notations and basic definitions}
+We consider an unbounded stream $E = (e_1, e_2, \dotsc, e_n, \dotsc)$ with elements belonging to an alphabet $\Gamma$.
 
-\begin{definition}[Duplicate detection filter]
-	A \emph{duplicate detection filter} (DDF) is a collection 
-	$\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$ of a state\footnote{Here, $\mathcal M$ denotes all the memory states that can be reached by the filter.} $\mathcal S \in \mathcal M$ and two algorithms,
-	\begin{itemize}
-		\item $\mathsf{Detect}: \mathcal M \times \Gamma \to \{\DUPLICATE, \UNSEEN\}$;
-		\item $\mathsf{Insert}: \mathcal M \times \Gamma \to \mathcal M$.
-	\end{itemize}
-	Informally, the $\mathsf{Detect}$ algorithm tentatively labels an element $e$ as duplicate or not, given the current state $\mathcal S$; whereas $\mathsf{Insert}$ takes as input the current state, an element $e$ to insert in the filter, and returns an updated memory state $\mathcal S'$.
-\end{definition}
+%A filter is an algorithm, which has a finite amount of memory $M$ and, for each new element $e$, outputs $\DUPLICATE$ or $\UNSEEN$ whether it thinks $e$ is a duplicate or not.;
 
-We usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathcal S| \ll |\Gamma|$.
-Otherwise, if $|\mathcal S| = |\Gamma|$ then the problem can be solved in constant time without errors \cite{10.1145/3297280.3297335}.
+We usually consider the situations where the available memory is too small for perfect detection, i.e., $M \ll |\Gamma|$.
+Otherwise, if $M = |\Gamma|$ then the problem can be solved in constant time without errors \cite{10.1145/3297280.3297335}.
 
-\begin{definition}[Duplicate element, unseen element over a sliding window]
-	Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
-In this case we write $e_j \wdup E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notwdup E$.
-\end{definition}
+An element $e_j$ is a duplicate in $E$ over the sliding window $w$, and we note $e_i \wdup E$ if there exists $j-w \leq i < j$ such that $e_i = e_j$.
+Otherwise we note $e_i \notwdup E$, and we say $e_i$ is unseen over $w$.
+A false positive over $w$ is an element $e\notwdup E$ which is classified as a duplicate, and a false negative is an element $e\wdup E$ which is classified as a not-duplicate.
 
-\begin{definition}[False positive, false negative over a sliding window]
-	Let $w \in \mathbb N$, $e \notwdup E$ (resp.
-$e \wdup E$) and let $\mathcal F$ be a DDF.
-We say that $e$ is a \emph{false positive} (resp.
-\emph{false negative}) over $w$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
-$\UNSEEN$).
-\end{definition}
-
-\begin{definition}[Probability of false positive, of false negative]
-	\label{def:pfp-pfn}
-	Let $E = (e_1, \dotsc)$ be a stream, $w\in \mathbb N$, $\mathcal F$ be a filter.
-The \emph{probability of false positive} (resp.
-\emph{probability of false negative}) of $\mathcal F$ after $i$ elements over a sliding window of size $w$, denoted $\FP^w_i$ (resp.
-$\FN^w_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp.
-false negative) over $w$.
-\end{definition}
-
-\begin{definition}[False positive rate, false negative rate over a sliding window]
-	Let $E$ be a stream, $\mathcal F$ be a DDF, $w \in \mathbb N$.
-The \emph{false positive} (resp.
-\emph{false negative}) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $w$, noted $\FPR^w_i$ (resp.
-$\FNR^w_i$), is defined as the number of false positives over $w$ divided by the number of unseen elements in $E$ over $w$ (resp.
-the number of false negative over $w$ divided by the number of duplicate elements over $w$).
-\end{definition}
-
-%\begin{definition}[Duplicate and unseen element]
-%Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$.
-Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$.
-In that case we write $e_j \dup E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notdup E$.
-%\end{definition}
-%
-
-%
-%\begin{definition}[False positive, false negative]
-%	Let $e \dup E$ (resp.
-$e \notdup E$) and $\mathcal F$ be a filter.
-We say that $e$ is a \emph{false positive} (resp.
-\emph{false negative}) when $\mathcal F.\mathsf{Detect}(e) = \DUPLICATE$ (resp.
-$\UNSEEN$).
-%\end{definition}
-%
-%\begin{definition}[False positive rate, false negative rate]
-%	Let $E$ be a stream, $\mathcal F$ be a filter.
-The \emph{false positive rate} (resp.
-\emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp.
-$\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $(e_1, \dotsc, e_i)\subset E$ (resp.
-the ratio of false negative divided by the number of duplicate elements in that subset).
-%\end{definition}
-%
-%However, it is more practical to work with another value, namely, the probability that after $m$ insertions, the element $e^\star$ is a false positive (resp. false negative). 
-%
-%\begin{definition}[Probability of false positive, of false negative]
-%	\label{def:pfp-pfn}
-%	Let $E = (e_1, \dotsc)$ be a stream, $\mathcal F$ be a filter.
-The \emph{probability of false positive} (resp.
-\emph{probability of false negative}) of $\mathcal F$ after $i$ elements, denoted $\FP_i$ (resp.
-$\FN_i$), is defined as the probability that $e_{i+1}$ is a false positive (resp.
-false negative).
-%\end{definition}
-
-We have $\FPR^w_n = \frac{1}{n}\sum_{i=1}^n \FP^w_i$, and similarly for $\FNR^w_n$.
+For a filter, the probability of false positive ($\FP^w_i$) is the probability that after $i$ insertions, the \emph{unseen} element $e_i\notwdup E$ is a false positive over $w$.
+The false positive rate $\FPR^w_i$ is the number of false positives divided by the number of unseen elements in E\footnote{We observe that $\FPR^w_n = \frac{1}{n}\sum_{i=1}^n \FP^w_i$, and similarly for $\FNR^w_n$.}.
+We similarly define the false negative probability $\FN^w_i$, and the false negative rate $\FNR^w_i$.
 
@@
 
-%\subsection{Filter Saturation and Sliding Windows}\label{sec:filsat}
-%Unfortunately, efficient duplicate detection over an infinite stream has been identified as an unsolvable problem \cite{10.1145/3297280.3297335}.
-As a matter of fact, as the number of bits of information of the stream grow to infinity, the filter can only remember an ever diminishing proportion of those bits, eventually having no advantage compared to a filter answering randomly.
+%\section{DDFs and the wDDP}
+%A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+The structure proposed in \cite{10.1145/1060745.1060753} is not desined for wDDP but a variant called `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
 %
-%In other terms, any DDF is asymptotically as good as a random guess:
-%	\begin{theorem}[\cite{10.1145/3297280.3297335}]\label{thm:sat_u}
-%	Let $\FNR_\infty$ and $\FPR_\infty$ be the asymptotic false negative and false positive rates of a filter of $M$ bits of memory (i.e. the FNR and FPR on a stream of size going to infinity).
-%	
-%	If $|\Gamma| \gg M$, then $\FNR_\infty + \FPR_\infty = 1$, which characterises random filters (i.e. filters answering randomly to any query).
-%\end{theorem}
-%
-%One way out of this situation is to lower our expectations and work on a sliding window:
-%
-%\begin{definition}[Sliding window DDP]
-%	Given a stream $E_n$ of fixed size $w$, with $E_n = (e_{n-w+1}, \dotsc, e_n)$ and an item $e^\star$, find whether $e^\star \in E_n$.
-%\end{definition} 
-%
-%We therefore introduce new definitions suited to that setting:
-%
-%\begin{definition}[Duplicate element, unseen element over a sliding window]
-%	Let $E = (e_1, e_2, \dotsc)$ be a stream over $\Gamma$, let $w\in \mathbb N$, an element $e_j \in E$ is called a \emph{duplicate} in $E$ over the sliding window of size $w$ if and only if there exists $j$ such that $j - w \leq i < j$  and $e_i = e_j$.
-In this case we write $e_j \wdup E$.
-Otherwise, $e_j$ is said to be \emph{unseen} and we write $e_j \notwdup E$.
-%\end{definition}
-%
-%\begin{definition}[False positive, false negative over a sliding window]
-%	Let $w \in \mathbb N$, $e \notwdup E$ (resp.
-$e \wdup E$) and let $\mathcal F$ be a DDF.
-We say that $e$ is a \emph{false positive} (resp.
-\emph{false negative}) over $w$ if $\mathsf{Detect}(e) = \DUPLICATE$ (resp.
-$\UNSEEN$).
-%\end{definition}
-%
-%\begin{definition}[False positive rate, false negative rate over a sliding window]
-%	Let $E$ be a stream, $\mathcal F$ be a DDF, $w \in \mathbb N$.
-The \emph{false positive} (resp.
-\emph{false negative}) rate of $\mathcal F$ over the first $i < n$ elements and the sliding window $w$, noted $\FPR^w_i$ (resp.
-$\FNR^w_i$), is defined as the number of false positives over $w$ divided by the number of unseen elements in $E$ over $w$ (resp.
-the number of false negative over $w$ divided by the number of duplicate elements over $w$).
-%\end{definition}
-
-\section{DDFs and the wDDP}
-A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
-The structure proposed in \cite{10.1145/1060745.1060753} is not desined for wDDP but a variant called `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
-
-Of these, only the A2 and b\_DBF were designed explicitly for the wDDP.
+%Of these, only the A2 and b\_DBF were designed explicitly for the wDDP.
 Others DDFs do not account for a finite-length sliding window, and therefore cannot be adjusted as a function of $w$.
@@
 
-\section{Optimal and Approximate Solutions}
-\subsection{Optimal wDDF}\label{sub:opt_solutions}
+\section{Approximate solution and SHF}
+%\subsection{Optimal wDDF}\label{sub:opt_solutions}
+%
+%Our goal is to minimise both the false positive and false negative rates of a DDF, given a fixed and limited amount of memory.
+Before going into details, we first explore the limits of the problem, i.e., when perfect or very performant solutions exist.
+%
+%\begin{theorem}
+%	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the wDDP can be solved exactly (with no errors) in constant time.
+%\end{theorem}
 
-Our goal is to minimise both the false positive and false negative rates of a DDF, given a fixed and limited amount of memory.
-Before going into details, we first explore the limits of the problem, i.e., when perfect or very performant solutions exist.
+%\begin{proof}
+%	We explicitly construct a DDF that performs the detection. Storing all $w$ elements in the sliding window takes $w\log_2(|\Gamma|)$ memory, using a FIFO queue $Q$; however 
+%	lookup has a worst-time complexity of $O(w)$. 
+%	
+%	We therefore rely on an
+%	ancillary data structure for the sake of quickly answering lookup questions.
+%	Namely we use a dictionary $D$ whose keys are elements from $\Gamma$ and values are counters.
+%	
+%	When an element $e$ is inserted in the DDF, $e$ is stored and $D[e]$ is incremented (if the key $e$ did not exist in $D$, it is created first, and
+%	$D[e]$ is set to $1$). In order to keep the number of stored elements to $w$, 
+%	we discard the oldest element $e_\text{last}$ in $Q$.
+As we do so, we also decrement $D[e_\text{last}]$, and if $D[e_{last}] = 0$ the key is deleted from $D$.
+The whole insertion procedure is therefore performed in constant time.
+%	
+%	Lookup of an element $e^\star$ is simply done by looking whether the key $D[e^\star]$ exists, which is done in constant time.
+%	
+%	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
+Thus a requirement of $w (\log_2(w) + 2\log_2(|\Gamma|))$ bits for this DDF to work.
+%
+%	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element is present in the sliding window.
+%\end{proof}
 
-\begin{theorem}
+\subsection{Optimal and Approximate Optimal wDDF}
+%The optimal filter described above requires that the size of $\Gamma$ is known in advance. The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing errors.
+\begin{restatable}{thm}{optwddf}\label{thm:opt_wddf}
 	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the wDDP can be solved exactly (with no errors) in constant time.
-\end{theorem}
+\end{restatable}
 
 \begin{proof}
-	We explicitly construct a DDF that performs the detection. Storing all $w$ elements in the sliding window takes $w\log_2(|\Gamma|)$ memory, using a FIFO queue $Q$; however 
-	lookup has a worst-time complexity of $O(w)$.
-
-	We therefore rely on an
-	ancillary data structure for the sake of quickly answering lookup questions.
-	Namely we use a dictionary $D$ whose keys are elements from $\Gamma$ and values are counters.
-
-	When an element $e$ is inserted in the DDF, $e$ is stored and $D[e]$ is incremented (if the key $e$ did not exist in $D$, it is created first, and
-	$D[e]$ is set to $1$). In order to keep the number of stored elements to $w$, 
-	we discard the oldest element $e_\text{last}$ in $Q$.
-As we do so, we also decrement $D[e_\text{last}]$, and if $D[e_{last}] = 0$ the key is deleted from $D$.
-The whole insertion procedure is therefore performed in constant time.
-
-	Lookup of an element $e^\star$ is simply done by looking whether the key $D[e^\star]$ exists, which is done in constant time.
-
-	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
-Thus a requirement of $w (\log_2(w) + 2\log_2(|\Gamma|))$ bits for this DDF to work.
-
-	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element is present in the sliding window.
+	Due to page limit restrictions, all theorem proofs' are in Appendix~\ref{app:proofs}.
 \end{proof}
 
-\subsection{Approximate Optimal wDDF}
-The optimal filter described above requires that the size of $\Gamma$ is known in advance. The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing errors.
+However, this optimal filter requires that the size of $\Gamma$ is known in advance. The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing errors.
 
-\begin{theorem}\label{thm:SHF}
+\begin{restatable}{thm}{shf}\label{thm:SHF}
 	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the wDDP can be solved with almost no error using $M$ bits of memory.
@@
 	Using $M \simeq 5w\log_2 w$ bits of memory, a constant-time filter with the same error rate can be constructed.
-\end{theorem}
+\end{restatable}
 Note that we only consider the probability of false positive after the filter has inserted at least $w$ elements, i.e., once the filter is full and has reached a stationary regime.
-\begin{proof}
-	Here again we explicitly construct the filters that attain the theorem's bounds.
 
-	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
-The birthday theorem \cite{10.1007/3-540-45708-9_19} states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
+%\begin{proof}
+%	Here again we explicitly construct the filters that attain the theorem's bounds.
+%
+%	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
+%The birthday theorem \cite{10.1007/3-540-45708-9_19} states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
 Therefore $2^{(2 \log_2 w) / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
@@
 The 50\% threshold we impose on $h$ is arbitrary but nonetheless practical.
-
-Let $\mathcal F$ be the following DDF: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
+%
+%Let $\mathcal F$ be the following DDF: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
 $\mathsf{Insert}(e)$ appends $h(e)$ to the queue before popping the queue.
-
-There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FN of $0$ and a FP of $1 - (1-\frac1{w^2})^w$.
-The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
-
-Note that this solution has a time complexity of $O(w)$.
+%
+%There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FN of $0$ and a FP of $1 - (1-\frac1{w^2})^w$.
+%The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
+%
+%Note that this solution has a time complexity of $O(w)$.
 Using an additional dictionary, as in the previous proof, but with keys of size $2\log_2(w)$, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, using $w \cdot 2\log_2 w + w \cdot (2\log_2(w) + \log_2(w)) = 5w\log_2 w$ bits of memory.
-\end{proof}
+%\end{proof}
 
@@
 
-\section{Short Hash Filter}
+%\section{Short Hash Filter}
 \subsection{Short Hash Filter Algorithm}
@@
 
-\begin{algorithm}[!h]
+\begin{algorithm}
 	\caption{SHF Setup, Lookup and Insert}\label{alg:SHF}
@@
 	\begin{algorithmic}[1]
-		\Function{Setup}{$\mathcal M, w$}
+	\Function{Setup}{$M, w$}
 	\Comment $M$ is the available memory, $w$ the size of the sliding window
@@
 	\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
-		\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h$ => counter (of max value $w$)
+	\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h \Rightarrow$  counter (of max value $w$)
 
-		\State\Return filter
+%	\State\Return filter
 	\EndFunction 
-%		\item[]
 	\end{algorithmic}
 
+	\begin{multicols}{2}
 	\begin{algorithmic}[1]
+	\item[]
+	\item[]
 	\Function{Lookup}{$e$}
@@
 	\EndFunction
-%	\item[]
+	\item[]
+	\item[]
 \end{algorithmic}
@@
 \end{algorithmic}
+	\end{multicols}
 \end{algorithm}
 
-\subsection{Compact Short Hash Filter}
-Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
+%\subsection{Compact Short Hash Filter}
+%Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
 The CSHF performs in linear time in $w$, and is a simple queue, the only point is that instead of storing $e$, one stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.
@@
 
-\subsection{Error Rates}
+\paragraph{Error Rates.}
 Let $w> 0$ be a window size and $M > 0$ the available memory.
 
-We write $\FN^w_\text{SHF}$ the probability of false negative of an SHF with these parameters. We similarly define $\FP^w_\text{SHF}$, $\FN^w_\text{CSHF}$, $\FP^w_\text{CSHF}$.
+%We write $\FN^w_\text{SHF}$ the probability of false negative of an SHF with these parameters. We similarly define $\FP^w_\text{SHF}$.%, $\FN^w_\text{CSHF}$, $\FP^w_\text{CSHF}$.
 
-\begin{theorem}	
-	\begin{align*}
-		\FN_\text{SHF}^w&  = \FN_\text{CSHF}^w =0 \\
-		\FP_\text{SHF}^w & = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w \\
-		\FP_\text{CSHF}^w & = 1 - \left(1 - 2^{-M/w}\right)^w
-	\end{align*}
-\end{theorem}
+\begin{restatable}{thm}{fprSHF}\label{thm:fprSHF}	
+	$\FN_\text{SHF}^w  = 0$  and $\FP_\text{SHF}^w = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w$
+\end{restatable}
 
-\begin{proof}
-	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$, while a CSHF has fingerprints of size $h' = \frac Mw$.
-\end{proof}
+%\begin{proof}
+%	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$, while a CSHF has fingerprints of size $h' = \frac Mw$.
+%\end{proof}
 
-\paragraph{Remark:} A CSHF of size $M$ has the same error rate than an SHF of size $2M + w\log_2 w$.
-\subsection{Saturation}
-Both SHF and CSHF have strictly increasing error rates, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
+%\paragraph{Remark:} A CSHF of size $M$ has the same error rate than an SHF of size $2M + w\log_2 w$.
+\paragraph{Saturation.}
+SHF and have strictly increasing error rates, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
 Beyond this value, these filters saturate extremely quickly: in other words, most SHF will either have an error rate of $0$ or $1$.
@@
 An illustration of this phenomenon can be seen in Figure~\ref{fig:shorts}, 
-which shows the error rates for CSHF and SHF with $M=10^5$, against 
+which shows the error rates for SHF with $M=10^5$, against 
 a uniformly random stream of $18$-bit elements ($|\Gamma| = 2^{18}$). The benchmark used a finite stream of length $10^6$.
 
-\begin{figure}[!h]
+\begin{figure}[t]
+\makebox[\textwidth]{\makebox[1.05\textwidth]{%
+\begin{minipage}{.5\textwidth}
 	\centering
@@
 	\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:shorts}
+\end{minipage}
+\hfill
+\begin{minipage}{.5\textwidth}
+	\centering
+	\begin{tikzpicture}
+		\input{graphs/er_n_artificial}
+	\end{tikzpicture}
+	\caption{Error rate (times 100) of DDFs of 1Mb as a function of stream length. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
+\end{minipage}
+}}
 \end{figure}
@@
 The value $w_\text{max}$ can be obtained by solving (numerically) for $\FP^{w_\text{max}} = 1/2$ for a given $M$.
-We numerically solved the equation $\FP^w = 0.5$ for these two filters, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$.
+%We numerically solved the equation $\FP^w = 0.5$ for these two filters, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$.
 Results
 % are given in Figure~\ref{fig:w_opt} and 
-indicate an approximately linear relationship between $M$ and $w_\text{max}$: %for large values of $M$:
- $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).
+Experiments indicate an approximately linear relationship between $M$ and $w_\text{max}$: %for large values of $M$:
+ %$w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and
+$w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).
 
@@
 However, they sometimes prove to be efficient in some specific wDDP settings.
-
 This bound is useful for several reasons, notably it provides an estimation of how close to optimality existing filters are.
 
-\begin{theorem}
-	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $ER_n = \FP_n + \FN_n$ satisfies
-	\begin{equation}
+\begin{restatable}{thm}{asymptoticSaturation}\label{thm:asymptoticSaturation}
+	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $E_n = \FP_n + \FN_n$ satisfies
+$
 	E_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
-	\end{equation}
+$
 	for any $n > M$.
-\end{theorem}
+\end{restatable}
 In particular, the asymptotic error rate $E_\infty$ satisfies 
-\begin{equation*}
+$
 	E_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|.
-\end{equation*}
+$
 
-\begin{proof}
-	By definition, a perfect filter has the lowest possible error rate.
-	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
+%\begin{proof}
+%	By definition, a perfect filter has the lowest possible error rate.
+%	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
 Up to reordering the stream, without loss of generality because it is random, we may assumethat the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
-
-	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
+%	
+%	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
 On the other hand, if the element is not in memory, a perfect filter can choose to answer randomly.
@@
 An optimal filter will lower the error rate of any filter using the same strategy with a different probability.
-
-	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
+%	
+%	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
 For this reason, this filter has an FP probability of $p$.
-
-	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
+%	
+%	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
 Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
 Then $e^\star$ triggers a false negative with probability
-	\begin{align*}
-		\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
-		& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
-		\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
-	\end{align*}
-	Hence, the error probability of the filter is
-	\begin{align*}
-		E_n 
-		& = \FN_n + p
-		=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
-		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
-	\end{align*}
-	which is minimized when $p = 0$. 
-\end{proof}
+%	\begin{align*}
+%		\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
+%		& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
+%		\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
+%	\end{align*}
+%	Hence, the error probability of the filter is
+%	\begin{align*}
+%		E_n 
+%		& = \FN_n + p
+%		=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
+%		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
+%	\end{align*}
+%	which is minimized when $p = 0$. 
+%\end{proof}
 
@@
 These filters are run against a stream of uniformly sampled elements from an alphabet of $2^{26}$ elements.
-This results in around 8\% duplicates (up to statistical fluctuations) amongst the 150 000 000 elements in the longest stream used.
+This results in around 8\% duplicates amongst the 150 000 000 elements in the longest stream used.
 %As a comparison, we also run the same benchmark against a stream obtained from crawling data, the same one as \cite{10.1145/3297280.3297335}, a real-world source which is highly non-uniform --- note that in this case, our lower bound on the error rate does not apply, owing to the stream being compressible.
@@
 Results are plotted in Figure~\ref{fig:graph_n}.
-
-%\begin{figure*}[!h]
-%	\begin{tikzpicture}
-%	\begin{groupplot}[
-%	group style = {
-%		group size = 2 by 1,
-%		horizontal sep = 35pt,
-%	},
-%	axis lines = left,
-%	ylabel near ticks,
-%	width = 0.4\textwidth,
-%	height = 0.27\textwidth,
-%	]
-%	\input{er_n_artificial}
-%	\input{er_n_real}
-%	%\input{10e6_sum_zipf}
-%	\end{groupplot}
-%    \path (top)--(bot) coordinate[midway] (group center);
-%%	\node[above,rotate=90] at (group center -| current bounding box.west) {Error rate (\%)};
-%	\node[right=1em,inner sep=0pt] at(group center -| current bounding box.east) {\pgfplotslegendfromname{legend_n}};
-%	\end{tikzpicture}
-%
-%%	\input{er_n_artificial}
-%	\caption{Error rate (times 100) of DDFs of 1Mb, over a real and artificial stream, depending on the size of the stream, without any sliding window.
-Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
-%\end{figure*}
-
-\begin{figure}[!h]
-	\begin{tikzpicture}
-	\input{er_n_artificial}
-	\end{tikzpicture}
-	\caption{Error rate (times 100) of DDFs of 1Mb as a function of stream length. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
-\end{figure}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
+\makebox[\textwidth]{\makebox[1.25\textwidth]{%
+	\begin{minipage}{.5\textwidth}
 	\centering
@@
 	\label{fig:nwddf-in-wddp}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{.7\textwidth}
+	\centering
+	\input{fig/queuef.tex}
+	\caption{Architecture of the queuing filter.
+The filter is composed of $L$ subfilters $\mathcal F$, each containing up to $c$ elements.
+Once the newest subfilter has inserted $c$ elements in its structure, the oldest one is expired.
+As such, it is dropped and a new one is created and put under population at the beginning of the queue.
+In this example, the sub-sliding window of $\mathcal F_1$ is $(e_{m-2}, e_{m-3}, e_{m-4})$.} \label{fig:scheme}
+	\end{minipage}
+}}
 \end{figure}
@@
 As such, we can consider that each subfilter operates on a sub-sliding window of size $c$, which makes the overall construction a DDF operating over a sliding window of size $w = cL$.
-
-\begin{figure}
-	\input{fig/queuef.tex}
-	\caption{Architecture of the queuing filter.
-The filter is composed of $L$ subfilters $\mathcal F$, each containing up to $c$ elements.
-Once the newest subfilter has inserted $c$ elements in its structure, the oldest one is expired.
-As such, it is dropped and a new one is created and put under population at the beginning of the queue.
-In this example, the sub-sliding window of $\mathcal F_1$ is $(e_{m-2}, e_{m-3}, e_{m-4})$.} \label{fig:scheme}
-\end{figure}
 
@@
 		\State \textbf{store} (subfilters, $L$, $m$, counter)
-		\State\Return filter
+%		\State\Return filter
 	\EndFunction 
-	\item[]
 	\end{algorithmic}
 
+	\begin{multicols}{2}
 	\begin{algorithmic}[1]
@@
 	\end{algorithmic}
+	\end{multicols}
 \end{algorithm}
@@
 
-\begin{theorem}
+\begin{restatable}{thm}{pfpQueue}
 	\label{thm:queue-pfp}
-	 Let $\FP_{\mathcal Q, m}^w$ be the probability of false positive (def. \ref{def:pfp-pfn}) of $\mathcal Q$ after $m > w$ insertions, over a sliding window of size $w = cL$, we have:
-	\begin{equation}
+	 Let $\FP_{\mathcal Q, m}^w$ be the probability of false positive %(def. \ref{def:pfp-pfn})
+	 of $\mathcal Q$ after $m > w$ insertions, over a sliding window of size $w = cL$, we have \\
+	$$%\begin{equation}
 		\label{eq:queue-pfp}
 		\FP_{\mathcal Q, m}^w = 1 - \left(1 - \FP_{\mathcal F,c}\right)^{L-1} \left(1 - \FP_{\mathcal F, m \bmod c }\right)
-	\end{equation}
+	$$ %\end{equation}
 	where $\bmod$ is the modulo operator and 
-	 $\FP_{\mathcal F,m}$ be the probability of false positive a subfilter $\mathcal F$ after $m$ insertions.
-\end{theorem}
+	 $\FP_{\mathcal F,m}$ is the probability of false positive of a subfilter $\mathcal F$ after $m$ insertions.
+\end{restatable}
 
-\begin{proof}
-	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream and $e^\star \notwdup E$.
-
-	Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
+%\begin{proof}
+%	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream and $e^\star \notwdup E$. 
+%	
+%	Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
 Conversely, $e^\star$ is \emph{not} a false positive when all subqueries $\mathcal F_i.\mathsf{Lookup(e^\star)}$ return \UNSEEN, i.e., when $e^\star$ is not a false positive for each subfilter.
-
-	Each subfilter has undergone $c$ insertions, safe for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
-\end{proof}
+%	
+%	Each subfilter has undergone $c$ insertions, safe for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
+%\end{proof}
 
@@
 \subsubsection{Probability of False Negative}\label{sub:fnr}
-\begin{theorem}
+\begin{restatable}{thm}{pfnQueue}
 	\label{thm:queue-pfn}
 	Let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation}
+	$$%\begin{equation}
 	\FN_{\mathcal Q, m}^w 
 	=  u_c^{L-1} u_{m \bmod c}
-	\end{equation}
+	$$%\end{equation}
 	where $\bmod$ is the modulo operator, and we have introduced the short-hand notation $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$ where 
 	$\FN_{\mathcal F,\eta}$ (resp. $\FP_{\mathcal F, \eta}$) is the probability of false negative (resp. false positive) of the subfilter $\mathcal F$ after $\eta$ insertions, and
-	\begin{equation*}
+	$%\begin{equation*}
 		p_\eta = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^\eta}{1-\left(1-\frac 1{|\Gamma|}\right)^w} \approx \frac{\eta}{w}.
-	\end{equation*}
-\end{theorem}
+	$%\end{equation*}
+\end{restatable}
 
-\begin{proof}
-	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
-
-	Then $e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$. There can be two cases:
-	\begin{itemize}
-		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window;
-		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window.
-	\end{itemize}
-In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
+%\begin{proof}
+%	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$. 
+%	
+%	Then $e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$. There can be two cases:
+%	\begin{itemize}
+%		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window;
+%		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window.
+%	\end{itemize}
+%In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
 This happens with probability $\FN_{\mathcal F,c}$ by definition, except for $\mathcal F_0$, for which the probability is $\FN_{\mathcal F, m\bmod c}$.
-
-In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$, which happens with probability $1-\FP_{\mathcal F,c}$, execpt for $\mathcal F_0$, for which the probability is $1-\FP_{\mathcal F, m\bmod c}$.
-
-Finally, each event is weighted by the probability $p_c$ that $e^\star$ is in $\mathcal F_i$'s sub-sliding window:
-\begin{align*}
-	p_c 
-	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
-	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
-	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
-%		\end{align*}\begin{align*}p_c
-	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
-	& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
-\end{align*}
-This concludes the proof.
-\end{proof}
-\paragraph{Remark.} As previously, the effect of $w < cL$ is negiglible for all practical purposes and Theorem~\ref{thm:queue-pfn} is considered a good approximation in that regime.
+%
+%In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$, which happens with probability $1-\FP_{\mathcal F,c}$, execpt for $\mathcal F_0$, for which the probability is $1-\FP_{\mathcal F, m\bmod c}$.
+%
+%Finally, each event is weighted by the probability $p_c$ that $e^\star$ is in $\mathcal F_i$'s sub-sliding window:
+%\begin{align*}
+%	p_c 
+%	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
+%	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
+%	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
+%%		\end{align*}\begin{align*}p_c
+%	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
+%	& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
+%\end{align*}
+%This concludes the proof.
+%\end{proof}
+\paragraph{Remark.} As previously, the effect of $w < cL$ is negligible for all practical purposes and Theorem~\ref{thm:queue-pfn} is considered a good approximation in that regime.
 
@@
 From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR when $m = cn$ for $n$ a positive integer.
-\begin{theorem}
+\begin{restatable}{thm}{fprQueue}
 	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
@@
 	\end{equation*}
-\end{theorem}
-\begin{proof}
+\end{restatable}
+%\begin{proof}
+%
+%\begin{align*}
+%	\FPR_{\mathcal Q, cn}^w
+%	& = \frac{1}{cn} \sum_{k=1}^{cn} \FP_{\mathcal Q, k}^w 
+%	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, k + \ell}^w 
+%	 = \frac1c \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, \ell}^w \\
+%	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
+%	& = 1 - \frac1c(1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
+%\end{align*}
+%\end{proof}
 
-\begin{align*}
-	\FPR_{\mathcal Q, cn}^w
-	& = \frac{1}{cn} \sum_{k=1}^{cn} \FP_{\mathcal Q, k}^w 
-	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, k + \ell}^w 
-	 = \frac1c \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, \ell}^w \\
-	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
-	& = 1 - \frac1c(1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
-\end{align*}
-\end{proof}
-
-\begin{theorem}
+\begin{restatable}{thm}{fnrQueue}
 	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
@@
 	\end{equation*}
-\end{theorem}
+\end{restatable}
 
-\begin{proof}
-\begin{align*}
-	\FNR_{\mathcal Q, cn}^w 
-	& = \frac{1}{cn} \sum_{k=1}^{cn} \FN_{\mathcal Q, k}^w 
-	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, k + \ell}^w 
-	= \frac1c \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, \ell}^w \\
-	& = \frac1c \sum_{\ell = 0}^{c-1} u_c^{L-1} u_{\ell} 
-	 = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
-\end{align*}
-\end{proof}
+%\begin{proof}
+%\begin{align*}
+%	\FNR_{\mathcal Q, cn}^w 
+%	& = \frac{1}{cn} \sum_{k=1}^{cn} \FN_{\mathcal Q, k}^w 
+%	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, k + \ell}^w 
+%	= \frac1c \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, \ell}^w \\
+%	& = \frac1c \sum_{\ell = 0}^{c-1} u_c^{L-1} u_{\ell} 
+%	 = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
+%\end{align*}
+%\end{proof}
 As for the probabilities, the expressions derived above for the FNR and FNR are valid to first order in $(w - cL)/|\Gamma|$, i.e. they are good approximations even when $w \approx cL$.
@@
 Because $u_\eta = p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$, differentiating with respect to $L$, knowing that $w = Lc$, and equating the derivative to $0$, one can find the optimal value for $L$ by solving for $x$, which has been obtained via Mathematica:
+%\begin{equation*}
 
-%\begin{equation*}
 \begin{align*}
-&-\alpha \beta^{-1+x} \log(\beta)  \\ 
-&+ \left(\beta + \FN_{\mathcal F, c} (-1+x)\right)^{-2+x} x^{-x} \left[\vphantom{\left(\FN^{\FN}\right)}\right. \\
-&\quad
+&-\alpha \beta^{-1+x} \log(\beta) 
++ \left(\beta + \FN_{\mathcal F, c} (-1+x)\right)^{-2+x} x^{-x} \left[\vphantom{\left(\FN^{\FN}\right)}\right. 
 	-\alpha \beta + \FN_{\mathcal F, c} \left(-\beta (-2+x)+ \FN_{\mathcal F, c} (-1+x)\right) \\
-&\quad	+ \left(\alpha+ \FN_{\mathcal F, c} (-1+x)\right) \\
-& \quad \quad \times\left(\beta + \FN_{\mathcal F, c} (-1+x)\right) \left(\log\left(\beta + \FN_{\mathcal F, c} (-1+x)\right)-\log(x)\right) \\
-&\left.\vphantom{\left(\FN^{\FN}\right)}\right] = 0
+&\quad	+ \left(\alpha+ \FN_{\mathcal F, c} (-1+x)\right)
+\times\left(\beta + \FN_{\mathcal F, c} (-1+x)\right) \left(\log\left(\beta + \FN_{\mathcal F, c} (-1+x)\right)-\log(x)\right)
+\left.\vphantom{\left(\FN^{\FN}\right)}\right] = 0
 \end{align*}
+
 If numerically solving the equation for individual cases is feasible, it seems unlikely that a closed-form formula exists.
@@
 It remains to decide which subfilter construction to choose.
-The results of an experimental comparison of different DDFs (details about the benchmark are given in Section~\ref{sub:saturation}) are summarizes in Figure~\ref{fig:graph_n}.
-It appears that the most efficient filter (in terms of saturation rate) is the QHT \cite{10.1145/3297280.3297335}.
+The results of an experimental comparison of different DDFs (details about the benchmark are given in Section~\ref{sub:saturation}) are summarized in Figure~\ref{fig:graph_n}.
+It appears that the most efficient filter (in terms of saturation rate) is the QHT, from \cite{10.1145/3297280.3297335}.
 
@@
 
-\begin{figure}[!h]
+\begin{figure}[t]
+\makebox[\textwidth]{\makebox[1.15\textwidth]{%
+	\begin{minipage}{.5\textwidth}
+		\centering
 		\input{graphs/compare_queues.tex}
 		\caption{Error rate (times 100) of queuing filters as a function of window size, $M=10^5$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{.6\textwidth}
+		\centering
+		\input{graphs/bench_l.tex}
+		\caption{Evolution of the error rate of a queueing QHT as a function of $L$, for several window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
+	\end{minipage}
+}}
 \end{figure}
+
 %\begin{table}[]
@@
 
-\begin{figure}[!h]
-	\input{graphs/bench_l.tex}
-	\caption{Evolution of the error rate of a queueing QHT as a function of $L$, for several window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
-\end{figure}
-
 We observe that the optimal value for $L$ does indeed depend on the desired sliding window.
@@
 
-\begin{figure}[!h]
+\begin{figure}[t]
+	\centering
 	\input{graphs/improvement.tex}
@@
 The game has two distinct parts.
-
 \begin{itemize}
@@
 
-\subsection{False positive and false negative resistance}
+\subsubsection{False positive and false negative resistance}
 
@@
 
-\subsection{Bound on false positive resistance}
+%\paragraph{\textbf{Bound on false positive resistance}}
 
-\begin{theorem}
+\begin{restatable}[Bound on false positive resistance]{thm}{fprRes}
 	Let $\mathcal Q$ be a filter of $L$ subfilters $\mathcal F_i$, with $c$ insertions maximum per subfilter, let $w$ be a sliding window.
@@
 	If $cL > w$, the adversary has a probability of success of at least $1-(1-p)^L$.
-\end{theorem}
+\end{restatable}
 
-\begin{proof}
-	If $cL \leq w$, then information-theoretically the subfilters only have information on elements in the sliding window.
-	The probability of false positive for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$, which is strictly increasing with $\FP_{\mathcal F,c}$.
+%\begin{proof}
+%	If $cL \leq w$, then information-theoretically the subfilters only have information on elements in the sliding window.
+%	The probability of false positive for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$, which is strictly increasing with $\FP_{\mathcal F,c}$.
 Hence, the optimal solution is reached by to maximising the probability of false positive in each subfilter $\mathcal F_i$.
 By hypothesis the latter is bounded above by $p$ after $c$ insertions.
-
-	On the other hand, if $cL > w$ then oldest filter holds information about elements that are not in the sliding window anymore.
+%	
+%	On the other hand, if $cL > w$ then oldest filter holds information about elements that are not in the sliding window anymore.
 Hence, a strategy for the attacker trying to trigger a false positive on $e^\star$ could be to make it so these oldest elements are all equal to $e^\star$.
@@
 The adversary $\mathcal A$ can create a new stream $E' = e^\star | e^\star | \dotsc | E$ where $e^\star$ is prepended $cL - w$ times to $E$.
+%	
+%	After $w$ insertions, the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ probability of success.
+If, for some reason, the last subfilter answers $\DUPLICATE$ with probability less than $p$, then the same reasoning as for when $cL \leq w$ still applies, hence we get the correspondig lower bound (which is, in this case, an equality).
+%\end{proof}
+%%
+%\paragraph{\textbf{Bounds on false negative resistance}}
 
-	After $w$ insertions, the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ probability of success.
-If, for some reason, the last subfilter answers $\DUPLICATE$ with probability less than $p$, then the same reasoning as for when $cL \leq w$ still applies, hence we get the correspondig lower bound (which is, in this case, an equality).
-\end{proof}
-
-\subsection{Bounds on false negative resistance}
-
-\begin{theorem}
+\begin{restatable}[Bounds on false negative resistance]{thm}{fnrRes}
 	Let $\mathcal Q$ be a filter of $L$ subfilters of kind $\mathcal F$, with $c$ insertions maximum per subfilter, and let $w$ be a sliding window.
@@
 	On the other hand if $w > (L-1)c$ then $\mathcal Q$ is  $(\max(1 - q, p)^{L}, w)$-resistant to false negative attacks on the sliding window $w$.
-\end{theorem}
+\end{restatable}
 
-\begin{proof}
-	Let us first prove that a PPT adversary $\mathcal A$ can win the game with probability at least $p^L$.
-	For this, let us consider the adversarial game against the subfilter $\mathcal F$: after $c$ insertions from an aversarial stream $E_c$, $\mathcal A$ choses a duplicate $e^\star$ which will be a false negative with proability $p$.
-	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c \mid E_c \mid \cdots \mid E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a probability of success for $\mathcal A$ of $p^L$.
-
-	Now, Let us prove the case where $w\leq (L-1)c$.
+%\begin{proof}
+%	Let us first prove that a PPT adversary $\mathcal A$ can win the game with probability at least $p^L$.
+%	For this, let us consider the adversarial game against the subfilter $\mathcal F$: after $c$ insertions from an aversarial stream $E_c$, $\mathcal A$ choses a duplicate $e^\star$ which will be a false negative with proability $p$.
+%	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c \mid E_c \mid \cdots \mid E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a probability of success for $\mathcal A$ of $p^L$.
+%	
+%	Now, Let us prove the case where $w\leq (L-1)c$.
 In this case, at any time, $\mathcal Q$ remembers all elements from inside the sliding window.
@@
 The probability of a subfilter to answer $\UNSEEN$ is:
-
-	\begin{itemize}
-		\item $\FN'_{\mathcal F,c}$ if $e^\star$ is in the subfilter's sub-sliding window;
-		\item $1 - \FP'_{\mathcal F, c}$ if $e^\star$ is not in the subfilter's sub-sliding window
-	\end{itemize}
-	where $\FN'$ and $\FP'$ are the probabilities of false negative and positives on the adversarial stream (which may be different from a random uniform stream).
-
-	However, since $e^\star$ is a duplicate, it is in at least one subfilter's sub-sliding window.
+%	
+%	\begin{itemize}
+%		\item $\FN'_{\mathcal F,c}$ if $e^\star$ is in the subfilter's sub-sliding window;
+%		\item $1 - \FP'_{\mathcal F, c}$ if $e^\star$ is not in the subfilter's sub-sliding window
+%	\end{itemize}
+%	where $\FN'$ and $\FP'$ are the probabilities of false negative and positives on the adversarial stream (which may be different from a random uniform stream).
+%	
+%	However, since $e^\star$ is a duplicate, it is in at least one subfilter's sub-sliding window.
 As such, the optimal strategy for $\mathcal A$ is to maximise the probability of all subfilters to answer $\UNSEEN$.
-	Now, $\FN'_{\mathcal F,c}$ is bounded above by $p$ and $1 - \FP'_{\mathcal F, c}$ is bounded above by $1-q$, so the best strategy is where as many filters as possible answer $\UNSEEN$ with probability $\max(p, 1-q)$, knowing that at least one filter must contain $e^\star$ and as such its probability for returning $\UNSEEN$ is at most $p$, hence the result.
-
-	Now, let us consider the case when $w > (L-1)c$.
+%	Now, $\FN'_{\mathcal F,c}$ is bounded above by $p$ and $1 - \FP'_{\mathcal F, c}$ is bounded above by $1-q$, so the best strategy is where as many filters as possible answer $\UNSEEN$ with probability $\max(p, 1-q)$, knowing that at least one filter must contain $e^\star$ and as such its probability for returning $\UNSEEN$ is at most $p$, hence the result.
+%	
+%	Now, let us consider the case when $w > (L-1)c$.
 We have already introduce the element $e^\star$ in the last $w$ elements, and we want to insert it again.
 It is possible, for the adversary, to create the following stream $E = (e_1, e_2, \dotsc, e_{c-1}, e^\star, e_{c+1}, \dotsc, e_{Lc}, e_{Lc + 1})$, and to insert $e^\star$ afterwards.
-
-	When $e_{Lc+1}$ is inserted, all elements $(e_1, \dotsc, e_{c-1}, e^\star)$ are dropped as the oldest subfilter is popped.
+%	
+%	When $e_{Lc+1}$ is inserted, all elements $(e_1, \dotsc, e_{c-1}, e^\star)$ are dropped as the oldest subfilter is popped.
 Hence, in this context $e^\star$ is not in any subfilter anymore, so by adapting the previous analysis, $\mathcal A$ can get a false negative with probability at most $\max(1 - q, p)^{L}$.
-\end{proof}
+%\end{proof}
 %% Acknowledgements 
@@
 %% Bibliography
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{qhtv2}
-
-%% Appendix
-\appendix
-
-\section{Effects of the simulation's finiteness}
-\label{app:finite}
-
-Theoretical results about the queuing construction apply in principle to an infinite stream.
-However, simulations are necessarily finite, and for very large windows (that are approximately the same size as the whole stream) this causes interesting artefacts in the error rates.
-
-Note that these effects have very little impact on practical implementations of queuing filters, since almost all use cases assume a window size much smaller than the stream (or, equivalently, a very large stream).
-Nevertheless we illustrate the effect of the finite simulation and the parameters affecting it, if only to motivate a further analytical study of this phenomenon.
-
-Figure~\ref{fig:strangess} measures the error rate as a function of $w$, for different stream sizes $N$.
-A visible decrease in $ER$ can be found around $w\approx N$.
-While we do not have any explanation for the difference in the peaks sizes and exact location, we give the hypothesis that it is related to the choice of $|\Gamma|$.
-
-\begin{figure}[]
-	\centering
-	\input{graphs/stream_size_qht.tex}
-	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
-\end{figure}
-
-As can be seen on this simulation, there is only disagreement around $w \approx N/L$, and increasing $N$ results in a later and smaller peak.
-
-It is also possible to run simulations for different alphabet sizes $\Gamma$, which shows that the peak's position increases with $|\Gamma|$, although the relationship is not obvious to quantify.
-
-\section{Filters vs queued filters (complement)}\label{app:improvement}
-We here run a comparison of the Cuckoo Filter relative to the Queueing Cuckoo Filter, as well as the SBF relatively to the queueing SBF. The results are given in Figure~\ref{fig:appendix_improvement}.
-
-\begin{figure}[]
-\begin{tikzpicture}
-	\begin{semilogxaxis}[legend cell align = left,%
-		 %legend pos=outer north east, 
-	legend style={at={(0.02,0.98)},anchor=north west},%
-		 xlabel=$w$, ylabel=$\FPR^w + \FNR^w (\times 100)$]
-	\addplot[color=teal, mark=triangle] table[x=w,y=Error] {Queueing_Cuckoo.dat};
-	\addlegendentry{Q\_Cuckoo};
-	\addplot[color=teal, mark=triangle, dashed] table[x=w,y=Error] {Cuckoo.dat};
-	\addlegendentry{Cuckoo};
-	%%
-	\addplot[color=olive, mark=square, mark options = {scale=0.7}] table[x=w,y=Error] {Queueing_StableBloom.dat};
-	\addlegendentry{Q\_SBF};
-	\addplot[color=olive, mark=square, mark options = {scale=0.7}, dashed] table[x=w,y=Error] {SBF.dat};
-	\addlegendentry{SBF};
-
-	%\addplot[mark=x,^8$}
-	\end{semilogxaxis}
-
-\end{tikzpicture}
-	\caption{Comparing performances of the Cuckoo and SBF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
-\end{figure}
-\end{document}

### 2020-04-15 fig/queuef.tex
add part 7 + small fixes
COCOON version

@@
-\begin{tikzpicture}[scale=0.4]
+\begin{tikzpicture}[scale=0.37]
 
@@
 	%stream 
-	\draw [<-, >=latex] (0, 5.5) -- (19, 5.5) node[above, midway] {Stream};
+	\draw [<-, >=latex] (0, 5.5) -- (19, 5.5) node[above, midway] {Stream (most recent on the left)};
 	\foreach \x in {1, 3,...,18}
@@
 	\draw (0, -5) rectangle (1, -5.5) node[midway] {\tiny $\mathcal F$};
-	\draw (1.25, -5.25) node[anchor=west] {\tiny Subfilter being populated};
+	\draw (1.25, -5.25) node[anchor=west,align=left] {\tiny Subfilter being\\ \tiny populated};
 
 	\draw[pattern=north west lines, pattern color=gray] (7, -5) rectangle (8, -5.5) node[midway] {\tiny $\mathcal F_i$};
-	\draw (8.25, -5.25) node[anchor=west] {\tiny Populated active subfilter};
+	\draw (8.25, -5.25) node[anchor=west,align=left] {\tiny Populated active\\\tiny subfilter};
 

### 2020-04-15 samplepaper.tex
COCOON version

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\input{preamble}
%\usepackage{times}
\usepackage[moderate]{savetrees}
\usepackage{multicol}

\usepackage{graphicx}

% Several figures with different labels
\usepackage{float}
\restylefloat*{figure}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Approaching Optimal Duplicate Detection in a Sliding Window}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Rémi Géraud--Stewart\inst{1} \and
Marius Lombard-Platet\inst{1,2} \and
David Naccache\inst{1}}
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University, Paris, France \and
Be-ys Research Lab, Clermont-Ferrand, France\\
\email{\{first\}.\{last\}@ens.fr}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Duplicate detection is the problem of identifying whether a given item has previously appeared in a (possibly infinite) stream of data, when only a limited amount of memory is available.

%Building on the Bloom filter \cite{bloom_spacetime_1970}, an early data structure amenable to duplicate detection, several generalizations and variants were proposed that reduce error rates while maintaining constant memory.

Unfortunately the infinite stream setting is ill-posed, and error rates of duplicate detection filters turn out to be heavily constrained.%: as a consequence they appear to provide no advantage, asymptotically, over a biased coin toss \cite{10.1145/3297280.3297335}.

%Both as a better-behaved setting and as a construction technique, a
%\emph{windowed} variant of the duplicate detection problem was 
%introduced in \cite{She08,Yoo10} which consists in finding duplicate 
%entries amongst the last $w$ elements of the stream for a fixed integer $w$.

In this paper we formalize the sliding window setting introduced by  \cite{She08,Yoo10}, and show that a perfect (zero error) solution can be used up to a maximal window size $w_\text{max}$. Above this threshold we show that some existing duplicate detection filters (designed for the \emph{non-windowed} setting) perform better that those targeting the windowed problem. Finally, we introduce a \enquote{queuing construction} that improves on the performance of some duplicate detection filters in the windowed setting.

We also analyse the security of our filters in an adversarial setting. 
\keywords{TODO}
\end{abstract}
%
%
%
\input{article_content}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
 \bibliographystyle{splncs04}
\bibliography{bibli_short}
%\bibliography{qhtv2}

\appendix
\input{appendix}

\end{document}

### 2020-04-15 appendix.tex
fixes

@@
 
+\section{Compact Hash Short Filter}\label{app:CSHF}
+Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
+The CSHF performs in linear time in $w$, and is a simple queue, the only point is that instead of storing $e$, one stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.
+
+%\begin{algorithm}[!h]
+%	\caption{CSHF, Setup, Lookup and Insert}\label{alg:CSHF}
+%	
+%	\begin{algorithmic}[1]
+%		\Function{Setup}{$\mathcal M, w$}
+%		\Comment $M$ is the available memory, $w$ the size of the sliding window
+%		\State $h \gets$ hash function of codomain size $\lfloor \frac Mw \rfloor$
+%		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
+%		\State\Return filter
+%		\EndFunction 
+%		\item[]
+%	\end{algorithmic}
+%	
+%	\begin{algorithmic}[1]
+%		\Function{Lookup}{$e$}
+%		\State \Return $h(e) \in Q$ 
+%		\EndFunction
+%		\item[]
+%	\end{algorithmic}
+%	
+%	\begin{algorithmic}[1]
+%		\Function{Insert}{$e$}
+%		\State $Q.\mathsf{Push\_Front}(h(e))$
+%		
+%		\If{$Q.\mathsf{length}() > w$}
+%			\State $h' \gets Q.\mathsf{Pop\_back}()$
+%		\EndIf
+%		\EndFunction
+%	\end{algorithmic}
+%\end{algorithm}
+
+\paragraph{Error Rate.}
+Let $w> 0$ be a window size and $M > 0$ the available memory.
+
+%We write $\FN^w_\text{SHF}$ the probability of false negative of an SHF with these parameters. We similarly define $\FP^w_\text{SHF}$.%, $\FN^w_\text{CSHF}$, $\FP^w_\text{CSHF}$.
+
+\begin{restatable}{thm}{fprSHF}\label{thm:fprCHF}	
+	$\FN_\text{CSHF}^w  = 0$  and $\FP_\text{CSHF}^w = 1 - \left(1 - 2^{-M/w}\right)^w$
+\end{restatable}
+
+\begin{proof}
+	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. A CSHF has fingerprints of size $h' = \frac Mw$.
+\end{proof}
+
+\paragraph{Remark:} A CSHF of size $M$ has the same error rate than an SHF of size $2M + w\log_2 w$.
+
+\paragraph{Saturation.}
+Simlarly to SHF, CSHF saturates quickly over a certain $w_\text{max}$. We compare SHF and CSHF saturations in Figure~\ref{fig:app_shorts}.
+
+\begin{figure}[t]
+		\centering
+		\input{graphs/bench_shorts_both.tex}
+		\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:app_shorts}
+\end{figure}
+
+Experimentally, we get $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$).
+
 \section{Proofs}\label{app:proofs}
@@
 	we discard the oldest element $e_\text{last}$ in $Q$.
-As we do so, we also decrement $D[e_\text{last}]$, and if $D[e_{last}] = 0$ the key is deleted from $D$.
+As we do so, we also decrement $D[e_\text{last}]$, and if $D[e_{\text{last}}] = 0$ the key is deleted from $D$.
 The whole insertion procedure is therefore performed in constant time.
@@
 
-	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
+	The queue  size is $w\log_2 |\Gamma|$, the dictionary size is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
 Thus a requirement of $w (\log_2(w) + 2\log_2(|\Gamma|))$ bits for this DDF to work.
@@
 	\begin{align*}
-		\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
-		& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
-		\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
+		\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)
+		 = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) \\
+		\FN_n &=  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p)
+			=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
 	\end{align*}
@@
 	\begin{align*}
-		E_n 
+		EP_n 
 		& = \FN_n + p
@@
 
-	Each subfilter has undergone $c$ insertions, safe for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
+	Each subfilter has undergone $c$ insertions, except for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
 \qed\end{proof}
@@
 	p_c 
-	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
-	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
-	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
+	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]
+	 = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
+	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}
 %		\end{align*}\begin{align*}p_c
-	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
-	& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
+	 = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
+	p_c& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
 \end{align*}
@@
 	If $cL \leq w$, then information-theoretically the subfilters only have information on elements in the sliding window.
-	The probability of false positive for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$, which is strictly increasing with $\FP_{\mathcal F,c}$.
-Hence, the optimal solution is reached by to maximising the probability of false positive in each subfilter $\mathcal F_i$.
+	The false positive probability for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$, which is strictly increasing with $\FP_{\mathcal F,c}$.
+Hence, the optimal solution is reached by to maximising the false positive probability in each subfilter $\mathcal F_i$.
 By hypothesis the latter is bounded above by $p$ after $c$ insertions.
 
-	On the other hand, if $cL > w$ then oldest filter holds information about elements that are not in the sliding window anymore.
+	On the other hand, if $cL > w$ then the oldest filter holds information about elements that are not in the sliding window anymore.
 Hence, a strategy for the attacker trying to trigger a false positive on $e^\star$ could be to make it so these oldest elements are all equal to $e^\star$.
@@
 
-	After $w$ insertions, the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ probability of success.
+	After $w$ insertions, the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ success probability.
 If, for some reason, the last subfilter answers $\DUPLICATE$ with probability less than $p$, then the same reasoning as for when $cL \leq w$ still applies, hence we get the correspondig lower bound (which is, in this case, an equality).
@@
 	For this, let us consider the adversarial game against the subfilter $\mathcal F$: after $c$ insertions from an aversarial stream $E_c$, $\mathcal A$ choses a duplicate $e^\star$ which will be a false negative with proability $p$.
-	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c \mid E_c \mid \cdots \mid E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a probability of success for $\mathcal A$ of $p^L$.
+	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c \mid E_c \mid \cdots \mid E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a success probability for $\mathcal A$ of $p^L$.
 
@@
 In this case, at any time, $\mathcal Q$ remembers all elements from inside the sliding window.
-As we have seen in the previous example, the probability of success of $\mathcal A$ is strictly increasing with the probability of each subfilter to answer $\UNSEEN$.
+As we have seen in the previous example, the success probability of $\mathcal A$ is strictly increasing with the probability of each subfilter to answer $\UNSEEN$.
 The probability of a subfilter to answer $\UNSEEN$ is:

### 2020-04-15 article_content.tex
fixes

@@
 \subsection{Contributions}
-In this paper, we start from a naïve solution for the wDDP to then derive bounds for when it can be solved within $M$ bits of memory, up to a window size $w_\text{max}$, in constant time.
+In this paper, we start from a naïve solution for the wDDP to then derive bounds for when it can be solved within $M$ memory bits, up to a window size $w_\text{max}$, in constant time.
 We then introduce a generalization of the naïve solution, and study its error rate.
@@
 
-For a filter, the probability of false positive ($\FP^w_i$) is the probability that after $i$ insertions, the \emph{unseen} element $e_i\notwdup E$ is a false positive over $w$.
+For a filter, the false positive probability ($\FP^w_i$) is the probability that after $i$ insertions, the \emph{unseen} element $e_i\notwdup E$ is a false positive over $w$.
 The false positive rate $\FPR^w_i$ is the number of false positives divided by the number of unseen elements in E\footnote{We observe that $\FPR^w_n = \frac{1}{n}\sum_{i=1}^n \FP^w_i$, and similarly for $\FNR^w_n$.}.
@@
 \begin{restatable}{thm}{shf}\label{thm:SHF}
-	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the wDDP can be solved with almost no error using $M$ bits of memory.
+	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the wDDP can be solved with almost no error using $M$ memory bits.
 
@@
 \end{restatable}
-Note that we only consider the probability of false positive after the filter has inserted at least $w$ elements, i.e., once the filter is full and has reached a stationary regime.
+Note that we only consider the false positive probability after the filter has inserted at least $w$ elements, i.e., once the filter is full and has reached a stationary regime.
 
@@
 The approximate filter we described uses hashes of size $2\log_2(w)$ for a given sliding window $w$.
-However, this hash size is arbitrary, and while it guarantees a very low error rate, it can be changed.
+However, this hash size is arbitrary, and while the current hash size guarantees a very low error rate, it can be changed.
 More importantly, in some practical cases the maximal amount of available memory is fixed beforehand.
@@
 This gives us the Short Hash Filter (SHF), described in Algorithm~\ref{alg:SHF}.
-The implementation relies on a double-ended queue or a ring buffer, which allows pushing at beggining of a queue and popping at the end in constant time.
+The implementation relies on a double-ended queue or a ring buffer, which allows pushing at beginning of a queue and popping at the end in constant time.
+A variant is described in Appendix~\ref{app:CSHF}.
 
 \begin{algorithm}
-	\caption{SHF Setup, Lookup and Insert}\label{alg:SHF}
+	\caption{SHF \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:SHF}
 
@@
 	\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h \Rightarrow$  counter (of max value $w$)
-
-%	\State\Return filter
 	\EndFunction 
@@
 	\begin{multicols}{2}
-	\begin{algorithmic}[1]
-	\item[]
-	\item[]
-	\Function{Lookup}{$e$}
-	\If{$D[h(e)] > 0$}
-	\State \Return \DUPLICATE
-	\EndIf
-	\State \Return \UNSEEN
-	\EndFunction
-	\item[]
-	\item[]
-\end{algorithmic}
-
 	\begin{algorithmic}[1]
@@
 	\end{algorithmic}
+
+	\begin{algorithmic}[1]
+	\item[]
+	\Function{Lookup}{$e$}
+	\If{$D[h(e)] > 0$}
+	\State \Return \DUPLICATE
+	\Else
+	\State \Return \UNSEEN
+	\EndIf
+	\EndFunction
+	\item[]
+\end{algorithmic}
+
 	\end{multicols}
@@
 \paragraph{Saturation.}
-SHF and have strictly increasing error rates, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
+SHF has strictly increasing error rates, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
 Beyond this value, these filters saturate extremely quickly: in other words, most SHF will either have an error rate of $0$ or $1$.
@@
 	\input{graphs/bench_shorts.tex}
-	\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:shorts}
+	\caption{Error rates of SHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:shorts}
 \end{minipage}
@@
 \begin{restatable}{thm}{asymptoticSaturation}\label{thm:asymptoticSaturation}
-	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $E_n = \FP_n + \FN_n$ satisfies
+	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $EP_n = \FP_n + \FN_n$ satisfies
 $
-	E_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
+	EP_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
 $
@@
 $
-	E_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|.
+	EP_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|.
 $
@@
 \begin{itemize}
-	\item QHT \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint.
-	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$
-	\item Cuckoo Filter \cite{Fan14}, cells containing 1 element of 3 bits each
-	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02
+	\item QHT \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint;
+	\item SQF \cite{Dut13}, 1 bucket per row, $r = 2$ and $r' = 1$;
+	\item Cuckoo Filter \cite{Fan14}, cells containing 1 element of 3 bits each;
+	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02.
 %	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
@@
 	\input{fig/queuef.tex}
-	\caption{Architecture of the queuing filter.
-The filter is composed of $L$ subfilters $\mathcal F$, each containing up to $c$ elements.
-Once the newest subfilter has inserted $c$ elements in its structure, the oldest one is expired.
-As such, it is dropped and a new one is created and put under population at the beginning of the queue.
+	\caption{Architecture of the queuing filter, which consists of $L$ subfilters $\mathcal F_i$, each containing up to $c$ elements.
+Once the newest subfilter has inserted $c$ elements in its structure, the oldest one expires.
+As such, the latter is dropped and a new one is created and put under population at the beginning of the queue.
 In this example, the sub-sliding window of $\mathcal F_1$ is $(e_{m-2}, e_{m-3}, e_{m-4})$.} \label{fig:scheme}
@@
 Rather than allocating the whole memory to $\mathcal F$, we will create $L$ copies of $\mathcal F$, each using a fraction of the available memory.
-Each of these \emph{subfilters} as a limited timespan, and is allowed up to $c$ insertions.
+Each of these \emph{subfilters} has a limited timespan, and is allowed up to $c$ insertions.
 The subfilters are organised in a queue.
@@
 \begin{algorithm}[]
-	\caption{Queuing Filter Setup, Lookup and Insert}\label{alg:queuing}
+	\caption{Queuing Filter \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:queuing}
 
@@
 		\State subfilters[0]$.\mathsf{Insert}(e)$
-		\State counter $\gets$ counter + 1 
+		\State counter$++$
 		\If{counter == $c$}
@@
 
-\subsubsection{Probability of False Positive}
+\subsubsection{False Positive Probability}
 
@@
 	\label{thm:queue-pfp}
-	 Let $\FP_{\mathcal Q, m}^w$ be the probability of false positive %(def. \ref{def:pfp-pfn})
+	 Let $\FP_{\mathcal Q, m}^w$ be the false positive probability%(def. \ref{def:pfp-pfn})
 	 of $\mathcal Q$ after $m > w$ insertions, over a sliding window of size $w = cL$, we have \\
@@
 	$$ %\end{equation}
-	where $\bmod$ is the modulo operator and 
-	 $\FP_{\mathcal F,m}$ is the probability of false positive of a subfilter $\mathcal F$ after $m$ insertions.
+	where %$\bmod$ is the modulo operator and 
+	 $\FP_{\mathcal F,m}$ is the false positive probability of a subfilter $\mathcal F$ after $m$ insertions.
 \end{restatable}
@@
 %	
-%	Each subfilter has undergone $c$ insertions, safe for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
+%	Each subfilter has undergone $c$ insertions, except for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
 %\end{proof}
@@
 
-\subsubsection{Probability of False Negative}\label{sub:fnr}
+\subsubsection{False Negative Probability}\label{sub:fnr}
 \begin{restatable}{thm}{pfnQueue}
 	\label{thm:queue-pfn}
-	Let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
+	Let $\FN_{\mathcal Q, m}^w$ be the false negative probability of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
 	$$%\begin{equation}
@@
 	$$%\end{equation}
-	where $\bmod$ is the modulo operator, and we have introduced the short-hand notation $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$ where 
-	$\FN_{\mathcal F,\eta}$ (resp. $\FP_{\mathcal F, \eta}$) is the probability of false negative (resp. false positive) of the subfilter $\mathcal F$ after $\eta$ insertions, and
+	where %$\bmod$ is the modulo operator, and
+	we have introduced the short-hand notation $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$ where 
+	$\FN_{\mathcal F,\eta}$ (resp. $\FP_{\mathcal F, \eta}$) is the false negative probability (resp. false positive) of the subfilter $\mathcal F$ after $\eta$ insertions, and
 	$%\begin{equation*}
@@
 
-A very interesting observation is that $Lw$ approaches the size of the stream, there is a drop in the error.
+A surprising observation is that when $Lw$ approaches the size of the stream, there is a drop in the error.
 This is an artifact due to the finite size of our simulations; the stream should be considered infinite, and this drop disappears as the simulation is run for longer (see Appendix~\ref{app:finite}).
@@
 The number of subfilters $L$ is an important parameter in the queuing construction, as it affects the filter's error rate in a nontrivial way.
-An illustration of this dependence is shown in Figure~\ref{fig:bench_l} which plots the error rate of a queueing QQHTD on an uniform stream of alphabet size $\Gamma = 2^{16}$, with $10^5$ elements in the stream, on various sliding window sizes.
+An illustration of this dependence is shown in Figure~\ref{fig:bench_l} which plots the error rate of a queueing QHT on an uniform stream of alphabet size $\Gamma = 2^{16}$, with $10^5$ elements in the stream, on various sliding window sizes.
 
@@
 
-In order to create a realistic adversary model, we assume like in \cite{DBLP:journals/corr/abs-1709-08920} that the adversary does not have access to the internal memory representation of the filter.
+To create a realistic adversary model, we assume like in \cite{DBLP:journals/corr/abs-1709-08920} that the adversary does not have access to the filter's internal memory.
 Nonetheless, after every insertion she knows whether the inserted element was detected as a duplicate or not.
@@
 \begin{itemize}
-	\item In the first part, $\mathcal A$ can feed up to $n$ elements to $\mathcal Q$ and learn $\mathcal Q$'s response for each insertion.
+	\item In the first part, $\mathcal A$ can feed up to $n$ elements to $\mathcal Q$ and learns $\mathcal Q$'s response for each insertion.
 	\item In the second part, $\mathcal A$ sends a unique element $e^\star$.
@@
 \begin{definition}[Adversarial False Positive Resistance]
-	We say that a DDF $\mathcal F$ is $(p, n)$-\emph{resistant to adversarial false positives} if no polynomial-time probabilistic (PPT) adversary $\mathcal A$ can win the $n-$false positive adversarial game with probability more than $p$.
+	We say that a DDF $\mathcal F$ is $(p, n)$-\emph{resistant to adversarial false positives} if no polynomial-time probabilistic (PPT) adversary $\mathcal A$ can win the $n-$false positive adversarial game with probability greater than $p$.
 \end{definition}
@@
 
-	If $cL > w$, the adversary has a probability of success of at least $1-(1-p)^L$.
+	If $cL > w$, the adversary has a success probability of at least $1-(1-p)^L$.
 \end{restatable}
@@
 
-	Furthermore, for $q$ the lower bound on the probability of false positive $\FP_{\mathcal F,c}$ for a given stream, if $w \leq (L-1)c$ then $\mathcal Q$ is $(\min(1 - q, p)^{L-1}p, w)$-resistant to false negative attacks on the sliding window $w$.
+	Furthermore, for $q$ the lower bound on the false positive probability $\FP_{\mathcal F,c}$ for a given stream, if $w \leq (L-1)c$ then $\mathcal Q$ is $(\min(1 - q, p)^{L-1}p, w)$-resistant to false negative attacks on the sliding window $w$.
 	On the other hand if $w > (L-1)c$ then $\mathcal Q$ is  $(\max(1 - q, p)^{L}, w)$-resistant to false negative attacks on the sliding window $w$.

### 2020-04-15 samplepaper.tex
fixes

@@
 
-Unfortunately the infinite stream setting is ill-posed, and error rates of duplicate detection filters turn out to be heavily constrained.%: as a consequence they appear to provide no advantage, asymptotically, over a biased coin toss \cite{10.1145/3297280.3297335}.
+Unfortunately the infinite stream setting is ill-posed, and error rates of duplicate detection filters turn out to be heavily constrained: consequently they appear to provide no advantage, asymptotically, over a biased coin toss \cite{10.1145/3297280.3297335}.
 
@@
 %introduced in \cite{She08,Yoo10} which consists in finding duplicate 
-%entries amongst the last $w$ elements of the stream for a fixed integer $w$.
+%entries amongst the last $w$ e	lements of the stream for a fixed integer $w$.
 

### 2020-05-09 appendix.tex
Arxiv version from COCOON

--- 2020-04-15 appendix.tex
@@
 \begin{figure}[t]
-\makebox[\textwidth]{\makebox[1.05\textwidth]{%
-	\begin{minipage}{.5\textwidth}
+%\makebox[\textwidth]{\makebox[1.05\textwidth]{%
+%	\begin{minipage}{.5\textwidth}
 	\centering
@@
 		\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
-	\end{minipage}
-\hfill
-	\begin{minipage}{.5\textwidth}
+%	\end{minipage}
+%\hfill
+\end{figure}
+
+As can be seen on this simulation, there is only disagreement around $w \approx N/L$, and increasing $N$ results in a later and smaller peak.
+
+It is also possible to run simulations for different alphabet sizes $\Gamma$, which shows that the peak's position increases with $|\Gamma|$, although the relationship is not obvious to quantify.
+
+\section{Filters vs queued filters (complement)}\label{app:improvement}
+We here run a comparison of the Cuckoo Filter relative to the Queueing Cuckoo Filter, as well as the SBF relatively to the queueing SBF. The results are given in Figure~\ref{fig:appendix_improvement}.
+
+\begin{figure}[t]
 	\centering
@@
 		\begin{semilogxaxis}[
-			width=\textwidth,
 			legend cell align = left,%
@@
 		\addlegendentry{SBF};
-
-		%\addplot[mark=x,^8$}
 		\end{semilogxaxis}
@@
 	\caption{Comparing performances of the Cuckoo and SBF filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
-	\end{minipage}
-}}
+
 \end{figure}
-
-As can be seen on this simulation, there is only disagreement around $w \approx N/L$, and increasing $N$ results in a later and smaller peak.
-
-It is also possible to run simulations for different alphabet sizes $\Gamma$, which shows that the peak's position increases with $|\Gamma|$, although the relationship is not obvious to quantify.
-
-\section{Filters vs queued filters (complement)}\label{app:improvement}
-We here run a comparison of the Cuckoo Filter relative to the Queueing Cuckoo Filter, as well as the SBF relatively to the queueing SBF. The results are given in Figure~\ref{fig:appendix_improvement}.
-
-\section{Proofs}\label{app:proofs}
-In this appendix, we give the proofs of all theorems stated in the paper. For the sake of convenience, each theorem is restated before giving its proof.
-
-\optwddf*
-
-\begin{proof}
-	We explicitly construct a DDF that performs the detection. Storing all $w$ elements in the sliding window takes $w\log_2(|\Gamma|)$ memory, using a FIFO queue $Q$; however 
-	lookup has a worst-time complexity of $O(w)$.
-
-	We therefore rely on an
-	ancillary data structure for the sake of quickly answering lookup questions.
-	Namely we use a dictionary $D$ whose keys are elements from $\Gamma$ and values are counters.
-
-	When an element $e$ is inserted in the DDF, $e$ is stored and $D[e]$ is incremented (if the key $e$ did not exist in $D$, it is created first, and
-	$D[e]$ is set to $1$). In order to keep the number of stored elements to $w$, 
-	we discard the oldest element $e_\text{last}$ in $Q$.
-As we do so, we also decrement $D[e_\text{last}]$, and if $D[e_{last}] = 0$ the key is deleted from $D$.
-The whole insertion procedure is therefore performed in constant time.
-
-	Lookup of an element $e^\star$ is simply done by looking whether the key $D[e^\star]$ exists, which is done in constant time.
-
-	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
-Thus a requirement of $w (\log_2(w) + 2\log_2(|\Gamma|))$ bits for this DDF to work.
-
-	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element is present in the sliding window.
-\qed\end{proof}
-
-\shf*
-\begin{proof}
-	Here again we explicitly construct the filters that attain the theorem's bounds.
-
-	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
-The birthday theorem \cite{10.1007/3-540-45708-9_19} states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
-Therefore $2^{(2 \log_2 w) / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
-$h(e_i) = h(e_j)$).
-The 50\% threshold we impose on $h$ is arbitrary but nonetheless practical.
-
-Let $\mathcal F$ be the following DDF: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
-$\mathsf{Insert}(e)$ appends $h(e)$ to the queue before popping the queue.
-
-There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FN of $0$ and a FP of $1 - (1-\frac1{w^2})^w$.
-The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
-
-Note that this solution has a time complexity of $O(w)$.
-Using an additional dictionary, as in the previous proof, but with keys of size $2\log_2(w)$, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, using $w \cdot 2\log_2 w + w \cdot (2\log_2(w) + \log_2(w)) = 5w\log_2 w$ bits of memory.
-\qed\end{proof}
-
-\fprSHF*
-
-\begin{proof}
-	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}.
-An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$.%, while a CSHF has fingerprints of size $h' = \frac Mw$.
-\qed\end{proof}
-
-\asymptoticSaturation*
-
-\begin{proof}
-	By definition, a perfect filter has the lowest possible error rate.
-	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
-Up to reordering the stream, without loss of generality because it is random, we may assume that the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
-
-	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
-On the other hand, if the element is not in memory, a perfect filter can choose to answer randomly.
-Let $p$ be the probability that a filter answers \DUPLICATE when an element is not in memory.
-An optimal filter will lower the error rate of any filter using the same strategy with a different probability.
-
-	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
-For this reason, this filter has an FP probability of $p$.
-
-	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
-Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
-Then $e^\star$ triggers a false negative with probability
-	\begin{align*}
-		\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
-		& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
-		\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
-	\end{align*}
-	Hence, the error probability of the filter is
-	\begin{align*}
-		E_n 
-		& = \FN_n + p
-		=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p
-		= 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
-	\end{align*}
-	which is minimized when $p = 0$. 
-\qed\end{proof}
-
-\pfpQueue*
-
-\begin{proof}
-	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream and $e^\star \notwdup E$.
-
-	Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
-Conversely, $e^\star$ is \emph{not} a false positive when all subqueries $\mathcal F_i.\mathsf{Lookup(e^\star)}$ return \UNSEEN, i.e., when $e^\star$ is not a false positive for each subfilter.
-
-	Each subfilter has undergone $c$ insertions, safe for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
-\qed\end{proof}
-
-\pfnQueue*
-
-\begin{proof}
-	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
-
-	Then $e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$. There can be two cases:
-	\begin{itemize}
-		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window;
-		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window.
-	\end{itemize}
-In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
-This happens with probability $\FN_{\mathcal F,c}$ by definition, except for $\mathcal F_0$, for which the probability is $\FN_{\mathcal F, m\bmod c}$.
-
-In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$, which happens with probability $1-\FP_{\mathcal F,c}$, execpt for $\mathcal F_0$, for which the probability is $1-\FP_{\mathcal F, m\bmod c}$.
-
-Finally, each event is weighted by the probability $p_c$ that $e^\star$ is in $\mathcal F_i$'s sub-sliding window:
-\begin{align*}
-	p_c 
-	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
-	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
-	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
-%		\end{align*}\begin{align*}p_c
-	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
-	& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
-\end{align*}
-This concludes the proof.
-\qed\end{proof}
-
-\fprQueue*
-
-\begin{proof}
-
-\begin{align*}
-	\FPR_{\mathcal Q, cn}^w
-	& = \frac{1}{cn} \sum_{k=1}^{cn} \FP_{\mathcal Q, k}^w 
-	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, k + \ell}^w 
-	 = \frac1c \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, \ell}^w \\
-	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
-	& = 1 - \frac1c(1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
-\end{align*}
-\qed\end{proof}
-
-\fnrQueue*
-
-\begin{proof}
-\begin{align*}
-	\FNR_{\mathcal Q, cn}^w 
-	& = \frac{1}{cn} \sum_{k=1}^{cn} \FN_{\mathcal Q, k}^w 
-	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, k + \ell}^w 
-	= \frac1c \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, \ell}^w \\
-	& = \frac1c \sum_{\ell = 0}^{c-1} u_c^{L-1} u_{\ell} 
-	 = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
-\end{align*}
-\qed\end{proof}
-
-\fprRes*
-
-\begin{proof}
-	If $cL \leq w$, then information-theoretically the subfilters only have information on elements in the sliding window.
-	The probability of false positive for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$, which is strictly increasing with $\FP_{\mathcal F,c}$.
-Hence, the optimal solution is reached by to maximising the probability of false positive in each subfilter $\mathcal F_i$.
-By hypothesis the latter is bounded above by $p$ after $c$ insertions.
-
-	On the other hand, if $cL > w$ then oldest filter holds information about elements that are not in the sliding window anymore.
-Hence, a strategy for the attacker trying to trigger a false positive on $e^\star$ could be to make it so these oldest elements are all equal to $e^\star$.
-Let $E$ be the optimal adversarial stream for triggering a false positive on the sliding window $w$ with the element $e^\star$, when $cL \leq w$.
-The adversary $\mathcal A$ can create a new stream $E' = e^\star | e^\star | \dotsc | E$ where $e^\star$ is prepended $cL - w$ times to $E$.
-
-	After $w$ insertions, the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ probability of success.
-If, for some reason, the last subfilter answers $\DUPLICATE$ with probability less than $p$, then the same reasoning as for when $cL \leq w$ still applies, hence we get the correspondig lower bound (which is, in this case, an equality).
-\qed\end{proof}
-
-\fnrRes*
-
-\begin{proof}
-	Let us first prove that a PPT adversary $\mathcal A$ can win the game with probability at least $p^L$.
-	For this, let us consider the adversarial game against the subfilter $\mathcal F$: after $c$ insertions from an aversarial stream $E_c$, $\mathcal A$ choses a duplicate $e^\star$ which will be a false negative with proability $p$.
-	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c \mid E_c \mid \cdots \mid E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a probability of success for $\mathcal A$ of $p^L$.
-
-	Now, Let us prove the case where $w\leq (L-1)c$.
-In this case, at any time, $\mathcal Q$ remembers all elements from inside the sliding window.
-As we have seen in the previous example, the probability of success of $\mathcal A$ is strictly increasing with the probability of each subfilter to answer $\UNSEEN$.
-The probability of a subfilter to answer $\UNSEEN$ is:
-
-	\begin{itemize}
-		\item $\FN'_{\mathcal F,c}$ if $e^\star$ is in the subfilter's sub-sliding window;
-		\item $1 - \FP'_{\mathcal F, c}$ if $e^\star$ is not in the subfilter's sub-sliding window
-	\end{itemize}
-	where $\FN'$ and $\FP'$ are the probabilities of false negative and positives on the adversarial stream (which may be different from a random uniform stream).
-
-	However, since $e^\star$ is a duplicate, it is in at least one subfilter's sub-sliding window.
-As such, the optimal strategy for $\mathcal A$ is to maximise the probability of all subfilters to answer $\UNSEEN$.
-	Now, $\FN'_{\mathcal F,c}$ is bounded above by $p$ and $1 - \FP'_{\mathcal F, c}$ is bounded above by $1-q$, so the best strategy is where as many filters as possible answer $\UNSEEN$ with probability $\max(p, 1-q)$, knowing that at least one filter must contain $e^\star$ and as such its probability for returning $\UNSEEN$ is at most $p$, hence the result.
-
-	Now, let us consider the case when $w > (L-1)c$.
-We have already introduce the element $e^\star$ in the last $w$ elements, and we want to insert it again.
-It is possible, for the adversary, to create the following stream $E = (e_1, e_2, \dotsc, e_{c-1}, e^\star, e_{c+1}, \dotsc, e_{Lc}, e_{Lc + 1})$, and to insert $e^\star$ afterwards.
-
-	When $e_{Lc+1}$ is inserted, all elements $(e_1, \dotsc, e_{c-1}, e^\star)$ are dropped as the oldest subfilter is popped.
-Hence, in this context $e^\star$ is not in any subfilter anymore, so by adapting the previous analysis, $\mathcal A$ can get a false negative with probability at most $\max(1 - q, p)^{L}$.
-\qed
-\end{proof}
+%\section{Compact Hash Short Filter}\label{app:CSHF}
+%Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
+The CSHF performs in linear time in $w$, and is a simple double-ended queue, the only point is that instead of storing $e$, the filter stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.
+%
+%%\begin{algorithm}[!h]
+%%	\caption{CSHF, Setup, Lookup and Insert}\label{alg:CSHF}
+%%	
+%%	\begin{algorithmic}[1]
+%%		\Function{Setup}{$\mathcal M, w$}
+%%		\Comment $M$ is the available memory, $w$ the size of the sliding window
+%%		\State $h \gets$ hash function of codomain size $\lfloor \frac Mw \rfloor$
+%%		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
+%%		\State\Return filter
+%%		\EndFunction 
+%%		\item[]
+%%	\end{algorithmic}
+%%	
+%%	\begin{algorithmic}[1]
+%%		\Function{Lookup}{$e$}
+%%		\State \Return $h(e) \in Q$ 
+%%		\EndFunction
+%%		\item[]
+%%	\end{algorithmic}
+%%	
+%%	\begin{algorithmic}[1]
+%%		\Function{Insert}{$e$}
+%%		\State $Q.\mathsf{Push\_Front}(h(e))$
+%%		
+%%		\If{$Q.\mathsf{length}() > w$}
+%%			\State $h' \gets Q.\mathsf{Pop\_back}()$
+%%		\EndIf
+%%		\EndFunction
+%%	\end{algorithmic}
+%%\end{algorithm}
+%
+%\paragraph{Error Rate.}
+%Let $w> 0$ be a window size and $M > 0$ the available memory.
+%
+%%We write $\FN^w_\text{SHF}$ the probability of false negative of an SHF with these parameters. We similarly define $\FP^w_\text{SHF}$.%, $\FN^w_\text{CSHF}$, $\FP^w_\text{CSHF}$. 
+%
+%\begin{restatable}{thm}{fprCHF}\label{thm:fprCHF}	
+%	$\FN_\text{CSHF}^w  = 0$  and $\FP_\text{CSHF}^w = 1 - \left(1 - 2^{-M/w}\right)^w$
+%\end{restatable}
+%
+%\begin{proof}
+%	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. A CSHF has fingerprints of size $h' = \frac Mw$.
+%\end{proof}
+%
+%\paragraph{Remark:} A CSHF of size $M$ on a sliding window $w$ has the same error rate than an SHF of sliding window of size $2M + w\log_2 w$.
+%
+%\paragraph{Saturation.}
+%Simlarly to SHF, CSHF saturates quickly over a certain $w_\text{max}$. We compare SHF and CSHF saturations in Figure~\ref{fig:app_shorts}.
+%
+%
+%\begin{figure}[t]
+%		\centering
+%		\input{graphs/bench_shorts_both.tex}
+%		\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:app_shorts}
+%\end{figure}
+%
+%Experimentally, we get $w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$).

### 2020-05-09 article_content.tex
Arxiv version from COCOON

@@
 Approximate duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures.
-Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.
+Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753} and others.
+Please note that approximate detection is a different problem than detection of approximate duplicates \cite{Monge97anefficient}, in which the goal is to find elements similar but not necessarily equal to the target.
 
@@
 We show that this construction, which we call Short Hash Filter (SHF), can push the value $w_\text{max}$ further while operating in constant time --- at the cost of some errors.
-%We also provide a different tradeoff, the Compact Short Hash Filter (CSHF), which uses fewer memory but operates in linear time.
+We also provide a different tradeoff, the Compact Short Hash Filter (CSHF), which uses fewer memory but operates in linear time.
 
@@
 \subsection{Related work}\label{sub:related}
-The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}.%; but several variations exist that are incomparable to one another (e.g.
+The notion of sliding window was, as far as we know, first introduced in \cite{10.1145/1060745.1060753}; but several variations exist that are incomparable to one another (e.g.
 \cite{shtul2020agepartitioned}).
@@
 
-%A filter is an algorithm, which has a finite amount of memory $M$ and, for each new element $e$, outputs $\DUPLICATE$ or $\UNSEEN$ whether it thinks $e$ is a duplicate or not.;
+A filter is an algorithm, which has a finite amount of memory $M$ and, for each new element $e$, outputs $\DUPLICATE$ or $\UNSEEN$ whether it thinks $e$ is a duplicate or not.
 
@@
 Otherwise we note $e_i \notwdup E$, and we say $e_i$ is unseen over $w$.
-A false positive over $w$ is an element $e\notwdup E$ which is classified as a duplicate, and a false negative is an element $e\wdup E$ which is classified as a not-duplicate.
+A false positive over $w$ is an element $e\notwdup E$ which is classified as a duplicate, and a false negative is an element $e\wdup E$ which is classified as unseen.
 
@@
 \section{Approximate solution and SHF}
-%\subsection{Optimal wDDF}\label{sub:opt_solutions}
+%\subsection{imal wDDF}\label{sub:opt_solutions}
 %
@@
 %The optimal filter described above requires that the size of $\Gamma$ is known in advance. The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing errors.
-\begin{restatable}{thm}{optwddf}\label{thm:opt_wddf}
+\begin{theorem}\label{thm:opt_wddf}
 	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the wDDP can be solved exactly (with no errors) in constant time.
-\end{restatable}
+\end{theorem}
 
 \begin{proof}
-	Due to page limit restrictions, all theorem proofs' are in Appendix~\ref{app:proofs}.
+	We explicitly construct a DDF that performs the detection. Storing all $w$ elements in the sliding window takes $w\log_2(|\Gamma|)$ memory, using a FIFO queue $Q$; however 
+	lookup has a worst-time complexity of $O(w)$.
+
+	We therefore rely on an
+	ancillary data structure for the sake of quickly answering lookup questions.
+	Namely we use a dictionary $D$ whose keys are elements from $\Gamma$ and values are counters.
+
+	When an element $e$ is inserted in the DDF, $e$ is stored and $D[e]$ is incremented (if the key $e$ did not exist in $D$, it is created first, and
+	$D[e]$ is set to $1$). In order to keep the number of stored elements to $w$, 
+	we discard the oldest element $e_\text{last}$ in $Q$.
+As we do so, we also decrement $D[e_\text{last}]$, and if $D[e_{\text{last}}] = 0$ the key is deleted from $D$.
+The whole insertion procedure is therefore performed in constant time.
+
+	Lookup of an element $e^\star$ is simply done by looking whether the key $D[e^\star]$ exists, which is done in constant time.
+
+	The queue  size is $w\log_2 |\Gamma|$, the dictionary size is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long).
+Thus a requirement of $w (\log_2(w) + 2\log_2(|\Gamma|))$ bits for this DDF to work.
+
+	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element is present in the sliding window.
 	\end{proof}
@@
 
-\begin{restatable}{thm}{shf}\label{thm:SHF}
+\begin{theorem}\label{thm:SHF}
 	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the wDDP can be solved with almost no error using $M$ memory bits.
@@
 	Using $M \simeq 5w\log_2 w$ bits of memory, a constant-time filter with the same error rate can be constructed.
-\end{restatable}
+\end{theorem}
 Note that we only consider the false positive probability after the filter has inserted at least $w$ elements, i.e., once the filter is full and has reached a stationary regime.
 
-%\begin{proof}
-%	Here again we explicitly construct the filters that attain the theorem's bounds.
-%
-%	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
-%The birthday theorem \cite{10.1007/3-540-45708-9_19} states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
+\begin{proof}
+	Here again we explicitly construct the filters that attain the theorem's bounds.
+
+	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
+	The birthday theorem \cite{10.1007/3-540-45708-9_19} states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision.
 Therefore $2^{(2 \log_2 w) / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e.
@@
 The 50\% threshold we impose on $h$ is arbitrary but nonetheless practical.
-%
-%Let $\mathcal F$ be the following DDF: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
+
+	Let $\mathcal F$ be the following DDF: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise.
 $\mathsf{Insert}(e)$ appends $h(e)$ to the queue before popping the queue.
-%
-%There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FN of $0$ and a FP of $1 - (1-\frac1{w^2})^w$.
-%The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
-%
-%Note that this solution has a time complexity of $O(w)$.
+
+	There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FN of $0$ and a FP of $1 - (1-\frac1{w^2})^w$.
+	The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
+
+	Note that this solution has a time complexity of $O(w)$.
 Using an additional dictionary, as in the previous proof, but with keys of size $2\log_2(w)$, we get a filter with an error rate of about $\frac 1w$ and constant time for insertion and lookup, using $w \cdot 2\log_2 w + w \cdot (2\log_2(w) + \log_2(w)) = 5w\log_2 w$ bits of memory.
-%\end{proof}
+	\end{proof}
 
@@
 %\section{Short Hash Filter}
-\subsection{Short Hash Filter Algorithm}
+\subsection{Short Hash Filter and Compact Short Hash Filter Algorithms}
+\paragraph{Short Hash Filter (SHF)}
 The approximate filter we described uses hashes of size $2\log_2(w)$ for a given sliding window $w$.
@@
 The implementation relies on a double-ended queue or a ring buffer, which allows pushing at beginning of a queue and popping at the end in constant time.
-A variant is described in Appendix~\ref{app:CSHF}.
+%A variant is described in Appendix~\ref{app:CSHF}.
 
@@
 
+\paragraph{Compact Short Hash Filter (CSHF)}
 %\subsection{Compact Short Hash Filter}
-%Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
+Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
 The CSHF performs in linear time in $w$, and is a simple queue, the only point is that instead of storing $e$, one stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.
@@
 
-\paragraph{Error Rates.}
+\paragraph{Error Probabilities.}
 Let $w> 0$ be a window size and $M > 0$ the available memory.
 
-%We write $\FN^w_\text{SHF}$ the probability of false negative of an SHF with these parameters. We similarly define $\FP^w_\text{SHF}$.%, $\FN^w_\text{CSHF}$, $\FP^w_\text{CSHF}$.
+We write $\FN^w_\text{SHF}$ the probability of false negative of an SHF with these parameters. We similarly define $\FP^w_\text{SHF}$, $\FN^w_\text{CSHF}$, $\FP^w_\text{CSHF}$.
 
-\begin{restatable}{thm}{fprSHF}\label{thm:fprSHF}	
-	$\FN_\text{SHF}^w  = 0$  and $\FP_\text{SHF}^w = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w$
-\end{restatable}
+\begin{theorem}\label{thm:fprSHF}
+	We have:
+	\begin{itemize}
+		\item $\FN_\text{SHF}^w  = 0$  and $\FP_\text{SHF}^w = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w$
+		\item$\FN_\text{CSHF}^w  = 0$  and $\FP_\text{CSHF}^w = 1 - \left(1 - 2^{-M/w}\right)^w$
+	\end{itemize}	
+\end{theorem}
 
-%\begin{proof}
-%	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$, while a CSHF has fingerprints of size $h' = \frac Mw$.
-%\end{proof}
+\begin{proof}
+	This is an immediate adaptation of the proof from Theorem~\ref{thm:SHF}. An SHF has fingerprints of size $h = \frac M{2w} - \frac 12 \log_2 w$, while a CSHF has fingerprints of size $h' = \frac Mw$.
+\end{proof}
 
-%\paragraph{Remark:} A CSHF of size $M$ has the same error rate than an SHF of size $2M + w\log_2 w$.
+\paragraph{Remark:} A CSHF of size $M$ on a sliding window $w$ has the same error rate than an SHF of sliding window of size $2M + w\log_2 w$.
+
 \paragraph{Saturation.}
-SHF has strictly increasing error rates, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
+SHF has strictly increasing error probabilities, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
 Beyond this value, these filters saturate extremely quickly: in other words, most SHF will either have an error rate of $0$ or $1$.
@@
 \begin{figure}[t]
-\makebox[\textwidth]{\makebox[1.05\textwidth]{%
-\begin{minipage}{.5\textwidth}
 	\centering
-	\input{graphs/bench_shorts.tex}
-	\caption{Error rates of SHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:shorts}
-\end{minipage}
-\hfill
-\begin{minipage}{.5\textwidth}
-	\centering
-	\begin{tikzpicture}
-		\input{graphs/er_n_artificial}
-	\end{tikzpicture}
-	\caption{Error rate (times 100) of DDFs of 1Mb as a function of stream length. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
-\end{minipage}
-}}
+	\input{graphs/bench_shorts_both.tex}
+	\caption{Error rates of SHFs and CSHFs for $M = 10^5$ bits, for varying window sizes $w$.}\label{fig:shorts}
 \end{figure}
@@
 % are given in Figure~\ref{fig:w_opt} and 
-Experiments indicate an approximately linear relationship between $M$ and $w_\text{max}$: %for large values of $M$:
- %$w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and
+Experiments (numerical resolution of $\FP^\text{max} = 1/2$, for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$) indicate an approximately linear relationship between $M$ and $w_\text{max}$: %for large values of $M$:
+$w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and
 $w_\text{max}^\text{SHF} = 0.0233 M + 186$ ($r^2 = 0.9977$).
@@
 
-\begin{restatable}{thm}{asymptoticSaturation}\label{thm:asymptoticSaturation}
+\begin{theorem}\label{thm:asymptoticSaturation}
 	Let $E$ be a stream of $n$ elements uniformly selected from an alphabet of size $|\Gamma|$. For any DDF using $M$ bits of memory, the error probability $EP_n = \FP_n + \FN_n$ satisfies
-$
+$$
 	EP_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
-$
+$$
 	for any $n > M$.
-\end{restatable}
-In particular, the asymptotic error rate $E_\infty$ satisfies 
-$
+\end{theorem}
+In particular, the asymptotic error rate $EP_\infty$ satisfies 
+$$
 	EP_\infty \geq \left(1 - \frac{1}{|\Gamma|}\right)^{M} \approx 1 - M/|\Gamma|.
-$
+$$
 
-%\begin{proof}
-%	By definition, a perfect filter has the lowest possible error rate.
-%	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
-Up to reordering the stream, without loss of generality because it is random, we may assumethat the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
-%	
-%	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
+\begin{proof}
+	By definition, a perfect filter has the lowest possible error rate.
+	With $M$ bits of memory, a perfect filter can store at most $M$ elements in memory \cite[Theorem 2.1]{10.1145/3297280.3297335}.
+Up to reordering the stream, without loss of generality because it is random, we may assume that the filter stores the $M$ last elements of the stream: any other strategy cannot yield a strictly lower error rate.
+
+	If an element is already stored in the filter, then the optimal filter will necessarily answer \DUPLICATE.
 On the other hand, if the element is not in memory, a perfect filter can choose to answer randomly.
@@
 An optimal filter will lower the error rate of any filter using the same strategy with a different probability.
-%	
-%	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
+
+	An unseen element, by definition, will be unseen in the $M$ last elements of the stream, and hence will not be in the filter's memory, so the filter will return \UNSEEN with probability $1-p$.
 For this reason, this filter has an FP probability of $p$.
-%	
-%	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
+
+	On the other hand, a duplicate $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
 Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
 Then $e^\star$ triggers a false negative with probability
-%	\begin{align*}
-%		\FN_n &= (1 - \Pr[C | D])(1-p) =  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
-%		& = \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) =  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p) \\
-%		\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
-%	\end{align*}
-%	Hence, the error probability of the filter is
-%	\begin{align*}
-%		E_n 
-%		& = \FN_n + p
-%		=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p \\
-%		& = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
-%	\end{align*}
-%	which is minimized when $p = 0$. 
-%\end{proof}
+	\begin{align*}
+	\FN_n &= (1 - \Pr[C | D])(1-p) \\ &=  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
+	&= \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) \\
+	&=  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p)\\
+	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
+	\end{align*}
+	Hence, the error probability of the filter is
+	\begin{align*}
+	EP_n 
+	& = \FN_n + p \\
+	&=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p\\
+	EP_n & = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
+	\end{align*}
+	which is minimized when $p = 0$. 
+	\end{proof}
 
@@
 
+\begin{figure}[t]
+	\centering
+	\begin{tikzpicture}
+		\input{graphs/er_n_artificial}
+	\end{tikzpicture}
+	\caption{Error rate (times 100) of DDFs of 1Mb as a function of stream length. Hatched area represents over-optimal (impossible) values.}\label{fig:graph_n}
+\end{figure}
+
 The best results are given by the following filters, in order: QHT, SQF, Cuckoo and SBF.
@@
 \begin{itemize}
-	\item block decaying Bloom Filter\footnote{Note that by design, a b\_DBF of $10^5$ bits cannot be built over a sliding window bigger than $6000$.} (b\_DBF) \cite{She08}, sliding window of size $w$
+	\item block decaying Bloom Filter\footnote{Note that by design, a b\_DBF of $10^5$ bits cannot operate for $w > 6000$.} (b\_DBF) \cite{She08}, sliding window of size $w$
 	\item A2 filter \cite{Yoo10}, changing subfilter every $w/2$ insertions
-	\item QHT \cite{10.1145/1060745.1060753}, 1 bucket per row, $3$ bits per fingerprint
+	\item QHT \cite{10.1145/3297280.3297335}, 1 bucket per row, $3$ bits per fingerprint
 \end{itemize}
@@
 \begin{figure}[t]
-\makebox[\textwidth]{\makebox[1.25\textwidth]{%
-	\begin{minipage}{.5\textwidth}
+%\makebox[\textwidth]{\makebox[1.25\textwidth]{%
+%	\begin{minipage}{.5\textwidth}
 	\centering
@@
 	\label{fig:nwddf-in-wddp}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{.7\textwidth}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}{.7\textwidth}
+%	\centering
+%	\input{fig/queuef.tex}
+%	\caption{Architecture of the queuing filter, which consists of $L$ subfilters $\mathcal F_i$, each containing up to $c$ elements.
+Once the newest subfilter has inserted $c$ elements in its structure, the oldest one expires.
+As such, the latter is dropped and a new one is created and put under population at the beginning of the queue.
+In this example, the sub-sliding window of $\mathcal F_1$ is $(e_{m-2}, e_{m-3}, e_{m-4})$.} \label{fig:scheme}
+%	\end{minipage}
+%}}
+\end{figure}
+
+\section{Queuing filters}\label{sec:queue}
+We now describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
+A scheme describing our structure is detailed in Figure~\ref{fig:scheme}.
+
+\begin{figure}[t]
 	\centering
@@
 In this example, the sub-sliding window of $\mathcal F_1$ is $(e_{m-2}, e_{m-3}, e_{m-4})$.} \label{fig:scheme}
-	\end{minipage}
-}}
 \end{figure}
-
-\section{Queuing filters}\label{sec:queue}
-We now describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
-A scheme describing our structure is detailed in Figure~\ref{fig:scheme}.
 
@@
 We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
-Here \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first position.\footnote{Two standard ways to implement this are a double-ended queue (deque) and a ring buffer.}
+Here \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first position.%\footnote{Two standard ways to implement this are a double-ended queue (deque) and a ring buffer.}
 
@@
 
-As a result, if $w < cL$, the queuing filter can hold information about \emph{more than $w$ elements}.
+Hence, if $w < cL$, the queuing filter can hold information about \emph{more than $w$ elements}.
 
@@
 
-\begin{restatable}{thm}{pfpQueue}
+\begin{theorem}
 	\label{thm:queue-pfp}
@@
 	 $\FP_{\mathcal F,m}$ is the false positive probability of a subfilter $\mathcal F$ after $m$ insertions.
-\end{restatable}
+\end{theorem}
 
-%\begin{proof}
-%	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream and $e^\star \notwdup E$. 
-%	
-%	Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
+\begin{proof}
+	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream and $e^\star \notwdup E$.
+
+	Therefore, $e^\star$ is a false positive if and only if at least one subquery $\mathcal F_i.\mathsf{Lookup(e^\star)}$ returns \DUPLICATE.
 Conversely, $e^\star$ is \emph{not} a false positive when all subqueries $\mathcal F_i.\mathsf{Lookup(e^\star)}$ return \UNSEEN, i.e., when $e^\star$ is not a false positive for each subfilter.
-%	
-%	Each subfilter has undergone $c$ insertions, except for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
-%\end{proof}
+
+	Each subfilter has undergone $c$ insertions, except for the first subfilter which has only undergone $m \bmod c$, we immediately get Eq.~(\ref{eq:queue-pfp}).
+\end{proof}
 
@@
 \subsubsection{False Negative Probability}\label{sub:fnr}
-\begin{restatable}{thm}{pfnQueue}
+\begin{theorem}
 	\label{thm:queue-pfn}
@@
 	$%\end{equation*}
-\end{restatable}
+\end{theorem}
 
-%\begin{proof}
-%	Let $E = \{e_1, \dotsc, e_m, \dotsc\}$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$. 
-%	
-%	Then $e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$. There can be two cases:
-%	\begin{itemize}
-%		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window;
-%		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window.
-%	\end{itemize}
-%In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
+\begin{proof}
+	Let $E = (e_1, \dotsc, e_m, \dotsc)$ be a stream, let $w$ be a sliding window and let $e^\star \wdup E$.
+
+	Then $e^\star$ is a false negative if and only if all subfilters $\mathcal F_i$ answer $\mathcal F_i.\mathsf{Detect}(e^\star) = \UNSEEN$. There can be two cases:
+	\begin{itemize}
+		\item $e^\star$ is present in $\mathcal F_i$'s sub-sliding window;
+		\item $e^\star$ is not present in $\mathcal F_i$'s sub-sliding window.
+	\end{itemize}
+	In the first case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is a false negative for $\mathcal F_i$.
 This happens with probability $\FN_{\mathcal F,c}$ by definition, except for $\mathcal F_0$, for which the probability is $\FN_{\mathcal F, m\bmod c}$.
-%
-%In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$, which happens with probability $1-\FP_{\mathcal F,c}$, execpt for $\mathcal F_0$, for which the probability is $1-\FP_{\mathcal F, m\bmod c}$.
-%
-%Finally, each event is weighted by the probability $p_c$ that $e^\star$ is in $\mathcal F_i$'s sub-sliding window:
-%\begin{align*}
-%	p_c 
-%	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
-%	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
-%	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
-%%		\end{align*}\begin{align*}p_c
-%	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
-%	& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
-%\end{align*}
-%This concludes the proof.
-%\end{proof}
+
+	In the second case, $\mathcal F_i.\mathsf{Detect}(e^\star)$ returns \UNSEEN if and only if $e^\star$ is not a false positive for $\mathcal F_i$, which happens with probability $1-\FP_{\mathcal F,c}$, execpt for $\mathcal F_0$, for which the probability is $1-\FP_{\mathcal F, m\bmod c}$.
+
+	Finally, each event is weighted by the probability $p_c$ that $e^\star$ is in $\mathcal F_i$'s sub-sliding window:
+	\begin{align*}
+	p_c 
+	& = \Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window | } e^\star \wdup E]\\
+	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window } \cap e^\star \wdup E]}{\Pr[e^\star \wdup E]}\\
+	& = \frac{\Pr[\text{$e^\star$ is in }\mathcal F_i \text{ sub-sliding window}]}{\Pr[e^\star \wdup E]}\\
+	%		\end{align*}\begin{align*}p_c
+	& = \frac{1 - \Pr[\text{$e^\star$ is not in }\mathcal F_i \text{ sub-sliding window }]}{1 - \Pr[e^\star \notwdup E]}\\
+	p_c& = \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^c}{1 - \left(1-\frac{1}{|\Gamma|}\right)^w}
+	\end{align*}
+	This concludes the proof.
+\end{proof}
+
 \paragraph{Remark.} As previously, the effect of $w < cL$ is negligible for all practical purposes and Theorem~\ref{thm:queue-pfn} is considered a good approximation in that regime.
@@
 From the above expressions we can derive relatively compact explicit formulas for the queuing filter's FPR and FNR when $m = cn$ for $n$ a positive integer.
-\begin{restatable}{thm}{fprQueue}
+\begin{theorem}
 	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
@@
 	\end{equation*}
-\end{restatable}
-%\begin{proof}
-%
-%\begin{align*}
-%	\FPR_{\mathcal Q, cn}^w
-%	& = \frac{1}{cn} \sum_{k=1}^{cn} \FP_{\mathcal Q, k}^w 
-%	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, k + \ell}^w 
-%	 = \frac1c \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, \ell}^w \\
-%	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
-%	& = 1 - \frac1c(1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
-%\end{align*}
-%\end{proof}
+\end{theorem}
+\begin{proof}
 
-\begin{restatable}{thm}{fnrQueue}
+	\begin{align*}
+	\FPR_{\mathcal Q, cn}^w
+	& = \frac{1}{cn} \sum_{k=1}^{cn} \FP_{\mathcal Q, k}^w 
+	= \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, k + \ell}^w 
+	= \frac1c \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, \ell}^w \\
+	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
+	& = 1 - \frac1c(1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell})
+	\end{align*}
+\end{proof}
+
+\begin{theorem}
 	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
@@
 	\end{equation*}
-\end{restatable}
+\end{theorem}
 
-%\begin{proof}
-%\begin{align*}
-%	\FNR_{\mathcal Q, cn}^w 
-%	& = \frac{1}{cn} \sum_{k=1}^{cn} \FN_{\mathcal Q, k}^w 
-%	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, k + \ell}^w 
-%	= \frac1c \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, \ell}^w \\
-%	& = \frac1c \sum_{\ell = 0}^{c-1} u_c^{L-1} u_{\ell} 
-%	 = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
-%\end{align*}
-%\end{proof}
+\begin{proof}
+	\begin{align*}
+	\FNR_{\mathcal Q, cn}^w 
+	& = \frac{1}{cn} \sum_{k=1}^{cn} \FN_{\mathcal Q, k}^w 
+	= \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, k + \ell}^w 
+	= \frac1c \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, \ell}^w \\
+	& = \frac1c \sum_{\ell = 0}^{c-1} u_c^{L-1} u_{\ell} 
+	= \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
+	\end{align*}
+\end{proof}
+
 As for the probabilities, the expressions derived above for the FNR and FNR are valid to first order in $(w - cL)/|\Gamma|$, i.e. they are good approximations even when $w \approx cL$.
@@
 \begin{figure}[t]
-\makebox[\textwidth]{\makebox[1.15\textwidth]{%
-	\begin{minipage}{.5\textwidth}
+%\makebox[\textwidth]{\makebox[1.15\textwidth]{%
+%	\begin{minipage}{.5\textwidth}
 		\centering
@@
 		\caption{Error rate (times 100) of queuing filters as a function of window size, $M=10^5$, $L=10$, $|\Gamma| = 2^{18}$, on a stream of size $10^7$.}\label{tab:comparing_queuing}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{.6\textwidth}
-		\centering
-		\input{graphs/bench_l.tex}
-		\caption{Evolution of the error rate of a queueing QHT as a function of $L$, for several window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
-	\end{minipage}
-}}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}{.6\textwidth}
+%		\centering
+%		\input{graphs/bench_l.tex}
+%		\caption{Evolution of the error rate of a queueing QHT as a function of $L$, for several window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
+%	\end{minipage}
+%}}
 \end{figure}
@@
 
+\begin{figure}[t]
+	\centering
+	\input{graphs/bench_l.tex}
+	\caption{Evolution of the error rate of a queueing QHT as a function of $L$, for several window sizes, with $M=10^5$, $|\Gamma| = 2^{18}$, on a stream of size $10^6$.}\label{fig:bench_l}
+\end{figure}
 We observe that the optimal value for $L$ does indeed depend on the desired sliding window.
@@
 
-\subsubsection{False positive and false negative resistance}
+%\subsubsection{False positive and false negative resistance}
 
@@
 
-\begin{restatable}[Bound on false positive resistance]{thm}{fprRes}
+\begin{theorem}[Bound on false positive resistance]
 	Let $\mathcal Q$ be a filter of $L$ subfilters $\mathcal F_i$, with $c$ insertions maximum per subfilter, let $w$ be a sliding window.
@@
 	If $cL > w$, the adversary has a success probability of at least $1-(1-p)^L$.
-\end{restatable}
+\end{theorem}
 
-%\begin{proof}
-%	If $cL \leq w$, then information-theoretically the subfilters only have information on elements in the sliding window.
-%	The probability of false positive for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$, which is strictly increasing with $\FP_{\mathcal F,c}$.
-Hence, the optimal solution is reached by to maximising the probability of false positive in each subfilter $\mathcal F_i$.
+\begin{proof}
+	If $cL \leq w$, then information-theoretically the subfilters only have information on elements in the sliding window.
+	The false positive probability for $\mathcal Q$ is $1 - (1 - \FP_{\mathcal F, c})^L$, which is strictly increasing with $\FP_{\mathcal F,c}$.
+Hence, the optimal solution is reached by to maximising the false positive probability in each subfilter $\mathcal F_i$.
 By hypothesis the latter is bounded above by $p$ after $c$ insertions.
-%	
-%	On the other hand, if $cL > w$ then oldest filter holds information about elements that are not in the sliding window anymore.
+
+	On the other hand, if $cL > w$ then the oldest filter holds information about elements that are not in the sliding window anymore.
 Hence, a strategy for the attacker trying to trigger a false positive on $e^\star$ could be to make it so these oldest elements are all equal to $e^\star$.
@@
 The adversary $\mathcal A$ can create a new stream $E' = e^\star | e^\star | \dotsc | E$ where $e^\star$ is prepended $cL - w$ times to $E$.
-%	
-%	After $w$ insertions, the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ probability of success.
+
+	After $w$ insertions, the last subfilter will answer $\DUPLICATE$ with probability at least $p$, hence giving a lower bound on $\mathcal A's$ success probability.
 If, for some reason, the last subfilter answers $\DUPLICATE$ with probability less than $p$, then the same reasoning as for when $cL \leq w$ still applies, hence we get the correspondig lower bound (which is, in this case, an equality).
-%\end{proof}
+\end{proof}
+
 %%
@@
 
-\begin{restatable}[Bounds on false negative resistance]{thm}{fnrRes}
+\begin{theorem}[Bounds on false negative resistance]
 	Let $\mathcal Q$ be a filter of $L$ subfilters of kind $\mathcal F$, with $c$ insertions maximum per subfilter, and let $w$ be a sliding window.
@@
 	On the other hand if $w > (L-1)c$ then $\mathcal Q$ is  $(\max(1 - q, p)^{L}, w)$-resistant to false negative attacks on the sliding window $w$.
-\end{restatable}
+\end{theorem}
 
-%\begin{proof}
-%	Let us first prove that a PPT adversary $\mathcal A$ can win the game with probability at least $p^L$.
-%	For this, let us consider the adversarial game against the subfilter $\mathcal F$: after $c$ insertions from an aversarial stream $E_c$, $\mathcal A$ choses a duplicate $e^\star$ which will be a false negative with proability $p$.
-%	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c \mid E_c \mid \cdots \mid E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a probability of success for $\mathcal A$ of $p^L$.
-%	
-%	Now, Let us prove the case where $w\leq (L-1)c$.
+\begin{proof}
+	Let us first prove that a PPT adversary $\mathcal A$ can win the game with probability at least $p^L$.
+	For this, let us consider the adversarial game against the subfilter $\mathcal F$: after $c$ insertions from an aversarial stream $E_c$, $\mathcal A$ choses a duplicate $e^\star$ which will be a false negative with proability $p$.
+	Hence, if $\mathcal A$ crafts, for the filter $\mathcal Q$, the following adversarial stream $E' = E_c \mid E_c \mid \cdots \mid E_c$ consisting of $L$ concatenations of the stream $E_c$, then $e^\star$ is a false negative for $\mathcal Q$ if and only if it is a false negative for all subfilters $\mathcal F_i$, hence a success probability for $\mathcal A$ of $p^L$.
+
+	Now, Let us prove the case where $w\leq (L-1)c$.
 In this case, at any time, $\mathcal Q$ remembers all elements from inside the sliding window.
-As we have seen in the previous example, the probability of success of $\mathcal A$ is strictly increasing with the probability of each subfilter to answer $\UNSEEN$.
+As we have seen in the previous example, the success probability of $\mathcal A$ is strictly increasing with the probability of each subfilter to answer $\UNSEEN$.
 The probability of a subfilter to answer $\UNSEEN$ is:
-%	
-%	\begin{itemize}
-%		\item $\FN'_{\mathcal F,c}$ if $e^\star$ is in the subfilter's sub-sliding window;
-%		\item $1 - \FP'_{\mathcal F, c}$ if $e^\star$ is not in the subfilter's sub-sliding window
-%	\end{itemize}
-%	where $\FN'$ and $\FP'$ are the probabilities of false negative and positives on the adversarial stream (which may be different from a random uniform stream).
-%	
-%	However, since $e^\star$ is a duplicate, it is in at least one subfilter's sub-sliding window.
+
+	\begin{itemize}
+		\item $\FN'_{\mathcal F,c}$ if $e^\star$ is in the subfilter's sub-sliding window;
+		\item $1 - \FP'_{\mathcal F, c}$ if $e^\star$ is not in the subfilter's sub-sliding window
+	\end{itemize}
+	where $\FN'$ and $\FP'$ are the probabilities of false negative and positives on the adversarial stream (which may be different from a random uniform stream).
+
+	However, since $e^\star$ is a duplicate, it is in at least one subfilter's sub-sliding window.
 As such, the optimal strategy for $\mathcal A$ is to maximise the probability of all subfilters to answer $\UNSEEN$.
-%	Now, $\FN'_{\mathcal F,c}$ is bounded above by $p$ and $1 - \FP'_{\mathcal F, c}$ is bounded above by $1-q$, so the best strategy is where as many filters as possible answer $\UNSEEN$ with probability $\max(p, 1-q)$, knowing that at least one filter must contain $e^\star$ and as such its probability for returning $\UNSEEN$ is at most $p$, hence the result.
-%	
-%	Now, let us consider the case when $w > (L-1)c$.
+	Now, $\FN'_{\mathcal F,c}$ is bounded above by $p$ and $1 - \FP'_{\mathcal F, c}$ is bounded above by $1-q$, so the best strategy is where as many filters as possible answer $\UNSEEN$ with probability $\max(p, 1-q)$, knowing that at least one filter must contain $e^\star$ and as such its probability for returning $\UNSEEN$ is at most $p$, hence the result.
+
+	Now, let us consider the case when $w > (L-1)c$.
 We have already introduce the element $e^\star$ in the last $w$ elements, and we want to insert it again.
-It is possible, for the adversary, to create the following stream $E = (e_1, e_2, \dotsc, e_{c-1}, e^\star, e_{c+1}, \dotsc, e_{Lc}, e_{Lc + 1})$, and to insert $e^\star$ afterwards.
-%	
-%	When $e_{Lc+1}$ is inserted, all elements $(e_1, \dotsc, e_{c-1}, e^\star)$ are dropped as the oldest subfilter is popped.
+It is possible, for the adversary, to create the following stream $E = (e_1, e_2, \dotsc, e_{c-1}, e^\star, e_{c+1}, \dotsc,$ $ e_{Lc}, e_{Lc + 1})$, and to insert $e^\star$ afterwards.
+
+	When $e_{Lc+1}$ is inserted, all elements $(e_1, \dotsc, e_{c-1}, e^\star)$ are dropped as the oldest subfilter is popped.
 Hence, in this context $e^\star$ is not in any subfilter anymore, so by adapting the previous analysis, $\mathcal A$ can get a false negative with probability at most $\max(1 - q, p)^{L}$.
-%\end{proof}
+\end{proof}
+
 %% Acknowledgements 

### 2020-05-09 samplepaper.tex
Arxiv version from COCOON

@@
 %
-\documentclass[runningheads]{llncs}
+\documentclass[]{article}
 %
@@
 %\usepackage{times}
-\usepackage[moderate]{savetrees}
+%\usepackage[moderate]{savetrees}
 \usepackage{multicol}
@@
 \restylefloat*{figure}
+
+\usepackage{authblk}
+% Keywords command
+\providecommand{\keywords}[1]
+{
+	\small	
+	\textbf{\textit{Keywords---}} #1
+}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\newtheorem{definition}{Definition}
+\newtheorem{theorem}{Theorem}
 
@@
 %
-\author{Rémi Géraud--Stewart\inst{1} \and
-Marius Lombard-Platet\inst{1,2} \and
-David Naccache\inst{1}}
+\author[1]{Rémi Géraud--Stewart}
+\author[1,2]{Marius Lombard-Platet}
+\author[1]{David Naccache}
+\affil[1]{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University, Paris, France}
+\affil[2]{Be-ys Research Lab, Clermont-Ferrand, France}
+\affil[ ]{\texttt{\{first\}.\{last\}@ens.fr}}
 %
+\date{}
 %\authorrunning{F. Author et al.}
@@
 %
-\institute{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University, Paris, France \and
-Be-ys Research Lab, Clermont-Ferrand, France\\
-\email{\{first\}.\{last\}@ens.fr}
-}
+%\institute{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University, Paris, France \and
+%Be-ys Research Lab, Clermont-Ferrand, France\\
+%\email{\{first\}.\{last\}@ens.fr}
+%}
 %
@@
 We also analyse the security of our filters in an adversarial setting. 
-\keywords{TODO}
+\keywords{Duplicate detection, Streaming algorithms, Sliding window}
 \end{abstract}
@@
 %
+
  \bibliographystyle{splncs04}
-\bibliography{bibli_short}
-%\bibliography{qhtv2}
+
+%\bibliography{bibli_short}
+\bibliography{qhtv2}
 

### 2020-05-09 appendix.tex
i hate arxiv

@@
 			xlabel=$w$, ylabel=$\FPR^w + \FNR^w (\times 100)$]
-		\addplot[color=teal, mark=triangle] table[x=w,y=Error] {graphs/Queueing_Cuckoo.dat};
+		\addplot[color=teal, mark=triangle] table[x=w,y=Error] {graphs/queueing_cuckoo.dat};
 		\addlegendentry{Q\_Cuckoo};
-		\addplot[color=teal, mark=triangle, dashed] table[x=w,y=Error] {graphs/Cuckoo.dat};
+		\addplot[color=teal, mark=triangle, dashed] table[x=w,y=Error] {graphs/cuckoo.dat};
 		\addlegendentry{Cuckoo};
 		%%
-		\addplot[color=olive, mark=square, mark options = {scale=0.7}] table[x=w,y=Error] {graphs/Queueing_StableBloom.dat};
+		\addplot[color=olive, mark=square, mark options = {scale=0.7}] table[x=w,y=Error] {graphs/queueing_stablebloom.dat};
 		\addlegendentry{Q\_SBF};
-		\addplot[color=olive, mark=square, mark options = {scale=0.7}, dashed] table[x=w,y=Error] {graphs/SBF.dat};
+		\addplot[color=olive, mark=square, mark options = {scale=0.7}, dashed] table[x=w,y=Error] {graphs/sbf.dat};
 		\addlegendentry{SBF};

### 2020-05-10 appendix.tex
fixes

--- 2020-04-15 appendix.tex
@@
 Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF).
-The CSHF performs in linear time in $w$, and is a simple queue, the only point is that instead of storing $e$, one stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.
+The CSHF performs in linear time in $w$, and is a simple queue, the only point is that instead of storing $e$, the filter stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.
 
@@
 
-\begin{restatable}{thm}{fprSHF}\label{thm:fprCHF}	
+\begin{restatable}{thm}{fprCSHF}\label{thm:fprCHF}	
 	$\FN_\text{CSHF}^w  = 0$  and $\FP_\text{CSHF}^w = 1 - \left(1 - 2^{-M/w}\right)^w$
@@
 
-\paragraph{Remark:} A CSHF of size $M$ has the same error rate than an SHF of size $2M + w\log_2 w$.
+\paragraph{Remark:} A CSHF of size $M$ on a sliding window $w$ has the same error rate than an SHF of sliding window $w$ and size $2M + w\log_2 w$.
 
@@
 
-	On the other hand, $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
+	On the other hand, a duplicate $e^\star\in E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
 Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.

### 2020-05-10 article_content.tex
fixes

--- 2020-04-15 article_content.tex
@@
 Similarly, the construction in \cite{shtul2020agepartitioned} only works with Bloom Filters.
-
+%A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+The structure proposed in \cite{10.1145/1060745.1060753} is not designed for wDDP but a variant called `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
 %\section{Duplicate Detection and Filter Saturation}
@@
 \begin{proof}
-	Due to page limit restrictions, all theorem proofs' are in Appendix~\ref{app:proofs}.
+	Due to page limit restrictions, all theorem proofs are in Appendix~\ref{app:proofs}.
 \end{proof}
@@
 
-\paragraph{Error Rates.}
+\paragraph{Error Probabilities.}
 Let $w> 0$ be a window size and $M > 0$ the available memory.
@@
 \paragraph{Saturation.}
-SHF has strictly increasing error rates, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
+SHF has strictly increasing error probabilities, which reach a threshold of $1/2$ for some maximum window size $w_\text{max}$.
 Beyond this value, these filters saturate extremely quickly: in other words, most SHF will either have an error rate of $0$ or $1$.
@@
 % are given in Figure~\ref{fig:w_opt} and 
-Experiments indicate an approximately linear relationship between $M$ and $w_\text{max}$: %for large values of $M$:
+Experiments (numerical resolution of $\FP^\text{max} = 1/2$ for about 200 different values of $M$, uniformly distributed \emph{on a log scale} between $10^2$ and $10^6$) indicate an approximately linear relationship between $M$ and $w_\text{max}$: %for large values of $M$:
  %$w_\text{max}^\text{CSHF} = 0.0627 M + 443$ ($r^2 = 0.9981$) and
@@
 \end{restatable}
-In particular, the asymptotic error rate $E_\infty$ satisfies 
+In particular, the asymptotic error probability $EP_\infty$ satisfies 
 $
@@
 %
-\begin{itemize}
+\begin{compactitem}
 	\item QHT \cite{10.1145/3297280.3297335}, 1 bucket per row, 3 bits per fingerprint;
@@
 %	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
-%	\item Block-Decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of 6000 elements.
-\end{itemize}
+%	\item Block-Decaying Bloom Filter (b\_DBF) \cite{She08}, sliding window of  elements.
+\end{compactitem}
 %
@@
 We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
-Here \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first position.\footnote{Two standard ways to implement this are a double-ended queue (deque) and a ring buffer.}
+Here \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first position.
 
@@
 The game has two distinct parts.
-\begin{itemize}
+\begin{compactitem}
 	\item In the first part, $\mathcal A$ can feed up to $n$ elements to $\mathcal Q$ and learns $\mathcal Q$'s response for each insertion.
 	\item In the second part, $\mathcal A$ sends a unique element $e^\star$.
-\end{itemize} 
+\end{compactitem} 
  $\mathcal A$ wins the $n$-false positive adversarial game (resp. $n$-false negative adversarial game) if and only if $e^\star$ is a false positive (resp. a false negative).

### 2020-05-10 article_content.tex
fixes

@@
 \end{restatable}
-In particular, the asymptotic error probability $EP_\infty$ satisfies 
+In particular, the asymptotic error probability $EP  _\infty$ satisfies 
 $

### 2020-05-10 article_content.tex
update

--- 2020-05-09 article_content.tex
@@
 Similarly, the construction in \cite{shtul2020agepartitioned} only works with Bloom Filters.
+
+A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+The structure proposed in \cite{10.1145/1060745.1060753} is not designed for wDDP but a variant called `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
 
@@
 
-\paragraph{Remark:} A CSHF of size $M$ on a sliding window $w$ has the same error rate than an SHF of sliding window of size $2M + w\log_2 w$.
+\paragraph{Remark:} A CSHF of size $M$ on a sliding window $w$ has the same error rate than an SHF of sliding window $w$ of size $2M + w\log_2 w$.
 
@@
 
-	On the other hand, a duplicate $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
+	On the other hand, a duplicate $e^\star \in E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN.
 Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}.
@@
 
-%As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
+%As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and  filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP.
 This raises the question of whether recursive constructions (queuing filters of queuing filters) have particularly interesting properties, which we leave open for future work.

### 2020-05-10 article_content.tex
add literature review

--- 2020-05-10 article_content.tex
@@
 Similarly, the construction in \cite{shtul2020agepartitioned} only works with Bloom Filters.
-%A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}.
+Literature review collects the following DDFs \cite{Yoo10,Den06,10.1145/3297280.3297335,Dut13,She08,Fan14}, which we will consider in this paper .
 The structure proposed in \cite{10.1145/1060745.1060753} is not designed for wDDP but a variant called `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.
@@
 \end{restatable}
+
 In particular, the asymptotic error probability $EP_\infty$ satisfies
+
 $

### 2020-06-22 appendix.tex
COCOON preparing camera-ready

@@
+\section{SHF and queueing filter algorithms}\label{app:algo}
+In this appendix, we give the pseudocode of our two structures, which we removed from the main part of the paper for page limit reasons.
+\begin{algorithm}
+	\caption{SHF \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:SHF}
+
+	\begin{algorithmic}[1]
+		\Function{Setup}{$M, w$}
+		\Comment $M$ is the available memory, $w$ the size of the sliding window
+		\State $h \gets$ hash function of codomain size $\lfloor \frac M{2w} - \frac 12 \log_2 w \rfloor$ bits
+		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
+		\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h \Rightarrow$  counter (of max value $w$)
+		\EndFunction 
+	\end{algorithmic}
+
+	\begin{multicols}{2}
+		\begin{algorithmic}[1]
+			\Function{Insert}{$e$}
+			\State $Q.\mathsf{Push\_Front}(h(e))$
+			\State $D[h(e)]$++
+
+			\If{$Q.\mathsf{length}() > w$}
+			\State $h' \gets Q.\mathsf{Pop\_back}()$
+			\State $D[h']$-{}-
+			\If{$D[h'] = 0$}
+			\State Erase key $D[h']$
+			\EndIf
+			\EndIf
+			\EndFunction
+		\end{algorithmic}
+
+		\begin{algorithmic}[1]
+			\item[]
+			\Function{Lookup}{$e$}
+			\If{$D[h(e)] > 0$}
+			\State \Return \DUPLICATE
+			\Else
+			\State \Return \UNSEEN
+			\EndIf
+			\EndFunction
+			\item[]
+		\end{algorithmic}
+
+	\end{multicols}
+\end{algorithm}
+
+\begin{algorithm}[]
+	\caption{Queuing Filter \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:queuing}
+	\begin{algorithmic}[1]
+		\Function{Setup}{$\mathcal F, M, L, c$}
+		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
+		\State subfilters $\gets \emptyset$
+		\State counter $\gets 0$
+		\State $m \gets \lfloor M/L \rfloor$
+		\For{$i$ from $0$ to $L-1$}
+		\State subfilters.push\_first$(\mathcal F.\mathsf{Setup}(m))$
+		\EndFor
+		\State \textbf{store} (subfilters, $L$, $m$, counter)
+		%		\State\Return filter
+		\EndFunction 
+	\end{algorithmic}
+
+	\begin{multicols}{2}
+		\begin{algorithmic}[1]
+			\Function{Lookup}{$e$}
+			\For{$i$ from $0$ to $L-1$}
+			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
+			\State \Return $\DUPLICATE$			
+			\EndIf
+			\EndFor
+			\State \Return \UNSEEN
+			\EndFunction
+			\item[]
+		\end{algorithmic}
+
+		\begin{algorithmic}[1]
+			\Function{Insert}{$e$}
+			\State subfilters[0]$.\mathsf{Insert}(e)$
+			\State counter$++$
+			\If{counter == $c$}
+			\State subfilters.pop()
+			\State subfilters.push\_first($\mathcal F.\textsf{Setup}(m)$)
+			\EndIf
+			\EndFunction
+		\end{algorithmic}
+	\end{multicols}
+\end{algorithm}
 \section{Effects of the simulation's finiteness}

### 2020-06-22 article_content.tex
COCOON preparing camera-ready

@@
 \end{definition}
+
+A filter attempting to solve the wDDP is called a duplicate detection filter (DDF).
 %Even when the stream is bounded, i.e. $\lim_{n\to\infty}|E_n| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable. 
@@
 We show that some of them outperform dedicated data structures, including SHF, in the $w > w_\text{max}$ regime.
+However, we exhibit a lower bound on the error rate of such filters.
 
 We then introduce the \enquote{queuing construction}, a black box transformation of non-windowed data structures into windowed ones, that improves their performance in the wDDP setting.
-
 Finally, we provide an analysis of our queueing construction's resistance to adversarial streams.
@@
 The wDDP formulation we rely on is due to \cite{Yoo10,She08}, which also introduce algorithms for solving the wDDP approximately.
+To the best of our knowledge, the discrepancy between the wDDP and the DDP and the wDDP has not been studied.
+Similarly, the relation between $w$ (the sliding window size), the error rate and $M$ (the available memory) is not always present in similar papers, one exception being \cite{She08}.
 
@@
 \section{Notations and basic definitions}
-We consider an unbounded stream $E = (e_1, e_2, \dotsc, e_n, \dotsc)$ with elements belonging to an alphabet $\Gamma$.
+We consider an unbounded stream $E = (e_1, e_2, \dotsc, e_n, \dotsc)$ of elements from an alphabet $\Gamma$.
 
@@
 
-For a filter, the false positive probability ($\FP^w_i$) is the probability that after $i$ insertions, the \emph{unseen} element $e_i\notwdup E$ is a false positive over $w$.
+The filter false positive probability ($\FP^w_i$) is the probability that after $i$ insertions, the \emph{unseen} element $e_i\notwdup E$ is a false positive over $w$.
 The false positive rate $\FPR^w_i$ is the number of false positives divided by the number of unseen elements in E\footnote{We observe that $\FPR^w_n = \frac{1}{n}\sum_{i=1}^n \FP^w_i$, and similarly for $\FNR^w_n$.}.
@@
 
-\paragraph{Remark.} For benchmarking, we usually measure the error rate $ER = \FPR^w + \FNR^w$, as it allows a practical ranking of the solutions.
+\paragraph{Remark.} For benchmarking, we usually measure the error rate $ER^w = \FPR^w + \FNR^w$, as it allows a practical ranking of the solutions.
 An error rate of $0$ means a perfect filter, while a filter answering randomly has an error rate of $1$.
@@
 \begin{proof}
-	Due to page limit restrictions, all theorem proofs are in Appendix~\ref{app:proofs}.
+	Due to page limit restrictions, all proofs are in Appendix~\ref{app:proofs}.
 \end{proof}
@@
 	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the wDDP can be solved with almost no error using $M$ memory bits.
-
 	More precisely, it is possible to create a filter of $M$ bits with an FN of $0$, an FP of $1 - (1-\frac1{w^2})^w \sim \frac 1w$, and a time complexity of $O(w)$.
@@
 
-This gives us the Short Hash Filter (SHF), described in Algorithm~\ref{alg:SHF}.
+This gives us the Short Hash Filter (SHF), described in Algorithm~\ref{alg:SHF}, in Appendix~\ref{app:algo}.
 The implementation relies on a double-ended queue or a ring buffer, which allows pushing at beginning of a queue and popping at the end in constant time.
@@
 
-\begin{algorithm}
-	\caption{SHF \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:SHF}
-
-	\begin{algorithmic}[1]
-	\Function{Setup}{$M, w$}
-	\Comment $M$ is the available memory, $w$ the size of the sliding window
-	\State $h \gets$ hash function of codomain size $\lfloor \frac M{2w} - \frac 12 \log_2 w \rfloor$
-	\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
-	\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h \Rightarrow$  counter (of max value $w$)
-	\EndFunction 
-	\end{algorithmic}
-
-	\begin{multicols}{2}
-	\begin{algorithmic}[1]
-		\Function{Insert}{$e$}
-		\State $Q.\mathsf{Push\_Front}(h(e))$
-		\State $D[h(e)]$++
-
-		\If{$Q.\mathsf{length}() > w$}
-		\State $h' \gets Q.\mathsf{Pop\_back}()$
-		\State $D[h']$-{}-
-		\If{$D[h'] = 0$}
-		\State Erase key $D[h']$
-		\EndIf
-		\EndIf
-		\EndFunction
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\item[]
-	\Function{Lookup}{$e$}
-	\If{$D[h(e)] > 0$}
-	\State \Return \DUPLICATE
-	\Else
-	\State \Return \UNSEEN
-	\EndIf
-	\EndFunction
-	\item[]
-\end{algorithmic}
-
-	\end{multicols}
-\end{algorithm}
+%\begin{algorithm}
+%	\caption{SHF \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:SHF}
+%	
+%	\begin{algorithmic}[1]
+%	\Function{Setup}{$M, w$}
+%	\Comment $M$ is the available memory, $w$ the size of the sliding window
+%	\State $h \gets$ hash function of codomain size $\lfloor \frac M{2w} - \frac 12 \log_2 w \rfloor$
+%	\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
+%	\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h \Rightarrow$  counter (of max value $w$)
+%	\EndFunction 
+%	\end{algorithmic}
+%
+%	\begin{multicols}{2}
+%	\begin{algorithmic}[1]
+%		\Function{Insert}{$e$}
+%		\State $Q.\mathsf{Push\_Front}(h(e))$
+%		\State $D[h(e)]$++
+%		
+%		\If{$Q.\mathsf{length}() > w$}
+%		\State $h' \gets Q.\mathsf{Pop\_back}()$
+%		\State $D[h']$-{}-
+%		\If{$D[h'] = 0$}
+%		\State Erase key $D[h']$
+%		\EndIf
+%		\EndIf
+%		\EndFunction
+%	\end{algorithmic}	
+%		
+%	\begin{algorithmic}[1]
+%	\item[]
+%	\Function{Lookup}{$e$}
+%	\If{$D[h(e)] > 0$}
+%	\State \Return \DUPLICATE
+%	\Else
+%	\State \Return \UNSEEN
+%	\EndIf
+%	\EndFunction
+%	\item[]
+%\end{algorithmic}
+%
+%
+%	\end{multicols}
+%\end{algorithm}
 
@@
 Beyond this value, these filters saturate extremely quickly: in other words, most SHF will either have an error rate of $0$ or $1$.
-
 An illustration of this phenomenon can be seen in Figure~\ref{fig:shorts}, 
@@
 
-In particular, the asymptotic error probability $EP_\infty$ satisfies
-
+The asymptotic error probability $EP_\infty$ satisfies 
 $
@@
 	\item Cuckoo Filter \cite{Fan14}, cells containing 1 element of 3 bits each;
-	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hash functions, targeted FPR of 0.02.
+	\item Stable Bloom Filter (SBF) \cite{Den06}, 2 bits per cell, 2 hashes, targeted FPR of 0.02.
 %	\item $A2$ Filter \cite{Yoo10}, targeted FPR of $0.1$ on the sliding window.
@@
 We now consider the performance of the filters just discussed in the \emph{windowed} setting, for which they were \emph{not} designed.
-In particular, it is not possible to adjust their parameters as a function of $w$.
-
+In particular, they cannot adjust their parameters as a function of $w$.
 Remarkably, some of these filters still outperform dedicated windowed filters for some window sizes at least, as shown in Figure~\ref{fig:nwddf-in-wddp}.
 In this benchmark, we used the following filters:
-\begin{itemize}
+\begin{compactitem}
 	\item block decaying Bloom Filter\footnote{Note that by design, a b\_DBF of $10^5$ bits cannot operate for $w > 6000$.} (b\_DBF) \cite{She08}, sliding window of size $w$
@@
 	\item QHT \cite{10.1145/3297280.3297335}, 1 bucket per row, $3$ bits per fingerprint
-\end{itemize}
+\end{compactitem}
 
@@
 The subfilters are organised in a queue.
-
 When inserting a new element in the queuing filter, it is inserted in the topmost subfilter of the queue.
@@
 \paragraph{Pseudocode.}
-We give a brief pseudocode for the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in Algorithm~\ref{alg:queuing}.
+We give a brief pseudocode for the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in Algorithm~\ref{alg:queuing}, in Appendix~\ref{app:algo}.
 We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$.
@@
 
-\begin{algorithm}[]
-	\caption{Queuing Filter \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:queuing}
-
-	\begin{algorithmic}[1]
-	\Function{Setup}{$\mathcal F, M, L, c$}
-		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
-		\State subfilters $\gets \emptyset$
-		\State counter $\gets 0$
-		\State $m \gets \lfloor M/L \rfloor$
-		\For{$i$ from $0$ to $L-1$}
-			\State subfilters.push\_first$(\mathcal F.\mathsf{Setup}(m))$
-		\EndFor
-		\State \textbf{store} (subfilters, $L$, $m$, counter)
-%		\State\Return filter
-	\EndFunction 
-	\end{algorithmic}
-
-	\begin{multicols}{2}
-	\begin{algorithmic}[1]
-	\Function{Lookup}{$e$}
-		\For{$i$ from $0$ to $L-1$}
-			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
-				\State \Return $\DUPLICATE$			
-			\EndIf
-		\EndFor
-		\State \Return \UNSEEN
-	\EndFunction
-	\item[]
-	\end{algorithmic}
-
-	\begin{algorithmic}[1]
-	\Function{Insert}{$e$}
-		\State subfilters[0]$.\mathsf{Insert}(e)$
-		\State counter$++$
-		\If{counter == $c$}
-			\State subfilters.pop()
-			\State subfilters.push\_first($\mathcal F.\textsf{Setup}(m)$)
-		\EndIf
-	\EndFunction
-	\end{algorithmic}
-	\end{multicols}
-\end{algorithm}
+%\begin{algorithm}[]
+%	\caption{Queuing Filter \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:queuing}
+%	\begin{algorithmic}[1]
+%	\Function{Setup}{$\mathcal F, M, L, c$}
+%		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
+%		\State subfilters $\gets \emptyset$
+%		\State counter $\gets 0$
+%		\State $m \gets \lfloor M/L \rfloor$
+%		\For{$i$ from $0$ to $L-1$}
+%			\State subfilters.push\_first$(\mathcal F.\mathsf{Setup}(m))$
+%		\EndFor
+%		\State \textbf{store} (subfilters, $L$, $m$, counter)
+%%		\State\Return filter
+%	\EndFunction 
+%	\end{algorithmic}
+%
+%	\begin{multicols}{2}
+%	\begin{algorithmic}[1]
+%	\Function{Lookup}{$e$}
+%		\For{$i$ from $0$ to $L-1$}
+%			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
+%				\State \Return $\DUPLICATE$			
+%			\EndIf
+%		\EndFor
+%		\State \Return \UNSEEN
+%	\EndFunction
+%	\item[]
+%	\end{algorithmic}
+%
+%	\begin{algorithmic}[1]
+%	\Function{Insert}{$e$}
+%		\State subfilters[0]$.\mathsf{Insert}(e)$
+%		\State counter$++$
+%		\If{counter == $c$}
+%			\State subfilters.pop()
+%			\State subfilters.push\_first($\mathcal F.\textsf{Setup}(m)$)
+%		\EndIf
+%	\EndFunction
+%	\end{algorithmic}
+%	\end{multicols}
+%\end{algorithm}
 
@@
 
-Hence, if $w < cL$, the queuing filter can hold information about \emph{more than $w$ elements}.
+If $w < cL$, the queuing filter can hold information about \emph{more than $w$ elements}.
 
@@
 	 Let $\FP_{\mathcal Q, m}^w$ be the false positive probability%(def. \ref{def:pfp-pfn})
-	 of $\mathcal Q$ after $m > w$ insertions, over a sliding window of size $w = cL$, we have \\
-	$$%\begin{equation}
+	 of $\mathcal Q$ after $m > w$ insertions, over a sliding window of size $w = cL$, we have
+	$%\begin{equation}
 		\label{eq:queue-pfp}
 		\FP_{\mathcal Q, m}^w = 1 - \left(1 - \FP_{\mathcal F,c}\right)^{L-1} \left(1 - \FP_{\mathcal F, m \bmod c }\right)
-	$$ %\end{equation}
+	$ %\end{equation}
 	where %$\bmod$ is the modulo operator and 
@@
 	Let $\FN_{\mathcal Q, m}^w$ be the false negative probability of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
-	$$%\begin{equation}
+	$%\begin{equation}
 	\FN_{\mathcal Q, m}^w 
 	=  u_c^{L-1} u_{m \bmod c}
-	$$%\end{equation}
+	$%\end{equation}
 	where %$\bmod$ is the modulo operator, and
@@
 	Let $\FPR_{\mathcal Q, m}^w$ be the false positive rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation*}
+	$%\begin{equation*}
 	\FPR_{\mathcal Q, cn}^w = 1 -  \frac{(1 - \FP_{\mathcal F, c})^{L-1}}{c}\sum_{\ell = 0}^{c-1} (1-\FP_{\mathcal F, \ell}).
-	\end{equation*}
+	$%\end{equation*}
 \end{restatable}
@@
 	Let $\FNR_{\mathcal Q, m}^w$ be the false negative rate of $\mathcal Q$ after $m=cn > w$ insertions on a sliding window of size $w = cL$, we have
-	\begin{equation*}
+	$%\begin{equation*}
 	\FNR_{\mathcal Q, cn}^w = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell.
-	\end{equation*}
+	$%\end{equation*}
 \end{restatable}
@@
 %\begin{equation*}
-
 \begin{align*}
@@
 Therefore we lose nothing by replacing atomically one subfilter by a more efficient one.
-Applying this to each subfilter we end up with a homogenous selection.
+Applying this to each subfilter we end with a homogenous selection.
 
@@
 
-This section provides details and additional information on the benchmarking experiments run to validate the above analysis. All code is accessible online and will be disclosed after peer review.
+This section provides details and additional information on the benchmarking experiments run to validate the above analysis.
+Our code is accessible online\footnote{\url{https://github.com/mariuslp/duplicate_sliding_benchmark}}.
 
@@
 	Let $\mathcal Q$ be a filter of $L$ subfilters of kind $\mathcal F$, with $c$ insertions maximum per subfilter, and let $w$ be a sliding window. 
-
 	If $\mathcal F$ is $(p, c)$-resistant to adversarial false negative attacks, then $\mathcal A$ can win the adversarial game on the sliding window $w$ with probability at least $p^L$.

### 2020-07-08 samplepaper.tex
fixes
COCOON preparing camera-ready
cocoon

--- 2020-04-15 samplepaper.tex
@@
 %\usepackage{times}
-\usepackage[moderate]{savetrees}
+\usepackage[subtle]{savetrees}
 \usepackage{multicol}
+\usepackage{paralist}
 
@@
 %
-\author{Rémi Géraud--Stewart\inst{1} \and
+\author{Rémi Géraud-Stewart\inst{1} \and
 Marius Lombard-Platet\inst{1,2} \and
@@
 \institute{Département d'informatique de l'ENS, ENS, CNRS, PSL Research University, Paris, France \and
-Be-ys Research Lab, Clermont-Ferrand, France\\
+Be-Studys, Be-Ys group, Châtelaine, Switzerland\\
 \email{\{first\}.\{last\}@ens.fr}
@@
  \bibliographystyle{splncs04}
-\bibliography{bibli_short}
+%\bibliography{bibli_short}
 %\bibliography{qhtv2}
+\bibliography{bibli_semishort}
 

### 2020-08-19 slides/graphs/bench_short.tex
slides

\begin{tikzpicture}
\begin{semilogxaxis}[%legend pos = outer north east, 
	legend pos= north east,%
	xlabel=$w$, ylabel=$\FPR^w+\FNR^w (\times 100)$, xmin=40,ymin=0,mlineplot]

\addplot[color=blue, mark=o] table[x=w,y=Error] {graphs/shf.dat};

\addplot [draw=none,pattern=north west lines,pattern color=black,domain=10:1843,stack plots=y] {100} \closedcycle;
\addlegendentry{SHF}

%\addplot[color=red, mark=x] table[x=a,y=b] {graphs/CSHF.dat};
%\addlegendentry{CSHF}

\end{semilogxaxis}
\end{tikzpicture}

### 2020-08-19 slides/graphs/queuef.tex
slides

\begin{tikzpicture}[scale=0.37]

	% First subfilter
	\draw<-8> (11, 0) rectangle (13, 1) node[midway] {$\mathcal F_0$}; \pause

	\draw[pattern=north west lines, pattern color=gray, draw=none] (12, 0) rectangle (13, 1);\pause
	\draw[pattern=north west lines, pattern color=gray, draw=none] (11, 0) rectangle (12, 1);
	\draw [<->,>=latex] (11, 1.5) -- (13, 1.5) node[above, midway] {\footnotesize $c$ elements}; \pause

	\draw<-8> (8, 0) rectangle (10, 1) node[midway] {$\mathcal F_1$};\pause

	\draw[pattern=north west lines, pattern color=gray, draw=none] (10, 0) rectangle (9, 1);\pause

	\draw[pattern=north west lines, pattern color=gray, draw=none] (8, 0) rectangle (10, 1);

	\node at (6.5, 0.3) {...};

	\draw<-8> (3, 0) rectangle (5, 1) node[midway] {$\mathcal F_{L-1}$};
	\draw [pattern=north west lines, pattern color=gray, draw=none] (3, 0) rectangle (5, 1);
	\draw<-8> (0, 0) rectangle (2, 1) node[midway] {$\mathcal F_L$};
	\draw (-0.5, 2.5) rectangle (14.1, -2.5) node[anchor=south east] {Queuing filter}; \pause

	\draw<-8>[pattern=north west lines, pattern color=gray, draw=none] (0, 0) rectangle (2, 1); \pause

	% We shift the filters
	\draw (11, 0) rectangle (13, 1) node[midway] {$\mathcal F_1$};
	\draw (8, 0) rectangle (10, 1) node[midway] {$\mathcal F_2$};
	\draw (3, 0) rectangle (5, 1) node[midway] {$\mathcal F_{L}$};
	% old subfilters
	\draw[dashed] (15, 0) rectangle (17, 1) node[midway] {$\mathcal F_{0}$}; \pause
	\draw (0, 0) rectangle (2, 1) node[midway] {$\mathcal F_{L+1}$}; \pause
%	\draw[dashed] (17, 0) rectangle (19, 1) node[midway] {$\mathcal F_{L+1}$};

	% arrows
%	\draw [<->,>=latex] (0, -3) -- (13, -3) node[below, midway] {Capacity of $Lc \approx w$ elements};
	\draw [<->,>=latex] (1, 3) -- (16, 3) node[above, midway] {Current sliding window (of size $w$)};
	\end{tikzpicture}

### 2020-08-19 slides/main.tex
slides

\documentclass[aspectratio=169]{beamer}

\usepackage[utf8]{inputenc}
%\usepackage{kotex}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usepackage{xspace}

%\usepackage[sfdefault]{FiraSans}
%\usepackage{FiraMono}

% Plots
\usepackage{pgfplots}
\pgfplotsset{compat=1.14}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{fillbetween}
\tikzset{mynode/.style={circle,draw,font=\small,minimum width=1cm,font=\sffamily}}
\pgfdeclarepatternformonly{north east lines wide}%
{\pgfqpoint{-1pt}{-1pt}}%
{\pgfqpoint{10pt}{10pt}}%
{\pgfqpoint{6pt}{6pt}}%
{
	\pgfsetlinewidth{0.1pt}
	\pgfpathmoveto{\pgfqpoint{0pt}{0pt}}
	\pgfpathlineto{\pgfqpoint{6.1pt}{6.1pt}}
	\pgfusepath{stroke}
}
\newcommand*{\FPR}{\operatorname{FPR}}
\newcommand*{\FNR}{\operatorname{FNR}}
\newcommand*{\FN}{\operatorname{FN}}
\newcommand*{\FP}{\operatorname{FP}}
\newcommand*{\EP}{\operatorname{EP}}

\newcommand*{\DUPLICATE}{\textsf{DUPLICATE}\xspace}
\newcommand*{\UNSEEN}{\textsf{UNSEEN}\xspace}

\usepackage{graphicx}

\usetheme{metropolis}           % Use metropolis theme

\titlegraphic{%
	\hfill\includegraphics[width=.3\textwidth]{logo-institute.png}\hfill
}

%\titlegraphic{\hfill \includegraphics[width=.2\textwidth]{logo-institute.png}\hfill}
\title{Approaching Optimal Duplicate Detection in a Sliding Window}
\date{August 30th, 2020}
\author{Rémi Géraud-Stewart, \textbf{Marius Lombard-Platet}, David Naccache}
\institute{Information security group, DIENS, École normale supérieure, PSL Research University (Paris, France)}

\begin{document}
\begin{frame}
	\maketitle
\end{frame}
\section{Introduction and motivation}

\begin{frame}{Finding duplicates}
	Let us consider a stream $E = (e_1, \dotsc, e_n, \dotsc)$ of elements, and a machine with a limited amount of memory $\mathcal M$.

	\begin{alertblock}{Question}
		How to detect if an element $e$ has already been seen in the past?
	\end{alertblock}%\pause

%	\begin{alertblock}{Second question}
%		Why do we care?
%	\end{alertblock}
%
%	\begin{exampleblock}{}
%			\begin{itemize}
%			\item Cache for CPU or webservers
%			\item Fraud detection (identical payments)
%			\item Cryptography (nonce reuse)
%			\item Security (check if URL is in a denylist)
%			\item ...
%		\end{itemize}
%	\end{exampleblock}

\end{frame}

\begin{frame}{Example}
This question leads to a second question: \pause

Why do we care?
\pause

There are several applications of detecting duplicates.
\begin{itemize}
	\item Cache for CPU or webservers
	\item Fraud detection (identical payments)
	\item Cryptography (nonce reuse)
	\item Security (check if URL is in a denylist)
	\item ...
\end{itemize}
\end{frame}

\begin{frame}{What is a duplicate filter?}
Quickly said, a duplicate filter is:
\begin{itemize}
	\item An algorithm operating with a finite amount of memory \pause
	\item When presented to a new element, outputs $\DUPLICATE$ or $\UNSEEN$ \pause
	\item Tries to keep memory of the previous elements
\end{itemize}
\end{frame}

\begin{frame}{Sub-problems of duplicate detection}
	In the literature, we can find several variants of the duplicate detection problem (DDP). We can match an element against:\pause
	\begin{itemize}
		\item a fixed, non-evolutive set (fixed duplicate detection, FDDP) \pause
		\item an evolutive set (streaming duplicate detection problem, SDDP) \pause comprising of:
		\begin{itemize}
			\item {\color<6->{red}the last $w$ elements of the stream ($w$DDP)} \pause
			\item all previous elements of the stream ($\infty$DDP)
		\end{itemize} 
	\end{itemize}
\pause
\end{frame}

\bgroup
\let\oldfootnoterule\footnoterule
\def\footnoterule{\only<2->\oldfootnoterule}
\begin{frame}{Prior work}
	Perfect solutions for $\infty$DDP and FDDP on an alphabet of size $\Gamma$ requires $\Gamma$ bits of memory\pause

	One can significantly reduce the amount of memory while keeping the errors under a certain value\footnote<2->{Burton H. Bloom. 1979. \textit{Space/Time Trade-offs in Hash Coding with Allowable Errors}} \pause

	Asymptotically, no filter can perform better than random on the $\infty$DDP\footnote<3->{Rémi Géraud, Marius Lombard-Platet, and David Naccache. 2019. \textit{Quotient hash tables: efficiently detecting duplicates in streaming data}}

\end{frame}

\begin{frame}{Contributions}
	We introduce a lower bound on the error rate for $\infty$DDP \pause

	We introduce two new structures for the $w$DDP:
	\begin{itemize}
		\item One for small values $w$
		\item One for adapting $\infty$DDP algorithms to the $w$DDP \pause
	\end{itemize}

	For these structures, we analyse their error rate and their resistance to adversarial attacks.
\end{frame}
\egroup

\section{Limitations of the $\infty$DDP}

\begin{frame}{Lower bound on $\infty$DDP error rate}
	Let be a filter of $M$ bits of memory on an alphabet of size $\Gamma$

	For $\FP_n, \FN_n$ the probability of a false positive/negative after $n$ insertions, and $\EP_n = \FN_n + \FP_n$ the error probability,\pause

	$$
	EP_n \geq 1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n} 
	$$

	We observe that asymptotically, $\EP_\infty \gtrapprox 1 - \frac M\Gamma$

\end{frame}
\begin{frame}{Experimental saturation}
	Assuming a large alphabet of size $U$, a filter quickly saturates, to the point of answering randomly (FPR + FNR = 1)

	\begin{figure}
		\centering
		\scalebox{.7}{\begin{tikzpicture}
		\input{graphs/er_n_artificial}
		\end{tikzpicture}}
		\caption{Error rate (times 100) of DDFs of 1Mb as a function of stream length. Hatched area represents over-optimal (impossible) values.}
	\end{figure}
\end{frame}

\section{New Structures for the $w$DDP}

\begin{frame}{How to detect duplicates?}
	\textbf{Optimal detection}: $w\log_2 \Gamma$ bits.\pause

	\textbf{Initial idea}: all $w$ elements in a queue \pause
	\begin{itemize}
		\item optimal size, no error
		\item complexity increases with $w$
	\end{itemize}
\pause
	\textbf{Second idea}: add a counter for each element \pause
	\begin{itemize}
		\item O(1) complexity while keeping a constant size
		\item no errors
	\end{itemize}\pause

	Problem solved?
\end{frame}
\begin{frame}{Optimal detection}
	Let $\mathcal M$ the available memory, $w$ the size of the sliding window and $\Gamma$ the size of the alphabet, \pause

	\begin{itemize}
		\item If $M \geq w(\log_2(w) + 2\log_2(\Gamma))$ the wDDP can be perfectly solved in constant time. \pause

		\item If $M \geq 5w\log_2(w)$, the wDDP can be solved with an FPR of $\approx \frac 1w$, and FNR of $0$ and constant time.
	\end{itemize}

\end{frame}

\begin{frame}{Detection with smaller-than-optimal memory}
	As we just saw, detection is optimally solved when the memory is large enough. \pause

	So let's see what happens with smaller memory (or bigger $w$).
\end{frame}

\begin{frame}{A first try: SHF}
	We take the previous optimal solution: a queue and a counter \pause

	Rather than each element $e$, we store a \emph{hash} $h(e)$, of size $\lfloor \frac M{2w} - \frac 12 \log_2(w)\rfloor$. \pause 
	This value is chosen so that we can store a hash of each element of the sliding window.

	That's the SHF. \pause

	\begin{itemize}
		\item $\FN = 0$
		\item$\FP = 1 - \left(1 - \sqrt{w2^{-M/w}}\right)^w$
	\end{itemize}
\end{frame}

\begin{frame}{SHF saturation}

	\begin{columns}
		\begin{column}{0.5\textwidth}
	SHF saturates quickly after reaching a turning point.

	\vspace{6em}
	\textbf{Conclusion}: SHF can be used for optimal cases and a bit more.
		\end{column}
		\begin{column}{0.5\textwidth}  %%<--- here
			\begin{figure}[t]
			\centering
			\scalebox{.7}{
				\input{graphs/bench_short.tex}
			}
			\caption{Error rate (times 100) of SHF on various $w$ sizes. Hatched area represents cases where optimal solutions exist.}
		\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Another idea: Queuing Filter}
	The idea is to adopt $\infty$DDP filters into the $w$DDP context. For this, we create a queue of subfilters $\mathcal F_i$. \pause

	\begin{figure}
		\centering
		\scalebox{.8}{
			\input{graphs/queuef.tex}
		}
	\end{figure}
\onslide<+->{We chose the parameters $L, c$ so that $Lc \approx w$.}
\end{frame}

\begin{frame}{Queueing Filter error probabilities}
	\begin{columns}
		\begin{column}{0.5\textwidth}
		FP and FN probabilities have been derived for a queueing filter using any kind of subfilter, but are a bit complicated to use. \pause

	\vspace{1em}

	Let's rather look at experiments.
		\end{column}
		\begin{column}{0.5\textwidth}  %%<--- here
			\begin{figure}[t]
			\centering
			\scalebox{.7}{
				\input{graphs/queue_bench.tex}
			}
			\caption{QHT-queuing filter and a QHT filter on various sliding window sizes. Hatched area represents values for which optimal solution exists.}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\section{Queueing Filter Security}
\begin{frame}{Filters in adversarial environment}
	An adversary chooses the stream sent to the filter \pause

	She does not have access to the memory state, only to the filter's output ($\DUPLICATE$ or $\UNSEEN$) \pause

	She wins the $(p, n)$-adversarial game if after a training period not longer than $n$, she can force a false positive (or a false negative) with probability $\geq p$
\end{frame}

\begin{frame}{FP security of queueing filter}
	Let $\mathcal Q$ be a queueing filter consisting of $L$ subfilters $\mathcal F_i$, each filled with $c$ items.

	If $\mathcal F$ is $(p, c)$-resistant to adversarial FP attacks and $cL \leq w$, then $\mathcal Q$ is $(1 - (1 - p)^L, w)$-resistant to FP attacks.
\end{frame}

\begin{frame}{FN security of queueing filter}
	Let $\mathcal Q$ be a queueing filter consisting of $L$ subfilters $\mathcal F_i$, each filled with $c$ items, and assume $w \leq (L-1)c$.

	Let $q = \displaystyle\min_{i \leq c} \FN_{\mathcal F, i}$, then $\mathcal Q$ is $(\min(1-q, p)^{L-1}p, w)$-resistant to adversarial FN attacks.
\end{frame}

\section{Conclusion}

\begin{frame}{Summing it up}
	\begin{itemize}
		\item For most cases, $\infty$DDP is an ill-posed problem and existing solutions are close to optimality \pause
		\item $w$DDP can be optimally solved if the memory is big enough \pause
		\item For w close (or inside) optimality, a excellent solution is the SHF \pause
		\item For $w$ slightly bigger, queueing filters are more interesting \pause
		\item For $w$ bigger, then existing $\infty$DDP solutions are the best solution
	\end{itemize}
\end{frame}

\begin{frame}[standout]{Thank you for your attention}
Any question?

\vspace{2em}

\footnotesize \texttt{remi.geraud@ens.fr\\marius.lombard-platet@ens.fr\\david.naccache@ens.fr}
\end{frame}

\end{document}
